### 2016-07-05 Reproducible_Research.Rmd
Initial commit to new repository for reproducible research manuscript

---
title: "What Does Reproducible Research Mean for Plant Pathology?"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: "5 July 2016"
output:
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
bibliography: bibliography.bib
csl: phytopathology.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, 
Toowoomba, Qld 4350, Australia
2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA
Agricultural Research Service, Corvallis, OR 97330, USA
4. Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural
Research Service, Corvallis, OR 97330, USA

# ABSTRACT

Abstracts are mandatory and limited to one 200 word paragraph.

## WHAT IS REPRODUCICBLE RESEARCH?

**Definitions.** Reproducible research
Replicable research

## WHY REPRODUCIBLE RESEARCH?

## HOW TO MAKE REPRODUCIBLE RESEARCH
Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.

## DISCUSSION

## ACKOWLEDGEMENTS

### LITERATURE CITED

### 2016-07-06 README.rmd
Move Reproducible_Research.rmd to README.rmd
When knitting the Rmd file keep the md file, so a README.md file is
generated, which is the whole matter of the manuscript.

--- 2016-07-05 Reproducible_Research.Rmd
@@
     reference_docx: Phytopathology_Style_Reference.docx
+    keep_md: TRUE
 bibliography: bibliography.bib

### 2016-09-05 README.rmd
Restructure file names, add new references and materials, update style reference
Added several new references to the bibliography

Added new material to manuscript outline to start fleshing out the
materials

Moved the document from README.Rmd to What Does Reproducible Research
Mean for Plant Pathology.Rmd

README.Rmd produces a GitHub Markdown document and will contain the
abstract and links to the MS Word document and Rmd file used to
generate it

@@
 
-## WHAT IS REPRODUCICBLE RESEARCH?
+# MAIN TEXT
+Reproductibility and replicability in scientific research have once again been
+highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.
 
-**Definitions.** Reproducible research
-Replicable research
+Patil et al. [-@Patil066803] have provided several definitions to clarify the
+concepts surrounding reproducibility and replicability. For the purposes of this
+paper we follow the definitions as given by Patil et al. [-@Patil066803].
 
-## WHY REPRODUCIBLE RESEARCH?
+* Why reproducible research
 
-## HOW TO MAKE REPRODUCIBLE RESEARCH
-Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
+## BEST METHODS FOR REPRODUCIBLE RESEARCH
+* Provide definitions (provide defintions for terms used so it's clear)
+* Data
+  * Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
+  * Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
+* When publishing
+  * Provide data
+  * Provide code
+* Using GitHub for code (and small data?)
+* Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
+
+## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
+* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
 for readers.
+* Duku et al. [-@Duku2016] provide 
+[http://adamhsparks.github.io/MICCORDEA/](models, data and code) necessary to
+replicate the entire study modelling the effects of climate change on rice
+bacterial blight and rice leaf blast in Tanzania.
+* Sparks et al. [-@Sparks2011; -@Sparks2014] provide 
+[http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/](models, data and code)
+necessary to replicate model development and the subsequent the study on the effects
+of climate change on potato late blight.
+* Other examples from plant pathology providing e-Xtras or supplemental material
 
@@
 
+### Notes
+https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/
+
 ### LITERATURE CITED

### 2016-09-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
Restructure file names, add new references and materials, update style reference
Added several new references to the bibliography

Added new material to manuscript outline to start fleshing out the
materials

Moved the document from README.Rmd to What Does Reproducible Research
Mean for Plant Pathology.Rmd

README.Rmd produces a GitHub Markdown document and will contain the
abstract and links to the MS Word document and Rmd file used to
generate it

--- 2016-09-05 README.rmd
@@
 author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
-date: "5 July 2016"
+date: "`r Sys.Date()`"
 output:
@@
     reference_docx: Phytopathology_Style_Reference.docx
-    keep_md: TRUE
 bibliography: bibliography.bib

### 2016-09-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
Remove redundant files, add links in README.Rmd, fix links in manuscript

@@
 for readers.
-* Duku et al. [-@Duku2016] provide 
-[http://adamhsparks.github.io/MICCORDEA/](models, data and code) necessary to
+* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
 replicate the entire study modelling the effects of climate change on rice
 bacterial blight and rice leaf blast in Tanzania.
-* Sparks et al. [-@Sparks2011; -@Sparks2014] provide 
-[http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/](models, data and code)
+* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
 necessary to replicate model development and the subsequent the study on the effects

### 2016-09-05 README.rmd
Fix README.Rmd and README.md

--- 2016-07-05 Reproducible_Research.Rmd
@@
 ---
-title: "What Does Reproducible Research Mean for Plant Pathology?"
+title: "What Does Reproducible Research Mean for Plant Pathology"
 author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
-date: "5 July 2016"
-output:
-  word_document:
-    reference_docx: Phytopathology_Style_Reference.docx
-bibliography: bibliography.bib
-csl: phytopathology.csl
+output: github_document
 ---
@@
 ```
-1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, 
-Toowoomba, Qld 4350, Australia
+
+1.  Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
 2.  Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
-3. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA
-Agricultural Research Service, Corvallis, OR 97330, USA
-4. Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural
-Research Service, Corvallis, OR 97330, USA
+3.  Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
+4.  Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
 
-# ABSTRACT
+ABSTRACT
+========
 
-Abstracts are mandatory and limited to one 200 word paragraph.
+Once complete the abstract will be here.
 
-## WHAT IS REPRODUCICBLE RESEARCH?
+Full text
+=========
 
-**Definitions.** Reproducible research
-Replicable research
-
-## WHY REPRODUCIBLE RESEARCH?
-
-## HOW TO MAKE REPRODUCIBLE RESEARCH
-Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
-for readers.
-
-## DISCUSSION
-
-## ACKOWLEDGEMENTS
-
-### LITERATURE CITED
+The full text of the document can be found here in a [MS Word file](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/blob/master/What_Does_Reproducible_Research_Mean_for_Plant_Pathology.docx) compiled from this [R Markdown document](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/blob/master/What%20Does%20Reproducible%20Research%20Mean%20for%20Plant%20Pathology.Rmd).

### 2016-09-06 What Does Reproducible Research Mean for Plant Pathology.Rmd
Add link to r-opensci blog post about R Rsearch Compendiums

@@
 ### Notes
+These are links to resources that may be useful for writing this or as suggested resources in the final
+document that aren't easily printable for inclusion in the Dropbox folder.
+
 https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/
 
+https://github.com/ropensci/rrrpkg
+
 ### LITERATURE CITED

### 2016-12-05 src/README.Rmd
Rename Rmd in src directory

---
title: "Journal Article Sampling Methodology"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating a sample of articles

The top 20 journals in the discipline of plant pathology were selected according to Google Scholar's ranking by h-index, (https://scholar.google.com.au/citations?view_op=top_venues&hl=en&vq=bio_plantpathology).

100 articles are chosen at random with the assumption that journals publish an average 10 articles per issue, and using a confidence level of 95% and confidence interval of 10% we only need 88 samples, so to round it up and make it even, we'll select 100 articles over the last five years from a population that should be ~1000.

## R setup
Set up the R environment

```{r library, message=FALSE}
library(dplyr)

set.seed(27)
```
## Import data
The list of the top 20 plant pathology journals was retrieved from Google Scholar on December 5, 2016 and saved as a CSV file for reproducibility.

```{r journal_list}
journal_list <- read.csv("../data/Google Scholar Top 20 Plant Pathology Journals 05-12-2016.csv")

journal_list[1:20, -4] # drop h-index median value
```

## Create random lists
Create a randomised list of the journals

```{r journal_sample_order}
journals <- as.data.frame(sample(1:20, 100, replace = TRUE))
names(journals) <- "Rank"
# reorder joural list
journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
```

## Randomly select articles
Generate a random list of years between 2012 and 2016 and a random list of start pages between 1 and 150 since some journals start numbering at 1 with every issue. Then bind the columns of the randomised list of journals with the randomised years and page start numbers. This then assumes that there is no temporal effect, i.e., the time of year an article is published does not affect whether or not it is reproducible.

*How to handle reviews or letters?*

```{r years_and_articles}

year <- sample(2012:2016, 100, replace = TRUE)

start_page <- sample.int(150, 100)

journals <- cbind(journals, year, start_page)

journals[1:100, -1]
```

### 2016-12-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
Add Rmd describing how sample articles were selected
Add to methods on how randomised lists were generated

@@
 
+## RANDOM SAMPLING OF ARTICLES FROM THE TOP 20 PLANT PATHOLOGY JOURNALS
+The top 20 plant pathology discipline journals as ranked by Google Scholar, https://scholar.google.com/ (accessed 05 Dec.
+2016), were used to create a database of journals from which to randomly select articles for inspection.
+One hundred articles were randomly selected from 2012 to 2016 from a list of randomly selected start pages assigned to a randomised list of the 20 journals [@Sparks2017].
+The start pages list was numbered from page one and went to 150.
+This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
+
+The list of journals was saved as a comma separated value (CSV) file and imported into R (R2016).
+
 ## DISCUSSION

### 2016-12-07 src/README.Rmd
Update list sampling methods
Select only articles from the top 10 journals so that only higher level
journals are included

@@
 
-journal_list[1:20, -4] # drop h-index median value
+journal_list[1:20, -4] # drop h-index median value just to tidy things up.
+
+journal_list[1:10, ] # select the top ten journals in plant pathology only
 ```
@@
 ```{r journal_sample_order}
-journals <- as.data.frame(sample(1:20, 100, replace = TRUE))
+journals <- as.data.frame(sample(1:10, 100, replace = TRUE))
 names(journals) <- "Rank"

### 2016-12-07 src/README.Rmd
add first two articles to list

@@
 ```
+
+(Morphological and biochemical responses of five tobacco cultivars to simultaneous infection with Pythium aphanidermatum and Meloidogyne incognita
+Mujeebur Rahman KHAN, Ziaul HAQUE)[http://www.fupress.net/index.php/pm/article/view/11386]
+(The Periplasmic PDZ Domain–Containing Protein Prc Modulates Full Virulence, Envelops Stress Responses, and Directly Interacts with Dipeptidyl Peptidase of Xanthomonas oryzae pv.
+oryzae)[http://apsjournals.apsnet.org/doi/abs/10.1094/MPMI-08-13-0234-R]

### 2016-12-07 src/README.Rmd
Add third article

@@
 oryzae)[http://apsjournals.apsnet.org/doi/abs/10.1094/MPMI-08-13-0234-R]
+(The development of a species-specific test to detect Hymenoschyphus pseudoalbidus in ash tissues)[http://onlinelibrary.wiley.com/doi/10.1111/efp.12078/full]

### 2016-12-11 What Does Reproducible Research Mean for Plant Pathology.Rmd
Correct R citation on line 62
Added example of reproducible report

@@
 author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
-date: "`r Sys.Date()`"
+date: '`r Sys.Date()`'
 output:
   word_document:
+    keep_md: yes
     reference_docx: Phytopathology_Style_Reference.docx
+  html_document: default
+csl: phytopathology.csl
 bibliography: bibliography.bib
-csl: phytopathology.csl
 ---
@@
 * Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
-necessary to replicate model development and the subsequent the study on the effects
-of climate change on potato late blight.
+necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
+* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
 * Other examples from plant pathology providing e-Xtras or supplemental material
@@
 
-The list of journals was saved as a comma separated value (CSV) file and imported into R (R2016).
+The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2016].
 

### 2016-12-11 src/README.Rmd
Knit .md files, remove extra file

--- 2016-12-07 src/README.Rmd
@@
 ---
-title: "Journal Article Sampling Methodology"
+title: "README"
 output: github_document
@@
 
-journal_list[1:20, -4] # drop h-index median value just to tidy things up.
-
-journal_list[1:10, ] # select the top ten journals in plant pathology only
+journal_list[1:20, -4] # drop h-index median value
 ```
@@
 ```{r journal_sample_order}
-journals <- as.data.frame(sample(1:10, 100, replace = TRUE))
+journals <- as.data.frame(sample(1:20, 100, replace = TRUE))
 names(journals) <- "Rank"
@@
 journals[1:100, -1]
+
 ```
+
+### Check the number of articles per journal
+
+```{r}
+journals %>%  
+ group_by(Publication) %>% 
+    tally(sort = TRUE)
+
+```

### 2017-04-03 src/example_tibble.R
Add example tibble and update .gitignore

@@ -1,0 +1,24 @@
+reproducibility <- tibble::tibble(
+  Article = "The Area Under the Disease Progress Stairs: Calculation, Advantage, and Application",
+  DOI = "PHYTO-07-11-0216",
+  Journal = "Phytopathology",
+  Authors =  "Ivan Simko and Hans-Peter Piepho",
+  Year = 2012,
+  Vol = 102,
+  Iss = 4,
+  pp = "381-389",
+  IF = 3.011,
+  Journal_class = "Fundamental",
+  Page_charges = 130,
+  Country =  "USA",
+  Open_or_Restricted = "Optional",
+  Reproducibility_instructions = FALSE,
+  Iss_per_Year = 12,
+  Supl_mats = TRUE,
+  Comp_methods = 2,
+  Raw_data = 0,
+  Reproducibility_score = NA
+)
+
+reproducibility$Reproducibility_score <- reproducibility$Comp_methods + reproducibility$Raw_data
+

### 2017-04-04 reproducibility_criteria.Rmd
new; adapted from issue #5

---
title: "Criteria for evaluating reproducibility"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

* Raw data availability
    0. Not available or not mentioned in the publication
    1. Available upon request to author
    2. Online, but inconvenient/non-permanent (e.g. login needed, pay wall, FTP server, personal lab website)
    3. Freely available online to anonymous users for foreseeable future
* Raw data annotation
    0. No annotation
    1. The structure/content of the data is clear, but the relevance to the study is not
    2. Fully understandable in the context of the paper
    3. Fully understandable without reading the paper
* Raw data tidiness
    0. Not easily parsed with code or loaded by standard office software (e.g. unstructured raw text or binary equipment outputs or no raw data)
    1. Difficult, but possible, to parse with code or manipulate with standard office software (i.e. you technically could, but would not want to)
    2. Able to parse using code with minimal cleanup (e.g. you might need a few extra lines of code for clean up or do a few extra steps to work with your operating system. An example would be a text file with multiple tables)
    3. Tidy data in a standardized format (e.g. tsv) that is loaded correctly without cleanup or using uncommon parsing tools.
* Computational methods availability
    0. Not available or not mentioned in the publication
    1. Available upon request to author
    2. Online, but inconvenient/non-permanent (e.g. login needed, pay wall, FTP server, personal/lab website)
    3. Freely available online to anonymous users for foreseeable future
* Availability of software used
    0. Not available or not mentioned in the publication
    1. Uses expensive proprietary software that only institutions would typically purchase (i.e. ArcGIS standard is $7000)
    2. Uses proprietary software that most individuals can afford (e.g. Excel, Matlab? ($500))
    3. Uses entirely open source and free software (e.g. R).
* Citation of software used
    0. Not available or not mentioned in the publication
    1. Software mentioned by name only
    2. Attempts at citing
    3. Properly cited
* Analysis automation
    0. All steps were performed manually with no choesive document describing exactly what was done
    1. Steps were performed manually, but with a detailed record (e.g. pasted commands in a text file)
    2. A set of runnable scripts were used, but have to be executed individually or the outputs require manually modifications
    3. A makefile or master script was provided that runs the entire analysis from raw data to published results

### 2017-04-04 reproducibility_criteria.Rmd
modified format for github

@@
 
-* Raw data availability
+### Raw data
+
+#### Raw data availability
+
 0. Not available or not mentioned in the publication
@@
 3. Freely available online to anonymous users for foreseeable future
-* Raw data annotation
+
+#### Raw data annotation
+
 0. No annotation
@@
 3. Fully understandable without reading the paper
-* Raw data tidiness
+
+#### Raw data tidiness
+
 0. Not easily parsed with code or loaded by standard office software (e.g. unstructured raw text or binary equipment outputs or no raw data)
@@
 3. Tidy data in a standardized format (e.g. tsv) that is loaded correctly without cleanup or using uncommon parsing tools.
-* Computational methods availability
+
+### Computational methods
+
+#### Computational methods availability
+
 0. Not available or not mentioned in the publication
@@
 3. Freely available online to anonymous users for foreseeable future
-* Availability of software used
+
+#### Availability of software used
+
 0. Not available or not mentioned in the publication
@@
 3. Uses entirely open source and free software (e.g. R).
-* Citation of software used
+
+#### Citation of software used
+
 0. Not available or not mentioned in the publication
@@
 3. Properly cited
-* Analysis automation
+
+#### Analysis automation
+
 0. All steps were performed manually with no choesive document describing exactly what was done

### 2017-04-04 reproducibility_criteria.Rmd
Edits to reproducibility criteria for spelling; update example_tibble.R
Update example_tibble.R with new reproducibility criteria scoring

@@
 
-0. All steps were performed manually with no choesive document describing exactly what was done
+0. All steps were performed manually with no cohesive document describing exactly what was done
 1. Steps were performed manually, but with a detailed record (e.g. pasted commands in a text file)
-2. A set of runnable scripts were used, but have to be executed individually or the outputs require manually modifications
+2. A set of runnable scripts were used, but have to be executed individually or the outputs require manual modifications
 3. A makefile or master script was provided that runs the entire analysis from raw data to published results

### 2017-04-04 src/example_tibble.R

@@ -15,10 +15,21 @@ reproducibility <- tibble::tibble(
   Reproducibility_instructions = FALSE,
   Iss_per_Year = 12,
   Supl_mats = TRUE,
-  Comp_methods = 2,
-  Raw_data = 0,
-  Reproducibility_score = NA
+  Comp_methods_availability = 2,
+  Software_availability = 1,
+  Software_citation = 3,
+  Analysis_automation = 0,
+  Data_availability = 0,
+  Data_annotation = 0,
+  Data_tidiness = 0
 )
 
-reproducibility$Reproducibility_score <- reproducibility$Comp_methods + reproducibility$Raw_data
+reproducibility <- dplyr::mutate(reproducibility,
+                                 Reproducibility_score = sum(Comp_methods_availability,
+                                                             Software_availability,
+                                                             Software_citation,
+                                                             Analysis_automation,
+                                                             Data_availability,
+                                                             Data_annotation,
+                                                             Data_tidiness))
 

### 2017-04-04 reproducibility_criteria.Rmd
Add reproducibility tibble to reproducibility criteria Rmd

@@
 3. A makefile or master script was provided that runs the entire analysis from raw data to published results
+
+# Example of reproducibility `tibble`
+
+```{r}
+reproducibility <- tibble::tibble(
+  Article = "The Area Under the Disease Progress Stairs: Calculation, Advantage, and Application",
+  DOI = "PHYTO-07-11-0216",
+  Journal = "Phytopathology",
+  Authors =  "Ivan Simko and Hans-Peter Piepho",
+  Year = 2012,
+  Vol = 102,
+  Iss = 4,
+  pp = "381-389",
+  IF = 3.011,
+  Journal_class = "Fundamental",
+  Page_charges = 130,
+  Country =  "USA",
+  Open_or_Restricted = "Optional",
+  Reproducibility_instructions = FALSE,
+  Iss_per_Year = 12,
+  Supl_mats = TRUE,
+  Comp_methods_availability = 2,
+  Software_availability = 1,
+  Software_citation = 3,
+  Analysis_automation = 0,
+  Data_availability = 0,
+  Data_annotation = 0,
+  Data_tidiness = 0
+)
+
+reproducibility <- dplyr::mutate(reproducibility,
+                                 Reproducibility_score = sum(Comp_methods_availability,
+                                                             Software_availability,
+                                                             Software_citation,
+                                                             Analysis_automation,
+                                                             Data_availability,
+                                                             Data_annotation,
+                                                             Data_tidiness))
+
+reproducibility
+
+reproducibility$Reproducibility_score
+```

### 2017-04-04 src/example_tibble.R

@@ -1,35 +1,0 @@
-reproducibility <- tibble::tibble(
-  Article = "The Area Under the Disease Progress Stairs: Calculation, Advantage, and Application",
-  DOI = "PHYTO-07-11-0216",
-  Journal = "Phytopathology",
-  Authors =  "Ivan Simko and Hans-Peter Piepho",
-  Year = 2012,
-  Vol = 102,
-  Iss = 4,
-  pp = "381-389",
-  IF = 3.011,
-  Journal_class = "Fundamental",
-  Page_charges = 130,
-  Country =  "USA",
-  Open_or_Restricted = "Optional",
-  Reproducibility_instructions = FALSE,
-  Iss_per_Year = 12,
-  Supl_mats = TRUE,
-  Comp_methods_availability = 2,
-  Software_availability = 1,
-  Software_citation = 3,
-  Analysis_automation = 0,
-  Data_availability = 0,
-  Data_annotation = 0,
-  Data_tidiness = 0
-)
-
-reproducibility <- dplyr::mutate(reproducibility,
-                                 Reproducibility_score = sum(Comp_methods_availability,
-                                                             Software_availability,
-                                                             Software_citation,
-                                                             Analysis_automation,
-                                                             Data_availability,
-                                                             Data_annotation,
-                                                             Data_tidiness))
-

### 2017-04-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
Update What Does Reproducible Research Mean for Plant Pathology.Rmd

@@
 ```
-1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, 
-Toowoomba, Qld 4350, Australia
+1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
 2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
-3. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA
-Agricultural Research Service, Corvallis, OR 97330, USA
-4. Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural
-Research Service, Corvallis, OR 97330, USA
+3. Zachary S. L. Foster: Department of Botany and Plant Pathology, ORegon State Unviersity, Corvallis, OR 97330, USA
+4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
 
@@
 * Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
+* Example from my lab: 
+  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
+  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
 * Other examples from plant pathology providing e-Xtras or supplemental material
@@
 
-### Notes
-These are links to resources that may be useful for writing this or as suggested resources in the final
-document that aren't easily printable for inclusion in the Dropbox folder.
-
-https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/
-
-https://github.com/ropensci/rrrpkg
-
 ### LITERATURE CITED

### 2017-04-05 README.rmd
Update README.rmd and output .md file
Update README.rmd

@@
 output: github_document
+date: "`r Sys.Date()`"
 ---
@@
 
+AUTHORS and AFFILIATIONS
+========
 1.  Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
 2.  Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
-3.  Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
-4.  Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
+3.  Zachary S. L. Foster: Dept. Botany and Plant Pathology, Oregon State University, Corvallis, OR 97330, USA
+4.  Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
 

### 2017-04-10 src/README.Rmd
Update article selection based on @emdelponte
Updated to 200 articles from the journals suggested by @emdelponte in
https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/
issues/6

@@
 
-The top 20 journals in the discipline of plant pathology were selected according to Google Scholar's ranking by h-index, (https://scholar.google.com.au/citations?view_op=top_venues&hl=en&vq=bio_plantpathology).
+Twenty journals in the discipline of plant pathology were selected by the authors as being the primary choice for most plant pathologists when publishing manuscripts.
 
-100 articles are chosen at random with the assumption that journals publish an average 10 articles per issue, and using a confidence level of 95% and confidence interval of 10% we only need 88 samples, so to round it up and make it even, we'll select 100 articles over the last five years from a population that should be ~1000.
+Using the assumption that journals publish an average 10 articles per issue, for a population of ~1000 articles, using a confidence level of 95% and confidence interval of 10% we need 88 samples.
+In [Issue #3](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/issues/3), we decided to select 200 articles to have a large sample of the population.
 
@@
 
-set.seed(27)
+set.seed(1)
 ```
@@
 ```{r journal_list}
-journal_list <- read.csv("../data/Google Scholar Top 20 Plant Pathology Journals 05-12-2016.csv")
+journal_list <- tibble(
+  seq(1:20),
+  c("Australasian Plant Pathology",
+    "Canadian Journal of Plant Pathology",
+    "Crop Protection",
+    "European Journal of Plant Pathology",
+    "Forest Pathology",
+    "Journal of General Plant Pathology",
+    "Journal of Phytopathology",
+    "Journal of Plant Pathology",
+    "Journal of Plant Virology",
+    "Molecular Plant Pathology",
+    "Nematology",
+    "Physiological and Molecular Plant Pathology",
+    "Phytoparasitica",
+    "Phytopathologia Mediterranea",
+    "Phytopathology",
+    "Plant Disease",
+    "Plant Health Progress",
+    "Plant Pathology",
+    "Revista Mexicana de Fitopatología",
+    "Tropical Plant Pathology"))
 
-journal_list[1:20, -4] # drop h-index median value
+names(journal_list) <- c("number", "publication")
 ```
@@
 
-```{r journal_sample_order}
-journals <- as.data.frame(sample(1:20, 100, replace = TRUE))
-names(journals) <- "Rank"
-# reorder joural list
-journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
+```{r journal_sample}
+journals <- tibble(sample(1:20, 200, replace = TRUE))
+names(journals) <- "number"
+journals <- left_join(journals, journal_list, "number")
 ```
@@
 
-*How to handle reviews or letters?*
-
 ```{r years_and_articles}
 
-year <- sample(2012:2016, 100, replace = TRUE)
+year <- sample(2012:2016, 200, replace = TRUE)
 
-start_page <- sample.int(150, 100)
+start_page <- sample.int(150, 200, replace = TRUE)
 
-journals <- cbind(journals, year, start_page)
-
-journals[1:100, -1]
+(journals <- cbind(journals, year, start_page)[, -1])
 
@@
 
-### Check the number of articles per journal
+## Check the number of articles per journal
 
-```{r}
+```{r, count}
 journals %>%  
- group_by(Publication) %>% 
+ group_by(publication) %>% 
     tally(sort = TRUE) 
+```
 
+## R Session Info
+```{r, session_info}
+sessionInfo()
 ```

### 2017-04-10 src/README.Rmd
Add assignees to articles

@@
 
-Twenty journals in the discipline of plant pathology were selected by the authors as being the primary choice for most plant pathologists when publishing manuscripts.
+Twenty journals in the discipline of plant pathology were selected by the assignee as being the primary choice for most plant pathologists when publishing manuscripts.
 
@@
 ## Create random lists
-Create a randomised list of the journals
+
+### Create a randomised list of the journals
 
@@
 
-## Randomly select articles
+### Randomly select articles
 Generate a random list of years between 2012 and 2016 and a random list of start pages between 1 and 150 since some journals start numbering at 1 with every issue.
@@
 This then assumes that there is no temporal effect, i.e., the time of year an article is published does not affect whether or not it is reproducible.
+
+### Create list of reviewers
+From the four authors of this paper, create a list for us to use that will randomly assign articles for us to evaluate for this manuscript.
+
+```{r assignee}
+assignee <- rep(c("Adam", "Emerson", "Zach", "Nik"), 50)
+
+```
 
@@
 
-(journals <- cbind(journals, year, start_page)[, -1])
+journals <- cbind(journals[, -1], year, start_page, assignee)
+
+arrange(journals, assignee)
 

### 2017-04-10 src/README.Rmd
Cleanup text associated with article selection/assignements

@@
 ```
-## Import data
-The list of the top 20 plant pathology journals was retrieved from Google Scholar on December 5, 2016 and saved as a CSV file for reproducibility.
+## Create list of journals
 
@@
 
+## Create list of assignees
+From the four authors of this paper, create a list for us to use that will randomly assign articles for us to evaluate for this manuscript.
+
+```{r assignee}
+assignee <- rep(c("Adam", "Emerson", "Zach", "Nik"), 50)
+
+```
+
 ## Create random lists
@@
 Then bind the columns of the randomised list of journals with the randomised years and page start numbers.
-This then assumes that there is no temporal effect, i.e., the time of year an article is published does not affect whether or not it is reproducible.
-
-### Create list of reviewers
-From the four authors of this paper, create a list for us to use that will randomly assign articles for us to evaluate for this manuscript.
-
-```{r assignee}
-assignee <- rep(c("Adam", "Emerson", "Zach", "Nik"), 50)
-
-```
+This then assumes that there is no temporal effect, _i.e._, the time of year an article is published does not affect whether or not it is reproducible.
 

### 2017-04-11 src/README.Rmd
Use Packrat; Include MPMI in journal list

@@
 
-Twenty journals in the discipline of plant pathology were selected by the assignee as being the primary choice for most plant pathologists when publishing manuscripts.
+Twenty one journals in the discipline of plant pathology were selected by the four authors as being the primary choice for most plant pathologists when publishing manuscripts.
 
@@
 set.seed(1)
+
+# For printing tibble in total
+options(tibble.print_max = 21, tibble.print_min = 21)
 ```
@@
 journal_list <- tibble(
-  seq(1:20),
+  seq(1:21),
   c("Australasian Plant Pathology",
@@
     "Journal of Plant Virology",
+    "Molecular Plant-Microbe Interactions",
     "Molecular Plant Pathology",
@@
 ```{r journal_sample}
-journals <- tibble(sample(1:20, 200, replace = TRUE))
+journals <- tibble(sample(1:21, 200, replace = TRUE))
 names(journals) <- "number"
@@
 
-arrange(journals, assignee)
+arrange(journals, publication, year, start_page)
 

### 2017-04-11 src/README.Rmd
Update journal list and add csv of comments/DOI
Update journal list to use "Virology Journal (Plant Viruses Section)"

Add "data/journals.csv", which contains the randomised journal
information with DOIs and comments about the journals to be merged with
bibliography once both are completed.

Update packages via packrat

@@
     "Journal of Plant Pathology",
-    "Journal of Plant Virology",
+    "Virology Journal (Plant Viruses Section)",
     "Molecular Plant-Microbe Interactions",

### 2017-04-11 src/README.Rmd
Add articles for review in CSV along with notes about them
Still need to left join these data

@@
 library(dplyr)
+library(readr)
 
@@
 
+# Joining articles with assignees
+The articles were searched for and citations were downloaded, DOIs were saved in a CSV file with notes related to the articles and selections.
+Using this CSV file along with a CSV file generated from an export of the bibliography information from Zotero, join the two files.
+
+```{r join_files}
+articles <- read.csv("data/Journals_for_review.csv", strip.white = TRUE)
+
+notes <- read.csv("data/Article_notes.csv", strip.white = TRUE)
+
+# todo join articles and notes
+
+```
+
 ## R Session Info

### 2017-04-13 src/README.Rmd
Correct Article_notes.csv; convert DOIs to lowercase in Rmd
DOI values now all converted to lowercase in RMD to join on

Still need to get complete file from office computer as the DOIs and
notes for this file in repository are incomplete currently

Then join the files together for complete reference and notes about
files
Import Bib file into R; update bibliography with missing refs and article notes csv file

@@
 ```{r join_files}
-articles <- read.csv("data/Journals_for_review.csv", strip.white = TRUE)
+articles <- RefManageR::ReadBib("data/Journals_for_review.bib")
+articles <- as.data.frame(articles)
 
 notes <- read.csv("data/Article_notes.csv", strip.white = TRUE)
+notes$DOI <- tolower(notes$DOI)
 

### 2017-04-13 src/README.Rmd
Retrieve article citations using R, merge with notes

--- 2017-04-11 src/README.Rmd
@@
 
+# Joining articles with assignees
+The articles were searched for and DOIs were saved in a CSV file with notes related to the articles and selections.
+Using this CSV file retrieve the BibTex citations for those available and write a "Assigned_Articles.bib" file to disk as well as the updated "Assigned_Articles.csv".
+
+```{r join_files, warning=FALSE}
+notes <- read.csv("Assigned_article_notes.csv", strip.white = TRUE)
+
+bib <- RefManageR::GetBibEntryWithDOI(notes$doi)
+
+# Join articles and references for saving to CSV for reference
+Assigned_Articles <- dplyr::left_join(as.data.frame(bib), notes, by = "doi")
+
+write.csv(Assigned_Articles, "Assigned_Articles.csv")
+
+RefManageR::WriteBib(bib, "Assigned_Articles.bib")
+
+```
+
+Note that not all of the articles have DOIs and some of the DOIs don't appear to work, so we'll manually add them here.
+
+```{r add_missing_articles}
+
+```
+
 ## R Session Info

### 2017-04-19 README.rmd
Convert project to R package

--- 2016-09-05 README.rmd
@@
 ---
-title: "What Does Reproducible Research Mean for Plant Pathology"
-author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
 output: github_document
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+<!-- README.md is generated from README.Rmd. Please edit that file -->
+
+```{r, echo = FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  fig.path = "README-"
+)
 ```
 
-1.  Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
-2.  Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
-3.  Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
-4.  Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
+# Links to various resources that are useful for this document
 
-ABSTRACT
-========
+[Replication data collection highlights value in diversity of replication attempts](http://www.nature.com/articles/sdata201728)
 
-Once complete the abstract will be here.
+[The reproducibility crisis in science and prospects for R](https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/)
 
-Full text
-=========
-
-The full text of the document can be found here in a [MS Word file](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/blob/master/What_Does_Reproducible_Research_Mean_for_Plant_Pathology.docx) compiled from this [R Markdown document](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/blob/master/What%20Does%20Reproducible%20Research%20Mean%20for%20Plant%20Pathology.Rmd).
+[rrrpkg - Use of an R package to facilitate reproducible research](https://github.com/ropensci/rrrpkg)

### 2017-04-19 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
Convert project to R package

--- 2017-04-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
@@
 * Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
-* Example from my lab: 
+* Example from Grunwald lab: 
   - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI

### 2017-04-21 R/data.R
Package now passes checks, add pkgdown site

@@ -1,0 +1,36 @@
+#' article_assignments
+#' @format A data frame with 201 observations of 17 elements:
+#' \describe{
+#'   \item{publication}{}
+#'   \item{year.x}{}
+#'   \item{start_page}{}
+#'   \item{assignee}{}
+#'   \item{doi}{}
+#'   \item{comments}{}
+#'   \item{bibtype}{}
+#'   \item{url}{}
+#'   \item{month}{}
+#'   \item{publisher}{}
+#'   \item{volume}{}
+#'   \item{number}{}
+#'   \item{pages}{}
+#'   \item{author}{}
+#'   \item{title}{}
+#'   \item{journal}{}
+#'   \item{editor}{}
+#' }
+#'
+"article_assignments"
+
+#' assigned_article_notes
+#' @format A data frame with 199 observations of 6 elements:
+#' \describe{
+#' \item{publication}{}
+#' \item{year}{}
+#' \item{start_page}{}
+#' \item{assignee}{}
+#' \item{doi}{}
+#' \item{comments}{}
+#' }
+#'
+"assigned_article_notes"

### 2017-04-21 README.rmd
Update README.Rmd and reproduciblitiy_criteria.Rmd

@@
 ---
+title: "Reproducible Plant Pathology"
 output: github_document
@@
 
-<!-- README.md is generated from README.Rmd. Please edit that file -->
+[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/phytopathology/Reproducible.Plant.Pathology/commits/master) 
+[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
+[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
+[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.png?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology) 
+[![codecov.io](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology/coverage.svg?branch=master)](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology?branch=master)
 
-```{r, echo = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "README-"
-)
+## Research compendium for a report on the reproducibility of research in plant pathology
+
+### Compendium DOI:
+
+http://dx.doi.org/xxxxxxx
+
+The files at the URL above will generate the results as found in the publication.
+The files hosted at https://github.com/phytopathology/Reproducible.Plant.Pathology are the development versions and may have changed since the report was published
+
+### Authors  of this repository:
+
+Adam H Sparks (adamhsparks@gmail.com)
+Emerson M Del Ponte
+Zachary Foster
+Niklas J Grünwald
+
+### Published in:
+
+### Overview of contents
+
+This repository is our research compendium that details our methodology for examining the state of reproducible research in plant pathology.
+The compendium contains all data, code, and text associated with the publication XXXX published in XXX.
+The `Rmd` files in the `inst/paper/` directory contain details of how all the analyses reported in the paper were conducted.
+Instructions on how to rerun the analysis to reproduce the results are found in the vingette, in the `vingettes/` directory.
+
+### The supplementary files
+
+The `inst/` directory contains:
+
+- the manuscript as submitted (in MS Word format) and its Rmd source file (in the `paper/` directory)  
+- supplementary information source files (in R markdown format) and executed versions  
+- all the figures that are included in the paper (in the `figures/` directory)
+
+### The R package
+
+This repository is organized as an R package.
+There are no actual R functions in this package - all the R code is in the Rmd file.
+I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much about how to organise the files.
+
+To download the package source as you see it on GitHub, for offline browsing, use this line at the shell prompt (assuming you have Git installed on your computer):
+
+```{r eval=FALSE}
+git clone https://github.com/phytopathology/Reproducible.Plant.Pathology.git
 ```
 
-# Links to various resources that are useful for this document
+Once the download is complete, open the `Reproducible.Plant.Pathology.Rproj` in RStudio to begin working with the package and compendium files.
 
-[Replication data collection highlights value in diversity of replication attempts](http://www.nature.com/articles/sdata201728)
+The package has a number of dependencies on other R packages, and programs outside of R.
+These are listed at the bottom of this README.
+Installing these can be time-consuming and complicated, so we've done two things to simpify access to the compendium.
+First is the `packrat/` directory, which contains the source code for all the packages we depend on.
+If all works well, these will be installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio.
+<!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis.
+The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.
 
-[The reproducibility crisis in science and prospects for R](https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/)
+### The Docker image
 
-[rrrpkg - Use of an R package to facilitate reproducible research](https://github.com/ropensci/rrrpkg)
+A Docker image is a lightweight GNU/Linux virtual computer that can be run as a piece of software on Windows and OSX (and other Linux systems).
+To capture the complete computational environment used for this project we have a Dockerfile that specifies how to make the Docker image that we developed this project in.
+The Docker image includes all of the software dependencies needed to run the code in this project, as well as the R package and other compendium files.
+To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer.
+At the Docker prompt, enter:
+
+    docker run -dp 8787:8787 phytopathology/Reproducible.Plant.Pathology
+
+This will start a server instance of RStudio.
+Then open your web browser at localhost:8787 or or run `docker-machine ip default` in the shell to find the correct IP address, and log in with rstudio/rstudio.
+
+Once logged in, use the Files pane (bottom right) to navigate to `/` (the root directory), then open the folder for this project, and open the `.Rproj` file for this project.
+Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R markdown document, and knit them to produce the results in the paper.
+More information about using RStudio in Docker is avaiable at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
+
+We developed and tested the package on this Docker container, so this is the only platform that We're confident it works on, and so recommend to anyone wanting to use this package to generate the vignette, etc.
+--->
+
+### Licenses
+
+Manuscript: [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
+
+Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H Sparks
+
+Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
+
+### Dependencies
+
+We used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu 16.04 LTS.
+
+### Contact
+
+Adam H Sparks, Associate Professor, Centre for Crop Health
+University of Southern Queensland
+Toowoomba, Queensland 4350
+
+(+61) (7) 4831 1948   e. adam.sparks@usq.edu.au
+https://staffprofile.usq.edu.au/Profile/Adam-Sparks
+
+### Credits
+This research compendium was based on https://github.com/benmarwick/researchcompendium but not
+forked from because it was already under development when I found Ben's.

### 2017-04-23 README.rmd
Finalise conversion to R package
Ready for articles to be evaluated by us

Need to add bib entries to bib file in `inst/paper`

_Other changes_

- Add coverage
- Check spelling
- Finalise fetching references
- Add “examined_articles.bib” to `inst/paper`
- New function to get bib entries given a doi, `doi2bib()`
- Clean up vignettes
- Clean up README
- Use Travis and Appveyor
- Update packrat repository

@@
 [![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.png?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology) 
+[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/Reproducible.Plant.Pathology?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/Reproducible.Plant.Pathology)
 [![codecov.io](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology/coverage.svg?branch=master)](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology?branch=master)
@@
 The files at the URL above will generate the results as found in the publication.
-The files hosted at https://github.com/phytopathology/Reproducible.Plant.Pathology are the development versions and may have changed since the report was published
+The files hosted at https://github.com/phytopathology/Reproducible.Plant.Pathology are the development versions and may have changed since the report was published.
 
@@
 Adam H Sparks (adamhsparks@gmail.com)  
-Emerson M Del Ponte
-Zachary Foster
-Niklas J Grünwald
+Emerson M Del Ponte (delponte@ufv.br)  
+Zachary Foster (zacharyfoster1989@gmail.com)  
+Niklaus J Grünwald (grunwaln@science.oregonstate.edu)
 
@@
 The compendium contains all data, code, and text associated with the publication XXXX published in XXX.
-The `Rmd` files in the `inst/paper/` directory contain details of how all the analyses reported in the paper were conducted.
-Instructions on how to rerun the analysis to reproduce the results are found in the vingette, in the `vingettes/` directory.
+The `R markdown format` (`Rmd`) files in the `inst/paper/` directory contain details of how all the analyses reported in the paper were conducted.
+Detailed instructions on methods used and how to rerun the analysis to reproduce the results are found in the vignettes, in the `vingettes/` directory.
 
@@
 
-- the manuscript as submitted (in MS Word format) and its Rmd source file (in the `paper/` directory)  
-- supplementary information source files (in R markdown format) and executed versions  
+- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in the `paper/` directory)  
+- supplementary information source files (in `Rmd` format) and executed versions  
 - all the figures that are included in the paper (in the `figures/` directory)
@@
 This repository is organized as an R package.
-There are no actual R functions in this package - all the R code is in the Rmd file.
-I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much about how to organise the files.
+There is one R function, `doi2bib()`, that is used in this repository, along with the data, `assigned_article_notes.rda` that are located in `data` directory.
+We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.
 
@@
 
-```{r eval=FALSE}
+```
 git clone https://github.com/phytopathology/Reproducible.Plant.Pathology.git
@@
 These are listed at the bottom of this README.
-Installing these can be time-consuming and complicated, so we've done two things to simpify access to the compendium.
+Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium.
 First is the `packrat/` directory, which contains the source code for all the packages we depend on.

### 2017-04-23 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
Finalise conversion to R package
Ready for articles to be evaluated by us

Need to add bib entries to bib file in `inst/paper`

_Other changes_

- Add coverage
- Check spelling
- Finalise fetching references
- Add “examined_articles.bib” to `inst/paper`
- New function to get bib entries given a doi, `doi2bib()`
- Clean up vignettes
- Clean up README
- Use Travis and Appveyor
- Update packrat repository

--- 2017-04-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
@@
 2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
-3. Zachary S. L. Foster: Department of Botany and Plant Pathology, ORegon State Unviersity, Corvallis, OR 97330, USA
+3. Zachary S. L. Foster: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR 97330, USA
 4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
@@
 # MAIN TEXT
-Reproductibility and replicability in scientific research have once again been
+Reproducibility and replicability in scientific research have once again been
 highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.
@@
 ## BEST METHODS FOR REPRODUCIBLE RESEARCH
-* Provide definitions (provide defintions for terms used so it's clear)
+* Provide definitions (provide definitions for terms used so it's clear)
 * Data
@@
 ## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
-* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
+* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
 for readers.
@@
 necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
-* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
-* Example from my lab: 
+* Del Ponte provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied.
+* Example from Grünwald lab: 
   - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
@@
 ## RANDOM SAMPLING OF ARTICLES FROM THE TOP 20 PLANT PATHOLOGY JOURNALS
-The top 20 plant pathology discipline journals as ranked by Google Scholar, https://scholar.google.com/ (accessed 05 Dec.
-2016), were used to create a database of journals from which to randomly select articles for inspection.
-One hundred articles were randomly selected from 2012 to 2016 from a list of randomly selected start pages assigned to a randomised list of the 20 journals [@Sparks2017].
-The start pages list was numbered from page one and went to 150.
+The 21 plant pathology discipline journals were selected by the authors as representations of discipline-based journals where others in the field of phytopathology are likely to publish were used to create a database of journals from which to randomly select articles for inspection.
+Two hundred articles were randomly selected from 2012 to 2016 from a list of randomly selected pages assigned to a randomised list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
+The pages list was numbered from page one and went to 150.
 This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
@@
 
-The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2016].
+The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2017].
 

### 2017-04-23 R/data.R

@@ -1,36 +1,12 @@
-#' article_assignments
-#' @format A data frame with 201 observations of 17 elements:
-#' \describe{
-#'   \item{publication}{}
-#'   \item{year.x}{}
-#'   \item{start_page}{}
-#'   \item{assignee}{}
-#'   \item{doi}{}
-#'   \item{comments}{}
-#'   \item{bibtype}{}
-#'   \item{url}{}
-#'   \item{month}{}
-#'   \item{publisher}{}
-#'   \item{volume}{}
-#'   \item{number}{}
-#'   \item{pages}{}
-#'   \item{author}{}
-#'   \item{title}{}
-#'   \item{journal}{}
-#'   \item{editor}{}
-#' }
-#'
-"article_assignments"
-
 #' assigned_article_notes
 #' @format A data frame with 199 observations of 6 elements:
 #' \describe{
-#' \item{publication}{}
-#' \item{year}{}
-#' \item{start_page}{}
-#' \item{assignee}{}
-#' \item{doi}{}
-#' \item{comments}{}
+#' \item{journal}{Journal name}
+#' \item{year}{Year}
+#' \item{start_page}{Random number used to select articles wherein this number falls}
+#' \item{assignee}{Person assigned to examine article}
+#' \item{doi}{DOI if available}
+#' \item{comments}{Comments regarding the article}
 #' }
 #'
 "assigned_article_notes"

### 2017-04-23 R/doi2bib.R

@@ -1,0 +1,42 @@
+#' Convert doi to bibtex
+#'
+#' Convert a digital object identifier (doi) string into a bibtex entry using
+#' the web service <http://www.doi2bib.org>.
+#'
+#' @param doi The character string of the doi.
+#' @return a bibtex entry as a character string.
+#'
+#' @examples
+#' doi2bib("10.4454/jpp.fa.2012.002")
+#'
+#' @note
+#' Original script from William Keith Morris,
+#' <https://gist.github.com/wkmor1/ae2cc96acad472d49c35>.  Documented for use
+#' in an R package by Adam H Sparks
+#'
+#' @author William Keith Morris <wkmor1@gmail.com> and Adam H Sparks
+#'
+#' @name doi2bib
+#' @rdname doi2bib-methods
+#' @exportMethod doi2bib
+
+setGeneric("doi2bib",
+           function(doi) {
+             standardGeneric("doi2bib")
+           })
+
+#' @rdname doi2bib-methods
+#' @aliases doi2bib,ANY-method
+setMethod("doi2bib",
+          c(doi = "character"),
+          function(doi) {
+            httr::content(
+              httr::GET(
+                url    = "http://www.doi2bib.org/",
+                config = httr::accept("application/x-bibtex"),
+                path   = "doi2bib",
+                query  = list(id = doi)
+              ),
+              as = "text"
+            )
+          })

### 2017-04-23 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(Reproducible.Plant.Pathology)
+
+test_check("Reproducible.Plant.Pathology")

### 2017-04-23 tests/testthat/test_doi2bib.R

@@ -1,0 +1,7 @@
+context("doi2bib")
+
+test_that("doi2bib fetches a bib object", {
+  skip_on_cran()
+  expect_equal(doi2bib("10.4454/jpp.fa.2012.002"),
+               " @article{F. Suárez-Estrella_M.A. Bustamante_R. Moral_M.C. Vargas-García_M.J. López_J. Moreno_2012, title={IN VITRO CONTROL OF FUSARIUM WILT USING AGROINDUSTRIAL SUBPRODUCT-BASED COMPOSTS}, volume={94}, ISSN={1125-4653}, url={http://doi.org/10.4454/jpp.fa.2012.002}, DOI={10.4454/jpp.fa.2012.002}, number={1}, journal={Journal of Plant Pathology}, author={F. Suárez-Estrella and M.A. Bustamante and R. Moral and M.C. Vargas-García and M.J. López and J. Moreno}, year={2012}}\n")
+})

### 2017-04-23 README.rmd
Commit for Travis build
Remove appveyor for now

@@
 [![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.png?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology) 
-[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/Reproducible.Plant.Pathology?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/Reproducible.Plant.Pathology)
 [![codecov.io](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology/coverage.svg?branch=master)](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology?branch=master)

### 2017-04-23 README.rmd
Use svg not png; remove coverage

@@
 [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
-[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.png?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology) 
-[![codecov.io](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology/coverage.svg?branch=master)](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology?branch=master)
+[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology)
 

### 2017-05-19 R/data.R
Update article assignment and comment docs
Documents now generated in R and exported to Google Sheets for
collaborative edits

@@ -1,12 +1,0 @@
-#' assigned_article_notes
-#' @format A data frame with 199 observations of 6 elements:
-#' \describe{
-#' \item{journal}{Journal name}
-#' \item{year}{Year}
-#' \item{start_page}{Random number used to select articles wherein this number falls}
-#' \item{assignee}{Person assigned to examine article}
-#' \item{doi}{DOI if available}
-#' \item{comments}{Comments regarding the article}
-#' }
-#'
-"assigned_article_notes"

### 2017-07-05 README.rmd
Update README file with more information about project

@@
 
-- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in the `paper/` directory)  
+- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in
+the `paper/` directory)
+
 - supplementary information source files (in `Rmd` format) and executed versions
+
 - all the figures that are included in the paper (in the `figures/` directory)
+
+### The external files
+
+Much of the collaborative work was done outside of GitHub and R using Google
+Sheets. You can view the [article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M) that we collected in the "article_evaluations" tab. Where "template" and
+"article_notes" are used in creating that tab and are explained the "Assigning
+Articles" vignette of this R package.
 
@@
 
-This repository is organized as an R package.
-There is one R function, `doi2bib()`, that is used in this repository, along with the data, `assigned_article_notes.rda` that are located in `data` directory.
-We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.
+This repository is organized as an R package. There is one R function,
+`doi2bib()`, that is used in this repository, along with the data,
+`assigned_article_notes.rda` that are located in `data` directory. We have used
+the R package structure to help manage dependencies, to take advantage of
+continuous integration for automated code testing and for file organisation.
 
-To download the package source as you see it on GitHub, for offline browsing, use this line at the shell prompt (assuming you have Git installed on your computer):
+To download the package source as you see it on GitHub, for offline browsing,
+use this line at the shell prompt (assuming you have Git installed on your
+computer):
 
@@
 
-Once the download is complete, open the `Reproducible.Plant.Pathology.Rproj` in RStudio to begin working with the package and compendium files.
+Once the download is complete, open the `Reproducible.Plant.Pathology.Rproj` in
+RStudio to begin working with the package and compendium files.
 
-The package has a number of dependencies on other R packages, and programs outside of R.
+The package has a number of dependencies on other R packages, and programs
+outside of R.
 These are listed at the bottom of this README.
 Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium.
-First is the `packrat/` directory, which contains the source code for all the packages we depend on.
-If all works well, these will be installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio.
+First is the `packrat/` directory, which contains the
+source code for all the packages we depend on. If all works well, these will be
+installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio.
 <!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis.
@@
 
-Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H Sparks
+Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(),
+"%Y")`, copyright holder: Adam H Sparks
 
-Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
+Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
+requested in reuse
 
@@
 
-We used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu 16.04 LTS.
+We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
+16.04 LTS.
+
+We also used [JabRef](http://www.jabref.org/) and [Google Sheets](https://www.google.com/sheets/about/).
 

### 2017-07-05 README.rmd
Cleanup README.Rmd
Remove a few badges and fix commented out text regarding Docker

@@
 
-[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/phytopathology/Reproducible.Plant.Pathology/commits/master) 
-[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
 [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
@@
 
-## Research compendium for a report on the reproducibility of research in plant pathology
+## A research compendium for a report on the reproducibility of research in plant pathology
 
@@
 installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio.
+
 <!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis.

### 2017-08-13 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
Commit for Travis build
Remove appveyor for now
Added diagram, abstract,  text and modified html template

@@
 ---
-title: "What Does Reproducible Research Mean for Plant Pathology?"
+title: "Status and Best Practices for Reproducible Research In Plant Pathology"
 author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
-date: '`r Sys.Date()`'
-output:
-  word_document:
-    keep_md: yes
-    reference_docx: Phytopathology_Style_Reference.docx
-  html_document: default
+date: 'Last update: `r Sys.Date()`'
 csl: phytopathology.csl
 bibliography: bibliography.bib
+output:
+  html_document: 
+    css: my-style.css
+    theme: flatly
+    toc: true
+    toc_float: 
+     collapsed: true
+     smooth_scroll: true
+
 ---
@@
 ```
-1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
-2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
-3. Zachary S. L. Foster: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR 97330, USA
-4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
+First author: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia; second author: Departamento de Fitopatologia, Universidade Federal de Viçosa, Viçosa, MG, Brasil; third and fourth authors: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
 
-# ABSTRACT
+Accepted for publication:
 
-Abstracts are mandatory and limited to one 200 word paragraph.
+# Abstract
 
-# MAIN TEXT
-Reproducibility and replicability in scientific research have once again been
-highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.
+Reproducible research practices have been highlighted extensively during the last ten years in many fields of study as standard to promote transparency and replication of scientific results, a well known current issue in science.
+In fact, scientific claims can only be evaluated based on how: protocols, materials, equipments and methods were described; data were collected and prepared; and analyses conducted.
+Sharing of data and computational code are central for current scholarly dissemination and communication standadars, but in many fields, including Plant Pathology, the rate at which the researchers are engaged in this endeavour is apparently slow.
+We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, which were scrutinized to obtain data reflecting reproducibility.
+We found that..
+Protocols specific to plant pathology and open source tools for producing reproducible work and analysis is proposed to promote such practice among plant pathologists.
 
-Patil et al. [-@Patil066803] have provided several definitions to clarify the
-concepts surrounding reproducibility and replicability. For the purposes of this
-paper we follow the definitions as given by Patil et al. [-@Patil066803].
+# Main text
 
-* Why reproducible research
+## Introductory
 
-## BEST METHODS FOR REPRODUCIBLE RESEARCH
-* Provide definitions (provide definitions for terms used so it's clear)
-* Data
-  * Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
-  * Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
-* When publishing
-  * Provide data
-  * Provide code
-* Using GitHub for code (and small data?)
-* Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
+Modern plant pathological research has many facets given the array of disciplines and subdisciplines currently involved.
+Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve management.
+Scientific research in the field vary from purely observational/descriptive nature to inferential based on experimental or simulation-derived small/large datasets.
+Whenever the case, research findings are verifiable based on how much of the research materials, processes and outcomes, beyond what is reported in the scientific article, are made available.
+These include biological materials (strains), acid nucleic sequences, experimental and simulated raw data annotations, drawing and photographs, statistical analysis codes, among others.
 
-## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
+##3 Reproducible research
+
+Reproducibility and replicability in scientific research have once again been highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.
+Patil et al.
+[-@Patil066803] have provided several definitions to clarify the concepts surrounding reproducibility and replicability.
+For the purposes of this paper we follow the definitions as given by Patil et al.
+[-@Patil066803].
+
+## A general workflow
+
+A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
+Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Fig.
+1).
+
+A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used.
+A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow promptly access to the data and running the codes because of use of expensive commercial software or a paywall.
+A highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run more easily following download of data and codes.
+The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
+In the next section we present standards and tools that can be used to ensure reproducibility.
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+library(DiagrammeR)
+grViz("
+  digraph Fig1 {
+
+graph [fontsize = 8, nodesep=0.5]
+
+node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
+Question;  Methodology;  Data;  Analysis;  Manuscript;
+
+node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
+Description; Availability; Citation
+
+node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
+Binary_Code; Binary_File; Supplement
+
+node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
+Source_Code;  Data_File; Pub_Repository;
+
+Question->Methodology->Data->Analysis
+Analysis->Manuscript
+Methodology->Description
+Methodology->Citation
+Methodology->Availability
+Manuscript->Supplement
+Data->Data_File->Pub_Repository
+Analysis->Binary_Code->Supplement
+Analysis->Source_Code->Pub_Repository
+Data->Binary_File->Supplement
+}
+")
+
+```
+
+### Methods
+
+- Citation of methods, software, packages, etc.
+- deposit and annotate biological materials
+- provide full description for equipments, etc.
+
+### Data
+
+- Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
+- Data annotation
+- Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
+
+### Source code
+
+- The problem of commercial software and mouse-based routines
+- Why to avoid binary files as supplements?
+- Writing and documenting using open source software
+- Availability in public repositories
+
+### Repository
+- Using GitHub for code (and small data?)
+- Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
+
+## Status in Plant Pathology
+
 * Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
@@
 
-## RANDOM SAMPLING OF ARTICLES FROM THE TOP 20 PLANT PATHOLOGY JOURNALS
-The 21 plant pathology discipline journals were selected by the authors as representations of discipline-based journals where others in the field of phytopathology are likely to publish were used to create a database of journals from which to randomly select articles for inspection.
-Two hundred articles were randomly selected from 2012 to 2016 from a list of randomly selected pages assigned to a randomised list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
+Twenty-one plant pathology discipline journals were selected by the authors as representations of discipline-based journals target by the plant pathology research community.
+Among them, both fundamental and/or applied as well as journals covering specific group of pathogens/plants or broad areas were included.
+Two hundred articles were randomly selected from issues published from 2012 to 2016.
+A list of randomly selected pages was assigned to a randomised list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
 In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
@@
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-
 The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2017].
 
-## DISCUSSION
+## Discussion
 
-## ACKOWLEDGEMENTS
+## Acknowledgments
 
-### LITERATURE CITED
+## Literature cited

### 2017-08-14 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
Export PDF of Figure 1 in paper when knitting MS Word document

@@
 date: 'Last update: `r Sys.Date()`'
+output:
+  word_document:
+    keep_md: yes
+    reference_docx: Phytopathology_Style_Reference.docx
 csl: phytopathology.csl
 bibliography: bibliography.bib
-output:
-  html_document: 
-    css: my-style.css
-    theme: flatly
-    toc: true
-    toc_float: 
-     collapsed: true
-     smooth_scroll: true
-
+always_allow_html: yes
 ---
@@
 The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-In the next section we present standards and tools that can be used to ensure reproducibility.
+In the next section we present standards and tools that can be used to ensure reproducibility (Figure 1).
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(rsvg)
 
-library(DiagrammeR)
-grViz("
+p <- export_svg(grViz(
+  "
   digraph Fig1 {
@@
   }
-")
+  ",
+  width = 1000,
+  height = 750
+))
 
+rsvg_pdf(charToRaw(p), "Figure 1.pdf")
 ```

### 2017-08-14 inst/paper/paper.Rmd
Export PDF of Figure 1 in paper when knitting MS Word document

--- 2017-04-23 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
@@
 ---
-title: "What Does Reproducible Research Mean for Plant Pathology?"
+title: "Plant Pathology Journal Article Reproducibility Survey Results and Recomendations"
 author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
@@
 ```
-1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
+1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland,
+Toowoomba, Qld 4350, Australia
 2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
-3. Zachary S. L. Foster: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR 97330, USA
-4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
+3. Zachary S. L. Foster: Department of Botany and Plant Pathology, Oregon State
+University, Corvallis, OR 97330, USA
+4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA
+Agricultural Research Service, Corvallis, OR 97330, USA
 
@@
 # MAIN TEXT
+
 Reproducibility and replicability in scientific research have once again been
@@
 ## BEST METHODS FOR REPRODUCIBLE RESEARCH
+
 * Provide definitions (provide definitions for terms used so it's clear)
+
 * Data
+
+  * 10 things to make your data reproducible
+
   * Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
-  * Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
+
+  * Data storage (don't edit raw data files; use file permissions to prevent
+  changes to raw data files, use data bases where possible and appropriate;
+  etc.)
+
 * When publishing
+
   * Provide data
+
   * Provide code
+
 * Using GitHub for code (and small data?)
+
 * Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
@@
 ## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
-* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
-for readers.
-* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
+
+* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible
+examples for readers.
+
+* Duku et al. [-@Duku2016] provide models, data and code,
+(http://adamhsparks.github.io/MICCORDEA/) necessary to
 replicate the entire study modelling the effects of climate change on rice
 bacterial blight and rice leaf blast in Tanzania.
+
 * Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
-necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
-* Del Ponte provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied.
+necessary to replicate model development and the subsequent the study on the
+effects of climate change on potato late blight.
+
+* Del Ponte provides data and a reproducible report that explain in details all
+steps of the analysis and the R codes for conducting a meta-analysis for
+assessing heterogeneity in relationship between white mold incidence and soybean
+yield and between incidence and soybean tied.
+
 * Example from Grünwald lab: 
@@
   - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
+
 * Other examples from plant pathology providing e-Xtras or supplemental material
@@
 ## RANDOM SAMPLING OF ARTICLES FROM THE TOP 20 PLANT PATHOLOGY JOURNALS
-The 21 plant pathology discipline journals were selected by the authors as representations of discipline-based journals where others in the field of phytopathology are likely to publish were used to create a database of journals from which to randomly select articles for inspection.
-Two hundred articles were randomly selected from 2012 to 2016 from a list of randomly selected pages assigned to a randomised list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
-Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
-The pages list was numbered from page one and went to 150.
-This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
 
-The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2017].
+The 21 plant pathology discipline journals were selected by the authors as
+representations of discipline-based journals where others in the field of
+phytopathology are likely to publish were used to create a database of journals
+from which to randomly select articles for inspection. Two hundred articles were
+randomly selected from 2012 to 2016 from a list of randomly selected pages
+assigned to a randomised list of the 21 journals [@Sparks2017] where the page
+number fell within an article for the given journal. In cases where an article
+was not suitable, _e.g._, a review or otherwise not related to plant pathology,
+the next article was selected until a suitable article was found. Notes
+regarding the selection of articles can be found in the file, XXXX, available in
+this paper's repository. The pages list was numbered from page one and went to
+150. This was done since some journals restart their numbering with each issue
+and also ensures that the journal is more likely to have a page number
+corresponding to the randomly generated value. This also assumes that there is
+no effect or bias on reproducibility based on the time of year that an article
+was published, since most journals start with page number one at the beginning
+of the year.
+
+The list of journals was saved as a comma separated value (CSV) file and
+imported into R [@R2017].
 

### 2017-08-15 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
added ability to render all formats

@@
     reference_docx: Phytopathology_Style_Reference.docx
+  pdf_document: default
+  html_document: default
 csl: phytopathology.csl
@@
 ---
+
+<!-- 
+To render all formats:
+rmarkdown::render('What Does Reproducible Research Mean for Plant Pathology.Rmd', output_format = 'all')
+-->
 

### 2017-08-15 inst/paper/Sparks_et_al-main_text.Rmd
Rename What Does Reproducible Research Mean for Plant Pathology.Rmd to Sparks_et_al-main_text.Rmd

--- 2017-08-15 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
@@
 
-Reproducible research practices have been highlighted extensively during the last ten years in many fields of study as standard to promote transparency and replication of scientific results, a well known current issue in science.
-In fact, scientific claims can only be evaluated based on how: protocols, materials, equipments and methods were described; data were collected and prepared; and analyses conducted.
-Sharing of data and computational code are central for current scholarly dissemination and communication standadars, but in many fields, including Plant Pathology, the rate at which the researchers are engaged in this endeavour is apparently slow.
-We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, which were scrutinized to obtain data reflecting reproducibility.
+Reproducible research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and replication of scientific results.
+In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted.
+Sharing of data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow.
+We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting reproducibility.
 We found that..
-Protocols specific to plant pathology and open source tools for producing reproducible work and analysis is proposed to promote such practice among plant pathologists.
+Protocols specific to plant pathology and open source tools for producing reproducible work and analysis is proposed to promote reproducible practices among plant pathologists.
 
@@
 
-Modern plant pathological research has many facets given the array of disciplines and subdisciplines currently involved.
+Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
 Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve management.
-Scientific research in the field vary from purely observational/descriptive nature to inferential based on experimental or simulation-derived small/large datasets.
-Whenever the case, research findings are verifiable based on how much of the research materials, processes and outcomes, beyond what is reported in the scientific article, are made available.
-These include biological materials (strains), acid nucleic sequences, experimental and simulated raw data annotations, drawing and photographs, statistical analysis codes, among others.
+Scientific research in the field vary from purely observational/descriptive nature to inferential based on experimental or simulation-derived data sets.
+Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available, beyond what is reported in the scientific article.
+These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawing and photographs, statistical analysis codes, among other data.
 
@@
 
-Reproducibility and replicability in scientific research have once again been highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.
+Reproducibility in scientific research has once again been highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an important issue.
 Patil et al.
-[-@Patil066803] have provided several definitions to clarify the concepts surrounding reproducibility and replicability.
+[-@Patil066803] have provided several definitions to clarify the concepts surrounding reproducibility.
 For the purposes of this paper we follow the definitions as given by Patil et al.
@@
 A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used.
-A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow promptly access to the data and running the codes because of use of expensive commercial software or a paywall.
+A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a paywall.
 A highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run more easily following download of data and codes.
@@
 Two hundred articles were randomly selected from issues published from 2012 to 2016.
-A list of randomly selected pages was assigned to a randomised list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
 In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.

### 2017-08-15 inst/paper/Sparks_et_al-main_text.Rmd
Clean up files in /inst/paper directory and use flatly theme in html output
Also

- Drop md intermediate output when generating PDF, no need with HTML,
the HTML renders better, will link to HTML file using raw.github.com to
display the paper online from the README.md file

@@
 output:
+  html_document:
+    css: my-style.css
+    theme: flatly
+    toc: true
+    toc_float: 
+     collapsed: true
+     smooth_scroll: true
+  pdf_document: default
   word_document:
-    keep_md: yes
     reference_docx: Phytopathology_Style_Reference.docx
-  pdf_document: default
-  html_document: default
 csl: phytopathology.csl

### 2017-08-15 README.rmd
Housekeeping items
- Change name where necessary to reflect renaming repository, which
reflects the title of the paper more accurately

- Spell checking in the package and Rmd files

- Update the _pkgdown_ site to follow the flatly theme that the HTML
document uses

- Update package name/title

- Remove packrat files, need to think about checkpoint?

- Cleanup .gitignore

@@
 ---
-title: "Reproducible Plant Pathology"
+title: "Reproducibility in Plant Pathology"
 output: github_document
@@
 
-[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
-[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology)
+[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology)
 
 ## A research compendium for a report on the reproducibility of research in plant pathology
+
+For optimal webviewing of this report, please see the [HTML version](http://htmlpreview.github.io/?https://github.com/phytopathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).
 
@@
 The files at the URL above will generate the results as found in the publication.
-The files hosted at https://github.com/phytopathology/Reproducible.Plant.Pathology are the development versions and may have changed since the report was published.
+The files hosted at https://github.com/phytopathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.
 
@@
 Adam H Sparks (adamhsparks@gmail.com)
+
 Emerson M Del Ponte (delponte@ufv.br)
+
 Zachary Foster (zacharyfoster1989@gmail.com)
+
 Niklaus J Grünwald (grunwaln@science.oregonstate.edu)
@@
 ```
-git clone https://github.com/phytopathology/Reproducible.Plant.Pathology.git
+git clone https://github.com/phytopathology/Reproducibility_in_Plant_Pathology.git
 ```
 
-Once the download is complete, open the `Reproducible.Plant.Pathology.Rproj` in
+Once the download is complete, open the `Reproducibility_in_Plant_Pathology.Rproj` in
 RStudio to begin working with the package and compendium files.
@@
 source code for all the packages we depend on. If all works well, these will be
-installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio.
+installed on your computer when you open `Reproducibility_in_Plant_Pathology.Rproj` in RStudio.
 
@@
 
-    docker run -dp 8787:8787 phytopathology/Reproducible.Plant.Pathology
+    docker run -dp 8787:8787 phytopathology/Reproducibility_in_Plant_Pathology
 

### 2017-08-15 docs/articles/assigning_articles.Rmd
Housekeeping items
- Change name where necessary to reflect renaming repository, which
reflects the title of the paper more accurately

- Spell checking in the package and Rmd files

- Update the _pkgdown_ site to follow the flatly theme that the HTML
document uses

- Update package name/title

- Remove packrat files, need to think about checkpoint?

- Cleanup .gitignore

---
title: "Assigning Articles to Evaluators"
author: "Adam H Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Assigning Articles to Evaluators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Creating a sample of articles

Twenty one journals in the discipline of plant pathology were selected by the
four authors as being the primary choice for most plant pathologists when
publishing manuscripts.

Using the assumption that journals publish an average 10 articles per issue, for
a population of ~1000 articles, using a confidence level of 95% and confidence
interval of 10% we need 88 samples. In
[Issue #3](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/issues/3),
we decided to select 200 articles to have a large sample of the population.

There are three distinct steps involved:

1. Set up the journals, years, and page numbers and evaluators and assign
randomly. Create a tibble that holds these data along with empty fields
for the evaluation of the articles. Create a Google Sheets object to serve as a
template for the second step.

2. Look up the articles and check that the selected journal, year, page number
actually are appropriate and enter the DOI and other comments regarding
article selection in Google Sheets. Which is used in the third step.

3. Import article notes and DOIs from Google Sheets back to R, retrieve as many
bib entries as possible using the DOI. Merge the bib entries with the notes
and DOI values. Create a new tab in the Google Sheets object for the evaluators
to carry out evaluations.

## Step 1

### R setup

```{r library, message=FALSE}
library(dplyr)
library(readr)
library(bib2df)
library(googlesheets)
library(stringr)
library(Reproducible.Plant.Pathology)

set.seed(1)

# For printing tibble in total
options(tibble.print_max = 21, tibble.print_min = 21)
```
### Create list of journals

We hand-picked a list of 21 journals that we felt represented plant pathology
research. In this step, we will create a `tibble` in R of these journals,
assigning them a number so that we can randomise them.

```{r journal_list}
journal_list <- tibble(
  seq(1:21),
  c("Australasian Plant Pathology",
    "Canadian Journal of Plant Pathology",
    "Crop Protection",
    "European Journal of Plant Pathology",
    "Forest Pathology",
    "Journal of General Plant Pathology",
    "Journal of Phytopathology",
    "Journal of Plant Pathology",
    "Virology Journal (Plant Viruses Section)",
    "Molecular Plant-Microbe Interactions",
    "Molecular Plant Pathology",
    "Nematology",
    "Physiological and Molecular Plant Pathology",
    "Phytoparasitica",
    "Phytopathologia Mediterranea",
    "Phytopathology",
    "Plant Disease",
    "Plant Health Progress",
    "Plant Pathology",
    "Revista Mexicana de Fitopatología",
    "Tropical Plant Pathology"))

names(journal_list) <- c("number", "journal")
```

### Create list of evaluators

From the four authors of this paper, in this step, we will create a list for us
to use that will randomly assign articles for us to evaluate for this
manuscript.

```{r assignee}
assignee <- rep(c("Adam", "Emerson", "Zach", "Nik"), 50)

```

### Create randomised list

Now we will create a randomised list of journal articles to assign to each of
the four authors for this paper.

#### Create a randomised list of the journals

```{r journal_sample}
journals <- tibble(sample(1:21, 200, replace = TRUE))

names(journals) <- "number"

journals <- left_join(journals, journal_list, "number")
```

#### Randomly select articles

Generate a random list of years between 2012 and 2016 and a random list of start
pages between 1 and 150 since some journals start numbering at 1 with every
issue. Then bind the columns of the randomised list of journals with the
randomised years and page start numbers. This then assumes that there is no
temporal effect, _i.e._, the time of year an article is published does not
affect whether or not it is reproducible.

```{r years_and_articles}
year <- sample(2012:2016, 200, replace = TRUE)

contains_page <- sample.int(150, 200, replace = TRUE)

journals <- cbind(journals[, -1], year, contains_page, assignee)

journals <- arrange(.data = journals, assignee, journal, year, contains_page)

```

#### Check the number of articles per journal

```{r, count}
journals %>%
  group_by(journal) %>%
  tally(sort = TRUE)
```

Once this is done, the articles are manually examined for suitability. Reference
articles or off-topic articles are not included. Notes are provided regarding
these cases in `assigned_article_notes`. If the selected page number/article was
not suitable, the next sequential article was selected manually.

### Add empty columns for evaluations

A variety of information will be collected with each article to be used in the
analysis later. It is easiest to enter this using a spreadsheet application, so
we will add on the columns for what information we want to collect and save the
table as a csv for manual editing.

```{r}
to_record <- c(
  "doi",
  "IF_5year",
  "country",
  "open",
  "repro_inst",
  "iss_per_year",
  "art_class",
  "supl_mats",
  "comp_mthds_avail",
  "software_avail",
  "software_cite",
  "analysis_auto",
  "data_avail",
  "data_annot",
  "data_tidy",
  "reproducibility_score"
  )
  journals[to_record] <- ""

  journals <- 
    journals %>%
    group_by(assignee) %>%
    as_tibble()
```

### Write to Google Sheets

We decided to use Google Sheets so that we could concurrently edit the file
more easily. Once we're done filling in our evaluations, we will import the
data back to R. Jenny Bryan has created a handy package, _googlesheets_ that we
use here. _Note that this must be run interactively for `gs_new()` to work.
Knitting this .Rmd file will not generate any gsheets, it must be done in an
interactive R session._

Create a Google Sheets workbook to hold worksheets for this project. This first
sheet will serve as a template and is thus named "template".

```{r setup_gs, eval=FALSE}
# Give googlesheets permission to access spreadsheets and Google Drive
gs_auth()

# create Google Sheet for concurrent edits, first sheet: article notes template
gs_new(
  "article_notes",
  ws_title = "template",
  input = journals,
  trim = TRUE,
  verbose = FALSE
  )
```

## Step 2

### Add article DOI's

This step is completed in gsheets, Adam looked up articles and added notes and
DOIs to a gsheet, "article_notes" which will be imported to R in the next step.

## Step 3

### Generate a bibliography file to use with the paper

Using the DOIs in this file, we can retrieve the BibTex citations for those
articles that provide a DOI. Note that not all of the selected articles have a
DOI, so we'll have to manually generate those entries, or fetch them from the
journals' website later.

```{r join_files, warning=FALSE, message=FALSE, results="hide", eval=FALSE}
article_notes <- gs_title("article_notes")

notes <- 
  article_notes %>% 
    gs_read(ws = "article_notes")

# format DOIs to all be uniform, lower-case
notes$doi <- tolower(notes$doi)

# convert encodings for text with accents
notes$journal <- iconv(notes$journal, "latin1", "UTF-8")

# get bib references from the DOI (that exist)
bib <- unlist(lapply(notes$doi, doi2bib))
```

The _Journal of Plant Pathology_ does not supply valid bib entries via the DOI.
So we need to clean them up.

```{r first_bib_cleaning, warning=FALSE, message=FALSE, results="hide", eval=FALSE}

# locations of Journal of "Plant Pathology"" entries in bib object
clean_pp <- grep("journal=\\{Journal of Plant Pathology\\}", bib)

# create a dataset of just those bib entries
bib_clean_pp <- bib[clean_pp]

# function to clean the entries
clean_articles_pp <- function(x) {
  title_loc <- unlist(gregexpr(pattern = "title", x))
  y <- substr(x, start = title_loc[1], stop = nchar(x))
  y <- paste0("@article{jpp,\n\t" , y)
  y <- gsub("}, ", "},\n\t", y)
  y <- gsub("=", " = ", y)
  y <- gsub("}}\n", "}\n}", y)
}

# apply function and clean the bib entries
cleaned_pp <- unlist(lapply(bib_clean_pp, clean_articles_pp))

# remove the incorrect entries for Journal of Plant Pathology
bib <- bib[-clean_pp]
```

_Phytopathologia Mediterranea_ also provides some malformed bib entries. The
cite entries are malformed and `<em> </em>` is used rather than the proper
`\textit{}` for a BibTeX file.

```{r second_bib_cleaning, warning=FALSE, message=FALSE, results="hide", eval=FALSE}
clean_pm <- grep("journal=\\{Phytopathologia Mediterranea\\}", bib)
bib_clean_pm <- bib[clean_pm]
clean_articles_pm <- function(x) {
  x <- gsub(" @article\\{[[:print:]]+, title=\\{", "@article\\{PM, title = \\{", x)
  x <- gsub("<em>", "\\\textit\\{", x)
  x <- gsub("</em>", "}", x)
  }

# apply function and clean the bib entries
cleaned_pm <- unlist(lapply(bib_clean_pm, clean_articles_pm))
bib <- bib[-clean_pm]

```

The larger list of bib objects has some items that are supposedly invalid DOIs.
In this step we remove them and clean up the list. They'll be added back to the
database when we merge the notes at the end.

Also there are duplicates in the list somehow. Use `unique()` to clean the list
up.

```{r, clean_bib, eval=FALSE}
bib <- bib[bib != "Invalid DOI"]

bib <- unique(bib)
```

Next export the items as files to disk as .bib files to be cleaned using
JabRef. This will automatically assign unique cite keys and fix some issues with characters in the bib file. Open the file in JabRef and click "yes" when
prompted to regarding the cite keys.

```{r export_import_bib, eval=FALSE}
# clean up any existing files since we're appending
unlink("~/tmp/bib_article_notes.bib")

# write files to a local directory and clean up with JabRef
lapply(unlist(bib), write, "~/tmp/bib_article_notes.bib", append = TRUE)
lapply(unlist(cleaned_pp), write, "~/tmp/bib_article_notes.bib", append = TRUE)
lapply(unlist(cleaned_pm), write, "~/tmp/bib_article_notes.bib", append = TRUE)

```

*Important* Open resulting files in `~/tmp` directory in JabRef, create new
keys and resave. JabRef will generate unique keys and fix any inconsistencies
that may exist from the DOI search.

### Export Google Sheets

In this last bit, import the BibTeX file back into R and export to a tab in the
Google Sheets for collaborative edits.

```{r google, warning=FALSE, message=FALSE, results="hide", eval=FALSE}

# import both the Journal of Plant Pathology (cleaned_bib) and article_notes.bib
bib <- bib2df("~/tmp/bib_article_notes.bib")
names(bib) <- tolower(names(bib))

# join notes with bibliographic data
bib_df <- left_join(notes, bib)
bib_df <- arrange(bib_df, assignee)

# create Google Sheet for concurrent edits
article_notes <-
  article_notes %>%
    gs_ws_new(
    ws_title = "article_evaluations",
    input = bib_df,
    trim = TRUE,
    verbose = FALSE
    )

# clean up files to build R package properly with no NOTES
unlink(".httr-oauth")
```

### Last steps

The last few steps are completed outside of R in Google Docs, manually adding
the missing information to the spreadsheet and the assignees adding their
evaluations of their respective articles.

The Google Sheets can be found here:
https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381.

### 2017-08-15 docs/articles/reproducibility_criteria.Rmd
Housekeeping items
- Change name where necessary to reflect renaming repository, which
reflects the title of the paper more accurately

- Spell checking in the package and Rmd files

- Update the _pkgdown_ site to follow the flatly theme that the HTML
document uses

- Update package name/title

- Remove packrat files, need to think about checkpoint?

- Cleanup .gitignore

---
title: "Criteria for Evaluating Reproducibility"
author: "Adam H Sparks and Emerson M Del Ponte and Zachary S L Foster and Niklaus J. Grünwald"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Criteria for Evaluating Reproducibility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Key for data collection

This vignette documents the fields and values found in the
"article_evaluations" sheet in the "article_notes" Google Sheets
workbook,
https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381

### Autogenerated values

In the reproducibility score there are two parts, one part is automatically
generated, as much as possible, using the article DOI to retrieve the reference.

The articles' DOIs are looked up manually by Adam and assigned in the
"[article_notes](https://docs.google.com/spreadsheets/d/1YrIiQ3OBNjCHMlalkMi1yy8dy4hnj5dnR4PSTj7lDR4/edit#gid=0)" sheet in the googlesheets document, `doi`.

Nik has provided the five-year impact factor, `IF_5year`.

Other items including `journal`, `year`, and `contains_page` are auto-generated by the ["Assigning Articles"](https://github.com/phytopathology/Reproducible.Plant.Pathology/blob/master/vignettes/Assigning_Articles.Rmd) vignette.

#### "journal"

Auto-generated in Assigning Articles

Name of journal

Entered as character string in title case

#### "year"

Auto-generated in Assigning Articles

Year the article was published

Entered as a 4-digit number.

#### "contains_page"

Auto-generated in Assigning Articles

Randomly selected page number which is used to select article for evaluation.
The article is selected if it contains this page number in its page range.

#### "assignee"

Auto-generated in Assigning Articles

Randomly assigned evaluator selected from Adam, Emerson, Nik or Zach and
assigned to a particular article (row)

### Manually entered metadata

### "doi"

Articles are looked up by Adam using the "article_notes" sheet in googlesheets.
The DOI is entered as a character string or left as `NA` if one is not
provided.

Entered as a character string.

### "comments"

Comments column, Adam has used this to enter comments regarding article
selection in cases where the `contains_page` number does not align with
our criteria. Can be used by evaluator for other comments on the article
when evaluating.

Entered as a character string.

### "IF_5year"

Nik has looked up and provided the five-year impact factor for each journal and
entered it in the "article_notes".

Entered as a decimal value.

### Evaluation of reproducibility

#### "open"

Whether the journal is open-access or not

Entered as `TRUE`/`FALSE`/`BOTH`

#### "repro_inst"

Does the journal have guidelines for reproducibility?

- `0` - Not mentioned

- `1` - At least a suggestion to put data online, but not details on how/where.

- `2` - Detailed instructions on where to place data

- `3` - Detailed instructions on where to place data and code

#### "art_class"

What kind of research the article describes

One or more of the following:

- `Fundamental`

- `Applied`

- `Molecular`

Entered as an R `vector` object in comma-separated list with spaces.

For example: `c("Applied"", "Molecular")` or `Fundamental`

#### "comp_mthds_avail"

Score of computational methods documentation

Are the computational methods used readily available, _e.g._, R, SAS, Python
scripts are shared?

Entered as a number between `0` and `3`

- `0` - Not available and not mentioned in publication

- `1` - Available upon request to author

- `2` - Online, but inconvenient/non-permanent (_e.g._, login necessary,
pay wall, FTP server, personal lab website)

- `3` - Freely available online to anonymous users for foreseeable future
(_e.g_, GitHub, Figshare, Dataverse)

#### "software_avail"

Score of software availability

Entered as a number between `0` and `3`

- `0` - Not available or not mentioned in the publication

- `1` - Uses expensive proprietary software that only institutions would
typically purchase (_i.e._, ArcGIS standard is $7000)

- `2` - Uses proprietary software that most individuals can afford (_e.g._,
Excel, Matlab? ($500))

- `3` - Uses entirely open source and free software (_e.g._, R, Python).

#### "software_cite"

Score of citations for software used

Entered as a number between `0` and `3`

- `0` - not mentioned

- `1` - Software mentioned by name only

- `2` - Software cited with version number

- `3` - All software components (PROCs, packages) etc. cited

#### "software_used"

Entered as an R `vector` object in comma-separated list with spaces.

For example: `c("R", "TableTool")` or `R`

#### "data_avail"

Raw data availability score

Entered as a number between `0` and `3`

- `0` - Not available or not mentioned in the publication

- `1` - Available upon request to author

- `2` - Online, but inconvenient/non-permanent (_e.g._ login needed, pay wall,
FTP server, personal lab website)

- `3` - Freely available online to anonymous users for foreseeable future

#### "reproducibility_score"

Sum of the prior scores that are scored on a `0` - `3` scale. A score of `0` is
not reproducible a score of `21` is perfectly reproducible based on the
criteria agreed upon for this article.

## Bibliography fields

The following fields are automatically filled by searching for the DOI and
retrieving a BibTex entry, where applicable. In cases where a DOI is not
present or the data are incomplete or incorrect the evaluator should enter
the necessary data for the article assigned to them. In these cases, important
fields to enter are:

### "author"

Entered as character string in R `vector` format with spaces following BibTex
style, _e.g._, c("A H Sparks", "E {Del Ponte}", "Z Foster", "N Grünwald")

### "pages"

Entered as a character string in BibTex format, numbers separated by a double
"-", _e.g._, 1--18.

### "publisher"

Name of journal publisher.

Entered as character string, _e.g._ Springer or Wiley-Blackwell or
Scientific Societies

### "month"

Month in which the article was published

Entered as character string, _e.g._ jan, feb, mar...

### "number"

Issue number of the journal

Entered as an integer

### "title"

Article title

Entered as a character string

### "volume"

Volume number of the journal

Entered as an integer

## The following fields are automatically created by BibTex and are _optional_

### "category"

### "bibtexkey"

### "address"

### "annote"

### "booktitle"

### "chapter"

### "crossref"

### "edition"

### "editor"

### "howpublished"

### "institution"

### "key"

### "note"

### "organizations"

### "school"

### "series"

### "type"

### "url"

### "x.article.pm..title"

### 2017-08-15 inst/paper/Sparks_et_al-main_text.Rmd
Housekeeping items
- Change name where necessary to reflect renaming repository, which
reflects the title of the paper more accurately

- Spell checking in the package and Rmd files

- Update the _pkgdown_ site to follow the flatly theme that the HTML
document uses

- Update package name/title

- Remove packrat files, need to think about checkpoint?

- Cleanup .gitignore

@@
 A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used.
-A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a paywall.
+A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a pay-wall.
 A highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run more easily following download of data and codes.

### 2017-08-15 tests/testthat.R

@@ -1,4 +1,4 @@
 library(testthat)
-library(Reproducible.Plant.Pathology)
+library(Reproducibility.in.Plant.Pathology)
 
-test_check("Reproducible.Plant.Pathology")
+test_check("Reproducibility.in.Plant.Pathology")

### 2018-01-10 inst/paper/Sparks_et_al-main_text.Rmd
Update main text with a point about proper archives

@@
 - provide full description for equipments, etc.
+- rOpenSci Reproducible Research: http://ropensci.github.io/reproducibility-guide/sections/introduction/
 
@@
 - Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
+- Most ideal a library or other proper long-term data archival service
 

### 2018-01-10 inst/paper/Sparks_et_al-main_text.Rmd
Verbage around point for writing

@@
 - Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
-- Most ideal a library or other proper long-term data archival service
+- Or using, most ideally, a library or other proper long-term data archival service
 

### 2018-01-10 README.rmd
Add Sydney to list of authors in Readme and format e-mail links
Fix links to pkgdown site

@@
 
-[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology)
+[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology)
 
@@
 
-For optimal webviewing of this report, please see the [HTML version](http://htmlpreview.github.io/?https://github.com/phytopathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).
+For optimal webviewing of this report, please see the [HTML version](http://htmlpreview.github.io/?https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).
 
@@
 The files at the URL above will generate the results as found in the publication.
-The files hosted at https://github.com/phytopathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.
+The files hosted at https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.
 
@@
 
-Adam H Sparks (adamhsparks@gmail.com)
+Adam H Sparks (<adamhsparks@gmail.com>)
 
-Emerson M Del Ponte (delponte@ufv.br)
+Emerson M Del Ponte (<delponte@ufv.br>)
 
-Zachary Foster (zacharyfoster1989@gmail.com)
+Sydney Everhart (<everhart@unl.edu>)
 
-Niklaus J Grünwald (grunwaln@science.oregonstate.edu)
+Zachary Foster (<zacharyfoster1989@gmail.com>)
+
+Niklaus J Grünwald (<grunwaln@science.oregonstate.edu>)
 
@@
 ```
-git clone https://github.com/phytopathology/Reproducibility_in_Plant_Pathology.git
+git clone https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology.git
 ```
@@
 
-    docker run -dp 8787:8787 phytopathology/Reproducibility_in_Plant_Pathology
+    docker run -dp 8787:8787 openplantpathology/Reproducibility_in_Plant_Pathology
 

### 2018-04-07 README.rmd
Update README
Include Docker file information

@@
 These are listed at the bottom of this README.
-Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium.
-First is the `packrat/` directory, which contains the
-source code for all the packages we depend on. If all works well, these will be
-installed on your computer when you open `Reproducibility_in_Plant_Pathology.Rproj` in RStudio.
-
-<!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis.
+Installing these can be time-consuming and complicated, so we've provided a Docker image that includes all the necessary software, code and data to run our analysis.
 The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.
@@
 
-    docker run -dp 8787:8787 openplantpathology/Reproducibility_in_Plant_Pathology
+    docker run -dp 8787:8787 adamhsparks/reproducibility_in_plant_pathology
 
@@
 
-Once logged in, use the Files pane (bottom right) to navigate to `/` (the root directory), then open the folder for this project, and open the `.Rproj` file for this project.
+Once logged in, use the Files pane (bottom right) to navigate to `Reproduciblity_in_Plant_Pathology` folder for this project, and open the `.Rproj` file for this project.
 Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R markdown document, and knit them to produce the results in the paper.
-More information about using RStudio in Docker is avaiable at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
+More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
 
-We developed and tested the package on this Docker container, so this is the only platform that We're confident it works on, and so recommend to anyone wanting to use this package to generate the vignette, etc.
---->
+We developed and tested the package on this Docker container, so this is the only platform that we're confident it works on, and so recommend to anyone wanting to use this package to generate the vignette, etc.
 

### 2018-04-08 analysis/paper/paper.Rmd
Add analysis structure for paper Rmd file

---
title: "Title Goes Here"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

library(Reproducibility.in.Plant.Pathology) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

# Introduction

Here is a citation [@Marwick2017]

# Background

```{r demo, eval = FALSE}
1 + 1
```

# Methods

# Results

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv("../data/raw_data/my_csv_file.csv")
```

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

##### pagebreak

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
git2r::repository("../..")
```

### 2018-04-08 analysis/paper/paper.Rmd
Add phytopathology.csl file

@@
 bibliography: references.bib
-csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
+csl: "../templates/phytopathology.csl" # Insert path for the bib-style
 abstract: |

### 2018-04-08 analysis/paper/paper.Rmd
Add authors to paper

@@
 author:
-  - Author One
-  - Author Two
+  - Adam H. Sparks
+  - Emerson Del Ponte
+  - Sydney Everhart
+  - Zachary Foster
+  - Niklaus J Grünwald
 date: "`r format(Sys.time(), '%d %B, %Y')`"

### 2018-04-08 README.rmd
Clean up README

@@
 
-For optimal webviewing of this report, please see the [HTML version](http://htmlpreview.github.io/?https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).
+For optimal webviewing of this report, please see the
+[HTML version](http://htmlpreview.github.io/?https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).
 
@@
 
-This repository is our research compendium that details our methodology for examining the state of reproducible research in plant pathology.
-The compendium contains all data, code, and text associated with the publication XXXX published in XXX.
-The `R markdown format` (`Rmd`) files in the `inst/paper/` directory contain details of how all the analyses reported in the paper were conducted.
-Detailed instructions on methods used and how to rerun the analysis to reproduce the results are found in the vignettes, in the `vingettes/` directory.
+This repository is our research compendium that details our methodology for
+examining the state of reproducible research in plant pathology. The compendium
+contains all data, code, and text associated with the publication XXXX published
+in XXX. The `R markdown format` (`Rmd`) files in the `inst/paper/` directory
+contain details of how all the analyses reported in the paper were conducted.
+Detailed instructions on methods used and how to rerun the analysis to reproduce
+the results are found in the vignettes, in the `vingettes/` directory.
 
@@
 Much of the collaborative work was done outside of GitHub and R using Google
-Sheets. You can view the [article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M) that we collected in the "article_evaluations" tab. Where "template" and
+Sheets. You can view the
+[article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M)
+that we collected in the "article_evaluations" tab. Where "template" and
 "article_notes" are used in creating that tab and are explained the "Assigning
@@
 This repository is organized as an R package. There is one R function,
-`doi2bib()`, that is used in this repository, along with the data,
-`assigned_article_notes.rda` that are located in `data` directory. We have used
-the R package structure to help manage dependencies, to take advantage of
-continuous integration for automated code testing and for file organisation.
+`doi2bib()`, that is used in this repository, along with a bibliography file of
+the articles that were examined that are located in `inst/extdata` directory. We
+have used the R package structure to help manage dependencies, to take advantage
+of continuous integration for automated code testing and for file organisation.
 
@@
 
-Once the download is complete, open the `Reproducibility_in_Plant_Pathology.Rproj` in
-RStudio to begin working with the package and compendium files.
+Once the download is complete, open the
+`Reproducibility_in_Plant_Pathology.Rproj` in RStudio to begin working with the
+package and compendium files.
 
 The package has a number of dependencies on other R packages, and programs
-outside of R.
-These are listed at the bottom of this README.
-Installing these can be time-consuming and complicated, so we've provided a Docker image that includes all the necessary software, code and data to run our analysis.
-The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.
+outside of R. These are listed at the bottom of this README. Installing these
+can be time-consuming and complicated, so we've provided a Docker image that
+includes all the necessary software, code and data to run our analysis. The
+Docker image may give a quicker entry point to the project, and is more
+self-contained, so might save some fiddling with installing things.
 
@@
 
-A Docker image is a lightweight GNU/Linux virtual computer that can be run as a piece of software on Windows and OSX (and other Linux systems).
-To capture the complete computational environment used for this project we have a Dockerfile that specifies how to make the Docker image that we developed this project in.
-The Docker image includes all of the software dependencies needed to run the code in this project, as well as the R package and other compendium files.
-To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer.
-At the Docker prompt, enter:
+A Docker image is a lightweight GNU/Linux virtual computer that can be run as a
+piece of software on Windows and OSX (and other Linux systems). To capture the
+complete computational environment used for this project we have a Dockerfile
+that specifies how to make the Docker image that we developed this project in.
+The Docker image includes all of the software dependencies needed to run the
+code in this project, as well as the R package and other compendium files. To
+launch the Docker image for this project, first,
+[install Docker](https://docs.docker.com/installation/) on your computer. At the
+Docker prompt, enter:
 
@@
 
-This will start a server instance of RStudio.
-Then open your web browser at localhost:8787 or or run `docker-machine ip default` in the shell to find the correct IP address, and log in with rstudio/rstudio.
+This will start a server instance of RStudio. Then open your web browser at
+localhost:8787 or or run `docker-machine ip default` in the shell to find the
+correct IP address, and log in with rstudio/rstudio.
 
-Once logged in, use the Files pane (bottom right) to navigate to `Reproduciblity_in_Plant_Pathology` folder for this project, and open the `.Rproj` file for this project.
-Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R markdown document, and knit them to produce the results in the paper.
-More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
+Once logged in, use the Files pane (bottom right) to navigate to
+`Reproduciblity_in_Plant_Pathology` folder for this project, and open the
+`.Rproj` file for this project. Once that's open, you'll see the
+`analysis/paper` directory in the Files pane where you can find the R markdown
+document, and knit them to produce the results in the paper. More information
+about using RStudio in Docker is available at the
+[Rocker](https://github.com/rocker-org)
+[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
 
-We developed and tested the package on this Docker container, so this is the only platform that we're confident it works on, and so recommend to anyone wanting to use this package to generate the vignette, etc.
+We developed and tested the package on this Docker container, so this is the
+only platform that we're confident it works on, and so recommend to anyone
+wanting to use this package to generate the vignettes, etc.
 
@@
 
-We also used [JabRef](http://www.jabref.org/) and [Google Sheets](https://www.google.com/sheets/about/).
+We also used [JabRef](http://www.jabref.org/) and 
+[Google Sheets](https://www.google.com/sheets/about/).
 
@@
 ### Credits
-This research compendium was based on https://github.com/benmarwick/researchcompendium but not
-forked from because it was already under development when I found Ben's.
+This research compendium was based on
+https://github.com/benmarwick/researchcompendium but not forked from because it
+was already under development when I found Ben's.

### 2018-05-22 README.rmd
Update README.rmd/md and release for DOI

@@
 ---
-title: "Reproducibility in Plant Pathology"
 output: github_document
@@
 
+<!-- README.md is generated from README.Rmd. Please edit that file -->
+
+```{r, echo = FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  fig.path = "README-"
+)
+```
+
+# Reproducibility.in.Plant.Pathology
+
 [![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology) 
+[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
 
-## A research compendium for a report on the reproducibility of research in plant pathology
+This repository contains the data and code for our paper:
 
-For optimal webviewing of this report, please see the
-[HTML version](http://htmlpreview.github.io/?https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).
+> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
 
-### Compendium DOI:
+Our pre-print is online here:
 
-http://dx.doi.org/xxxxxxx
+> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
 
-The files at the URL above will generate the results as found in the publication.
-The files hosted at https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.
+### How to cite
 
-### Authors of this repository:
+Please cite this compendium as:
 
-Adam H Sparks (<adamhsparks@gmail.com>)
+> Authors, (`r format(Sys.Date(), "%Y")`).
+_Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_.
+Accessed `r format(Sys.Date(), "%d %b %Y")`.
+Online at <https://doi.org/10.5281/zenodo.1250665>
 
-Emerson M Del Ponte (<delponte@ufv.br>)
+### How to download or install
 
-Sydney Everhart (<everhart@unl.edu>)
-
-Zachary Foster (<zacharyfoster1989@gmail.com>)
-
-Niklaus J Grünwald (<grunwaln@science.oregonstate.edu>)
-
-### Published in:
-
-### Overview of contents
-
-This repository is our research compendium that details our methodology for
-examining the state of reproducible research in plant pathology. The compendium
-contains all data, code, and text associated with the publication XXXX published
-in XXX. The `R markdown format` (`Rmd`) files in the `inst/paper/` directory
-contain details of how all the analyses reported in the paper were conducted.
-Detailed instructions on methods used and how to rerun the analysis to reproduce
-the results are found in the vignettes, in the `vingettes/` directory.
-
-### The supplementary files
-
-The `inst/` directory contains:
-
-- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in
-the `paper/` directory)
-
-- supplementary information source files (in `Rmd` format) and executed versions
-
-- all the figures that are included in the paper (in the `figures/` directory)
-
-### The external files
-
-Much of the collaborative work was done outside of GitHub and R using Google
-Sheets. You can view the
-[article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M)
-that we collected in the "article_evaluations" tab. Where "template" and
-"article_notes" are used in creating that tab and are explained the "Assigning
-Articles" vignette of this R package.
-
-### The R package
+#### The R package
 
@@
 
-To download the package source as you see it on GitHub, for offline browsing,
-use this line at the shell prompt (assuming you have Git installed on your
-computer):
+You can download the compendium as a zip from from this URL: <https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/archive/master.zip>
 
-```
-git clone https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology.git
+Or you can install this compendium as an R package, Reproducibility.in.Plant.Pathology, from GitHub with:
+```{r gh-installation, eval = FALSE}
+# install.packages("devtools")
+devtools::install_github("adamhsparks/Reproducibility_in_Plant_Pathology")
 ```
@@
 
-### The Docker image
+#### The Docker image
 
@@
 
+## Meta
+
+### The external files
+
+Much of the collaborative work was done outside of GitHub and R using Google
+Sheets. You can view the
+[article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M)
+that we collected in the "article_evaluations" tab. Where "template" and
+"article_notes" are used in creating that tab and are explained the "Assigning
+Articles" vignette of this R package.
+
 ### Licenses
 
-Manuscript: [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
+**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
 
-Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(),
-"%Y")`, copyright holder: Adam H Sparks
+**Code :** See the [DESCRIPTION](DESCRIPTION) file
 
-Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
-requested in reuse
+**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
 
-### Dependencies
+### Contributions
 
-We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
-16.04 LTS.
-
-We also used [JabRef](http://www.jabref.org/) and 
-[Google Sheets](https://www.google.com/sheets/about/).
-
-### Contact
-
-Adam H Sparks, Associate Professor, Centre for Crop Health
-University of Southern Queensland
-Toowoomba, Queensland 4350
-
-(+61) (7) 4831 1948   e. adam.sparks@usq.edu.au
-https://staffprofile.usq.edu.au/Profile/Adam-Sparks
-
-### Credits
-This research compendium was based on
-https://github.com/benmarwick/researchcompendium but not forked from because it
-was already under development when I found Ben's.
+We welcome contributions from everyone.
+Before you get started, please see our [contributor guidelines](CONTRIBUTING.md).
+Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
+By participating in this project you agree to abide by its terms.

### 2018-06-01 README.rmd
Fix authors in citation
Update Zach's initials in author listing
Minor reformatting

--- 2018-04-08 README.rmd
@@
 ### Published in:
+
+Sparks et al. XXXX
 
@@
 
-Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(),
-"%Y")`, copyright holder: Adam H Sparks
+Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H Sparks
 
-Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
-requested in reuse
+Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
 
@@
 We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
-16.04 LTS.
+17.10.
 
@@
 
-(+61) (7) 4831 1948   e. adam.sparks@usq.edu.au
+(+61) (7) 4831 1948   adam.sparks@usq.edu.au
 https://staffprofile.usq.edu.au/Profile/Adam-Sparks

### 2018-06-01 README.rmd

--- 2018-05-22 README.rmd
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`).
+> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., (`r format(Sys.Date(), "%Y")`).
 _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_.
@@
 
-### The external files
+Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H Sparks
 
-Much of the collaborative work was done outside of GitHub and R using Google
-Sheets. You can view the
-[article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M)
-that we collected in the "article_evaluations" tab. Where "template" and
-"article_notes" are used in creating that tab and are explained the "Assigning
-Articles" vignette of this R package.
+Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
 
@@
 
-**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
+We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
+17.10.
 
@@
 
-### Contributions
+Adam H Sparks, Associate Professor, Centre for Crop Health  
+University of Southern Queensland  
+Toowoomba, Queensland 4350
 
-We welcome contributions from everyone.
-Before you get started, please see our [contributor guidelines](CONTRIBUTING.md).
-Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
-By participating in this project you agree to abide by its terms.
+(+61) (7) 4831 1948   adam.sparks@usq.edu.au
+https://staffprofile.usq.edu.au/Profile/Adam-Sparks

### 2018-06-01 inst/paper/Sparks_et_al-main_text.Rmd
Add Sydney to paper file author list

@@
 title: "Status and Best Practices for Reproducible Research In Plant Pathology"
-author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
+author: "A. H. Sparks, E. M. Del Ponte, S. Everhart, Z.S.L. Foster and N. J. Grünwald"
 date: 'Last update: `r Sys.Date()`'

### 2018-06-05 README.rmd

@@
 [![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
+[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
 

### 2018-06-09 README.rmd
Update static docs

@@
 
-# Reproducibility.in.Plant.Pathology
+# Reproducibility in Plant Pathology
 
@@
 
-> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
+> Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N., Sparks, A.H. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
 
@@
 
-> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., (`r format(Sys.Date(), "%Y")`).
+> Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., Sparks, A.H.
+(`r format(Sys.Date(), "%Y")`).
 _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_.

### 2019-01-02 README.rmd
Update pkgdown site
Update README file

--- 2018-06-05 README.rmd
@@
 
-> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., (`r format(Sys.Date(), "%Y")`).
+> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N.
+(`r format(Sys.Date(), "%Y")`).
 _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_.
@@
 ```{r gh-installation, eval = FALSE}
-# install.packages("devtools")
-devtools::install_github("adamhsparks/Reproducibility_in_Plant_Pathology")
+if (!require("remotes")) install.packages("remotes")
+remotes::install_github("openplantpathology/Reproducibility_in_Plant_Pathology")
 ```

### 2019-01-10 analysis/paper/paper.Rmd
Update paper.Rmd with existing text

@@
 
-# Introduction
+# Abstract
 
-Here is a citation [@Marwick2017]
+Reproducible research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and replication of scientific results.
+In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted.
+Sharing of data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow.
+We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting reproducibility.
+We found that..
+Protocols specific to plant pathology and open source tools for producing reproducible work and analysis is proposed to promote reproducible practices among plant pathologists.
 
-# Background
+# Main text
 
-```{r demo, eval = FALSE}
-1 + 1
+## Introductory
+
+Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
+Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve management.
+Scientific research in the field vary from purely observational/descriptive nature to inferential based on experimental or simulation-derived data sets.
+Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available, beyond what is reported in the scientific article.
+These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawing and photographs, statistical analysis codes, among other data.
+
+##3 Reproducible research
+
+Reproducibility in scientific research has once again been highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an important issue.
+Patil et al.
+[-@Patil066803] have provided several definitions to clarify the concepts surrounding reproducibility.
+For the purposes of this paper we follow the definitions as given by Patil et al.
+[-@Patil066803].
+
+## A general workflow
+
+A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
+Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Fig.
+1).
+
+A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used.
+A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a pay-wall.
+A highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run more easily following download of data and codes.
+The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
+In the next section we present standards and tools that can be used to ensure reproducibility (Figure 1).
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(rsvg)
+
+p <- export_svg(grViz(
+  "
+  digraph Fig1 {
+
+  graph [fontsize = 8, nodesep=0.5]
+
+  node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
+  Question;  Methodology;  Data;  Analysis;  Manuscript;
+
+  node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
+  Description; Availability; Citation
+
+  node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
+  Binary_Code; Binary_File; Supplement
+
+  node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
+  Source_Code;  Data_File; Pub_Repository;
+
+  Question->Methodology->Data->Analysis
+  Analysis->Manuscript
+  Methodology->Description
+  Methodology->Citation
+  Methodology->Availability
+  Manuscript->Supplement
+  Data->Data_File->Pub_Repository
+  Analysis->Binary_Code->Supplement
+  Analysis->Source_Code->Pub_Repository
+  Data->Binary_File->Supplement
+  }
+  ",
+  width = 1000,
+  height = 750
+))
+
+rsvg_pdf(charToRaw(p), "Figure 1.pdf")
 ```
 
-# Methods
+### Methods
 
-# Results
+- Citation of methods, software, packages, etc.
+- deposit and annotate biological materials
+- provide full description for equipments, etc.
+- rOpenSci Reproducible Research: http://ropensci.github.io/reproducibility-guide/sections/introduction/
 
-```{r get-data, eval = FALSE}
-# Note the path that we need to use to access our data files when rendering this document
-my_data <- readr::read_csv("../data/raw_data/my_csv_file.csv")
-```
+### Data
 
-# Discussion
+- Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
+- Data annotation
+- Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
 
-# Conclusion
+### Source code
+
+- The problem of commercial software and mouse-based routines
+- Why to avoid binary files as supplements?
+- Writing and documenting using open source software
+- Availability in public repositories
+
+### Repository
+- Using GitHub for code (and small data?)
+- Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
+- Or using, most ideally, a library or other proper long-term data archival service
+
+## Status in Plant Pathology
+
+* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
+for readers.
+* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
+replicate the entire study modelling the effects of climate change on rice
+bacterial blight and rice leaf blast in Tanzania.
+* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
+necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
+* Del Ponte provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied.
+* Example from Grünwald lab: 
+  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
+  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
+* Other examples from plant pathology providing e-Xtras or supplemental material
+
+Twenty-one plant pathology discipline journals were selected by the authors as representations of discipline-based journals target by the plant pathology research community.
+Among them, both fundamental and/or applied as well as journals covering specific group of pathogens/plants or broad areas were included.
+Two hundred articles were randomly selected from issues published from 2012 to 2016.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
+The pages list was numbered from page one and went to 150.
+This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
+The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2017].
+
+## Discussion
 

### 2019-01-10 analysis/paper/paper.Rmd
Update paper, references and template

@@
 ---
-title: "Title Goes Here"
+title: "Open Science, Open Plant Pathology"
 author:
@@
 output: 
-    bookdown::html_document2:
+    bookdown::word_document2:
       fig_caption: yes
@@
 abstract: |
-  Text of abstract
+  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results.
+In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted.
+Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow.
+We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
+We found that most of the articles failed to share data or code in a meaningful way.
+We propose that and open source tools for producing open and reproducible work and analysis is necessary and provide ideas and tools to promote reproducible practices among plant pathologists.
 keywords: |
-  keyword 1; keyword 2; keyword 3
+  open science; open data; reproducible research; FAIR data
 highlights: |
-  These are the highlights. 
+  Open research practices are highlighted extensively in the broader scientific community.
+Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists.
 ---
-
-<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->
 
@@
 
-library(Reproducibility.in.Plant.Pathology) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
+library(Reproducibility.in.Plant.Pathology)
 ```
 
-# Abstract
-
-Reproducible research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and replication of scientific results.
-In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted.
-Sharing of data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow.
-We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting reproducibility.
-We found that..
-Protocols specific to plant pathology and open source tools for producing reproducible work and analysis is proposed to promote reproducible practices among plant pathologists.
-
-# Main text
-
-## Introductory
+# Introduction
 
@@
 
-##3 Reproducible research
+## Reproducible research
 
-Reproducibility in scientific research has once again been highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an important issue.
+Reproducibility in scientific research has once again been highlighted recently [@Nature2016; @Baker2016a] as an important issue.
 Patil et al.
-[-@Patil066803] have provided several definitions to clarify the concepts surrounding reproducibility.
+[-@Patil2016] have provided several definitions to clarify the concepts surrounding reproducibility.
 For the purposes of this paper we follow the definitions as given by Patil et al.
-[-@Patil066803].
+[-@Patil2016].
 
@@
 A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Fig.
-1).
+Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure 1).
 
@@
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2017].
+The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2018].
 

### 2019-01-10 analysis/paper/paper.Rmd
Update figure 1, removes "_" from nodes

@@
 output: 
-    bookdown::word_document2:
+    bookdown::html_document2:
       fig_caption: yes
@@
 We found that most of the articles failed to share data or code in a meaningful way.
-We propose that and open source tools for producing open and reproducible work and analysis is necessary and provide ideas and tools to promote reproducible practices among plant pathologists.
+We propose that using open source tools for producing open and reproducible work and analysis is necessary and provide ideas and tools to promote reproducible practices among plant pathologists.
 keywords: |
@@
   Open research practices are highlighted extensively in the broader scientific community.
-Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists.
+Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproduciblity.
 ---
@@
 
-## A general workflow
+## Open science
+
+Open science has become highlighted lately with many donors expecting data to be available (XXXX) and other scientists interested in sharing and collaborating more widely.
+
+# A general workflow
 
@@
   node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
-  Binary_Code; Binary_File; Supplement
+  'Binary Code'; 'Binary File'; Supplement
 
   node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-  Source_Code;  Data_File; Pub_Repository;
+  'Source Code';  'Data File'; 'Public Repository';
 
@@
   Manuscript->Supplement
-  Data->Data_File->Pub_Repository
-  Analysis->Binary_Code->Supplement
-  Analysis->Source_Code->Pub_Repository
-  Data->Binary_File->Supplement
+  Data->'Data File'->'Public Repository'
+  Analysis->'Binary Code'->Supplement
+  Analysis->'Source Code'->'Public Repository'
+  Data->'Binary File'->Supplement
   }
@@
 
-## Status in Plant Pathology
+# Status in Plant Pathology
 
@@
 
-## Discussion
+# Discussion
 

### 2019-01-10 analysis/paper/paper.Rmd
Updates the paper text adding some ideas and fleshing out others

@@
 
-Open science has become highlighted lately with many donors expecting data to be available (XXXX) and other scientists interested in sharing and collaborating more widely.
+Open science has become highlighted lately with many donors expecting data to be available (XXXX) and other scientists interested in sharing and collaborating more widely (XXXX).
 
@@
 A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a pay-wall.
-A highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run more easily following download of data and codes.
+The highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
 The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
@@
 
-- Citation of methods, software, packages, etc.
+When making your science more open and reproducible, methods, software used (including things like R packages), etc.
+should be cited.
+This allows end users to identify what was used and identify the methods used more accurately.
+Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
+This also helps ensure that you as a researcher are able to reconstruct what you have done since you will have good notes and documentation.
+
 - deposit and annotate biological materials
+
 - provide full description for equipments, etc.
@@
 ### Repository
-- Using GitHub for code (and small data?)
-- Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
-- Or using, most ideally, a library or other proper long-term data archival service
+- Using GitHub, Gitlab, Bitbucket for code (and small data?)
+- Using Figshare, Dataverse or some other data repository for large data
+- Zenodo or OSF to generate DOIs
+- Why not use a lab website (DOIs, other reasons)
+- Most ideally, deposit in university library or other proper long-term data archival service
 

### 2019-01-23 analysis/paper/paper.Rmd
Edits to paper text

@@
 In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted.
-Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow.
+Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
 We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
-We found that most of the articles failed to share data or code in a meaningful way.
-We propose that using open source tools for producing open and reproducible work and analysis is necessary and provide ideas and tools to promote reproducible practices among plant pathologists.
+We found that most of the articles were not very open, failing to share data or code in a meaningful way.
+We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
 keywords: |
@@
   Open research practices are highlighted extensively in the broader scientific community.
-Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproduciblity.
+Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
 ---
@@
 Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve management.
-Scientific research in the field vary from purely observational/descriptive nature to inferential based on experimental or simulation-derived data sets.
-Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available, beyond what is reported in the scientific article.
-These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawing and photographs, statistical analysis codes, among other data.
+Scientific research in the field varies from the purely observational or descriptive nature to inferential based on experimental or simulation-derived data sets.
+Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article.
+These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other data.
 
-## Reproducible research
+## Reproducible Research
 
@@
 
-## Open science
+## Open Science
 
@@
 
-# A general workflow
+# A General Workflow
 
@@
 
-A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used.
-A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a pay-wall.
-The highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
-The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-In the next section we present standards and tools that can be used to ensure reproducibility (Figure 1).
+A first level of reproducibility involves openly available research materials such as strains and/or nucleic acid sequences in public collections and citations for methods used.
+A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
+The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
+The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
+In the next section we present standards and tools that can be used to ensure reproducibility \@ref(fig:workflow-dia).
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, results='hide', caption="An open and reproducible research workflow."}
 library(DiagrammeR)
@@
 When making your science more open and reproducible, methods, software used (including things like R packages), etc.
-should be cited.
+should be cited properly.
 This allows end users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher are able to reconstruct what you have done since you will have good notes and documentation.
+This also helps ensure that you as a researcher are able to reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, _e.g._ a package version, what effect it had on your research.
 
@@
 - provide full description for equipments, etc.
+
 - rOpenSci Reproducible Research: http://ropensci.github.io/reproducibility-guide/sections/introduction/
@@
 
-### Source code
+### Source Code
 

### 2019-02-15 analysis/paper/paper.Rmd
Insert figure 1 in Word doc AND generate PDF

@@
 A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure 1).
+Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices \@ref(fig:workflow-dia).
 
@@
 The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-In the next section we present standards and tools that can be used to ensure reproducibility \@ref(fig:workflow-dia).
-
-```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, results='hide', caption="An open and reproducible research workflow."}
-library(DiagrammeR)
-library(DiagrammeRsvg)
-library(rsvg)
-
-p <- export_svg(grViz(
-  "
-  digraph Fig1 {
-
-  graph [fontsize = 8, nodesep=0.5]
-
-  node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
-  Question;  Methodology;  Data;  Analysis;  Manuscript;
-
-  node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
-  Description; Availability; Citation
-
-  node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
-  'Binary Code'; 'Binary File'; Supplement
-
-  node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-  'Source Code';  'Data File'; 'Public Repository';
-
-  Question->Methodology->Data->Analysis
-  Analysis->Manuscript
-  Methodology->Description
-  Methodology->Citation
-  Methodology->Availability
-  Manuscript->Supplement
-  Data->'Data File'->'Public Repository'
-  Analysis->'Binary Code'->Supplement
-  Analysis->'Source Code'->'Public Repository'
-  Data->'Binary File'->Supplement
-  }
-  ",
-  width = 1000,
-  height = 750
-))
-
-rsvg_pdf(charToRaw(p), "Figure 1.pdf")
-```
+In the next section we present standards and tools that can be used to ensure reproducibility.
 
@@
 
-### Colophon
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+# Figures
+
+```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An open and reproducible research workflow.', cache=FALSE, fig.env='figure'}
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(rsvg)
+
+p <- export_svg(
+  grViz(
+    "digraph Fig1 {
+    graph [fontsize = 8, nodesep=0.5]
+
+    node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
+    Question; Methodology; Data; Analysis; Manuscript;
+
+    node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
+    Description; Availability; Citation
+
+    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
+    'Binary Code'; 'Binary File'; Supplement
+
+    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
+    'Source Code'; 'Data File'; 'Public Repository';
+
+    Question->Methodology->Data->Analysis
+    Analysis->Manuscript
+    Methodology->Description
+    Methodology->Citation
+    Methodology->Availability
+    Manuscript->Supplement
+    Data->'Data File'->'Public Repository'
+    Analysis->'Binary Code'->Supplement
+    Analysis->'Source Code'->'Public Repository'
+    Data->'Binary File'->Supplement
+  }",
+  width = 1000,
+  height = 750
+))
+rsvg_pdf(charToRaw(p), "Figure 1.pdf")
+
+knitr::include_graphics("Figure 1.pdf")
+```
+
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+# Colophon
 
@@
 # which R packages and versions?
-devtools::session_info()
+sessionInfo()
 ```

### 2019-02-15 analysis/paper/paper.Rmd
Update text in manuscript and include figure in Word document output

@@
 Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
-Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve management.
+Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve plant disease management.
 Scientific research in the field varies from the purely observational or descriptive nature to inferential based on experimental or simulation-derived data sets.
 Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article.
-These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other data.
+These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data.
+That is, open science leads to reproducibility and replicability.
 
-## Reproducible Research
+## Definitions
 
-Reproducibility in scientific research has once again been highlighted recently [@Nature2016; @Baker2016a] as an important issue.
-Patil et al.
-[-@Patil2016] have provided several definitions to clarify the concepts surrounding reproducibility.
-For the purposes of this paper we follow the definitions as given by Patil et al.
-[-@Patil2016].
+In order for us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
+Many of the terms used in this area have varying definitions that may or may not agree with each other.
+For instance, reproducible research is recently hightlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
+This has resulted in attepmts to define "reproducibility", _e.g._ [@Patil2016], therefore the following definitions will be used for these terms throughout this paper.
 
-## Open Science
+### Repeatability
+
+The International Union of Pure and Applied Chemistry defines repeatability in the "Compendium of Chemical Terminology Gold Book" [@mcnaughtcompendium],
+
+> "The closeness of agreement between independent results obtained with the same method on identical test material, under the same conditions (same operator, same apparatus, same laboratory and after short intervals of time).
+The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation.
+In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability."
+
+### Reproducibility
+
+The International Union of Pure and Applied Chemistry defines reproducibility in the "Compendium of Chemical Terminology Gold Book" [@mcnaughtcompendium],
+
+>"The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time).
+The measure of reproducibility is the standard deviation qualified with the term 'reproducibility' as reproducibility standard deviation.
+In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability.
+Note that a complete statement of reproducibility requires specification of the experimental conditions which differ."
+
+### Replicability
+
+XXXX
+
+### Open Science
 

### 2019-02-15 analysis/paper/paper.Rmd
Update citation for Gold Book

@@
 For instance, reproducible research is recently hightlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
-This has resulted in attepmts to define "reproducibility", _e.g._ [@Patil2016], therefore the following definitions will be used for these terms throughout this paper.
+This has resulted in attepmts to define "reproducibility", _e.g._ Patil
+_et al._ [-@Patil2016], therefore the following definitions will be used for these terms throughout this paper.
 
@@
 
-The International Union of Pure and Applied Chemistry defines repeatability in the "Compendium of Chemical Terminology Gold Book" [@mcnaughtcompendium],
+The International Union of Pure and Applied Chemistry defines repeatability in the "Compendium of Chemical Terminology -- Gold Book" as,
 
@@
 The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation.
-In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability."
+In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@mcnaught1997compendium].
 
@@
 
-The International Union of Pure and Applied Chemistry defines reproducibility in the "Compendium of Chemical Terminology Gold Book" [@mcnaughtcompendium],
+The International Union of Pure and Applied Chemistry defines reproducibility in the "Compendium of Chemical Terminology -- Gold Book" as,
 
@@
 In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability.
-Note that a complete statement of reproducibility requires specification of the experimental conditions which differ."
+Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@mcnaught1997compendium].
 

### 2019-02-15 analysis/paper/paper.Rmd
Add Peng's definition of reproducibility, which we'll use for this manuscript

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research is recently hightlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
-This has resulted in attepmts to define "reproducibility", _e.g._ Patil
-_et al._ [-@Patil2016], therefore the following definitions will be used for these terms throughout this paper.
-
-### Repeatability
-
-The International Union of Pure and Applied Chemistry defines repeatability in the "Compendium of Chemical Terminology -- Gold Book" as,
+For instance, reproducible research is recently highlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
+The International Union of Pure and Applied Chemistry provides
+definitions of repeatability in the "Compendium of Chemical Terminology -- Gold Book" as:
 
@@
 
-### Reproducibility
+and reproducibility is defined as:
 
-The International Union of Pure and Applied Chemistry defines reproducibility in the "Compendium of Chemical Terminology -- Gold Book" as,
-
->"The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time).
+> "The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time).
 The measure of reproducibility is the standard deviation qualified with the term 'reproducibility' as reproducibility standard deviation.
@@
 
-### Replicability
+However, while these definitions are clear and well accepted in physical sciences, in biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
+Therefore we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of ``reproducible research'':
 
-XXXX
+> "The replication of scientific findings using independent investigators, methods, data, equipment, and protocols has long been, and will continue to be, the standard by which scientific claims are evaluated.
+However, in many fields of study there are examples of scientific investigations that cannot be fully replicated because of a lack of time or resources.
+In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing.
+One candidate for this minimum standard is ``reproducible research'', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
+Peng, R.
+[-@Peng2009].
+Reproducible research and Biostatistics Biostatistics, 10 (3): 405-408.
 

### 2019-05-20 README.rmd
Update README

@@
 ```{r gh-installation, eval = FALSE}
-if (!require("remotes")) install.packages("remotes")
-remotes::install_github("openplantpathology/Reproducibility_in_Plant_Pathology")
+if (!require("remotes"))
+  install.packages("remotes")
+remotes::install_github("openplantpathology/Reproducibility_in_Plant_Pathology"
+)
 ```
@@
 package and compendium files.
-
-The package has a number of dependencies on other R packages, and programs
-outside of R. These are listed at the bottom of this README. Installing these
-can be time-consuming and complicated, so we've provided a Docker image that
-includes all the necessary software, code and data to run our analysis. The
-Docker image may give a quicker entry point to the project, and is more
-self-contained, so might save some fiddling with installing things.
-
-#### The Docker image
-
-A Docker image is a lightweight GNU/Linux virtual computer that can be run as a
-piece of software on Windows and OSX (and other Linux systems). To capture the
-complete computational environment used for this project we have a Dockerfile
-that specifies how to make the Docker image that we developed this project in.
-The Docker image includes all of the software dependencies needed to run the
-code in this project, as well as the R package and other compendium files. To
-launch the Docker image for this project, first,
-[install Docker](https://docs.docker.com/installation/) on your computer. At the
-Docker prompt, enter:
-
-    docker run -dp 8787:8787 adamhsparks/reproducibility_in_plant_pathology
-
-This will start a server instance of RStudio. Then open your web browser at
-localhost:8787 or or run `docker-machine ip default` in the shell to find the
-correct IP address, and log in with rstudio/rstudio.
-
-Once logged in, use the Files pane (bottom right) to navigate to
-`Reproduciblity_in_Plant_Pathology` folder for this project, and open the
-`.Rproj` file for this project. Once that's open, you'll see the
-`analysis/paper` directory in the Files pane where you can find the R markdown
-document, and knit them to produce the results in the paper. More information
-about using RStudio in Docker is available at the
-[Rocker](https://github.com/rocker-org)
-[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
-
-We developed and tested the package on this Docker container, so this is the
-only platform that we're confident it works on, and so recommend to anyone
-wanting to use this package to generate the vignettes, etc.
 
@@
 
-We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
-17.10.
-
 **Code :** See the [DESCRIPTION](DESCRIPTION) file
@@
 
-(+61) (7) 4831 1948   adam.sparks@usq.edu.au
-https://staffprofile.usq.edu.au/Profile/Adam-Sparks
++61 (7) 4831 1948   <adam.sparks@usq.edu.au>
+
+<https://adamhsparks.netlify.com/>

### 2019-05-21 tests/testthat/test_doi2bib.R
Update test_doi2bib.R

@@ -1,7 +1,6 @@
 context("doi2bib")
 
 test_that("doi2bib fetches a bib object", {
-  skip_on_cran()
   expect_equal(doi2bib("10.4454/jpp.fa.2012.002"),
-               " @article{F. Suárez-Estrella_M.A. Bustamante_R. Moral_M.C. Vargas-García_M.J. López_J. Moreno_2012, title={IN VITRO CONTROL OF FUSARIUM WILT USING AGROINDUSTRIAL SUBPRODUCT-BASED COMPOSTS}, volume={94}, ISSN={1125-4653}, url={http://doi.org/10.4454/jpp.fa.2012.002}, DOI={10.4454/jpp.fa.2012.002}, number={1}, journal={Journal of Plant Pathology}, author={F. Suárez-Estrella and M.A. Bustamante and R. Moral and M.C. Vargas-García and M.J. López and J. Moreno}, year={2012}}\n")
+              " @article{F. Suárez-Estrella_M.A. Bustamante_R. Moral_M.C. Vargas-García_M.J. López_J. Moreno_2012, title={IN VITRO CONTROL OF FUSARIUM WILT USING AGROINDUSTRIAL SUBPRODUCT-BASED COMPOSTS}, volume={94}, ISSN={1125-4653}, url={http://doi.org/10.4454/jpp.fa.2012.002}, DOI={10.4454/jpp.fa.2012.002}, number={1}, journal={Journal of Plant Pathology}, author={F. Suárez-Estrella and M.A. Bustamante and R. Moral and M.C. Vargas-García and M.J. López and J. Moreno}, year={2012} }\n")
 })

### 2019-05-21 R/workflow_dia.R
Delete workflow_dia.R

@@ -1,45 +1,0 @@
-
-#' Create Workflow Diagram Figure
-#'
-#' @return PDF of workflow diagram
-#' @export workflow_dia
-#'
-#' @examples
-#'
-#' workflow_dia()
-#'
-
-workflow_dia <- function() {
-  p <- DiagrameRsvg::export_svg(
-    DiagrammeR::grViz(
-      "digraph Fig1 {
-    graph [fontsize = 8, nodesep=0.5]
-
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
-    Question; Methodology; Data; Analysis; Manuscript;
-
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
-    Description; Availability; Citation
-
-    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
-    'Binary Code'; 'Binary File'; Supplement
-
-    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-    'Source Code'; 'Data File'; 'Public Repository';
-
-    Question->Methodology->Data->Analysis
-    Analysis->Manuscript
-    Methodology->Description
-    Methodology->Citation
-    Methodology->Availability
-    Manuscript->Supplement
-    Data->'Data File'->'Public Repository'
-    Analysis->'Binary Code'->Supplement
-    Analysis->'Source Code'->'Public Repository'
-    Data->'Binary File'->Supplement
-  }",
-      width = 1000,
-      height = 750
-    ))
-  return(rsvg::rsvg_pdf(charToRaw(p)))
-}

### 2019-05-21 R/workflow_dia.R
Revert "Delete workflow_dia.R"
This reverts commit aa0ea42595a2cbe646596f6dd8caef5ef9424e87.

@@ -1,0 +1,45 @@
+
+#' Create Workflow Diagram Figure
+#'
+#' @return PDF of workflow diagram
+#' @export workflow_dia
+#'
+#' @examples
+#'
+#' workflow_dia()
+#'
+
+workflow_dia <- function() {
+  p <- DiagrameRsvg::export_svg(
+    DiagrammeR::grViz(
+      "digraph Fig1 {
+    graph [fontsize = 8, nodesep=0.5]
+
+    node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
+    Question; Methodology; Data; Analysis; Manuscript;
+
+    node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
+    Description; Availability; Citation
+
+    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
+    'Binary Code'; 'Binary File'; Supplement
+
+    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
+    'Source Code'; 'Data File'; 'Public Repository';
+
+    Question->Methodology->Data->Analysis
+    Analysis->Manuscript
+    Methodology->Description
+    Methodology->Citation
+    Methodology->Availability
+    Manuscript->Supplement
+    Data->'Data File'->'Public Repository'
+    Analysis->'Binary Code'->Supplement
+    Analysis->'Source Code'->'Public Repository'
+    Data->'Binary File'->Supplement
+  }",
+      width = 1000,
+      height = 750
+    ))
+  return(rsvg::rsvg_pdf(charToRaw(p)))
+}

### 2019-05-21 R/table_of_journals.R
Update table_of_journals.R

@@ -1,17 +1,18 @@
 
 #' Create Table of Journals Surveyed
-#'
-#' @return pander table of journals surveyed
+#' @param rrpp `data.frame` of article evaluations
+#' @return \pkg{pander} table of journals surveyed
 #' @export table_of_journals
 #'
 #' @examples
+#' \donttest{
+#' rrpp <- gsheet::gsheet2tbl(
+#'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
+#')
+#' table_of_journals(rrpp)
+#' }
 #'
-#' table_of_journals()
-#'
-table_of_journals <- function() {
-  rrpp <- gsheet::gsheet2tbl(
-  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
-)
+table_of_journals <- function(rrpp) {
 
 rrpp_journals <- as.data.frame(table(rrpp[, 1]))
 names(rrpp_journals) <- c("Journal", "Count")

### 2019-06-04 R/table_of_journals.R
Revert "Delete table_of_journals()"
This reverts commit e40efbaa4c044453ee42e4c0b0ec1369ad6123b4.

@@ -1,0 +1,20 @@
+
+#' Create Table of Journals Surveyed
+#' @param rrpp `data.frame` of article evaluations
+#' @return \pkg{pander} table of journals surveyed
+#' @export table_of_journals
+#'
+#' @examples
+#' \donttest{
+#' rrpp <- gsheet::gsheet2tbl(
+#'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
+#')
+#' table_of_journals(rrpp)
+#' }
+#'
+table_of_journals <- function(rrpp) {
+
+rrpp_journals <- as.data.frame(table(rrpp[, 1]))
+names(rrpp_journals) <- c("Journal", "Count")
+return(pander::pander(rrpp_journals))
+}

### 2019-06-04 R/table_of_journals.R
Delete table_of_journals()
Just write it in the vignette and be done with it

@@ -1,20 +1,0 @@
-
-#' Create Table of Journals Surveyed
-#' @param rrpp `data.frame` of article evaluations
-#' @return \pkg{pander} table of journals surveyed
-#' @export table_of_journals
-#'
-#' @examples
-#' \donttest{
-#' rrpp <- gsheet::gsheet2tbl(
-#'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
-#')
-#' table_of_journals(rrpp)
-#' }
-#'
-table_of_journals <- function(rrpp) {
-
-rrpp_journals <- as.data.frame(table(rrpp[, 1]))
-names(rrpp_journals) <- c("Journal", "Count")
-return(pander::pander(rrpp_journals))
-}

### 2020-03-11 R/doi2bib.R
Fix Roxygen code

@@ -12,9 +12,9 @@
 #' @note
 #' Original script from William Keith Morris,
 #' <https://gist.github.com/wkmor1/ae2cc96acad472d49c35>.  Documented for use
-#' in an R package by Adam H Sparks
+#' in an R package by Adam H. Sparks
 #'
-#' @author William Keith Morris <wkmor1@gmail.com> and Adam H Sparks
+#' @author William Keith Morris <wkmor1@@gmail.com> adapted by Adam H. Sparks
 #'
 #' @name doi2bib
 #' @rdname doi2bib-methods

### 2020-03-11 tests/testthat/test_doi2bib.R
Update test

@@ -1,6 +1,6 @@
 context("doi2bib")
 
 test_that("doi2bib fetches a bib object", {
-  expect_equal(doi2bib("10.4454/jpp.fa.2012.002"),
+  expect_equal(doi2bib("10.1111/efp.12134"),
               " @article{F. Suárez-Estrella_M.A. Bustamante_R. Moral_M.C. Vargas-García_M.J. López_J. Moreno_2012, title={IN VITRO CONTROL OF FUSARIUM WILT USING AGROINDUSTRIAL SUBPRODUCT-BASED COMPOSTS}, volume={94}, ISSN={1125-4653}, url={http://doi.org/10.4454/jpp.fa.2012.002}, DOI={10.4454/jpp.fa.2012.002}, number={1}, journal={Journal of Plant Pathology}, author={F. Suárez-Estrella and M.A. Bustamante and R. Moral and M.C. Vargas-García and M.J. López and J. Moreno}, year={2012} }\n")
 })

### 2020-04-08 analysis/paper/paper.Rmd
Use italics in Peng quote
Add Kaique

@@
   - Zachary Foster
+  - Kaique dos Santos Alves
   - Niklaus J Grünwald
@@
 [-@Peng2009].
-Reproducible research and Biostatistics Biostatistics, 10 (3): 405-408.
+Reproducible research and _Biostatistics_.
+Biostatistics, 10 (3): 405-408.
 

### 2020-04-08 analysis/paper/paper.Rmd
Update paper template and add lua affiliations

@@
 author:
-  - Adam H. Sparks
-  - Emerson Del Ponte
-  - Sydney Everhart
+  - Adam H. Sparks:
+      email: Adam.Sparks@usq.edu.au
+      institute: USQ
+      correspondence: true
+      equal_contributor: true
+  - Emerson Del Ponte:
+      institute: UFV
+      equal_contributor: true
   - Zachary Foster
-  - Kaique dos Santos Alves
+  - Kaique dos Santos Alves:
+      institute: UFV
   - Niklaus J Grünwald
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland 4350, Australia
+  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
       reference_docx: "../templates/template.docx" # Insert path for the DOCX file
+      pandoc_args:
+        - '--lua-filter=scholarly-metadata.lua'
+        - '--lua-filter=author-info-blocks.lua'
 bibliography: references.bib
@@
 Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
+We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
 We found that most of the articles were not very open, failing to share data or code in a meaningful way.
@@
   Open research practices are highlighted extensively in the broader scientific community.
-Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
+Our survey of 300 randomly selected articles from 2012 to 2018 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
 ---

### 2020-04-08 README.rmd
Update web url of personal site
Clean up README

@@
 
-[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology)
 [![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
@@
 
-> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
+> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
 
@@
 
-> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N.
+> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N.
 (`r format(Sys.Date(), "%Y")`).
@@
 
-<https://adamhsparks.netlify.com/>
+<https://adamhsparks.com/>

### 2020-04-09 analysis/paper/paper.Rmd
Each sentence on own line for easier git tracking

@@
 
-When making your science more open and reproducible, methods, software used (including things like R packages), etc.
-should be cited properly.
+When making your science more open and reproducible, methods, software used (including things like R packages), etc. should be cited properly.
 This allows end users to identify what was used and identify the methods used more accurately.
@@
 * Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
-replicate the entire study modelling the effects of climate change on rice
-bacterial blight and rice leaf blast in Tanzania.
+replicate the entire study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
 * Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
@@
 Among them, both fundamental and/or applied as well as journals covering specific group of pathogens/plants or broad areas were included.
-Two hundred articles were randomly selected from issues published from 2012 to 2016.
+Two hundred articles were randomly selected from issues published from 2012 to 2018.
 A list of randomly selected pages was assigned to a randomized list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
@@
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2018].
+The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2020].
 

### 2020-04-20 analysis/paper/paper.Rmd
Add more references

@@
 [-@Peng2009].
-Reproducible research and _Biostatistics_.
+_Reproducible research and Biostatistics_.
 Biostatistics, 10 (3): 405-408.
@@
 
-Open science has become highlighted lately with many donors expecting data to be available (XXXX) and other scientists interested in sharing and collaborating more widely (XXXX).
+Open science has become highlighted lately with many donors expecting data to be available [@vannoorden2017; @ARC2018] and other scientists interested in sharing and collaborating more widely [@Wald2010].
 

### 2020-04-20 R/workflow_dia.R
Update R docs and correct bug in package spelling

@@ -10,7 +10,7 @@
 #'
 
 workflow_dia <- function() {
-  p <- DiagrameRsvg::export_svg(
+  p <- DiagrammeRsvg::export_svg(
     DiagrammeR::grViz(
       "digraph Fig1 {
     graph [fontsize = 8, nodesep=0.5]

### 2020-04-20 analysis/paper/paper.Rmd
add new reference and reorder authors alphabetically

@@
       equal_contributor: true
-  - Zachary Foster
   - Kaique dos Santos Alves:
       institute: UFV
-  - Niklaus J Grünwald
+  - Zachary Foster:
+  - Niklaus J Grünwald:
 institute:
@@
 
-Open science has become highlighted lately with many donors expecting data to be available [@vannoorden2017; @ARC2018] and other scientists interested in sharing and collaborating more widely [@Wald2010].
+Open science has become highlighted lately with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018] and other scientists interested in sharing and collaborating more widely [@Wald2010].
 

### 2020-04-20 README.rmd
Update README

@@
 
-This repository is organized as an R package. There is one R function,
-`doi2bib()`, that is used in this repository, along with a bibliography file of
-the articles that were examined that are located in `inst/extdata` directory. We
-have used the R package structure to help manage dependencies, to take advantage
-of continuous integration for automated code testing and for file organisation.
+This repository is organized as an R package.
+There are custom R functions, `doi2bib()`, `table_of_journals()` and `workflow_dia()` that are used in this repository, along with a bibliography file of the articles that were examined and the notes that are located in `inst/extdata` directory.
+We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.
 
@@
 
-Once the download is complete, open the
-`Reproducibility_in_Plant_Pathology.Rproj` in RStudio to begin working with the
-package and compendium files.
+Once the download is complete, open the `Reproducibility_in_Plant_Pathology.Rproj` in RStudio to begin working with the package and compendium files.
 

### 2020-04-20 analysis/paper/paper.Rmd
Flesh out more ideas in paper

@@
 Scientific research in the field varies from the purely observational or descriptive nature to inferential based on experimental or simulation-derived data sets.
-Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article.
-These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data.
+Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of your methods and results.
+These research findings include biological materials (isolates or strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated as a course of conducting research.
 That is, open science leads to reproducibility and replicability.
@@
 
-A first level of reproducibility involves openly available research materials such as strains and/or nucleic acid sequences in public collections and citations for methods used.
+A first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
 A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
@@
 
-When making your science more open and reproducible, methods, software used (including things like R packages), etc. should be cited properly.
+When making your science more open and reproducible, methods, software used, this includes items such as R or Python packages that were directly used in the analysis or production of the paper, etc.
+should be cited properly.
+Deposit and annotate biological materials with an herbarium or other repository.
+Provide a full description of all equipment used, _e.g._ a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one hour intervals.
 This allows end users to identify what was used and identify the methods used more accurately.
@@
 
-- deposit and annotate biological materials
-
-- provide full description for equipments, etc.
-
-- rOpenSci Reproducible Research: http://ropensci.github.io/reproducibility-guide/sections/introduction/
+The use of programming or scripting languages such as R, SAS or Python enable you as a scientist to keep very detailed records of what was computationally performed.
+This is as opposed to using software such as Microsoft's spreadsheet program Excel, which can be used for simple statistical analyses (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
 

### 2020-04-20 analysis/paper/paper.Rmd
Start expanding "Data" section

@@
 The use of programming or scripting languages such as R, SAS or Python enable you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as Microsoft's spreadsheet program Excel, which can be used for simple statistical analyses (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
+This is as opposed to using software such as spreadsheet programs like Excel, gsheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
 
@@
 
-- Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
-- Data annotation
-- Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
+In many cases, data sets are small enough and curated in spreadsheets, which if saved as a plain text file, _e.g._ comma separated (CSV) files, allows for additions or updates to the data can be tracked through a version control system such as Git, Mercurial among others.
+Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only, using file permissions to prevent changes to the raw data files or possibly where appropriate using a data base to store the data that have been collected.
+Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
+Unexpected changes to values in the data [@Ziemann2016] may also occur when using proprietary formats.
+
+If steps are followed to make the data FAIR (Findable, Accessible, Interoptable and Reusable) then it will be readable by humans and machines alike this will help support new discoveries and support further research.
+In turn sharing data will lead to new citations for your work as other discover and use it.
+
+To make your data the most widely useable, ensure that it has a persistent identifier.
+A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but handle is also an option (<https://handle.net/>).
+There are different options for generating a DOI for your data and other materials.
+FigShare, Zenodo and OSF all offer long-term archival along with a service to generate a DOI for your materials.
+The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
+
+For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.
 
@@
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2020].
+The list of journals was saved as a comma separated value (CSV) file and imported into R [@RCT2020].
 

### 2020-04-20 analysis/paper/paper.Rmd
Add Nature article introducing FAIR data

@@
 
-If steps are followed to make the data FAIR (Findable, Accessible, Interoptable and Reusable) then it will be readable by humans and machines alike this will help support new discoveries and support further research.
+If steps are followed to make the data FAIR (Findable, Accessible, Interoptable and Reusable) [@Wilkinson2016] then it will be readable by humans and machines alike this will help support new discoveries and support further research.
 In turn sharing data will lead to new citations for your work as other discover and use it.

### 2020-04-20 analysis/paper/paper.Rmd
Update paper.Rmd

@@
       institute: UFV
-  - Zachary Foster:
+  - Zachary Foster: OSU
   - Niklaus J Grünwald: 
+      institute: ARS
 institute:
@@
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
+  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR, USA
+  - ARS: Horticulural Crops Research Unit, USDA Agriocultural Research Service, Corvallis, OR, USA
 date: "`r format(Sys.time(), '%d %B, %Y')`"

### 2020-04-20 analysis/paper/paper.Rmd

--- 2020-04-20 analysis/paper/paper.Rmd
@@
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
+  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR, USA
+  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis, OR, USA
 date: "`r format(Sys.time(), '%d %B, %Y')`"

### 2020-04-20 analysis/paper/paper.Rmd
Fix up affiliations

--- 2020-04-20 analysis/paper/paper.Rmd
@@
   - Zachary Foster: 
+      institute: OSU
   - Niklaus J Grünwald: 
+      institute: ARS
 institute:
-  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland 4350, Australia
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
+  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR, USA
+  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis, OR, USA
 date: "`r format(Sys.time(), '%d %B, %Y')`"

### 2020-04-21 analysis/paper/paper.Rmd
Expand Data section

@@
 
+Prefer text files for saving small sets of data.
+Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
 In many cases, data sets are small enough and curated in spreadsheets, which if saved as a plain text file, _e.g._ comma separated (CSV) files, allows for additions or updates to the data can be tracked through a version control system such as Git, Mercurial among others.
-Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only, using file permissions to prevent changes to the raw data files or possibly where appropriate using a data base to store the data that have been collected.
+This also helps ensure that the data are reusable.
+
+Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
+While databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set that might be only a few rows and columns in a database.
+
+Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
+It should be noted, that the use of a database management system also allows for both of these at the expense of added complexity.
 Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
@@
 ### Repository
+
 - Using GitHub, Gitlab, Bitbucket for code (and small data?)

### 2020-04-21 analysis/paper/paper.Rmd
Delete source code section
Add text to Sharing Your Research section

@@
 A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
-The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
+The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
 The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
@@
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which if saved as a plain text file, _e.g._ comma separated (CSV) files, allows for additions or updates to the data can be tracked through a version control system such as Git, Mercurial among others.
-This also helps ensure that the data are reusable.
-
-Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._ comma separated (CSV) files.
+This also helps ensure that the data are reusable.Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
 While databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set that might be only a few rows and columns in a database.
@@
 
-If steps are followed to make the data FAIR (Findable, Accessible, Interoptable and Reusable) [@Wilkinson2016] then it will be readable by humans and machines alike this will help support new discoveries and support further research.
+If steps are followed to make the data FAIR then it will be readable by humans and machines alike this will help support new discoveries and support further research.
 In turn sharing data will lead to new citations for your work as other discover and use it.
@@
 
-### Source Code
+### Sharing Your Research
 
-- The problem of commercial software and mouse-based routines
-- Why to avoid binary files as supplements?
-- Writing and documenting using open source software
-- Availability in public repositories
+Once you have determined how to best manage your source code for analysis and the data sets the next step is to consider how to share your data.
+Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
 
-### Repository
+Other providers exist that allow for you to not only track changes but also to share the data openly, these include GitHub, Gitlab and Bitbucket.
+GitHub is arguably the most popular and widely used software development platform currently.
+Data that is encoded in CSV or other plain text formats can easily be deposited in a repository along with code for analysis to enable changes to be tracked and other users to download and replicate the work.
 
-- Using GitHub, Gitlab, Bitbucket for code (and small data?)
-- Using Figshare, Dataverse or some other data repository for large data
-- Zenodo or OSF to generate DOIs
-- Why not use a lab website (DOIs, other reasons)
-- Most ideally, deposit in university library or other proper long-term data archival service
+We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only though.
+Doing either of these leaves the work in an unstable state where future users may be unable to access the work.
+It is a best practice to always ensure that you have deposited the data with a provider such as Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessability.
+Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
+
+Readers should also consult with their local librarians about local resources.
+Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development respositories in some cases up as well.
+
+Readers are encouraged to avoid using lab websites and other personal pages for sharing projects over the longer term as they are fraught with link-rot and are not an optimal way to share your projects.
 

### 2020-04-21 R/import_rrpp.R
add new function to import and format data

@@ -1,0 +1,45 @@
+
+#' Import Reproducibility Score Notes
+#'
+#' Imports, formats data into proper types and calculates the final
+#'  reproducibility score
+#'
+#' @return A `tibble` object of reproducibility score notes formatted for use in
+#'  analysis and manuscript preparation
+#' @export import_rrpp
+#'
+#' @examples
+#' import_rrpp()
+#' pander::pander(head(rrpp))
+import_rrpp <- function() {
+  readr::read_csv(
+    system.file("extdata",
+                "article_notes.csv",
+                package = "Reproducibility.in.Plant.Pathology"),
+    na = "NA"
+  ) %>%
+    dplyr::mutate(
+      reproducibility_score =
+        dplyr::if_else(
+          condition = data_avail > 0,
+          true = as.integer(comp_mthds_avail) +
+            as.integer(software_avail) +
+            as.integer(software_cite) +
+            as.integer(data_avail),
+          false = as.integer(data_avail),
+          missing = as.integer(0)
+        )
+    ) %>%
+    dplyr::mutate(IF_5year =
+                    dplyr::if_else(
+                      condition = is.na(IF_5year),
+                      true = 0,
+                      false = IF_5year
+                    )) %>%
+    dplyr::mutate(art_class = as.factor(art_class)) %>%
+    dplyr::mutate(repro_inst = as.factor(repro_inst)) %>%
+    dplyr::mutate(open = as.factor(open)) %>%
+    dplyr::mutate(abbreviation = as.factor(abbreviation)) %>%
+    dplyr::mutate(assignee = as.factor(assignee)) %>%
+    dplyr::filter(!is.na(reproducibility_score))
+}

### 2020-04-21 analysis/paper/paper.Rmd
Flesh out methods and results from article surveys

@@
 
+## Article Selection
+
+In order for us to determine where we are as a discipline with regards to openly and reproducibly sharing data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
+Among the journals, both fundamental and/or applied as well as journals covering specific group of pathogens/plants or broad areas were included.
+Three hundred articles were randomly selected from issues published from 2012 to 2018.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
+The pages list was numbered from page one and went to 150.
+This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
+The list of journals was saved from Google's gsheets as a comma separated value (CSV) file for later use and distribution.
+
+## Scoring criteria
+
+Four individuals were assigned to rate a randomised list of journal articles.
+
+Journals were provided a score for whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
+The five-year impact factor for each journal was retreived from (XXXXX) and entered in the notes.
+
+Articles were provided classifications, whether they were fundamental or applied and a note was made whether the article's primary focus was molecular (TRUE/FALSE).
+
+Where possible the software used was recorded in the notes if it was cited or otherwise specified in the article text.
+
+Articles were scored in four areas for reproducibility on a scale of 0 to 3:
+
+  * **computational methods available**
+
+    * 0 - Not available or not mentioned in the publication
+
+    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
+    ArcGIS standard is $7000)
+
+    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel, Matlab? ($500))
+
+    * 3 - Uses entirely open source and free software (_e.g._, R, Python)
+
+    * NA - No software was used in the research that can be determined as the article is written
+
+  * **software available**
+
+    * 0 - Not available or not mentioned in the publication
+
+    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
+    ArcGIS standard is $7000)
+
+    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel, Matlab? ($500))
+
+    * 3 - Uses entirely open source and free software (_e.g._, R, Python).
+
+    * NA - No software was used in the research that can be determined as the article is written
+
+  * **software cited**
+
+    * 0 - not mentioned
+
+    * 1 - Software mentioned by name only
+
+    * 2 - Software cited with version number
+
+    * 3 - All software components (SAS PROCs, R or Python packages) etc. cited
+
+    * NA - No software was used in the research that can be determined as the article is written.
+
+  * **data available**
+
+    * 0 - Not available or not mentioned in the publication
+
+    * 1 - Available upon request to author
+
+    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, pay wall, FTP server, personal 
+    lab website that may disappear, or may have already disappeared)
+
+    * 3 - Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, 
+    dataverse or university library or some other proper archiving system)
+
+## Results
+
+No journals were completely closed, all offered at least an option for open access but some were completely open.
+
+The majority of the articles were classed as fundamental, 160, with 138 classed as applied.
+
+Most articles did not make any computational methods available in any fashion with two classing as "3" (0.007&nbsp;%), which was the highest score available, 287 were classed as "0" (96&nbsp;%) and 9 articles (0.03&nbsp;%) appeared to not use any computational methods.
+
+More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Table \@ref(tab:sa)).
+
+A custom R function, `Reproducibility.in.Plant.Pathology::import_rrpp()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+
+The majority of articles scored very low in our reproducibility assessment, 82.6&nbsp;% scored 0 out of 12, which was not reproducible at all (Table \@ref(tab:reproducibility)).
+The highest scoring article recieved an 11 out of 12.
+
 * Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
@@
 
-Twenty-one plant pathology discipline journals were selected by the authors as representations of discipline-based journals target by the plant pathology research community.
-Among them, both fundamental and/or applied as well as journals covering specific group of pathogens/plants or broad areas were included.
-Two hundred articles were randomly selected from issues published from 2012 to 2018.
-A list of randomly selected pages was assigned to a randomized list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
-Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
-The pages list was numbered from page one and went to 150.
-This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved as a comma separated value (CSV) file and imported into R [@RCT2020].
-
 # Discussion
@@
 
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
 ##### pagebreak
+
+# Tables
+
+```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
+library("dplyr")
+library("janitor")
+library("flextable")
+library("officer")
+
+import_rrpp() %>%
+  tabyl(journal) %>%
+  select(-percent) %>%
+  flextable() %>%
+  set_caption(
+    "Table: (\\#tab:journals) Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
+  ) %>% 
+  autofit()
+```
+
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+```{r software_avail, echo=FALSE, message=FALSE, warning=FALSE}
+import_rrpp() %>%
+  tabyl(software_avail) %>%
+  select(-percent) %>% 
+  rename(`software availability` = software_avail,
+         percent = valid_percent) %>% 
+  flextable() %>%
+  set_caption(
+    "Table: (\\#tab:sa) Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available."
+  ) %>% 
+  autofit()
+```
+
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+```{r reproducibility_score, echo=FALSE, message=FALSE, warning=FALSE}
+import_rrpp() %>% 
+  tabyl(reproducibility_score) %>% 
+  adorn_pct_formatting() %>% 
+  rename(score = reproducibility_score) %>% 
+  flextable() %>% 
+  set_caption("Table: (\\#tab:reproducibility) Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistcal analysis or other computational code) are freely available for download and use, and raw data are available for download and use.") %>%
+    autofit()
+
+```
 

### 2020-04-21 README.rmd
cleanup duplicated information in README for licences
Use doi2bib package

--- 2020-04-08 README.rmd
@@
 # Reproducibility in Plant Pathology
-
+![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
 [![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
@@
 
-This repository is organized as an R package. There is one R function,
-`doi2bib()`, that is used in this repository, along with a bibliography file of
-the articles that were examined that are located in `inst/extdata` directory. We
-have used the R package structure to help manage dependencies, to take advantage
-of continuous integration for automated code testing and for file organisation.
+This repository is organized as an R package. There are custom R functions, 
+`table_of_journals()` and `workflow_dia()` that are used in this repository, along with a bibliography file of the articles that were examined and the notes that are located in `inst/extdata` directory.
+We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.
 
@@
 Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
-
-### Licenses
-
-**Code :** See the [DESCRIPTION](DESCRIPTION) file
-
-**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
 

### 2020-04-21 R/doi2bib.R

@@ -1,42 +1,0 @@
-#' Convert doi to bibtex
-#'
-#' Convert a digital object identifier (doi) string into a bibtex entry using
-#' the web service <http://www.doi2bib.org>.
-#'
-#' @param doi The character string of the doi.
-#' @return a bibtex entry as a character string.
-#'
-#' @examples
-#' doi2bib("10.4454/jpp.fa.2012.002")
-#'
-#' @note
-#' Original script from William Keith Morris,
-#' <https://gist.github.com/wkmor1/ae2cc96acad472d49c35>.  Documented for use
-#' in an R package by Adam H. Sparks
-#'
-#' @author William Keith Morris <wkmor1@@gmail.com> adapted by Adam H. Sparks
-#'
-#' @name doi2bib
-#' @rdname doi2bib-methods
-#' @exportMethod doi2bib
-
-setGeneric("doi2bib",
-           function(doi) {
-             standardGeneric("doi2bib")
-           })
-
-#' @rdname doi2bib-methods
-#' @aliases doi2bib,ANY-method
-setMethod("doi2bib",
-          c(doi = "character"),
-          function(doi) {
-            httr::content(
-              httr::GET(
-                url    = "http://www.doi2bib.org/",
-                config = httr::accept("application/x-bibtex"),
-                path   = "doi2bib",
-                query  = list(id = doi)
-              ),
-              as = "text"
-            )
-          })

### 2020-04-21 tests/testthat/test_doi2bib.R

@@ -1,6 +1,0 @@
-context("doi2bib")
-
-test_that("doi2bib fetches a bib object", {
-  expect_equal(doi2bib("10.1111/efp.12134"),
-              " @article{F. Suárez-Estrella_M.A. Bustamante_R. Moral_M.C. Vargas-García_M.J. López_J. Moreno_2012, title={IN VITRO CONTROL OF FUSARIUM WILT USING AGROINDUSTRIAL SUBPRODUCT-BASED COMPOSTS}, volume={94}, ISSN={1125-4653}, url={http://doi.org/10.4454/jpp.fa.2012.002}, DOI={10.4454/jpp.fa.2012.002}, number={1}, journal={Journal of Plant Pathology}, author={F. Suárez-Estrella and M.A. Bustamante and R. Moral and M.C. Vargas-García and M.J. López and J. Moreno}, year={2012} }\n")
-})

### 2020-04-21 R/import_rrpp.R
Passes checks except for having no tests

@@ -9,9 +9,18 @@
 #' @export import_rrpp
 #'
 #' @examples
-#' import_rrpp()
+#' rrpp <- import_rrpp()
 #' pander::pander(head(rrpp))
+#'
+#' @importFrom magrittr "%>%"
+#'
 import_rrpp <- function() {
+
+  # CRAN Note Avoidance
+  data_avail <- comp_mthds_avail <- software_avail <- software_cite <-
+    IF_5year <- art_class <- repro_inst <- abbreviation <- assignee <-
+    reproducibility_score <- NULL
+
   readr::read_csv(
     system.file("extdata",
                 "article_notes.csv",

### 2020-04-21 analysis/paper/paper.Rmd
Rename import_rrpp() to import_notes() and import 5-year IF

@@
 
-A custom R function, `Reproducibility.in.Plant.Pathology::import_rrpp()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
 
@@
 
-import_rrpp() %>%
+import_notes() %>%
   tabyl(journal) %>%
@@
 ```{r software_avail, echo=FALSE, message=FALSE, warning=FALSE}
-import_rrpp() %>%
+import_notes() %>%
   tabyl(software_avail) %>%
@@
 ```{r reproducibility_score, echo=FALSE, message=FALSE, warning=FALSE}
-import_rrpp() %>% 
+import_notes() %>% 
   tabyl(reproducibility_score) %>% 

### 2020-04-21 R/import_notes.R

@@ -2,31 +2,45 @@
 #' Import Reproducibility Score Notes
 #'
 #' Imports, formats data into proper types and calculates the final
-#'  reproducibility score
+#'  reproducibility score. Also adds the 2 and 5 year impact factor values from
+#'  InCites Journal Citation Reports for 2018.
 #'
 #' @return A `tibble` object of reproducibility score notes formatted for use in
 #'  analysis and manuscript preparation
-#' @export import_rrpp
+#' @export import_notes
 #'
 #' @examples
-#' rrpp <- import_rrpp()
-#' pander::pander(head(rrpp))
+#' notes <- import_notes()
+#' pander::pander(head(notes))
 #'
 #' @importFrom magrittr "%>%"
 #'
-import_rrpp <- function() {
-
+import_notes <- function() {
   # CRAN Note Avoidance
-  data_avail <- comp_mthds_avail <- software_avail <- software_cite <-
-    IF_5year <- art_class <- repro_inst <- abbreviation <- assignee <-
+  data_avail <-
+    comp_mthds_avail <- software_avail <- software_cite <-
+    IF_5year <-
+    art_class <- repro_inst <- abbreviation <- assignee <-
     reproducibility_score <- NULL
 
-  readr::read_csv(
+  notes <- readr::read_csv(
     system.file("extdata",
                 "article_notes.csv",
                 package = "Reproducibility.in.Plant.Pathology"),
     na = "NA"
-  ) %>%
+  )
+
+  IF_5year <- readr::read_csv(
+    system.file("extdata",
+                "2018_5-year_IF.csv",
+                package = "Reproducibility.in.Plant.Pathology"),
+    na = "NA"
+  )
+
+  notes <- dplyr::left_join(notes, IF_5year, by = c("journal" = "Journal"))
+
+  notes <-
+    notes %>%
     dplyr::mutate(
       reproducibility_score =
         dplyr::if_else(
@@ -51,4 +65,6 @@ import_rrpp <- function() {
     dplyr::mutate(abbreviation = as.factor(abbreviation)) %>%
     dplyr::mutate(assignee = as.factor(assignee)) %>%
     dplyr::filter(!is.na(reproducibility_score))
+
+  return(notes)
 }

### 2020-04-22 analysis/paper/paper.Rmd
Update info about 5 Year IF

@@
 Journals were provided a score for whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
-The five-year impact factor for each journal was retreived from (XXXXX) and entered in the notes.
+The five-year impact factor for 2018 for each journal was retreived from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
+This was downloaded, saved as a .csv file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.
 

### 2020-04-22 analysis/paper/paper.Rmd
Spell check paper

@@
 
-To make your data the most widely useable, ensure that it has a persistent identifier.
+To make your data the most widely usable, ensure that it has a persistent identifier.
 A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but handle is also an option (<https://handle.net/>).
@@
 Doing either of these leaves the work in an unstable state where future users may be unable to access the work.
-It is a best practice to always ensure that you have deposited the data with a provider such as Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessability.
+It is a best practice to always ensure that you have deposited the data with a provider such as Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessibility.
 Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
@@
 Readers should also consult with their local librarians about local resources.
-Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development respositories in some cases up as well.
+Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories in some cases up as well.
 
@@
 
-Journals were provided a score for whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
-The five-year impact factor for 2018 for each journal was retreived from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
+Journals were provided a score for whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
+The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
 This was downloaded, saved as a .csv file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.
@@
 The majority of articles scored very low in our reproducibility assessment, 82.6&nbsp;% scored 0 out of 12, which was not reproducible at all (Table \@ref(tab:reproducibility)).
-The highest scoring article recieved an 11 out of 12.
+The highest scoring article received an 11 out of 12.
 
@@
   flextable() %>% 
-  set_caption("Table: (\\#tab:reproducibility) Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistcal analysis or other computational code) are freely available for download and use, and raw data are available for download and use.") %>%
+  set_caption("Table: (\\#tab:reproducibility) Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.") %>%
     autofit()

### 2020-04-22 tests/testthat/test-import_notes.R
Add test for import_notes()

@@ -1,0 +1,15 @@
+context("import_notes()")
+
+# Test that import_notes() returns expected results, a tibble with 47 cols
+# and columns that are set to factor are factors. All other default as read.
+test_that("import_notes returns expected results", {
+  notes <- import_notes()
+  expect_true(tibble::is_tibble(notes))
+  expect_equal(ncol(notes), 47)
+  expect_equal(class(notes$journal), "factor")
+  expect_equal(class(notes$art_class), "factor")
+  expect_equal(class(notes$art_class), "factor")
+  expect_equal(class(notes$repro_inst), "factor")
+  expect_equal(class(notes$open), "factor")
+  expect_equal(class(notes$assignee), "factor")
+})

### 2020-04-22 R/import_notes.R
Fix a CRAN NOTE (even though will never go to CRAN)

@@ -1,4 +1,5 @@
 
+
 #' Import Reproducibility Score Notes
 #'
 #' Imports, formats data into proper types and calculates the final
@@ -21,7 +22,7 @@ import_notes <- function() {
     comp_mthds_avail <- software_avail <- software_cite <-
     IF_5year <-
     art_class <- repro_inst <- abbreviation <- assignee <-
-    reproducibility_score <- NULL
+    reproducibility_score <- journal <- NULL
 
   notes <- readr::read_csv(
     system.file("extdata",
@@ -37,7 +38,8 @@ import_notes <- function() {
     na = "NA"
   )
 
-  notes <- dplyr::left_join(notes, IF_5year, by = c("journal" = "Journal"))
+  notes <-
+    dplyr::left_join(notes, IF_5year, by = c("journal" = "Journal"))
 
   notes <-
     notes %>%
@@ -59,6 +61,7 @@ import_notes <- function() {
                       true = 0,
                       false = IF_5year
                     )) %>%
+    dplyr::mutate(journal = as.factor(journal)) %>%
     dplyr::mutate(art_class = as.factor(art_class)) %>%
     dplyr::mutate(repro_inst = as.factor(repro_inst)) %>%
     dplyr::mutate(open = as.factor(open)) %>%

### 2020-04-22 analysis/paper/paper.Rmd
add more detail to scoring methods

@@
 Articles were provided classifications, whether they were fundamental or applied and a note was made whether the article's primary focus was molecular (TRUE/FALSE).
+This classification was based on the evaluator's own judgement of the article.
+
+Further classification as to whether the articles focused on using or developing molecular techniques was included.
 
@@
 
+A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+
 ## Results
@@
 
-The majority of the articles were classed as fundamental, 160, with 138 classed as applied.
+The majority of the articles were classed as fundamental, 160, with 138 classed as applied, nearly an even distribution between the types of article.
 
@@
 More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Table \@ref(tab:sa)).
-
-A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
 

### 2020-04-22 analysis/paper/paper.Rmd
Add more to methods on software used and add table of software used

--- 2020-04-22 analysis/paper/paper.Rmd
@@
 
+Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
+When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
+A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+
 ## Results
@@
 
-A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Table \@ref(tab:sc)).
+
+The most frequently cited software was SAS.
+The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 8th.
 
@@
     "Table: (\\#tab:sa) Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available."
+  ) %>% 
+  autofit()
+```
+
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+```{r software_cite, echo=FALSE, message=FALSE, warning=FALSE}
+import_notes() %>%
+  tabyl(software_cite) %>%
+  select(-percent) %>% 
+  rename(`software citation` = software_cite,
+         percent = valid_percent) %>% 
+  flextable() %>%
+  set_caption(
+    "Table: (\\#tab:sc) Article ratings for software citations where '0', not specified or mentioned in publication to '3', fully cited with proper version numbers and all procedures detailed."
+  ) %>% 
+  autofit()
+```
+
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+```{r software_used, echo=FALSE, message=FALSE, warning=FALSE}
+library(tidyr)
+
+rrpp_software <-
+  import_notes() %>%
+  transform(software_used = strsplit(software_used, ",")) %>%
+  unnest(software_used) %>% 
+  mutate(software_used = trimws(software_used)) %>% 
+  mutate(software_used = toupper(software_used)) # convert all to uppercase to standardise
+
+rrpp_software %>% 
+  tabyl(software_used) %>%
+  select(c(-percent, -valid_percent)) %>% 
+  rename(`software used` = software_used) %>% 
+  arrange(-n) %>% 
+  slice(seq_len(14)) %>% 
+  drop_na() %>% 
+  flextable() %>%
+  set_caption(
+    "Table: (\\#tab:su) Top 10 softwares cited in all articles.
+Software used is any software package mentioned by name or properly cited in the evaluated articles, n is the number of times it was mentioned.
+All software names were converted to fully upper-case letters to avoid any inter-evaluator data entry issues."
   ) %>% 

### 2020-04-23 R/import_notes.R
Update way reproducibility score is calculated
Calculate score as a %. So if an article didn't use specialised software but made all data available, then the score could be 100 %. Previously these sorts of articles would have been penalised with a lower score even though it was not possible for them to score higher.

@@ -1,5 +1,6 @@
 
 
+
 #' Import Reproducibility Score Notes
 #'
 #' Imports, formats data into proper types and calculates the final
@@ -39,22 +40,8 @@ import_notes <- function() {
   )
 
   notes <-
-    dplyr::left_join(notes, IF_5year, by = c("journal" = "Journal"))
-
-  notes <-
     notes %>%
-    dplyr::mutate(
-      reproducibility_score =
-        dplyr::if_else(
-          condition = data_avail > 0,
-          true = as.integer(comp_mthds_avail) +
-            as.integer(software_avail) +
-            as.integer(software_cite) +
-            as.integer(data_avail),
-          false = as.integer(data_avail),
-          missing = as.integer(0)
-        )
-    ) %>%
+    dplyr::left_join(x = notes, y = IF_5year, by = c("journal" = "journal")) %>%
     dplyr::mutate(IF_5year =
                     dplyr::if_else(
                       condition = is.na(IF_5year),
@@ -66,8 +53,32 @@ import_notes <- function() {
     dplyr::mutate(repro_inst = as.factor(repro_inst)) %>%
     dplyr::mutate(open = as.factor(open)) %>%
     dplyr::mutate(abbreviation = as.factor(abbreviation)) %>%
-    dplyr::mutate(assignee = as.factor(assignee)) %>%
-    dplyr::filter(!is.na(reproducibility_score))
+    dplyr::mutate(assignee = as.factor(assignee))
+
+  # add reproducibility score as a percent of total possible
+  #
+  # calcuate total possible score for a paper
+  total_possible <-
+    notes %>%
+    dplyr::select(comp_mthds_avail, software_avail, software_cite, data_avail) %>%
+    dplyr::mutate(total_possible = rowSums(!is.na(.)) * 3) %>%
+    dplyr::select(total_possible)
+
+  # calculate reproducibility score
+  notes <-
+    notes %>%
+    tibble::add_column(total_possible) %>%
+    dplyr::rowwise() %>%
+    dplyr::mutate(reproducibility_score =
+                    (
+                      sum(
+                        comp_mthds_avail,
+                        software_avail,
+                        software_cite,
+                        data_avail,
+                        na.rm = TRUE
+                      ) / total_possible
+                    ) * 100)
 
   return(notes)
 }

### 2020-04-23 tests/testthat/test-import_notes.R
Update tests for new repro score

@@ -5,7 +5,7 @@ context("import_notes()")
 test_that("import_notes returns expected results", {
   notes <- import_notes()
   expect_true(tibble::is_tibble(notes))
-  expect_equal(ncol(notes), 47)
+  expect_equal(ncol(notes), 48)
   expect_equal(class(notes$journal), "factor")
   expect_equal(class(notes$art_class), "factor")
   expect_equal(class(notes$art_class), "factor")

### 2020-04-23 analysis/paper/paper.Rmd
Update paper with recent changes to scoring

@@
 A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices \@ref(fig:workflow-dia).
+Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
 
@@
 
-In order for us to determine where we are as a discipline with regards to openly and reproducibly sharing data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
-Among the journals, both fundamental and/or applied as well as journals covering specific group of pathogens/plants or broad areas were included.
+In order for us to determine where we are as a discipline with regards to sharing openly and reproducible papers and data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
+The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
 Three hundred articles were randomly selected from issues published from 2012 to 2018.
-A list of randomly selected pages was assigned to a randomized list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
 In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
 Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
-The pages list was numbered from page one and went to 150.
+The pages list was numbered from page one and went to page 150.
 This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved from Google's gsheets as a comma separated value (CSV) file for later use and distribution.
+The list of journals was saved from Google's gsheets as a comma separated value (CSV) file for later use and distribution in a research compendium.
 
@@
 
-Journals were provided a score for whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
+Each journals was classified as to  whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
 The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as a .csv file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.
+This was downloaded, saved as a CSV file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.
 
-Articles were provided classifications, whether they were fundamental or applied and a note was made whether the article's primary focus was molecular (TRUE/FALSE).
+Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
 This classification was based on the evaluator's own judgement of the article.
 
-Further classification as to whether the articles focused on using or developing molecular techniques was included.
-
-Where possible the software used was recorded in the notes if it was cited or otherwise specified in the article text.
+Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
 
@@
     * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
-    ArcGIS standard is $7000)
+    ArcGIS standard is $7000US)
 
-    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel, Matlab? ($500))
+    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel) or SAS that is now available free for use with a univerisity login
 
@@
 
-    * 3 - All software components (SAS PROCs, R or Python packages) etc. cited
+    * 3 - All software components (SAS PROCs, R or Python packages) etc., cited
 
@@
 
-    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, pay wall, FTP server, personal 
-    lab website that may disappear, or may have already disappeared)
+    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, pay wall, FTP server, personal lab website that may disappear, or may have already disappeared)
 
-    * 3 - Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, 
-    dataverse or university library or some other proper archiving system)
+    * 3 - Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system)
 
@@
 
+A total reproducibility score was calculated as the percent of total possible for a given paper,
+_e.g._ some papers did not use specialized software therefore they were not scored for this category.
+
 ## Results
@@
 
-The majority of the articles were classed as fundamental, 160, with 138 classed as applied.
+The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
 
@@
 
-The majority of articles scored very low in our reproducibility assessment, 82.6&nbsp;% scored 0 out of 12, which was not reproducible at all (Table \@ref(tab:reproducibility)).
-The highest scoring article received an 11 out of 12.
+Forty-eight articles scored 0&nbsp;% out of a possible 100&nbsp;% for reproducibility.
+The mean value was 31.2&nbsp;% and the median value was 33.3&nbsp;%.
+One article scored 100&nbsp;%, or was classed as fully reproducible.
 

### 2020-05-18 analysis/paper/paper.Rmd
Correct Excel rank in text
Replace gsheet with googlesheets4 to simplify package usage

@@
 The use of programming or scripting languages such as R, SAS or Python enable you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, gsheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
+This is as opposed to using software such as spreadsheet programs like Excel, Google sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
 
@@
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved from Google's gsheets as a comma separated value (CSV) file for later use and distribution in a research compendium.
+The list of journals was saved from Google's sheets as a comma separated value (CSV) file for later use and distribution in a research compendium.
 
@@
 The most frequently cited software was SAS.
-The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 8th.
+The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 9th.
 

### 2020-05-18 R/import_notes.R

@@ -1,6 +1,4 @@
 
-
-
 #' Import Reproducibility Score Notes
 #'
 #' Imports, formats data into proper types and calculates the final

### 2020-05-18 R/table_of_journals.R

@@ -6,7 +6,7 @@
 #'
 #' @examples
 #' \donttest{
-#' rrpp <- gsheet::gsheet2tbl(
+#' rrpp <- googlesheets4::read_sheet(
 #'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
 #')
 #' table_of_journals(rrpp)

### 2020-05-18 analysis/paper/paper.Rmd
Add paragraph on scoring and Lehner reference for soybean white mould

@@
 The use of programming or scripting languages such as R, SAS or Python enable you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
+This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
 
@@
 
+We recognise that the scoring methods were developed by the auhors specifically for this exercise and are not entirely subjective.
+We have based our scoring decisions on our own experiences in the field of plant pathology.
+While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
+Thus, emphasis was given to using open source alternatives where possible over paid software packages.
+The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the least cost.
+
 ## Results
@@
 for readers.
+
 * Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
 replicate the entire study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+
 * Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
 necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
-* Del Ponte provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied.
+
+* Lehner et al.
+[-@Lehner2017] provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
+
+* Khaliq et al.
+[] offer a full research compendium with a Docker instance and DOI that enable readers to fully replicate the analysis using the data collected and step through other points where weather data were investigated and various models were fit before deciding on the best fit.
+
 * Example from Grünwald lab: 

### 2020-07-12 R/import_notes.R
Pass checks

@@ -15,13 +15,14 @@
 #'
 #' @importFrom magrittr "%>%"
 #'
+
 import_notes <- function() {
   # CRAN Note Avoidance
   data_avail <-
     comp_mthds_avail <- software_avail <- software_cite <-
     IF_5year <-
     art_class <- repro_inst <- abbreviation <- assignee <-
-    reproducibility_score <- journal <- NULL
+    reproducibility_score <- journal <- . <- NULL
 
   notes <- readr::read_csv(
     system.file("extdata",
@@ -55,7 +56,7 @@ import_notes <- function() {
 
   # add reproducibility score as a percent of total possible
   #
-  # calcuate total possible score for a paper
+  # calculate total possible score for a paper
   total_possible <-
     notes %>%
     dplyr::select(comp_mthds_avail, software_avail, software_cite, data_avail) %>%

### 2020-07-12 R/table_of_journals.R

@@ -7,7 +7,7 @@
 #' @examples
 #' \donttest{
 #' rrpp <- googlesheets4::read_sheet(
-#'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
+#'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"
 #')
 #' table_of_journals(rrpp)
 #' }

### 2020-07-15 R/import_notes.R
Year should be a factor during analysis

@@ -48,6 +48,7 @@ import_notes <- function() {
                       false = IF_5year
                     )) %>%
     dplyr::mutate(journal = as.factor(journal)) %>%
+    dplyr::mutate(year = as.factor(year)) %>%
     dplyr::mutate(art_class = as.factor(art_class)) %>%
     dplyr::mutate(repro_inst = as.factor(repro_inst)) %>%
     dplyr::mutate(open = as.factor(open)) %>%

### 2020-07-15 R/import_notes.R
Correct NOTE

@@ -22,7 +22,7 @@ import_notes <- function() {
     comp_mthds_avail <- software_avail <- software_cite <-
     IF_5year <-
     art_class <- repro_inst <- abbreviation <- assignee <-
-    reproducibility_score <- journal <- . <- NULL
+    reproducibility_score <- journal <- year <- . <- NULL
 
   notes <- readr::read_csv(
     system.file("extdata",

### 2020-07-23 analysis/paper/paper.Rmd
Add Analysis section and update references

@@
 The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation.
-In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@mcnaught1997compendium].
+In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@McNaught1997].
 
@@
 In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability.
-Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@mcnaught1997compendium].
+Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@McNaught1997].
 
@@
 The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the least cost.
+
+## Analysis
+
+Bayesian mixed effect models were fit using the contributed package brms [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+
+Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.
+
+The random effects were year and assignee for all models excepting the model which tested for year effects.
+In this model the random effects were the publication title and assignee.
+
+Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data.
+Each model was run for 3000 iterations in four chains.
+
+The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
+
+Model finesses were evaluated using model summaries and diagnostic plots from brms [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package bayesplot [@Gabry2019].
+
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package bayestestR [@Makowski2019].
 

### 2020-07-24 analysis/paper/paper.Rmd
Cleanup Rmd file

@@
 
-Bayesian mixed effect models were fit using the contributed package brms [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+Bayesian mixed effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
 
@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from brms [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package bayesplot [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].
 
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package bayestestR [@Makowski2019].
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].
 
@@
 
-No journals were completely closed, all offered at least an option for open access but some were completely open.
+Forty-eight articles scored 0&nbsp;% out of a possible 100&nbsp;% for reproducibility.
+The mean value was 31.2&nbsp;% and the median value was 33.3&nbsp;%.
+One article scored 100&nbsp;%, or was classed as fully reproducible.
+
+No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
 
@@
 
-Most articles did not make any computational methods available in any fashion with two classing as "3" (0.007&nbsp;%), which was the highest score available, 287 were classed as "0" (96&nbsp;%) and 9 articles (0.03&nbsp;%) appeared to not use any computational methods.
+Most articles did not make any computational methods available in any fashion with two, 0.007&nbsp;%, classing as "3", which was the highest score available.
+Two hundred eighty seven, 96&nbsp;%, were classed as "0" and 9 articles, 0.03&nbsp;%, appeared to not use any computational methods.
 
@@
 The most frequently cited software was SAS.
-The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 9th.
+The remainder were mostly specialised software with the exception of Microsoft Excel, tied for 9th (Table \@ref(tab:su)).
 
-Forty-eight articles scored 0&nbsp;% out of a possible 100&nbsp;% for reproducibility.
-The mean value was 31.2&nbsp;% and the median value was 33.3&nbsp;%.
-One article scored 100&nbsp;%, or was classed as fully reproducible.
+# Discussion
 
@@
 * Other examples from plant pathology providing e-Xtras or supplemental material
-
-# Discussion
 
@@
 ```{r software_used, echo=FALSE, message=FALSE, warning=FALSE}
-library(tidyr)
+library("tidyr")
 
@@
 ```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An open and reproducible research workflow.', cache=FALSE, fig.env='figure'}
-library(DiagrammeR)
-library(DiagrammeRsvg)
-library(rsvg)
+library("DiagrammeR")
+library("DiagrammeRsvg")
+library("rsvg")
 

### 2020-07-24 analysis/paper/knit_paper.R
Add script to knit and cleanup docx file

@@ -1,0 +1,23 @@
+# knits the paper using knitr, reimports the document to replace
+#  "Table: Table ..." with "Table: ..."
+#  Saves updated docx file
+
+library("knitr")
+library("officer")
+library("here")
+
+# Step 1. Knit Rmd file
+knit(input = here("analysis/paper/paper.Rmd"))
+
+# Step 2: Import .docx file
+paper <- read_docx(path = here("analysis/paper/paper.docx"))
+
+# Step 3: Replace "Table: Table ..." with "Table ..."
+paper <-
+  body_replace_all_text(x = paper,
+                        old_value = "Table: Table ",
+                        new_value = "Table ")
+
+# Step 4: Replace .docx file with updated version
+print(x = paper,
+      target = here("analysis/paper/paper.docx"))

### 2020-07-24 analysis/paper/paper.Rmd
Add packages used in paper to "Suggests"

@@
       correspondence: true
-      equal_contributor: true
   - Emerson Del Ponte:
       institute: UFV
-      equal_contributor: true
   - Kaique dos Santos Alves:

### 2020-07-24 README.rmd
Fix my contact information
Update Dockerfile directions in README

@@
 
+#### The Docker Instance
+
+Get the latest instance from Dockerhub, launch it and go to `localhost:8787` in your browser.
+Login with `rstudio`, password is `rstudio`.
+
+```
+docker pull adamhsparks/reproducibility_in_plant_pathology
+docker run -d -p 8787:8787
+```
+
+#### The Paper
+
+A script, `knit_paper.R` is located in `analysis/paper/knit_paper.R` that will knit the Word document
+
 ## Meta
@@
 
-+61 (7) 4831 1948   <adam.sparks@usq.edu.au>
++61 (7) 4631 1948   <adam.sparks@usq.edu.au>
 

### 2020-07-24 analysis/paper/knit_paper.R
Implement script to knit Paper in Docker

@@ -2,15 +2,17 @@
 #  "Table: Table ..." with "Table: ..."
 #  Saves updated docx file
 
-library("knitr")
+library("rmarkdown")
 library("officer")
 library("here")
 
 # Step 1. Knit Rmd file
-knit(input = here("analysis/paper/paper.Rmd"))
+render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.Rmd",
+       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
 
 # Step 2: Import .docx file
-paper <- read_docx(path = here("analysis/paper/paper.docx"))
+paper <-
+  read_docx(path = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
 
 # Step 3: Replace "Table: Table ..." with "Table ..."
 paper <-
@@ -19,5 +21,4 @@ paper <-
                         new_value = "Table ")
 
 # Step 4: Replace .docx file with updated version
-print(x = paper,
-      target = here("analysis/paper/paper.docx"))
+print(x = paper, target = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")

### 2020-10-15 analysis/paper/paper.Rmd
use officedown to knit Word doc

@@
 ---
-title: "Open Science, Open Plant Pathology"
+title: "How Can We Open Plant Pathology?"
 author:
@@
 output: 
-    bookdown::word_document2:
+  officedown::rdocx_document:
       fig_caption: yes
@@
         - '--lua-filter=author-info-blocks.lua'
+        - '--lua-filter=pagebreak.lua'
+      tables:
+        layout: autofit
+        width: 1.0
+        caption:
+          style: Table Caption
+          pre: 'Table '
+          sep: ': '
+        conditional:
+          first_row: true
+          first_column: false
+          last_row: false
+          last_column: false
+          no_hband: false
+          no_vband: true
 bibliography: references.bib
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+\newpage
 
@@
 
-```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
+```{r journals, tab.id="journals", tab.cap="Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated.", echo=FALSE, message=FALSE, warning=FALSE}
 library("dplyr")
@@
   flextable() %>%
-  set_caption(
-    "Table: (\\#tab:journals) Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
-  ) %>% 
   autofit()
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+\newpage
 
-```{r software_avail, echo=FALSE, message=FALSE, warning=FALSE}
+```{r software_avail, tab.id="sa", tab.cap="Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available.", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
   tabyl(software_avail) %>%
+  adorn_pct_formatting() %>% 
   select(-percent) %>% 
@@
   flextable() %>%
-  set_caption(
-    "Table: (\\#tab:sa) Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available."
-  ) %>% 
   autofit()
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+\newpage
 
-```{r software_cite, echo=FALSE, message=FALSE, warning=FALSE}
+```{r software_cite, tab.id="sc", tab.cap="Article ratings for software citations where '0', not specified or mentioned in publication to '3', fully cited with proper version numbers and all procedures detailed.", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
   tabyl(software_cite) %>%
+  adorn_pct_formatting() %>% 
   select(-percent) %>% 
@@
   flextable() %>%
-  set_caption(
-    "Table: (\\#tab:sc) Article ratings for software citations where '0', not specified or mentioned in publication to '3', fully cited with proper version numbers and all procedures detailed."
-  ) %>% 
   autofit()
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+\newpage
 
-```{r software_used, echo=FALSE, message=FALSE, warning=FALSE}
+```{r software_used, tab.id="su", tab.cap="ally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 library("tidyr")
@@
   tabyl(software_used) %>%
+  adorn_pct_formatting() %>% 
   select(c(-percent, -valid_percent)) %>% 
@@
   flextable() %>%
-  set_caption(
-    "Table: (\\#tab:su) Top 10 softwares cited in all articles.
-Software used is any software package mentioned by name or properly cited in the evaluated articles, n is the number of times it was mentioned.
-All software names were converted to fully upper-case letters to avoid any inter-evaluator data entry issues."
-  ) %>% 
   autofit()
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+\newpage
 
-```{r reproducibility_score, echo=FALSE, message=FALSE, warning=FALSE}
+```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
@@
   flextable() %>%
-  set_caption("Table: (\\#tab:reproducibility) Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.") %>%
   autofit()
-
 ```
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+\newpage
 

### 2020-10-15 analysis/paper/paper.Rmd
Copy edits

@@
 
-# A General Workflow
-
-A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
-
-A first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
-A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
-The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
-The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-In the next section we present standards and tools that can be used to ensure reproducibility.
-
 ### Methods
@@
 In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._ comma separated (CSV) files.
-This also helps ensure that the data are reusable.Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
+This also helps ensure that the data are reusable.
+Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
 While databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set that might be only a few rows and columns in a database.
@@
 Once you have determined how to best manage your source code for analysis and the data sets the next step is to consider how to share your data.
-Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
+Providers such as FigShare, Dataverse, OSF.io (the Open Science Framework) and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
 
@@
 Readers should also consult with their local librarians about local resources.
-Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories in some cases up as well.
+Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
 
@@
 
+# A General Workflow
+
+A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
+Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
+
+A first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
+A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
+The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
+The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
+In the next section we present standards and tools that can be used to ensure reproducibility.
+
 # Acknowledgements

### 2020-10-15 analysis/paper/knit_paper.R
Update knit_paper to remove search and replace in text, not needed

@@ -1,24 +1,7 @@
-# knits the paper using knitr, reimports the document to replace
-#  "Table: Table ..." with "Table: ..."
-#  Saves updated docx file
+# knits the paper using knitr
 
 library("rmarkdown")
-library("officer")
-library("here")
 
-# Step 1. Knit Rmd file
+# Knit Rmd file
 render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.Rmd",
        output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
-
-# Step 2: Import .docx file
-paper <-
-  read_docx(path = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
-
-# Step 3: Replace "Table: Table ..." with "Table ..."
-paper <-
-  body_replace_all_text(x = paper,
-                        old_value = "Table: Table ",
-                        new_value = "Table ")
-
-# Step 4: Replace .docx file with updated version
-print(x = paper, target = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")

### 2020-12-07 analysis/paper/paper.Rmd
Start hopefully final edits on paper to send to coauathors soon

@@
 ---
-title: "How Can We Open Plant Pathology?"
+title: "Insights Into Computational Reproducibility in Plant Pathology and a Way Forward"
 author:
@@
 However, while these definitions are clear and well accepted in physical sciences, in biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
-Therefore we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of ``reproducible research'':
+Therefore we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":
 
@@
 In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing.
-One candidate for this minimum standard is ``reproducible research'', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
+One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
 Peng, R.
@@
 
-### Open Science
+Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes and that software used are also easily obtainable and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
+
+## On Open Science and Reproducibility
 
 Open science has become highlighted lately with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018] and other scientists interested in sharing and collaborating more widely [@Wald2010].
+While open science and reproducibility are not the same, they are linked.
+By proactively practising open science, the work becomes more reproducible through the availability of data and code.
 
-### Methods
+# Methods
+
+We conducted a survey of a broad selection of articles to represent a broad swathe of publications in our discipline to evaluate the status of reproducibility and open science in our field.
+The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
+
+## Article Selection
+
+We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
+The pages list was numbered from page one and went to page 150.
+This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
+The list of journals was saved from Google's sheets as a comma separated value (CSV) file for later use and distribution in a research compendium.
+
+## Scoring criteria
+
+Four individuals were assigned to rate a randomised list of journal articles.
+
+Each journals was classified as to  whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
+The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
+This was downloaded, saved as a CSV file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
+
+Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
+This classification was based on the evaluator's own judgement of the article.
+
+Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
+
+Articles were scored in four areas for reproducibility on a scale of 0 to 3:
+
+  * **computational methods available**
+
+    * 0 - Not available or not mentioned in the publication
+
+    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
+    ArcGIS standard is $7000)
+
+    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel, Matlab? ($500))
+
+    * 3 - Uses entirely open source and free software (_e.g._, R, Python)
+
+    * NA - No software was used in the research that can be determined as the article is written
+
+  * **software available**
+
+    * 0 - Not available or not mentioned in the publication
+
+    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
+    ArcGIS standard is $7000US)
+
+    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel) or SAS that is now available free for use with a university login
+
+    * 3 - Uses entirely open source and free software (_e.g._, R, Python).
+
+    * NA - No software was used in the research that can be determined as the article is written
+
+  * **software cited**
+
+    * 0 - not mentioned
+
+    * 1 - Software mentioned by name only
+
+    * 2 - Software cited with version number
+
+    * 3 - All software components (SAS PROCs, R or Python packages) etc., cited
+
+    * NA - No software was used in the research that can be determined as the article is written.
+
+  * **data available**
+
+    * 0 - Not available or not mentioned in the publication
+
+    * 1 - Available upon request to author
+
+    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, pay wall, FTP server, personal lab website that may disappear, or may have already disappeared)
+
+    * 3 - Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system)
+
+Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
+When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
+A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+
+A total reproducibility score was calculated as the percent of total possible for a given paper,
+_e.g._ some papers did not use specialized software therefore they were not scored for this category.
+
+We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
+We have based our scoring decisions on our own experiences in the field of plant pathology.
+While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
+Thus, emphasis was given to using open source alternatives where possible over paid software packages.
+The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the least cost.
+
+## Analysis
+
+Bayesian mixed effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+
+Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.
+
+The random effects were year and assignee for all models excepting the model which tested for year effects.
+In this model the random effects were the publication title and assignee.
+
+Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data.
+Each model was run for 3000 iterations in four chains.
+
+The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
+
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].
+
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].
+
+## Results
+
+Forty-eight articles scored 0% out of a possible 100% for reproducibility.
+The mean value was 31.2% and the median value was 33.3%.
+One article scored 100%, or was classed as fully reproducible.
+
+No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
+
+The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
+
+Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available.
+Two hundred eighty seven, 96%, were classed as "0" and 9 articles, 0.03%, appeared to not use any computational methods.
+
+More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Table \@ref(tab:sa)).
+
+Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Table \@ref(tab:sc)).
+
+The most frequently cited software was SAS.
+The remainder were mostly specialised software with the exception of Microsoft Excel, tied for 9th (Table \@ref(tab:su)).
+
+# Discussion
+
+* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
+for readers.
+
+* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
+replicate the entire study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+
+* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
+necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
+
+* Lehner et al.
+[-@Lehner2017] provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
+
+* Khaliq et al.
+[] offer a full research compendium with a Docker instance and DOI that enable readers to fully replicate the analysis using the data collected and step through other points where weather data were investigated and various models were fit before deciding on the best fit.
+
+* Example from Grünwald lab: 
+  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
+  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
+* Other examples from plant pathology providing e-Xtras or supplemental material
+
+# A General Workflow
+
+A general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
+Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
+
+A first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
+A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
+The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
+The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
+In the next section we present standards and tools that can be used to ensure reproducibility.
 
@@
 Readers are encouraged to avoid using lab websites and other personal pages for sharing projects over the longer term as they are fraught with link-rot and are not an optimal way to share your projects.
-
-# Status in Plant Pathology
-
-## Article Selection
-
-In order for us to determine where we are as a discipline with regards to sharing openly and reproducible papers and data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
-The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
-Three hundred articles were randomly selected from issues published from 2012 to 2018.
-A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
-Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
-The pages list was numbered from page one and went to page 150.
-This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved from Google's sheets as a comma separated value (CSV) file for later use and distribution in a research compendium.
-
-## Scoring criteria
-
-Four individuals were assigned to rate a randomised list of journal articles.
-
-Each journals was classified as to  whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
-The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as a CSV file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.
-
-Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
-This classification was based on the evaluator's own judgement of the article.
-
-Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
-
-Articles were scored in four areas for reproducibility on a scale of 0 to 3:
-
-  * **computational methods available**
-
-    * 0 - Not available or not mentioned in the publication
-
-    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
-    ArcGIS standard is $7000)
-
-    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel, Matlab? ($500))
-
-    * 3 - Uses entirely open source and free software (_e.g._, R, Python)
-
-    * NA - No software was used in the research that can be determined as the article is written
-
-  * **software available**
-
-    * 0 - Not available or not mentioned in the publication
-
-    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
-    ArcGIS standard is $7000US)
-
-    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel) or SAS that is now available free for use with a univerisity login
-
-    * 3 - Uses entirely open source and free software (_e.g._, R, Python).
-
-    * NA - No software was used in the research that can be determined as the article is written
-
-  * **software cited**
-
-    * 0 - not mentioned
-
-    * 1 - Software mentioned by name only
-
-    * 2 - Software cited with version number
-
-    * 3 - All software components (SAS PROCs, R or Python packages) etc., cited
-
-    * NA - No software was used in the research that can be determined as the article is written.
-
-  * **data available**
-
-    * 0 - Not available or not mentioned in the publication
-
-    * 1 - Available upon request to author
-
-    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, pay wall, FTP server, personal lab website that may disappear, or may have already disappeared)
-
-    * 3 - Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system)
-
-Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
-When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
-
-A total reproducibility score was calculated as the percent of total possible for a given paper,
-_e.g._ some papers did not use specialized software therefore they were not scored for this category.
-
-We recognise that the scoring methods were developed by the auhors specifically for this exercise and are not entirely subjective.
-We have based our scoring decisions on our own experiences in the field of plant pathology.
-While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
-Thus, emphasis was given to using open source alternatives where possible over paid software packages.
-The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the least cost.
-
-## Analysis
-
-Bayesian mixed effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
-
-Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.
-
-The random effects were year and assignee for all models excepting the model which tested for year effects.
-In this model the random effects were the publication title and assignee.
-
-Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data.
-Each model was run for 3000 iterations in four chains.
-
-The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
-
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].
-
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].
-
-## Results
-
-Forty-eight articles scored 0&nbsp;% out of a possible 100&nbsp;% for reproducibility.
-The mean value was 31.2&nbsp;% and the median value was 33.3&nbsp;%.
-One article scored 100&nbsp;%, or was classed as fully reproducible.
-
-No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
-
-The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
-
-Most articles did not make any computational methods available in any fashion with two, 0.007&nbsp;%, classing as "3", which was the highest score available.
-Two hundred eighty seven, 96&nbsp;%, were classed as "0" and 9 articles, 0.03&nbsp;%, appeared to not use any computational methods.
-
-More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Table \@ref(tab:sa)).
-
-Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Table \@ref(tab:sc)).
-
-The most frequently cited software was SAS.
-The remainder were mostly specialised software with the exception of Microsoft Excel, tied for 9th (Table \@ref(tab:su)).
-
-# Discussion
-
-* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
-for readers.
-
-* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
-replicate the entire study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
-
-* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
-necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
-
-* Lehner et al.
-[-@Lehner2017] provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
-
-* Khaliq et al.
-[] offer a full research compendium with a Docker instance and DOI that enable readers to fully replicate the analysis using the data collected and step through other points where weather data were investigated and various models were fit before deciding on the best fit.
-
-* Example from Grünwald lab: 
-  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
-  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
-* Other examples from plant pathology providing e-Xtras or supplemental material
-
-# A General Workflow
-
-A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
-
-A first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
-A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
-The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
-The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-In the next section we present standards and tools that can be used to ensure reproducibility.
 

### 2020-12-07 analysis/paper/paper.Rmd
Use TPP citation style

@@
 bibliography: references.bib
-csl: "../templates/phytopathology.csl" # Insert path for the bib-style
+csl: "../templates/TPP.csl" # Insert path for the bib-style
 abstract: |

### 2020-12-07 analysis/paper/paper.Rmd
Reorder, clean up introduction

@@
 Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
-Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve plant disease management.
-Scientific research in the field varies from the purely observational or descriptive nature to inferential based on experimental or simulation-derived data sets.
-Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of your methods and results.
+Collectively, they contribute to increase our basic and applied knowledge of several aspects in pathogen biology and disease development to ultimately improve plant disease management.
+Scientific research in the field varies from the purely observational or descriptive nature to inferential, based on experimental or simulation-derived data sets.
+Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of the methods and results.
 These research findings include biological materials (isolates or strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated as a course of conducting research.
+
+Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@TPP2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
+
+While open science and reproducibility are not the same, they are linked.
+By proactively practising open science, the work becomes more reproducible through the availability of data and code.
 That is, open science leads to reproducibility and replicability.
@@
 
-## On Open Science and Reproducibility
+# Materials and methods
 
-Open science has become highlighted lately with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018] and other scientists interested in sharing and collaborating more widely [@Wald2010].
-While open science and reproducibility are not the same, they are linked.
-By proactively practising open science, the work becomes more reproducible through the availability of data and code.
-
-# Methods
+## Article Selection
 
@@
 The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
-
-## Article Selection
 

### 2020-12-07 analysis/paper/paper.Rmd
Rename or add section and subsection headers
Edit introduction and first paragraph of m&m

@@
 
-Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes and that software used are also easily obtainable and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
+Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes.
+And that the software used are also easily obtainable and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
+
+In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we conducted a survey of a broad selection of articles to represent a broad swathe of publications to evaluate our status.
 
@@
 
-We conducted a survey of a broad selection of articles to represent a broad swathe of publications in our discipline to evaluate the status of reproducibility and open science in our field.
+We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
 The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
-
-We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
 A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
@@
 
-## Analysis
+## Statistical analysis
 
@@
 
-## Results
+# Results
 
@@
 
-# A General Workflow
+## A General Workflow
 
@@
 Readers are encouraged to avoid using lab websites and other personal pages for sharing projects over the longer term as they are fraught with link-rot and are not an optimal way to share your projects.
+
+# Authors' contributions
+
+# Data availability statement
 

### 2020-12-07 analysis/paper/paper.Rmd
grammar and spelling corrections

@@
   Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results.
-In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted.
-Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
+Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared, and; analyses conducted.
+Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
+We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline and assigned them scores reflecting their openness and reproducibility.
 We found that most of the articles were not very open, failing to share data or code in a meaningful way.
@@
 Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
-Collectively, they contribute to increase our basic and applied knowledge of several aspects in pathogen biology and disease development to ultimately improve plant disease management.
+Collectively, they contribute to increasing our basic and applied knowledge of several aspects of pathogen biology and disease development to ultimately improve plant disease management.
 Scientific research in the field varies from the purely observational or descriptive nature to inferential, based on experimental or simulation-derived data sets.
@@
 
-In order for us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
+For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
@@
 Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes.
-And that the software used are also easily obtainable and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
+And that the software used are also easily obtained and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
 
-In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we conducted a survey of a broad selection of articles to represent a broad swathe of publications to evaluate our status.
+In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
 
@@
 We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
-The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
+The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
 A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
@@
 This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
-The list of journals was saved from Google's sheets as a comma separated value (CSV) file for later use and distribution in a research compendium.
+This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
+The list of journals was saved from Google's sheets as a comma-separated-value (CSV) file for later use and distribution in a research compendium.
 
@@
 
-Each journals was classified as to  whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
+Each journal was classified as to  whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
 The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
@@
 Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
-This classification was based on the evaluator's own judgement of the article.
+This classification was based on the evaluator's judgement of the article.
 
@@
 
-    * 1 - Available upon request to author
+    * 1 - Available upon request to the author
 
-    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, pay wall, FTP server, personal lab website that may disappear, or may have already disappeared)
+    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)
 
@@
 
-A total reproducibility score was calculated as the percent of total possible for a given paper,
+A total reproducibility score was calculated as the per cent of total possible for a given paper,
 _e.g._ some papers did not use specialized software therefore they were not scored for this category.
@@
 While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
-Thus, emphasis was given to using open source alternatives where possible over paid software packages.
+Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
 The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the least cost.
@@
 
-Bayesian mixed effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
 
@@
 The random effects were year and assignee for all models excepting the model which tested for year effects.
-In this model the random effects were the publication title and assignee.
+In this model, the random effects were the publication title and assignee.
 
@@
 The mean value was 31.2% and the median value was 33.3%.
-One article scored 100%, or was classed as fully reproducible.
+One article scored 100% or was classed as fully reproducible.
 
@@
 Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available.
-Two hundred eighty seven, 96%, were classed as "0" and 9 articles, 0.03%, appeared to not use any computational methods.
+Two hundred eighty-seven articles, 96%, were classed as "0" and nine articles, 0.03%, appeared to not use any computational methods.
 
@@
 The most frequently cited software was SAS.
-The remainder were mostly specialised software with the exception of Microsoft Excel, tied for 9th (Table \@ref(tab:su)).
+The remainder were mostly specialised software except for Microsoft Excel, tied for 9th (Table \@ref(tab:su)).
 
@@
 * Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
-necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
+necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
 
 * Lehner et al.
-[-@Lehner2017] provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
+[-@Lehner2017] provide data and a reproducible report that explains in detail all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
 
@@
 A general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
+Here we defined three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
 
-A first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
-A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
-The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code.
+The first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
+A second level involves providing raw data and code as binary files (PDF or other non-text files) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
+The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
 The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
@@
 Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, _e.g._ a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one hour intervals.
-This allows end users to identify what was used and identify the methods used more accurately.
+Provide a full description of all equipment used, _e.g._ a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
+This allows end-users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher are able to reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, _e.g._ a package version, what effect it had on your research.
+This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, _e.g._ a package version, what effect it had on your research.
 
-The use of programming or scripting languages such as R, SAS or Python enable you as a scientist to keep very detailed records of what was computationally performed.
+The use of programming or scripting languages such as R, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
 This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
@@
 
-If steps are followed to make the data FAIR then it will be readable by humans and machines alike this will help support new discoveries and support further research.
-In turn sharing data will lead to new citations for your work as other discover and use it.
+If steps are followed to make the data FAIR then it will be readable by humans and machines alike this will help support discoveries and support further research.
+In turn, sharing data will lead to new citations for your work as others discover and use it.
 

### 2020-12-07 analysis/paper/paper.Rmd
Remove date field from YAML, no need in final docx file

@@
   - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis, OR, USA
-date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: 

### 2020-12-07 analysis/paper/paper.Rmd
Include Julia in list of open software programming languages

@@
 
-    * 3 - Uses entirely open source and free software (_e.g._, R, Python)
+    * 3 - Uses entirely open source and free software (_e.g._, R, Julia, Python)
 
@@
 
-    * 3 - Uses entirely open source and free software (_e.g._, R, Python).
+    * 3 - Uses entirely open source and free software (_e.g._, R, Julia, Python).
 
@@
 
-    * 3 - All software components (SAS PROCs, R or Python packages) etc., cited
+    * 3 - All software components (SAS PROCs, R, Julia or Python packages) etc., cited
 
@@
 
-When making your science more open and reproducible, methods, software used, this includes items such as R or Python packages that were directly used in the analysis or production of the paper, etc.
+When making your science more open and reproducible, methods, software used, this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.
 should be cited properly.
@@
 
-The use of programming or scripting languages such as R, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
+The use of programming or scripting languages such as R, Julia, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
 This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.

### 2020-12-07 analysis/paper/paper.Rmd
Fleshing out the discussion section

@@
 
-* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
-for readers.
+Unfortunately using our scoring method, most articles scored poorly for reproducibility or openness.
+Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
 
-* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
-replicate the entire study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+The software availability score was better as was the citing of software and versions used.
+SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS.
+It is interesting to note however, that with the popularity of Python that it does not even appear in our survey results whereas R was the fourth most commonly used software.
 
-* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
-necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+While the articles that were surveyed did not score well, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.
 
-* Lehner et al.
-[-@Lehner2017] provide data and a reproducible report that explains in detail all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
+There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
+The first level is including tables of raw data or code with the paper as a supplemental file.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden et al.
+[-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra*\* with reproducible examples for readers to refer to.
+This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
 
-* Khaliq et al.
-[] offer a full research compendium with a Docker instance and DOI that enable readers to fully replicate the analysis using the data collected and step through other points where weather data were investigated and various models were fit before deciding on the best fit.
+At the second level, Lehner et al.
+[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
+The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work.
+Likewise, Duku et al.
+[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, http://adamhsparks.github.io/MICCORDEA/, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+
+The third level is the use of proper data repositories such as FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
+Sparks et al.
+[-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+
+The fourth level includes packaging the analysis as a software package, _e.g._ R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
+[@Khaliq2020] have done.
+Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of chickpea ascochyta conida dispersal using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+
+[@Miorini2018, @Miorini2019]
 
@@
   - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
-* Other examples from plant pathology providing e-Xtras or supplemental material
 
-## A General Workflow
+## A general workflow
 
@@
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
-
 For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.
 
-### Sharing Your Research
+### Sharing your research
 

### 2020-12-07 analysis/paper/paper.Rmd
Add description of data availability results and corresponding table

@@
 
+Likewise, data availability was mostly not available with 243 or 81.5% scoring "0" where the data was not available or mentioned in the article.
+However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Table \@ref(tab:da)).
+
 More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Table \@ref(tab:sa)).
@@
 
+```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._ archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
+import_notes() %>%
+  tabyl(data_avail) %>%
+  adorn_pct_formatting() %>% 
+  select(-percent) %>% 
+  rename(`data availability` = data_avail,
+         percent = valid_percent) %>% 
+  flextable() %>%
+  autofit()
+```
+
+\newpage
+
 ```{r software_used, tab.id="su", tab.cap="ally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}

### 2020-12-08 analysis/paper/paper.Rmd
Minor edits

@@
 Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
-The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the least cost.
+The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
 

### 2021-02-25 analysis/paper/paper.Rmd
Fix the caption for Figure 5

@@
 For instance, reproducible research is recently highlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
-The International Union of Pure and Applied Chemistry provides
-definitions of repeatability in the "Compendium of Chemical Terminology -- Gold Book" as:
+The International Union of Pure and Applied Chemistry provides definitions of repeatability in the "Compendium of Chemical Terminology -- Gold Book" as:
 
 > "The closeness of agreement between independent results obtained with the same method on identical test material, under the same conditions (same operator, same apparatus, same laboratory and after short intervals of time).
-The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation.
+The measure of repeatability is the standard deviation qualified with the term: \`repeatability' as repeatability standard deviation.
 In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@McNaught1997].
@@
 
-However, while these definitions are clear and well accepted in physical sciences, in biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
+However, while these definitions are clear and well accepted in physical sciences, in biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, *e.g.*, field trials that span years and locations or complex glasshouse experiments.
 Therefore we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":
@@
 One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
-Peng, R.
-[-@Peng2009].
-_Reproducible research and Biostatistics_.
-Biostatistics, 10 (3): 405-408.
+> Peng, R.
+> [-@Peng2009].
+> *Reproducible research and Biostatistics*.
+> Biostatistics, 10 (3): 405-408.
 
@@
 A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+In cases where an article was not suitable, *e.g.*, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
 Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
@@
 
-  * **computational methods available**
+-   **computational methods available**
 
-    * 0 - Not available or not mentioned in the publication
+    -   0 - Not available or not mentioned in the publication
 
-    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
-    ArcGIS standard is $7000)
+    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*i.e.*, ArcGIS standard is \$7000)
 
-    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel, Matlab? ($500))
+    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel, Matlab? (\$500))
 
-    * 3 - Uses entirely open source and free software (_e.g._, R, Julia, Python)
+    -   3 - Uses entirely open source and free software (*e.g.*, R, Julia, Python)
 
-    * NA - No software was used in the research that can be determined as the article is written
+    -   NA - No software was used in the research that can be determined as the article is written
 
-  * **software available**
+-   **software available**
 
-    * 0 - Not available or not mentioned in the publication
+    -   0 - Not available or not mentioned in the publication
 
-    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
-    ArcGIS standard is $7000US)
+    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*i.e.*, ArcGIS standard is \$7000US)
 
-    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel) or SAS that is now available free for use with a university login
+    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel) or SAS that is now available free for use with a university login
 
-    * 3 - Uses entirely open source and free software (_e.g._, R, Julia, Python).
+    -   3 - Uses entirely open source and free software (*e.g.*, R, Julia, Python).
 
-    * NA - No software was used in the research that can be determined as the article is written
+    -   NA - No software was used in the research that can be determined as the article is written
 
-  * **software cited**
+-   **software cited**
 
-    * 0 - not mentioned
+    -   0 - not mentioned
 
-    * 1 - Software mentioned by name only
+    -   1 - Software mentioned by name only
 
-    * 2 - Software cited with version number
+    -   2 - Software cited with version number
 
-    * 3 - All software components (SAS PROCs, R, Julia or Python packages) etc., cited
+    -   3 - All software components (SAS PROCs, R, Julia or Python packages) etc., cited
 
-    * NA - No software was used in the research that can be determined as the article is written.
+    -   NA - No software was used in the research that can be determined as the article is written.
 
-  * **data available**
+-   **data available**
 
-    * 0 - Not available or not mentioned in the publication
+    -   0 - Not available or not mentioned in the publication
 
-    * 1 - Available upon request to the author
+    -   1 - Available upon request to the author
 
-    * 2 - Online, but inconvenient or non-permanent (_e.g._, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)
+    -   2 - Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)
 
-    * 3 - Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system)
+    -   3 - Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system)
 
@@
 
-A total reproducibility score was calculated as the per cent of total possible for a given paper,
-_e.g._ some papers did not use specialized software therefore they were not scored for this category.
+A total reproducibility score was calculated as the per cent of total possible for a given paper, *e.g.* some papers did not use specialized software therefore they were not scored for this category.
 
@@
 At the second level, Lehner et al.
-[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
+[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
 The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work.
 Likewise, Duku et al.
-[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, http://adamhsparks.github.io/MICCORDEA/, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
 
@@
 
-The fourth level includes packaging the analysis as a software package, _e.g._ R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
+The fourth level includes packaging the analysis as a software package, *e.g.* R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
 [@Khaliq2020] have done.
@@
 
-* Example from Grünwald lab: 
-  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
-  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
+-   Example from Grünwald lab:
+
+    -   paper <http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI>
+    -   github repo <https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests>
 
@@
 Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, _e.g._ a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
+Provide a full description of all equipment used, *e.g.* a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
 This allows end-users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, _e.g._ a package version, what effect it had on your research.
+This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.* a package version, what effect it had on your research.
 
@@
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._ comma separated (CSV) files.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.* comma separated (CSV) files.
 This also helps ensure that the data are reusable.
@@
 # References
+
 <!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
-<div id="refs"></div>
+
+::: {#refs}
+:::
 
@@
 
-```{r software_used, tab.id="su", tab.cap="ally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 library("tidyr")

### 2021-02-26 analysis/paper/paper.Rmd
This fixes the caption...
Minor edits to paper

@@
 
-    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel, Matlab? (\$500))
+    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel, Matlab (\$500))
 
@@
 
-    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*i.e.*, ArcGIS standard is \$7000US)
+    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*e.g.*, ArcGIS standard is \$7000US)
 
@@
 [@Khaliq2020] have done.
-Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of chickpea ascochyta conida dispersal using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+When this level is employed, tools such as Binder,<https://mybinder.org> can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+used [-@Miorini2018, -@Miorini2019].
 
-[@Miorini2018, @Miorini2019]
-
--   Example from Grünwald lab:
+-   Example from Grünwald lab/Zhian:
 
     -   paper <http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI>
-    -   github repo <https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests>
-
-## A general workflow
+    -   github repo <https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests>/<https://github.com/zkamvar/Sudden_Oak_Death_in_Oregon_Forests>
 
@@
 The first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
-A second level involves providing raw data and code as binary files (PDF or other non-text files) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
+A second level involves providing raw data and code as binary files (PDF or other non-text files) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a paywall.
 The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
@@
 This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
-
-### Data
 
@@
 
-### Sharing your research
-
 Once you have determined how to best manage your source code for analysis and the data sets the next step is to consider how to share your data.
@@
 Readers are encouraged to avoid using lab websites and other personal pages for sharing projects over the longer term as they are fraught with link-rot and are not an optimal way to share your projects.
+
+***Need a good closing statement here.***
 

### 2021-03-12 analysis/paper/paper.Rmd
Update Adam's affiliations

@@
   - Adam H. Sparks:
-      email: Adam.Sparks@usq.edu.au
-      institute: USQ
+      email: Adam.Sparks@dpird.wa.gov.au
+      institute: DPIRD, USQ
       correspondence: true
@@
 institute:
+  - DPIRD: Department of Primary Industries and Regional Development, East Perth, Western Australia, Australia
   - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia

### 2021-03-12 analysis/paper/paper.Rmd
flesh out examples section with Kamvar et al.

@@
 
-The fourth level includes packaging the analysis as a software package, *e.g.* R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
+The fourth level includes packaging the analysis as a software package, *e.g.*, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
 [@Khaliq2020] have done.
 Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder,<https://mybinder.org> can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
 used [-@Miorini2018, -@Miorini2019].
-
--   Example from Grünwald lab/Zhian:
-
-    -   paper <http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI>
-    -   github repo <https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests>/<https://github.com/zkamvar/Sudden_Oak_Death_in_Oregon_Forests>
+Kamvar et al.
+[-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most ouptut files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
+While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
 

### 2021-03-12 analysis/paper/paper.Rmd
standardise handling of "e.g." and edit closing statement

@@
 
-A total reproducibility score was calculated as the per cent of total possible for a given paper, *e.g.* some papers did not use specialized software therefore they were not scored for this category.
+A total reproducibility score was calculated as the per cent of total possible for a given paper.
+However, some papers did not use specialized software therefore they were not scored for this category.
 
@@
 Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, *e.g.* a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
+Provide a full description of all equipment used, *e.g.*, a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
 This allows end-users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.* a package version, what effect it had on your research.
+This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on your research.
 
@@
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.* comma separated (CSV) files.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.*, comma separated (CSV) files.
 This also helps ensure that the data are reusable.
@@
 
-We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only though.
-Doing either of these leaves the work in an unstable state where future users may be unable to access the work.
+We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only are not an optimal way to preserve and share your work over the long term.
+Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
 It is a best practice to always ensure that you have deposited the data with a provider such as Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessibility.
 Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
+If readers are uncertain, we suggest to also consult with local librarians about possible resources.
+Most universities some other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
 
-Readers should also consult with their local librarians about local resources.
-Most universities provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
-
-Readers are encouraged to avoid using lab websites and other personal pages for sharing projects over the longer term as they are fraught with link-rot and are not an optimal way to share your projects.
+In this work we have evaluated the state of reproducibility in the plant pathology literature and presented suggestions for areas of improvement.
+One of the most important messages that we would like to share is that there is more to the work than just the paper.
+Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
 
@@
 
-```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._ archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
+```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
@@
 
-```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, *e.g.*, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 library("tidyr")
@@
 
-```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, *e.g.*, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%

### 2021-06-02 analysis/paper/paper.Rmd
Affiliation should just be "Perth" not "East Perth"

@@
 institute:
-  - DPIRD: Department of Primary Industries and Regional Development, East Perth, Western Australia, Australia
+  - DPIRD: Department of Primary Industries and Regional Development, Perth, Western Australia, Australia
   - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia

### 2021-06-02 R/table_of_journals.R
Fix errors when running package checks

@@ -1,11 +1,12 @@
 
 #' Create Table of Journals Surveyed
 #' @param rrpp `data.frame` of article evaluations
-#' @return \pkg{pander} table of journals surveyed
+#' @return \CRANpkg{pander} table of journals surveyed
 #' @export table_of_journals
 #'
 #' @examples
 #' \donttest{
+#' googlesheets4::gs4_deauth()
 #' rrpp <- googlesheets4::read_sheet(
 #'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"
 #')
@@ -13,8 +14,7 @@
 #' }
 #'
 table_of_journals <- function(rrpp) {
-
-rrpp_journals <- as.data.frame(table(rrpp[, 1]))
-names(rrpp_journals) <- c("Journal", "Count")
-return(pander::pander(rrpp_journals))
+  rrpp_journals <- as.data.frame(table(rrpp[, 1]))
+  names(rrpp_journals) <- c("Journal", "Count")
+  return(pander::pander(rrpp_journals))
 }

### 2021-06-02 README.rmd
Clarify directory structure in the README.md and update affiliation

@@
 
-You can download the compendium as a zip from from this URL: <https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/archive/master.zip>
+You can download the compendium as a zip from from this URL: <https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/archive/main.zip>
 
@@
 
+The file structure follows a normal R package with one exception.
+The top-level "/analysis" directory contains the directories and files necessary to reknit the MS Word document of the paper from an Rmd file, "/analysis/paper/paper.Rmd".
+
 A script, `knit_paper.R` is located in `analysis/paper/knit_paper.R` that will knit the Word document
@@
 
-Adam H Sparks, Associate Professor, Centre for Crop Health  
-University of Southern Queensland  
-Toowoomba, Queensland 4350
-
-+61 (7) 4631 1948   <adam.sparks@usq.edu.au>
+Adam H Sparks
+Senior Research Scientist
+Farming Systems Innovation
+Primary Industries Development
+Department of Primary Industries and Regional Development
+Level 5, 1 Nash St Perth WA 6000
 

### 2021-06-03 analysis/paper/paper.Rmd
Use state abbreviations for Australia

@@
 institute:
-  - DPIRD: Department of Primary Industries and Regional Development, Perth, Western Australia, Australia
-  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
+  - DPIRD: Department of Primary Industries and Regional Development, Perth, WA, Australia
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld, Australia
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil

### 2021-06-10 analysis/paper/paper.Rmd
adding comments to rmd

@@
 
+<!--# not sure we need a separate section for definitions, but presence continuously in the text -->
+
 ## Definitions
@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research is recently highlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
+For instance, reproducible research is recently highlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013; ]
+
+<!--# These references above are all prior 2017. We may want to update the list? -->
+
+as an important issue.
 The International Union of Pure and Applied Chemistry provides definitions of repeatability in the "Compendium of Chemical Terminology -- Gold Book" as:
@@
 Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@McNaught1997].
+
+<!--# I would simplify and just mention the Peng's definition as most appropriate for our context -->
 
@@
 In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
+
+<!--# I am leaning towards a sytle that shows the methods at the end in a separate section? -->
 
@@
 We have based our scoring decisions on our own experiences in the field of plant pathology.
-While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
+While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
 Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
@@
 When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
-used [-@Miorini2018, -@Miorini2019].
+used [-@Miorini2018, [-@Miorini2019]].
 Kamvar et al.

### 2021-06-10 analysis/paper/paper.Rmd
edits and comments in the manuscript

@@
 
-# Introduction
-
 Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
@@
 Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of the methods and results.
-These research findings include biological materials (isolates or strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated as a course of conducting research.
+These research findings include biological materials (host and pathogen genotypes), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated during the course of the research.
 
@@
 
-While open science and reproducibility are not the same, they are linked.
-By proactively practising open science, the work becomes more reproducible through the availability of data and code.
+## What is reproducibility?
+
+Reproducibility is one component under the umbrella of open science.
+By proactively practising open science, the work increases the chance to become more reproducible through the availability of data and code.
 That is, open science leads to reproducibility and replicability.
 
-<!--# not sure we need a separate section for definitions, but presence continuously in the text -->
-
-## Definitions
+<!--# not sure we need a separate section for definitions, but present continuously in the text -->
 
@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research is recently highlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013; ]
+For instance, reproducible research is recently highlighted by many authors[@preeyanon2018; @Wallach2018] [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013; ]
 
-<!--# These references above are all prior 2017. We may want to update the list? -->
+<!--# These references above are all prior 2017. We may want to update the list? I've added two using insert citation tool of the visual editor rmarkdown -->
 
@@
 
-In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
-
 <!--# I am leaning towards a sytle that shows the methods at the end in a separate section? -->
 
-# Materials and methods
+## Where do we stand in regards to reproducibility?
 
-## Article Selection
-
+In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
 We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
-The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
-A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
-In cases where an article was not suitable, *e.g.*, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
-Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
-The pages list was numbered from page one and went to page 150.
-This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
-The list of journals was saved from Google's sheets as a comma-separated-value (CSV) file for later use and distribution in a research compendium.
-
-## Scoring criteria
-
-Four individuals were assigned to rate a randomised list of journal articles.
-
-Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
-The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as a CSV file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
-
-Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
-This classification was based on the evaluator's judgement of the article.
-
-Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
-
-Articles were scored in four areas for reproducibility on a scale of 0 to 3:
-
--   **computational methods available**
-
-    -   0 - Not available or not mentioned in the publication
-
-    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*i.e.*, ArcGIS standard is \$7000)
-
-    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel, Matlab (\$500))
-
-    -   3 - Uses entirely open source and free software (*e.g.*, R, Julia, Python)
-
-    -   NA - No software was used in the research that can be determined as the article is written
-
--   **software available**
-
-    -   0 - Not available or not mentioned in the publication
-
-    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*e.g.*, ArcGIS standard is \$7000US)
-
-    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel) or SAS that is now available free for use with a university login
-
-    -   3 - Uses entirely open source and free software (*e.g.*, R, Julia, Python).
-
-    -   NA - No software was used in the research that can be determined as the article is written
-
--   **software cited**
-
-    -   0 - not mentioned
-
-    -   1 - Software mentioned by name only
-
-    -   2 - Software cited with version number
-
-    -   3 - All software components (SAS PROCs, R, Julia or Python packages) etc., cited
-
-    -   NA - No software was used in the research that can be determined as the article is written.
-
--   **data available**
-
-    -   0 - Not available or not mentioned in the publication
-
-    -   1 - Available upon request to the author
-
-    -   2 - Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)
-
-    -   3 - Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system)
-
-Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
-When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
-
-A total reproducibility score was calculated as the per cent of total possible for a given paper.
-However, some papers did not use specialized software therefore they were not scored for this category.
-
-We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
-We have based our scoring decisions on our own experiences in the field of plant pathology.
-While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
-Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
-The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
-
-## Statistical analysis
-
-Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
-
-Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.
-
-The random effects were year and assignee for all models excepting the model which tested for year effects.
-In this model, the random effects were the publication title and assignee.
-
-Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data.
-Each model was run for 3000 iterations in four chains.
-
-The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
-
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].
-
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].
-
-# Results
+The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications (See appendix for details on the methodology).
 
@@
 One article scored 100% or was classed as fully reproducible.
-
-No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
-
-The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
+No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
 
@@
 
-# Discussion
-
 Unfortunately using our scoring method, most articles scored poorly for reproducibility or openness.
@@
 It is interesting to note however, that with the popularity of Python that it does not even appear in our survey results whereas R was the fourth most commonly used software.
+
+## Are there good examples in the field?
 
@@
 At the second level, Lehner et al.
-[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
+[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([<https://emdelponte.github.io/paper-white-mold-meta-analysis/>](https://emdelponte.github.io/paper-white-mold-meta-analysis/){.uri}).
 The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work.
 Likewise, Duku et al.
-[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [<http://adamhsparks.github.io/MICCORDEA/>](http://adamhsparks.github.io/MICCORDEA/){.uri}, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
 
@@
 Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+When this level is employed, tools such as Binder, [<https://mybinder.org>](https://mybinder.org){.uri}, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
 used [-@Miorini2018, [-@Miorini2019]].
@@
 While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
+
+## Best practices to enhance reproducible research
 
@@
 To make your data the most widely usable, ensure that it has a persistent identifier.
-A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but handle is also an option (<https://handle.net/>).
+A digital object identifier (DOI) is the most common ([<https://www.doi.org/>](https://www.doi.org/){.uri}) but handle is also an option ([<https://handle.net/>](https://handle.net/){.uri}).
 There are different options for generating a DOI for your data and other materials.
@@
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
-For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.
+For more on FAIR data, visit Go-Fair [<https://www.go-fair.org/fair-principles/>](https://www.go-fair.org/fair-principles/){.uri}.
 
@@
 Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
+
+# Appendix
+
+## Article Selection
+
+We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
+The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
+In cases where an article was not suitable, *e.g.*, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
+The pages list was numbered from page one and went to page 150.
+This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
+The list of journals was saved from Google's sheets as a comma-separated-value (CSV) file for later use and distribution in a research compendium.
+
+## Scoring criteria
+
+Four individuals were assigned to rate a randomised list of journal articles.
+
+Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
+The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
+This was downloaded, saved as a CSV file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
+
+Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
+This classification was based on the evaluator's judgement of the article.
+
+Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
+
+<!--# I would prefer a table for the scores, but if this is to be shown in a appendix, it could stay as it is -->
+
+Articles were scored in four areas for reproducibility on a scale of 0 to 3:
+
+-   **computational methods available**
+
+    -   0 - Not available or not mentioned in the publication
+
+    -   1 - Uses <!--# should we use past tense or just "expensive .." --> expensive proprietary software that only institutions would typically purchase
+
+    -   <!--# suggest to remove the average prices -->
+
+    -   2 - Proprietary software that most individuals can afford (*e.g.*, Excel)
+
+    -   3 - Entirely open source and free software (*e.g.*, R, Julia, Python)
+
+    -   NA - No software was used in the research that can be determined
+
+-   **software available**
+
+    -   0 - Not available or not mentioned in the publication
+
+    -   1 - Expensive proprietary software that only institutions would typically purchase
+
+    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel) or SAS that is now available free for use with a university login
+
+    -   3 - Uses entirely open source and free software (*e.g.*, R, Julia, Python).
+
+    -   NA - No software was used in the research that can be determined
+
+-   **software cited**
+
+    -   0 - not mentioned
+
+    -   1 - Software mentioned by name only
+
+    -   2 - Software cited with version number
+
+    -   3 - All software components (SAS PROCs, R, Julia or Python packages) etc., cited
+
+    -   NA - No software was used in the research that can be determined as the article is written.
+
+-   **data available**
+
+    -   0 - Not available or not mentioned in the publication
+
+    -   1 - Available upon request to the author
+
+    -   2 - Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)
+
+    -   3 - Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or University library or some other proper archiving system)
+
+Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
+When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
+A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+
+A total reproducibility score was calculated as the per cent of total possible for a given paper.
+However, some papers did not use specialized software therefore they were not scored for this category.
+
+We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
+We have based our scoring decisions on our own experiences in the field of plant pathology.
+While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
+Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
+The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
+
+## Statistical analysis
+
+Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+
+Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.
+
+The random effects were year and assignee for all models excepting the model which tested for year effects.
+In this model, the random effects were the publication title and assignee.
+
+Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data.
+Each model was run for 3000 iterations in four chains.
+
+The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
+
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].
+
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].
 

### 2021-06-11 analysis/paper/paper.Rmd
Spell-check

@@
 
-<!--# I am leaning towards a sytle that shows the methods at the end in a separate section? -->
+<!--# I am leaning towards a style that shows the methods at the end in a separate section? -->
 
@@
 Kamvar et al.
-[-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most ouptut files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
+[-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
 While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

### 2021-06-11 R/data.R
Include a data frame of scoring criteria for table in paper

@@ -1,0 +1,12 @@
+#' Scoring criteria
+#'
+#' The scoring criteria used for scoring articles on reproducibility.
+#'
+#' @format A data frame with 19 rows and three variables:
+#' \describe{
+#'   \item{Category}{Scoring criterion category}
+#'   \item{Index Value}{The index score assigned}
+#'   \item{Definition}{Definition of the criteria used to assign an index value
+#'    score for an article in each category}
+#' }
+"scoring_criteria"

### 2021-06-11 analysis/paper/paper.Rmd
Replace *e.g.* with _e.g._

@@
 
-However, while these definitions are clear and well accepted in physical sciences, in biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, *e.g.*, field trials that span years and locations or complex glasshouse experiments.
+However, while these definitions are clear and well accepted in physical sciences, in biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
 Therefore we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":
@@
 
-The fourth level includes packaging the analysis as a software package, *e.g.*, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
+The fourth level includes packaging the analysis as a software package, _e.g._, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
 [@Khaliq2020] have done.
@@
 Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, *e.g.*, a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
+Provide a full description of all equipment used, _e.g._, a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
 This allows end-users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on your research.
+This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, _e.g._, a package version, what effect it had on your research.
 
@@
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.*, comma separated (CSV) files.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._, comma separated (CSV) files.
 This also helps ensure that the data are reusable.
@@
 A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
-In cases where an article was not suitable, *e.g.*, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
 Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
@@
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
-The list of journals was saved from Google's sheets as a comma-separated-value (CSV) file for later use and distribution in a research compendium.
+The list of journals was saved from Google's 'Sheets' as a comma-separated-value (CSV) file for later use and distribution in a research compendium.
 
@@
 
-Four individuals were assigned to rate a randomised list of journal articles.
+Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table @\ref(tab:scoring)).
 

### 2021-06-11 analysis/paper/paper.Rmd
Move criteria score to table

@@
 
-<!--# I would prefer a table for the scores, but if this is to be shown in a appendix, it could stay as it is -->
-
-Articles were scored in four areas for reproducibility on a scale of 0 to 3:
-
--   **computational methods available**
-
-    -   0 - Not available or not mentioned in the publication
-
-    -   1 - Uses <!--# should we use past tense or just "expensive .." --> expensive proprietary software that only institutions would typically purchase
-
-    -   <!--# suggest to remove the average prices -->
-
-    -   2 - Proprietary software that most individuals can afford (*e.g.*, Excel)
-
-    -   3 - Entirely open source and free software (*e.g.*, R, Julia, Python)
-
-    -   NA - No software was used in the research that can be determined
-
--   **software available**
-
-    -   0 - Not available or not mentioned in the publication
-
-    -   1 - Expensive proprietary software that only institutions would typically purchase
-
-    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel) or SAS that is now available free for use with a university login
-
-    -   3 - Uses entirely open source and free software (*e.g.*, R, Julia, Python).
-
-    -   NA - No software was used in the research that can be determined
-
--   **software cited**
-
-    -   0 - not mentioned
-
-    -   1 - Software mentioned by name only
-
-    -   2 - Software cited with version number
-
-    -   3 - All software components (SAS PROCs, R, Julia or Python packages) etc., cited
-
-    -   NA - No software was used in the research that can be determined as the article is written.
-
--   **data available**
-
-    -   0 - Not available or not mentioned in the publication
-
-    -   1 - Available upon request to the author
-
-    -   2 - Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)
-
-    -   3 - Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or University library or some other proper archiving system)
-
 Values for software packages were checked for spelling consistency and corrections were made manually where necessary.

### 2021-06-11 analysis/paper/paper.Rmd
Rework table displays and add new table for scoring criteria

@@
   select(-percent) %>%
+  rename(Journal = journal) %>% 
   flextable() %>%
+  colformat_num(na_str = "NA") %>% 
   autofit()
+```
+
+\newpage
+
+```{r scoring, tab.id="scoring", tab.cap ="Articles were scored in four areas for reproducibility on a scale of 0 to 3 by four independent assessors.", echo=FALSE, message=FALSE, warning=FALSE}
+scoring_criteria %>% 
+  rename(`Index Value` = Index.Value) %>% 
+  flextable() %>% 
+  colformat_num(na_str = "NA") %>% 
+  set_table_properties(layout = "autofit")
 ```
@@
   adorn_pct_formatting() %>% 
-  select(-percent) %>% 
-  rename(`software availability` = software_avail,
-         percent = valid_percent) %>% 
+  select(-valid_percent) %>% 
+  rename(`Software Availability` = software_avail,
+         Percent = percent) %>% 
   flextable() %>%
+  colformat_num(na_str = "NA") %>% 
   autofit()
@@
   adorn_pct_formatting() %>% 
-  select(-percent) %>% 
-  rename(`software citation` = software_cite,
-         percent = valid_percent) %>% 
+  select(-valid_percent) %>% 
+  rename(`Software citation` = software_cite,
+         Percent = percent) %>% 
   flextable() %>%
+  colformat_num(na_str = "NA") %>% 
   autofit()
@@
 
-```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
+```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
@@
   select(-percent) %>% 
-  rename(`data availability` = data_avail,
-         percent = valid_percent) %>% 
+  rename(`Data availability` = data_avail,
+         Percent = valid_percent) %>% 
   flextable() %>%
+  colformat_num(na_str = "NA") %>% 
   autofit()
@@
 
-```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, *e.g.*, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 library("tidyr")
@@
 
-```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, *e.g.*, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%

### 2021-06-11 analysis/paper/paper.Rmd
Add figure as requested by @emdelponte of aggregated scores

@@
 
+```{r article_scores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Aggregated article scores for each of the four categories.
+In subfigure `a`, `NA` indicates that no computational methods were used to generate the data, _e.g._ only PCR results were reported with no statistical analysis performed.', cache=FALSE, fig.env='figure'}
+library("ggplot2")
+library("patchwork")
+rrpp <- import_notes()
+theme_set(theme_classic())
+a <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
+  geom_bar() +
+  ggtitle("Computational Methods Availability") +
+  ylab("Score") +
+  xlab(NULL)
+
+b <- ggplot(rrpp, aes(y = software_avail)) +
+  geom_bar() +
+  ggtitle("Software Availability") +
+  xlab(NULL) +
+  ylab(NULL)
+
+c <- ggplot(rrpp, aes(y = software_cite)) +
+  geom_bar() +
+  ggtitle("Software Cited") +
+  ylab("Score")
+
+d <- ggplot(rrpp, aes(y = data_avail)) +
+  geom_bar() +
+  ggtitle("Data Availability") +
+  ylab(NULL)
+
+# put them all together
+p <- (a | b) / (c | d)
+p + plot_annotation(tag_levels = "a")
+```
+
+\newpage
+
 # Colophon

### 2021-06-11 analysis/paper/paper.Rmd
Clean up table formatting, digits, caps, etc.

@@
   adorn_pct_formatting() %>% 
-  select(-percent) %>% 
+  select(-valid_percent) %>% 
   rename(`Data availability` = data_avail,
-         Percent = valid_percent) %>% 
+         Percent = percent) %>% 
   flextable() %>%
@@
   select(c(-percent, -valid_percent)) %>% 
-  rename(`software used` = software_used) %>% 
+  rename(`Software Used` = software_used) %>% 
   arrange(-n) %>% 
@@
   tabyl(reproducibility_score) %>%
-  adorn_pct_formatting() %>%
-  rename(score = reproducibility_score) %>%
+  adorn_pct_formatting(digits = 1) %>%
+  rename(Score = reproducibility_score, Percent = percent) %>%
   flextable() %>%

### 2021-06-12 analysis/paper/paper.Rmd
Add statement about computer and R version used

@@
 Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
-When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].
+When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
+A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
 
@@
 
-Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
+Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
 
@@
 # which R packages and versions?
-sessionInfo()
+sessioninfo::session_info()
 ```

### 2021-06-12 analysis/paper/paper.Rmd
Correct spelling of "conidia"

@@
 [@Khaliq2020] have done.
-Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
 When this level is employed, tools such as Binder, [<https://mybinder.org>](https://mybinder.org){.uri}, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.

### 2021-06-12 R/data.R
Fix an error about data mismatch with docs

@@ -5,7 +5,7 @@
 #' @format A data frame with 19 rows and three variables:
 #' \describe{
 #'   \item{Category}{Scoring criterion category}
-#'   \item{Index Value}{The index score assigned}
+#'   \item{Index.Value}{The index score assigned}
 #'   \item{Definition}{Definition of the criteria used to assign an index value
 #'    score for an article in each category}
 #' }

### 2021-06-14 README.rmd
Update Docker instructions
Fix grammar in README

@@
 
-```
+```bash
 docker pull adamhsparks/reproducibility_in_plant_pathology
-docker run -d -p 8787:8787
+docker run -d -p 8787:8787 adamhsparks/reproducibility_in_plant_pathology
 ```
@@
 The file structure follows a normal R package with one exception.
-The top-level "/analysis" directory contains the directories and files necessary to reknit the MS Word document of the paper from an Rmd file, "/analysis/paper/paper.Rmd".
+The top-level "/analysis" directory contains the directories and files necessary to re-knit the MS Word document of the paper from an Rmd file, "/analysis/paper/paper.Rmd".
 
-A script, `knit_paper.R` is located in `analysis/paper/knit_paper.R` that will knit the Word document
+A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document.
 

### 2021-06-14 analysis/paper/paper.Rmd
Add statements of data and code availability

@@
 
-***Need a good closing statement here.***
-
 # Authors' contributions
@@
 # Data availability statement
+
+The raw data for this work are documented and available from DOI [https://doi.org/10.5281/zenodo.4941722](10.5281/zenodo.4941722).
+
+# Code availability statement
+
+All code used in the analyses and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
+A browsable webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.
 

### 2021-06-14 analysis/paper/paper.Rmd
wordsmith closing statement

@@
 One of the most important messages that we would like to share is that there is more to the work than just the paper.
-Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
+Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed and often leads to greater impact than for works that do not share data and or code.
+With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
 

### 2021-06-14 analysis/paper/paper.Rmd
edit compendium availability statement
Add statement of contributions

@@
 # Authors' contributions
+A.H.S, E.DP, Z.F. and N.J.G. conceived of the presented idea and scoring system.
+N.J.G. provided five-year impact factors.
+A.H.S, E.DP, Z.F. and K.dSA evaluated articles for scoring.
+A.H.S. designed the computational framework with feedback from E.DP and Z.F.
+A.H.S wrote the manuscript in consultation with E.DP.
+All authors provided critical feedback and helped contribute to the final version of the manuscript.
 
@@
 All code used in the analyses and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
-A browsable webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.
+A webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.
 

### 2021-06-14 analysis/paper/paper.Rmd
Full stop after Nik's middle initial

@@
       institute: OSU
-  - Niklaus J Grünwald: 
+  - Niklaus J. Grünwald: 
       institute: ARS

### 2021-06-14 analysis/paper/paper.Rmd
clarify priors
comment out last line of author contributions until have feedback from all

@@
 
-Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.
+Relatively flat priors were selected with a mean of 0 and a standard deviation of 10 for the fixed effects.
 
@@
 # Authors' contributions
+
 A.H.S, E.DP, Z.F. and N.J.G. conceived of the presented idea and scoring system.
@@
 A.H.S wrote the manuscript in consultation with E.DP.
-All authors provided critical feedback and helped contribute to the final version of the manuscript.
+<!-- All authors provided critical feedback and helped contribute to the final version of the manuscript. -->
 

### 2021-06-14 analysis/paper/paper.Rmd
Full stops after initials and clarify contributions further

@@
 
-A.H.S, E.DP, Z.F. and N.J.G. conceived of the presented idea and scoring system.
+A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
 N.J.G. provided five-year impact factors.
-A.H.S, E.DP, Z.F. and K.dSA evaluated articles for scoring.
-A.H.S. designed the computational framework with feedback from E.DP and Z.F.
-A.H.S wrote the manuscript in consultation with E.DP.
+A.H.S., E.DP., Z.F. and K.dSA. evaluated articles for scoring.
+A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
+A.H.S. wrote the manuscript in consultation with E.DP.
 <!-- All authors provided critical feedback and helped contribute to the final version of the manuscript. -->

### 2021-06-14 R/import_notes.R
Use ODS file in place of CSV files

@@ -24,18 +24,20 @@ import_notes <- function() {
     art_class <- repro_inst <- abbreviation <- assignee <-
     reproducibility_score <- journal <- year <- . <- NULL
 
-  notes <- readr::read_csv(
+  notes <- readODS::read_ods(
     system.file("extdata",
-                "article_notes.csv",
+                "Reproducibility_in_plant_pathology_notes.ods",
                 package = "Reproducibility.in.Plant.Pathology"),
-    na = "NA"
+    na = "NA",
+    sheet = "article_evaluations"
   )
 
-  IF_5year <- readr::read_csv(
+  IF_5year <- readODS::read_ods(
     system.file("extdata",
-                "2018_5-year_IF.csv",
+                "Reproducibility_in_plant_pathology_notes.ods",
                 package = "Reproducibility.in.Plant.Pathology"),
-    na = "NA"
+    na = "NA",
+    sheet = 4
   )
 
   notes <-

### 2021-06-14 R/import_notes.R
Redoc fixing title caps

@@ -1,12 +1,12 @@
 
-#' Import Reproducibility Score Notes
+#' Import reproducibility score notes
 #'
 #' Imports, formats data into proper types and calculates the final
-#'  reproducibility score. Also adds the 2 and 5 year impact factor values from
-#'  InCites Journal Citation Reports for 2018.
+#' reproducibility score. Also adds the 2 and 5 year impact factor values from
+#' InCites Journal Citation Reports for 2018.
 #'
 #' @return A `tibble` object of reproducibility score notes formatted for use in
-#'  analysis and manuscript preparation
+#' analysis and manuscript preparation
 #' @export import_notes
 #'
 #' @examples

### 2021-06-14 R/table_of_journals.R

@@ -1,5 +1,5 @@
 
-#' Create Table of Journals Surveyed
+#' Create table of journals surveyed
 #' @param rrpp `data.frame` of article evaluations
 #' @return \CRANpkg{pander} table of journals surveyed
 #' @export table_of_journals

### 2021-06-14 R/workflow_dia.R

@@ -1,5 +1,7 @@
 
-#' Create Workflow Diagram Figure
+#' Create workflow diagram figure
+#'
+#' Custom function to create a workflow diagram figure, 'Figure 1'.
 #'
 #' @return PDF of workflow diagram
 #' @export workflow_dia
@@ -38,8 +40,9 @@ workflow_dia <- function() {
     Analysis->'Source Code'->'Public Repository'
     Data->'Binary File'->Supplement
   }",
-      width = 1000,
-      height = 750
-    ))
+  width = 1000,
+  height = 750
+    )
+  )
   return(rsvg::rsvg_pdf(charToRaw(p)))
 }

### 2021-06-14 analysis/paper/paper.Rmd
Fixes citations on line 85

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research is recently highlighted by many authors[@preeyanon2018; @Wallach2018] [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013; ]
+For instance, reproducible research is recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013; ]
 

### 2021-06-14 analysis/paper/paper.Rmd
Take Emerson's suggestion and only use Peng's definition

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research is recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013; ]
+For instance, reproducible research is recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013;] as an important issue.
 
@@
 
-as an important issue.
-The International Union of Pure and Applied Chemistry provides definitions of repeatability in the "Compendium of Chemical Terminology -- Gold Book" as:
-
-> "The closeness of agreement between independent results obtained with the same method on identical test material, under the same conditions (same operator, same apparatus, same laboratory and after short intervals of time).
-The measure of repeatability is the standard deviation qualified with the term: \`repeatability' as repeatability standard deviation.
-In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@McNaught1997].
-
-and reproducibility is defined as:
-
-> "The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time).
-The measure of reproducibility is the standard deviation qualified with the term 'reproducibility' as reproducibility standard deviation.
-In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability.
-Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@McNaught1997].
-
-<!--# I would simplify and just mention the Peng's definition as most appropriate for our context -->
-
-However, while these definitions are clear and well accepted in physical sciences, in biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
+In biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
 Therefore we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":

### 2021-06-14 analysis/paper/paper.Rmd
Fix link formatting

@@
 At the second level, Lehner et al.
-[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([<https://emdelponte.github.io/paper-white-mold-meta-analysis/>](https://emdelponte.github.io/paper-white-mold-meta-analysis/){.uri}).
+[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
 The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work.
 Likewise, Duku et al.
-[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [<http://adamhsparks.github.io/MICCORDEA/>](http://adamhsparks.github.io/MICCORDEA/){.uri}, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
 
@@
 
-The fourth level includes packaging the analysis as a software package, _e.g._, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
+The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
 [@Khaliq2020] have done.
 Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder, [<https://mybinder.org>](https://mybinder.org){.uri}, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
 used [-@Miorini2018, [-@Miorini2019]].
@@
 To make your data the most widely usable, ensure that it has a persistent identifier.
-A digital object identifier (DOI) is the most common ([<https://www.doi.org/>](https://www.doi.org/){.uri}) but handle is also an option ([<https://handle.net/>](https://handle.net/){.uri}).
+A digital object identifier (DOI) is the most common ([https://www.doi.org/](https://www.doi.org/)) but handle is also an option ([https://handle.net/](https://handle.net/)).
 There are different options for generating a DOI for your data and other materials.
@@
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
-For more on FAIR data, visit Go-Fair [<https://www.go-fair.org/fair-principles/>](https://www.go-fair.org/fair-principles/){.uri}.
+For more on FAIR data, visit Go-Fair [https://www.go-fair.org/fair-principles/](https://www.go-fair.org/fair-principles/).
 

### 2021-06-14 analysis/paper/paper.Rmd
deletes an errant space
Revise CSV to ODS

@@
 The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as a CSV file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
+This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
 

### 2021-06-14 analysis/paper/paper.Rmd
Add name of file with notes on articles
Remove reference to list of files, it's all in the ODS file

@@
 In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
-Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
+Notes regarding the selection of articles can be found in the file, "Reproducibility_in_plant_pathology_notes.ods", available in this paper's repository in `/inst/extdata'.
 The pages list was numbered from page one and went to page 150.
@@
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
-The list of journals was saved from Google's 'Sheets' as a comma-separated-value (CSV) file for later use and distribution in a research compendium.
 

### 2021-06-14 analysis/paper/paper.Rmd
Simplify reference to `import_notes()`

@@
 When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
+A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
 

### 2021-06-14 analysis/paper/paper.Rmd
Delete Emerson's comment, as I agree and it's implemented
Use "_" not "*" for italics

@@
 
-<!--# I am leaning towards a style that shows the methods at the end in a separate section? -->
-
 ## Where do we stand in regards to reproducibility?
@@
 The first level is including tables of raw data or code with the paper as a supplemental file.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden et al.
-[-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra*\* with reproducible examples for readers to refer to.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden _et al._ [-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an _e-**X**tra_\* with reproducible examples for readers to refer to.
 This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
 
-At the second level, Lehner et al.
-[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
+At the second level, Lehner _et al._ [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
 The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work.
-Likewise, Duku et al.
-[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+Likewise, Duku _et al._ [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
 
 The third level is the use of proper data repositories such as FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
-Sparks et al.
-[-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+Sparks _et al._ [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
 
-The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
-[@Khaliq2020] have done.
-Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
-used [-@Miorini2018, [-@Miorini2019]].
-Kamvar et al.
-[-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
+The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq _et al._ [@Khaliq2020] have done.
+Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of _Ascochyta rabiei_ conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni _et al._ used [-@Miorini2018, [-@Miorini2019]].
+Kamvar _et al._ [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
 While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

### 2021-06-14 analysis/paper/paper.Rmd
Each sentence on it's own line
evaluate library using standard evaluation
Replace tables with four-panel figure

@@
 
-library(Reproducibility.in.Plant.Pathology)
+library("Reproducibility.in.Plant.Pathology")
 ```
@@
 
-Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available.
+Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available (Figure \@ref(fig:article-scores)a).
 Two hundred eighty-seven articles, 96%, were classed as "0" and nine articles, 0.03%, appeared to not use any computational methods.
 
-Likewise, data availability was mostly not available with 243 or 81.5% scoring "0" where the data was not available or mentioned in the article.
-However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Table \@ref(tab:da)).
+More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Figure  \@ref(fig:article-scores)b).
 
-More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Table \@ref(tab:sa)).
+Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:article-scores)c).
 
-Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Table \@ref(tab:sc)).
+However, data availability was mostly not available with 243 or 81.5% scoring "0" where the data was not available or mentioned in the article.
+However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Figure  \@ref(fig:article-scores)d).
 
@@
 
-```{r scoring, tab.id="scoring", tab.cap ="Articles were scored in four areas for reproducibility on a scale of 0 to 3 by four independent assessors.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r scoring, tab.id="scoring", tab.cap ="Articles were scored in four areas for reproducibility on a scale of '0' to '3' by four independent assessors to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.", echo=FALSE, message=FALSE, warning=FALSE}
 scoring_criteria %>% 
@@
 
-```{r software_avail, tab.id="sa", tab.cap="Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available.", echo=FALSE, message=FALSE, warning=FALSE}
-import_notes() %>%
-  tabyl(software_avail) %>%
-  adorn_pct_formatting() %>% 
-  select(-valid_percent) %>% 
-  rename(`Software Availability` = software_avail,
-         Percent = percent) %>% 
-  flextable() %>%
-  colformat_num(na_str = "NA") %>% 
-  autofit()
-```
-
-\newpage
-
-```{r software_cite, tab.id="sc", tab.cap="Article ratings for software citations where '0', not specified or mentioned in publication to '3', fully cited with proper version numbers and all procedures detailed.", echo=FALSE, message=FALSE, warning=FALSE}
-import_notes() %>%
-  tabyl(software_cite) %>%
-  adorn_pct_formatting() %>% 
-  select(-valid_percent) %>% 
-  rename(`Software citation` = software_cite,
-         Percent = percent) %>% 
-  flextable() %>%
-  colformat_num(na_str = "NA") %>% 
-  autofit()
-```
-
-\newpage
-
-```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
-import_notes() %>%
-  tabyl(data_avail) %>%
-  adorn_pct_formatting() %>% 
-  select(-valid_percent) %>% 
-  rename(`Data availability` = data_avail,
-         Percent = percent) %>% 
-  flextable() %>%
-  colformat_num(na_str = "NA") %>% 
-  autofit()
-```
-
-\newpage
-
-```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r software_used, tab.id="su", tab.cap="The top ten sofware programs that were found to be used in the papers that were surveyed.", echo=FALSE, message=FALSE, warning=FALSE}
 library("tidyr")
@@
 
-```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
@@
   rename(Score = reproducibility_score, Percent = percent) %>%
+  mutate(Score = round(Score, digits = 1)) %>% 
   flextable() %>%
@@
 
-```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An open and reproducible research workflow.', cache=FALSE, fig.env='figure'}
+<!-- @Emerson, can you please have a look at this caption, if I'm not mistaken, this is your diagram design. Can you confirm that what I've written is accurate and describes the workflow? -->
+
+```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example open and reproducible research workflow.
+Starting with the question, determine the methodology, describe it, make it available and cite it.
+Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
+Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time and a DOI for final released products.', cache=FALSE, fig.env='figure'}
 library("DiagrammeR")
@@
 
-```{r article_scores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Aggregated article scores for each of the four categories.
-In subfigure `a`, `NA` indicates that no computational methods were used to generate the data, _e.g._ only PCR results were reported with no statistical analysis performed.', cache=FALSE, fig.env='figure'}
+```{r article-scores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, a), computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
+b) Shows 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+c) Displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
+d) Shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, _e.g._ a methods paper.", cache=FALSE, fig.env='figure'}
 library("ggplot2")

### 2021-06-15 analysis/paper/paper.Rmd
Replace TPP with APS csl styles

@@
 bibliography: references.bib
-csl: "../templates/TPP.csl" # Insert path for the bib-style
+csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
 abstract: |

### 2021-06-15 analysis/paper/paper.Rmd
Replace TPP reference with proper reference

@@
 
-Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@TPP2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
+Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
 

### 2021-06-15 analysis/paper/paper.Rmd
retitle using Emerson's suggestion
Update text for Handle.Net

@@
 ---
-title: "Insights Into Computational Reproducibility in Plant Pathology and a Way Forward"
+title: "Reproducibility and plant pathology: where do we stand and a way forward"
 author:
@@
 In turn, sharing data will lead to new citations for your work as others discover and use it.
-
-To make your data the most widely usable, ensure that it has a persistent identifier.
-A digital object identifier (DOI) is the most common ([https://www.doi.org/](https://www.doi.org/)) but handle is also an option ([https://handle.net/](https://handle.net/)).
+To make your data the most widely discoverable and usable, ensure that it has a persistent identifier.
+A digital object identifier (DOI) is the most common ([https://www.doi.org/](https://www.doi.org/)) but the Handle.Net Registry (HNR) ([https://handle.net/](https://handle.net/)) is also an option.
 There are different options for generating a DOI for your data and other materials.

### 2021-06-15 analysis/paper/paper.Rmd
Fix table reference to scoring criteria

@@
 
-Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table @\ref(tab:scoring)).
+Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)).
 

### 2021-06-15 analysis/paper/paper.Rmd
Reorder tables so they appear in the order as in text
Remove section separator for reproduciblity
Label sequential items following APS guidelines

@@
 
-## What is reproducibility?
-
 Reproducibility is one component under the umbrella of open science.
@@
 
-Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available (Figure \@ref(fig:article-scores)a).
+Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available (Figure \@ref(fig:article-scores)i).
 Two hundred eighty-seven articles, 96%, were classed as "0" and nine articles, 0.03%, appeared to not use any computational methods.
 
-More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Figure  \@ref(fig:article-scores)b).
+More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Figure  \@ref(fig:article-scores)ii).
 
-Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:article-scores)c).
+Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:article-scores)iii).
 
 However, data availability was mostly not available with 243 or 81.5% scoring "0" where the data was not available or mentioned in the article.
-However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Figure  \@ref(fig:article-scores)d).
+However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Figure  \@ref(fig:article-scores)iv).
 
@@
 
-```{r scoring, tab.id="scoring", tab.cap ="Articles were scored in four areas for reproducibility on a scale of '0' to '3' by four independent assessors to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.", echo=FALSE, message=FALSE, warning=FALSE}
-scoring_criteria %>% 
-  rename(`Index Value` = Index.Value) %>% 
-  flextable() %>% 
-  colformat_num(na_str = "NA") %>% 
-  set_table_properties(layout = "autofit")
-```
-
-\newpage
-
 ```{r software_used, tab.id="su", tab.cap="The top ten sofware programs that were found to be used in the papers that were surveyed.", echo=FALSE, message=FALSE, warning=FALSE}
@@
   autofit()
+```
+
+\newpage
+
+```{r scoring, tab.id="scoring", tab.cap ="Articles were scored in four areas for reproducibility on a scale of '0' to '3' by four independent assessors to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.", echo=FALSE, message=FALSE, warning=FALSE}
+scoring_criteria %>% 
+  rename(`Index Value` = Index.Value) %>% 
+  flextable() %>% 
+  colformat_num(na_str = "NA") %>% 
+  set_table_properties(layout = "autofit")
 ```
@@
 
-```{r article-scores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, a), computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
-b) Shows 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-c) Displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-d) Shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, _e.g._ a methods paper.", cache=FALSE, fig.env='figure'}
+```{r article-scores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i), computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
+(ii) Shows 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+(iii) Displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
+(iv) Shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, _e.g._ a methods paper.", cache=FALSE, fig.env='figure'}
 library("ggplot2")
@@
 theme_set(theme_classic())
-a <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
+i <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
   geom_bar() +
@@
 
-b <- ggplot(rrpp, aes(y = software_avail)) +
+ii <- ggplot(rrpp, aes(y = software_avail)) +
   geom_bar() +
@@
 
-c <- ggplot(rrpp, aes(y = software_cite)) +
+iii <- ggplot(rrpp, aes(y = software_cite)) +
   geom_bar() +
@@
 
-d <- ggplot(rrpp, aes(y = data_avail)) +
+iv <- ggplot(rrpp, aes(y = data_avail)) +
   geom_bar() +
@@
 # put them all together
-p <- (a | b) / (c | d)
-p + plot_annotation(tag_levels = "a")
+p <- (i | ii) / (iii | iv)
+p + plot_annotation(tag_levels = "i")
 ```

### 2021-06-15 analysis/paper/paper.Rmd
Fix citation tags

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research is recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013;] as an important issue.
+For instance, reproducible research is recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
 

### 2021-06-15 analysis/paper/paper.Rmd
Update affiliation, output PDF, export .eps figures when knit

@@
 institute:
-  - DPIRD: Department of Primary Industries and Regional Development, Perth, WA, Australia
-  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld, Australia
+  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
@@
 output: 
-  officedown::rdocx_document:
-      fig_caption: yes
-      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
+# Uncomment from line 25 to 45 and comment 46 to line 54 for Word output
+# Comment from line 25 to 45 and uncomment 46 to line 54 for LaTeX output
+#  officedown::rdocx_document:
+#      fig_caption: yes
+#      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
+#      pandoc_args:
+#        - '--lua-filter=scholarly-metadata.lua'
+#        - '--lua-filter=author-info-blocks.lua'
+#        - '--lua-filter=pagebreak.lua'
+#      tables:
+#        layout: autofit
+#        width: 1.0
+#        caption:
+#          style: Table Caption
+#          pre: 'Table '
+#          sep: ': '
+#        conditional:
+#          first_row: true
+#          first_column: false
+#          last_row: false
+#          last_column: false
+#          no_hband: false
+#          no_vband: true
+    pdf_document:
+        keep_tex: true
+        latex_engine: xelatex
         pandoc_args:
@@
           - '--lua-filter=pagebreak.lua'
-      tables:
-        layout: autofit
-        width: 1.0
-        caption:
-          style: Table Caption
-          pre: 'Table '
-          sep: ': '
-        conditional:
-          first_row: true
-          first_column: false
-          last_row: false
-          last_column: false
-          no_hband: false
-          no_vband: true
+documentclass: article
+classoption: letterpaper
+fontsize: 12pt
+header-includes:
+   - \usepackage{lineno}
+   - \linenumbers
+   - \usepackage[T1]{fontenc}
+   - \usepackage{helvet}
+   - \renewcommand{\familydefault}{\sfdefault}
 bibliography: references.bib
 csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
-abstract: |
-  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results.
-Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared, and; analyses conducted.
-Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline and assigned them scores reflecting their openness and reproducibility.
-We found that most of the articles were not very open, failing to share data or code in a meaningful way.
-We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
 keywords: |
@@
   echo = FALSE,
+  fig.path = "../figures/",
+  dev = c("postscript"),
+  fig.width = 3.31,
+  fig.height = 3.31,
+  out.width = "100%",
+  dpi = 300,
   comment = "#>",
-  fig.path = "../figures/"
+  dev = "cairo_pdf"
 )
@@
 ```
+
+ \newpage
+
+# Abstract
+
+Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results.
+Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared, and; analyses conducted.
+Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
+We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline and assigned them scores reflecting their openness and reproducibility.
+We found that most of the articles were not very open, failing to share data or code in a meaningful way.
+We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
+
+\newpage
+
+# Introdution
 

### 2021-06-15 analysis/paper/paper.Rmd
fix issues that prevented PDF from building

@@
 
-```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, e.g., all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
@@
 
-This report was generated on `r Sys.time()` using the following computational environment and dependencies:
+This report was generated on $`r Sys.time()`$ using the following computational environment and dependencies:
 

### 2021-06-16 analysis/paper/paper.Rmd
Update affiliations, use word_document2, move libs to frontmatter

@@
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
-  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR, USA
-  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis, OR, USA
+  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
+  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97331, USA
 output: 
-# Uncomment from line 25 to 45 and comment 46 to line 54 for Word output
-# Comment from line 25 to 45 and uncomment 46 to line 54 for LaTeX output
-#  officedown::rdocx_document:
-#      fig_caption: yes
-#      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
-#      pandoc_args:
-#        - '--lua-filter=scholarly-metadata.lua'
-#        - '--lua-filter=author-info-blocks.lua'
-#        - '--lua-filter=pagebreak.lua'
-#      tables:
-#        layout: autofit
-#        width: 1.0
-#        caption:
-#          style: Table Caption
-#          pre: 'Table '
-#          sep: ': '
-#        conditional:
-#          first_row: true
-#          first_column: false
-#          last_row: false
-#          last_column: false
-#          no_hband: false
-#          no_vband: true
-    pdf_document:
-        keep_tex: true
-        latex_engine: xelatex
+  bookdown::word_document2:
+     fig_caption: yes
+     number_sections: FALSE
+     reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
@@
        - '--lua-filter=pagebreak.lua'
-documentclass: article
 classoption: letterpaper
 fontsize: 12pt
-header-includes:
-   - \usepackage{lineno}
-   - \linenumbers
-   - \usepackage[T1]{fontenc}
-   - \usepackage{helvet}
-   - \renewcommand{\familydefault}{\sfdefault}
 bibliography: references.bib
+link-citations: no
 csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
-keywords: |
-  open science; open data; reproducible research; FAIR data
-highlights: |
-  Open research practices are highlighted extensively in the broader scientific community.
-Our survey of 300 randomly selected articles from 2012 to 2018 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
 ---
 
-```{r, setup, echo = FALSE}
+```{r, setup, echo = FALSE, message=FALSE}
+library("officer")
+library("dplyr")
+library("janitor")
+library("flextable")
+library("Reproducibility.in.Plant.Pathology")
+library("tidyr")
+library("DiagrammeR")
+library("DiagrammeRsvg")
+library("rsvg")
+library("ggplot2")
+library("patchwork")
+
 knitr::opts_chunk$set(
@@
   comment = "#>",
-  dev = "cairo_pdf"
+  dev = "cairo_pdf",
+  cache = TRUE
 )
+```
 
-library("Reproducibility.in.Plant.Pathology")
-```
+**Keywords: open science, open data, reproducible research, FAIR data**
 
@@
 
-# Abstract
+# Abstract {-#abstract}
 
@@
 
-# Introdution
+# Introduction
 

### 2021-06-16 analysis/paper/paper.Rmd
Grammar on line 101
Update cross-refs for figs and tables to work with word_document2 output

@@
 In biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
-Therefore we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":
+Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":
 
@@
 
-Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available (Figure \@ref(fig:article-scores)i).
+Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available (Figure \@ref(fig:articleScores)i).
 Two hundred eighty-seven articles, 96%, were classed as "0" and nine articles, 0.03%, appeared to not use any computational methods.
 
-More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Figure  \@ref(fig:article-scores)ii).
+More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Figure  \@ref(fig:articleScores)ii).
 
-Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:article-scores)iii).
+Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)iii).
 
 However, data availability was mostly not available with 243 or 81.5% scoring "0" where the data was not available or mentioned in the article.
-However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Figure  \@ref(fig:article-scores)iv).
+However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).
 
 The most frequently cited software was SAS.
-The remainder were mostly specialised software except for Microsoft Excel, tied for 9th (Table \@ref(tab:su)).
+The remainder were mostly specialised software except for Microsoft Excel, tied for 9th (Table \@ref(tab:software-used)).
 
@@
 
-```{r journals, tab.id="journals", tab.cap="Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated.", echo=FALSE, message=FALSE, warning=FALSE}
-library("dplyr")
-library("janitor")
-library("flextable")
-library("officer")
-
+```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
@@
   colformat_num(na_str = "NA") %>%
-  autofit()
+  autofit() %>%
+  set_caption(
+    "Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
+  )
 ```
@@
 
-```{r software_used, tab.id="su", tab.cap="The top ten sofware programs that were found to be used in the papers that were surveyed.", echo=FALSE, message=FALSE, warning=FALSE}
-library("tidyr")
-
+```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
 rrpp_software <-
@@
   flextable() %>%
-  autofit()
+  autofit() %>%
+  set_caption(
+    "The top ten sofware programs that were found to be used in the papers that were surveyed."
+  )
 ```
@@
 
-```{r scoring, tab.id="scoring", tab.cap ="Articles were scored in four areas for reproducibility on a scale of '0' to '3' by four independent assessors to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
 scoring_criteria %>%
@@
   colformat_num(na_str = "NA") %>%
-  set_table_properties(layout = "autofit")
+  set_table_properties(layout = "autofit") %>%
+  set_caption(
+    "Articles were scored in four areas for reproducibility on a scale of '0' to '3' by four independent assessors to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.")
 ```
@@
 
-```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, e.g., all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
+```{r reproducibility_score, echo=FALSE, message=FALSE, warning=FALSE}
 import_notes() %>%
@@
   flextable() %>%
-  autofit()
+  autofit() %>%
+  set_caption(
+    "(\\#reproducibility) Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, e.g., all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use."
+  )
 ```
@@
 
-<!-- @Emerson, can you please have a look at this caption, if I'm not mistaken, this is your diagram design. Can you confirm that what I've written is accurate and describes the workflow? -->
-
 ```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example open and reproducible research workflow.
@@
 Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time and a DOI for final released products.', cache=FALSE, fig.env='figure'}
-library("DiagrammeR")
-library("DiagrammeRsvg")
-library("rsvg")
 
@@
 
-```{r article-scores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i), computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i), computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
 (ii) Shows 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
 (iii) Displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-(iv) Shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, _e.g._ a methods paper.", cache=FALSE, fig.env='figure'}
-library("ggplot2")
-library("patchwork")
+(iv) Shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
+a methods paper.", cache=FALSE, fig.env='figure'}
+
 rrpp <- import_notes()

### 2021-06-16 analysis/paper/paper.Rmd
Follow APS heading style
Remove unnecessary YAML options
these are defined in the template Word file

@@
        - '--lua-filter=pagebreak.lua'
-classoption: letterpaper
-fontsize: 12pt
 bibliography: references.bib
@@
 
-## Article Selection
+## Article selection
 

### 2021-06-16 analysis/paper/paper.Rmd
Standardise the use of "'" to surround scores throughout paper

@@
 
-Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as "3", which was the highest score available (Figure \@ref(fig:articleScores)i).
-Two hundred eighty-seven articles, 96%, were classed as "0" and nine articles, 0.03%, appeared to not use any computational methods.
+Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as '3', which was the highest score available (Figure \@ref(fig:articleScores)i).
+Two hundred eighty-seven articles, 96%, were classed as '0' and nine articles, 0.03%, appeared to not use any computational methods.
 
-More articles did a good job of using software that was reasonably available to anyone with 206 scoring "2" or "3" (Figure  \@ref(fig:articleScores)ii).
+More articles did a good job of using software that was reasonably available to anyone with 206 scoring '2' or '3' (Figure  \@ref(fig:articleScores)ii).
 
-Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)iii).
+Software citations were also reasonably well reported in the literature with 120 scoring '2' where the main software was cited with version numbers and 57 scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)iii).
 
-However, data availability was mostly not available with 243 or 81.5% scoring "0" where the data was not available or mentioned in the article.
+However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
 However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).

### 2021-06-16 analysis/paper/paper.Rmd
Tidy up figure and table captions

@@
   set_caption(
-    "(\\#reproducibility) Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, e.g., all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use."
+    "Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, e.g., all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use."
   )
@@
 
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i), computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
-(ii) Shows 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-(iii) Displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-(iv) Shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
+(ii) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+(iii) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
+(iv) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
 a methods paper.", cache=FALSE, fig.env='figure'}

### 2021-06-16 analysis/paper/paper.Rmd
Clarify use of hurdle model
Remove reproducibility score table as it duplicates figure 2

@@
 
-Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data.
+Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data and the assumption that a zero value would only come from one process, the scoring.
 Each model was run for 3000 iterations in four chains.
@@
 
-```{r reproducibility_score, echo=FALSE, message=FALSE, warning=FALSE}
-import_notes() %>%
-  tabyl(reproducibility_score) %>%
-  adorn_pct_formatting(digits = 1) %>%
-  rename(Score = reproducibility_score, Percent = percent) %>%
-  mutate(Score = round(Score, digits = 1)) %>%
-  flextable() %>%
-  autofit() %>%
-  set_caption(
-    "Tally of reproducibility scores where '0' is not reproducible and '12' is fully reproducible, e.g., all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use."
-  )
-```
-
-\newpage
-
 # Figures
@@
 Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
-Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time and a DOI for final released products.', cache=FALSE, fig.env='figure'}
+Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time and a DOI for final released products.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 

### 2021-06-16 analysis/paper/paper.Rmd
Specify figure paths in figure chunks

@@
   echo = FALSE,
-  fig.path = "../figures/",
   dev = c("postscript"),

### 2021-06-16 analysis/paper/paper.Rmd
Add instructions for importing fonts for embedding in .eps figs

@@
 )
+```
+
+```{r fonts, include=FALSE, message=FALSE, eval=FALSE}
+# Note 1: This chunk only needs to be run once on a computer to import fonts for
+# use in R. This chunk makes .ttf fonts available to R for use and embedding in
+# .eps figure outputs.
+#
+# Note 2: GhostScript needs to be installed at the system level for the PS files
+# to be generated.  MacOS users can use `brew install ghostscript`.  Windows
+# users should download and install. Linux users can use their package manager.
+#
+# Note 3: You may need to tell R where to find GhostScript's 'gs' executable.
+# Set `R_GSCMD="/opt/homebrew/bin/gs"` in .Renviron for MacOS users using
+# homebrew to install on a Mac M1.
+# 
+# Windows users can follow these directions:
+# 1.	Go to the GhostScript website
+#  (https://www.ghostscript.com/download/gsdnld.html)
+# 2.	Download the windows installer suitable for your machine
+# 3.	Run the installer file which you downloaded and follow the prompts
+# 4.	After running the installer click the windows "Start" button and type
+# "Edit environment variables for your account" and open
+# 5.	In the tab 'Advanced' click the button at the bottom
+# 'Environment Variables...'
+# 6.	Under 'System variables' find the variable 'Path', select 'Path' and click
+# the 'Edit' button
+# 7. 	Select a new line and copy the Ghostscript 'bin' folder location into the
+# field.
+## 7.1	If you installed ghostscript to the default folder location; then the
+# folder location will likely be "C:\Program Files\gs\gs9.52\bin", the version
+# number (9.52) may differ.
+# 8.	Save and exit the environmental variables window
+# This chunk is then run only if knitting on new computer that the files have
+# not been generated
+
+library("extrafont")
+font_import()
 ```

### 2021-06-16 analysis/paper/paper.Rmd
Export .eps file for figure 1

@@
 ))
-rsvg_pdf(charToRaw(p), "Figure 1.pdf")
-
-knitr::include_graphics("Figure 1.pdf")
+rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 1.eps")
+knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
 ```
@@
 (iv) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
-a methods paper.", cache=FALSE, fig.env='figure'}
+a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 
@@
   geom_bar() +
-  ggtitle("Computational Methods Availability") +
   ylab("Score") +
@@
   geom_bar() +
-  ggtitle("Software Availability") +
   xlab(NULL) +
@@
   geom_bar() +
-  ggtitle("Software Cited") +
   ylab("Score")
@@
   geom_bar() +
-  ggtitle("Data Availability") +
   ylab(NULL)
@@
 p <- (i | ii) / (iii | iv)
-p + plot_annotation(tag_levels = "i")
+p <- p + plot_annotation(tag_levels = "i")
+ggsave(filename = "../figures/Sparks et al Figure 2.eps",
+       plot = p,
+       device = "eps")
+extrafont::embed_fonts(
+   file = ("../figures/Sparks et al Figure 2.eps"),
+   outfile = ("figures/Sparks et al Figure 2.eps"),
+   options = "-dEPSCrop"
+)
+knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
 ```

### 2021-06-16 analysis/paper/paper.Rmd
Embed fonts in figure 1.eps file

@@
 rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 1.eps")
+extrafont::embed_fonts(
+   file = ("../figures/Sparks et al Figure 1.eps"),
+   outfile = ("figures/Sparks et al Figure 1.eps"),
+   options = "-dEPSCrop"
+)
 knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")

### 2021-06-17 analysis/paper/paper.Rmd
Update figure size

@@
        plot = p,
-       device = "eps")
+       device = "eps",
+       width = 6,
+       height = 6,
+       units = "in")
 extrafont::embed_fonts(

### 2021-06-20 analysis/paper/paper.Rmd
Remove a comment or two in the Rmd

@@
 # 1.	Go to the GhostScript website
-#  (https://www.ghostscript.com/download/gsdnld.html)
+#     <https://www.ghostscript.com/download/gsdnld.html>.
 # 2.	Download the windows installer suitable for your machine
@@
 #     field.
-## 7.1	If you installed ghostscript to the default folder location; then the
-# folder location will likely be "C:\Program Files\gs\gs9.52\bin", the version
-# number (9.52) may differ.
+## 7.1	If you installed Ghostscript to the default folder location; then the
+#     folder location will likely be "C:\Program Files\gs\gs9.52\bin", the
+#     version number (9.52) may differ.
 # 8.	Save and exit the environmental variables window
+#
 # This chunk is then run only if knitting on new computer that the files have
@@
 That is, open science leads to reproducibility and replicability.
-
-<!--# not sure we need a separate section for definitions, but present continuously in the text -->
 

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

@@
 ---
-title: "Reproducibility and plant pathology: where do we stand and a way forward"
+title: "Reproducibility in plant pathology: where do we stand and a way forward"
 author:
@@
       institute: UFV
-  - Zachary Foster:
+  - Zachary S. L. Foster:
       institute: OSU
@@
 
-Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results.
-Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared, and; analyses conducted.
+Open research practices have been highlighted extensively during the last ten years in many fields of scientific study as essential standards needed to promote transparency and reproducibility of scientific results.
+Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and, analyses were conducted.
 Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline and assigned them scores reflecting their openness and reproducibility.
-We found that most of the articles were not very open, failing to share data or code in a meaningful way.
-We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
+We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and reproducibility.
+We found that most of the articles were not following protocols for open science, and were failing to share data or code in a reproducible way.
+We also propose that use of open-source tools facilitates reproducible work and analyses benefitting not just readers, but the authors as well.
+We also provide ideas and tools to promote open, reproducible research practices among plant pathologists.
 

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

@@
   - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
-  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97331, USA
+  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
 output: 

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research is recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
+For instance, reproducible research was recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
 
@@
 
-In biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproduction, _e.g._, field trials that span years and locations or complex glasshouse experiments.
-Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines a minimum standard of "reproducible research":
+In the biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproducibility, _e.g._, field trials that span years and locations or complex glasshouse experiments.
+Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":
 
@@
 And that the software used are also easily obtained and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
+
+It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
+However, very often biological specimens such as strains, cultures or cultivars are often not available.
+These cases of a lack of reproducibility will not be covered here.
 

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

@@
 We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
-The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications (See appendix for details on the methodology).
+The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications (see appendix for details on the methodology).
 

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

@@
 
-At the second level, Lehner _et al._ [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
-The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work.
+At the second level, Lehner _et al._ [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
+The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
 Likewise, Duku _et al._ [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+A final example is provided by Carleson et al.
+[-@carleson2019population] who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on github, while providing all data on OSF.
 
-The third level is the use of proper data repositories such as FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
+The third level is the use of proper data repositories such as Github, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
 Sparks _et al._ [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+Similarly, Carleson et al. [-@carleson2019population] provided all data on OSF [-@Carleson_Grünwald_2019].
 

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

@@
 We also propose that use of open-source tools facilitates reproducible work and analyses benefitting not just readers, but the authors as well.  
-We also provide ideas and tools to promote open, reproducible research practices among plant pathologists.
+Finally, we also provide ideas and tools to promote open, reproducible research practices among plant pathologists.
 
@@
 
-When making your science more open and reproducible, methods, software used, this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.
-should be cited properly.
+When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
 Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, _e.g._, a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.
+Provide a full description of all equipment used, _e.g._, 'a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.'
 This allows end-users to identify what was used and identify the methods used more accurately.
@@
 
-Prefer text files for saving small sets of data.
+Text files for saving small sets of data are preferable. 
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._, comma separated (CSV) files.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._, comma separated (CSV) or tab separated (TSV) files.
 This also helps ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like MariaDB or PostgreSQL which provide users with several benefits but two important ones to mention here are data redundancy, no duplicated records; and data consistency, all of your records are sure to be recorded in the same way for every observation.
-While databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set that might be only a few rows and columns in a database.
+Larger data sets may warrant the use of a proper database like GenGank, MariaDB or PostgreSQL which provide users with several benefits but two important benefits to mention here are (1) data redundancy, ensuring no records are duplicated and (2) data consistency, ensuring that all records in a data set are recorded in the same fromat for every observation.
+While personal databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set. 
+Databases such a Genbank are preferable for molecular data ensuring data integrity and machine readability.
 
@@
 
-If steps are followed to make the data FAIR then it will be readable by humans and machines alike this will help support discoveries and support further research.
+If steps are followed to make the data FAIR then it will be readable by humans and machines alike and this will help support discoveries and support further research. 
 In turn, sharing data will lead to new citations for your work as others discover and use it.
@@
 There are different options for generating a DOI for your data and other materials.
-FigShare, Zenodo and OSF all offer long-term archival along with a service to generate a DOI for your materials.
+FigShare, Zenodo and OSF all offer persistent archives along with a services to generate a DOI for your materials. 
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
@@
 
-Once you have determined how to best manage your source code for analysis and the data sets the next step is to consider how to share your data.
+Once you have determined how to best manage your source code and the data sets for analysis the next step is to consider how to share your data.
 Providers such as FigShare, Dataverse, OSF.io (the Open Science Framework) and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
@@
 GitHub is arguably the most popular and widely used software development platform currently.
-Data that is encoded in CSV or other plain text formats can easily be deposited in a repository along with code for analysis to enable changes to be tracked and other users to download and replicate the work.
+Data that is encoded in CSV or other plain text formats can easily be deposited in a repository along with code for analysis to enable tracking of changes and other users to download and replicate the work.
 
-We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only are not an optimal way to preserve and share your work over the long term.
+We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only as these are not an optimal way to preserve and share your work over the long term. 
 Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
-It is a best practice to always ensure that you have deposited the data with a provider such as Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessibility.
+It is a best practice to always ensure that you have deposited the data with a provider such as Genbank, Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessibility.
 Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
 If readers are uncertain, we suggest to also consult with local librarians about possible resources.
-Most universities some other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
+Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
+The importnat aspect is that data once deposited cannot be modified anymore.
 
@@
 One of the most important messages that we would like to share is that there is more to the work than just the paper.
-Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed and often leads to greater impact than for works that do not share data and or code.
+Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
+This open sharing of code and data often leads to greater impact as work is cited if resources such as code or data are reused.
 With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
@@
 
-```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example open and reproducible research workflow.
+```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
 Starting with the question, determine the methodology, describe it, make it available and cite it.
 Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
-Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time and a DOI for final released products.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 

### 2021-06-22 analysis/paper/paper.Rmd
Spellcheck and reknit, also fix single and double quotes around scores

@@
 However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
-However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).
+However, more articles, 29 or 9.7%, scored '3' than "1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).
 
@@
 This also helps ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like GenGank, MariaDB or PostgreSQL which provide users with several benefits but two important benefits to mention here are (1) data redundancy, ensuring no records are duplicated and (2) data consistency, ensuring that all records in a data set are recorded in the same fromat for every observation.
+Larger data sets may warrant the use of a proper database like GenBank, MariaDB or PostgreSQL which provide users with several benefits but two important benefits to mention here are (1) data redundancy, ensuring no records are duplicated and (2) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
 While personal databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set. 
-Databases such a Genbank are preferable for molecular data ensuring data integrity and machine readability.
+Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
 
@@
 Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
-It is a best practice to always ensure that you have deposited the data with a provider such as Genbank, Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessibility.
+It is a best practice to always ensure that you have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessibility.
 Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
@@
 Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
-The importnat aspect is that data once deposited cannot be modified anymore.
+The important aspect is that data once deposited cannot be modified any more.
 

### 2021-06-22 analysis/paper/paper.Rmd
Fixes another single/double quote around a score

@@
 However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
-However, more articles, 29 or 9.7%, scored '3' than "1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).
+However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).
 

### 2021-06-22 analysis/paper/paper.Rmd
Fixes figure order, closes #54
Closes #54, corrects figure order, filenames and subfigure designations

@@
 
-Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as '3', which was the highest score available (Figure \@ref(fig:articleScores)i).
+Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
 Two hundred eighty-seven articles, 96%, were classed as '0' and nine articles, 0.03%, appeared to not use any computational methods.
 
-More articles did a good job of using software that was reasonably available to anyone with 206 scoring '2' or '3' (Figure  \@ref(fig:articleScores)ii).
+More articles did a good job of using software that was reasonably available to anyone with 206 scoring '2' or '3' (Figure  \@ref(fig:articleScores)B).
 
-Software citations were also reasonably well reported in the literature with 120 scoring '2' where the main software was cited with version numbers and 57 scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)iii).
+Software citations were also reasonably well reported in the literature with 120 scoring '2' where the main software was cited with version numbers and 57 scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)C).
 
 However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
-However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).
+However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).
 
@@
 
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
+(ii) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+(iii) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
+(iv) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
+a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+
+rrpp <- import_notes()
+theme_set(theme_classic())
+A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
+  geom_bar() +
+  ylab("Score") +
+  xlab(NULL)
+
+B <- ggplot(rrpp, aes(y = software_avail)) +
+  geom_bar() +
+  xlab(NULL) +
+  ylab(NULL)
+
+C <- ggplot(rrpp, aes(y = software_cite)) +
+  geom_bar() +
+  ylab("Score")
+
+D <- ggplot(rrpp, aes(y = data_avail)) +
+  geom_bar() +
+  ylab(NULL)
+
+# put them all together
+p <- (A | B) / (C | D)
+p <- p + plot_annotation(tag_levels = "A")
+ggsave(filename = "../figures/Sparks et al Figure 1.eps",
+       plot = p,
+       device = "eps",
+       width = 6,
+       height = 6,
+       units = "in")
+extrafont::embed_fonts(
+   file = ("../figures/Sparks et al Figure 1.eps"),
+   outfile = ("figures/Sparks et al Figure 1.eps"),
+   options = "-dEPSCrop"
+)
+knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
+```
+
+\newpage
+
 ```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
@@
 ))
-rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 1.eps")
-extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 1.eps"),
-   outfile = ("figures/Sparks et al Figure 1.eps"),
-   options = "-dEPSCrop"
-)
-knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
-```
-
-\newpage
-
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
-(ii) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-(iii) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-(iv) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
-a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
-
-rrpp <- import_notes()
-theme_set(theme_classic())
-i <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
-  geom_bar() +
-  ylab("Score") +
-  xlab(NULL)
-
-ii <- ggplot(rrpp, aes(y = software_avail)) +
-  geom_bar() +
-  xlab(NULL) +
-  ylab(NULL)
-
-iii <- ggplot(rrpp, aes(y = software_cite)) +
-  geom_bar() +
-  ylab("Score")
-
-iv <- ggplot(rrpp, aes(y = data_avail)) +
-  geom_bar() +
-  ylab(NULL)
-
-# put them all together
-p <- (i | ii) / (iii | iv)
-p <- p + plot_annotation(tag_levels = "i")
-ggsave(filename = "../figures/Sparks et al Figure 2.eps",
-       plot = p,
-       device = "eps",
-       width = 6,
-       height = 6,
-       units = "in")
+rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 2.eps")
 extrafont::embed_fonts(
    file = ("../figures/Sparks et al Figure 2.eps"),
-   outfile = ("figures/Sparks et al Figure 2.eps"),
+   outfile = ("figures/Sparks et al Figure 2eps"),
    options = "-dEPSCrop"

### 2021-06-22 analysis/paper/paper.Rmd
Add new reference on reproducibility being highlighted

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research was recently highlighted by many authors [@preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
+For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
 

### 2021-06-22 analysis/paper/paper.Rmd
remove unecessary spaces
Replace "donors" with "funding agencies"

@@
 
-Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
+Recently, open science has been highlighted with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
 

### 2021-06-22 analysis/paper/paper.Rmd
Insert missing "but" on line 153
Wordsmithing on line 153
Update Kaique's middle initial per his preferences

@@
       institute: UFV
-  - Kaique dos Santos Alves:
+  - Kaique S. Alves:
       institute: UFV
@@
 However, very often biological specimens such as strains, cultures or cultivars are often not available. 
-These cases of a lack of reproducibility will not be covered here.
+These cases constitute a lack of a lack of reproducibility but will not be covered here.
 

### 2021-06-23 analysis/paper/paper.Rmd
Fix "lack of lack of" on line 153
Remove "the the"

@@
 
-In the biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproducibility, _e.g._, field trials that span years and locations or complex glasshouse experiments.
+In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, _e.g._, field trials that span years and locations or complex glasshouse experiments.
 Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":
@@
 However, very often biological specimens such as strains, cultures or cultivars are often not available. 
-These cases constitute a lack of a lack of reproducibility but will not be covered here.
+These cases do constitute a lack of reproducibility but will not be covered here.
 

### 2021-06-23 analysis/paper/paper.Rmd
add paragraphs about OPP

@@
 
+As we prepared this letter, we became more aware of the urgent need to spread and establish an open science attitude and culture among plant pathologists.
+To assist in fostering this sort of change in our discipline, Open Plant Pathology (OPP), <https://www.openplantpathology.org>, an institution-independent and non-funded initiative, was founded in January 2018 by two of this letter's co-authors, Del Ponte and Sparks, in 2018 with the following vision: “foster a diverse community culture that values openness, transparency and reproducibility of scientific research data and methods in our field”.
+We started OPP with a minimal infrastructure and support from other enthusiastic colleagues that allows members to interact sharing and gathering ideas on how we can improve the openness and reproducibility in our discipline.
+
+We  believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
+
+<!-- need to edit this portion
+For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
+Second, it is beneficial to the reviewer in understanding and providing suggestions for improvements when reviewing and the end-user or reader to be able to verify the validity of the methods used and recreate the analysis which helps with knowledge transfer.
+Lastly, sharing work openly and making it discoverable can lead to new collaborations. 
+end edit portion -->
+
 # Appendix

### 2021-06-24 README.rmd
Update Kaique's middle initial per his preferences
Update pkgdown site

@@
 
-> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
+> Sparks, A.H., Del Ponte, E.M., Alves, K.
+S., Foster, Z., Grünwald, N.
+J.
+(YYYY).
+_Reproducibility in plant pathology: where do we stand and a way forward_.
+Name of journal/book <https://doi.org/xxx/xxx>
 
@@
 
-> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Authors, (YYYY). _Reproducibility in plant pathology: where do we stand and a way forward_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
 
@@
 
-> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N.
+> Sparks, A.H., Del Ponte, E.M., Alves, K.
+S., Foster, Z., Grünwald, N.
+J.
 (`r format(Sys.Date(), "%Y")`).
@@
 
-A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document.
+A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document in a Docker session.
 

### 2021-06-24 analysis/paper/paper.Rmd
Rework the last two paragraphs. Ready for co-author comment now

@@
 In this work we have evaluated the state of reproducibility in the plant pathology literature and presented suggestions for areas of improvement.
-One of the most important messages that we would like to share is that there is more to the work than just the paper.
-Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
-This open sharing of code and data often leads to greater impact as work is cited if resources such as code or data are reused.
-With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
-
 As we prepared this letter, we became more aware of the urgent need to spread and establish an open science attitude and culture among plant pathologists.
@@
 We  believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
-
-<!-- need to edit this portion
 For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
-Second, it is beneficial to the reviewer in understanding and providing suggestions for improvements when reviewing and the end-user or reader to be able to verify the validity of the methods used and recreate the analysis which helps with knowledge transfer.
-Lastly, sharing work openly and making it discoverable can lead to new collaborations. 
-end edit portion -->
+This letter was drafted over the course of several years as the authors had time to devote to it.
+Having everything in a reproducible framework made it easy to resume work and set-aside as necessary without losing information and having everything well-documented made it more simple to do this.
+Second, it benefits the reviewer by aiding their understanding of the work done and gives them more materials to use to make suggestions for improvements when reviewing and the end-user or reader is better able to verify the validity of the methods used and recreate the analysis.
+Perhaps more importantly, sharing these details help with knowledge transfer by showing other interested parties how something was done rather than simply describing it.
+Lastly, openly sharing your work and making it discoverable can lead to new collaborations and synergistic ideas.
+One of the most important messages that we would like to share is that there is more to the work than just the paper.
+Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
+This open sharing of code and data often leads to greater impact as work is cited if resources such as code or data are reused.
+With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
 

### 2021-06-24 R/import_notes.R
Use latest roxygen2 dev version for @examplesIf

@@ -9,7 +9,7 @@
 #' analysis and manuscript preparation
 #' @export import_notes
 #'
-#' @examples
+#' @examplesIf interactive()
 #' notes <- import_notes()
 #' pander::pander(head(notes))
 #'

### 2021-06-24 R/table_of_journals.R

@@ -4,8 +4,7 @@
 #' @return \CRANpkg{pander} table of journals surveyed
 #' @export table_of_journals
 #'
-#' @examples
-#' \donttest{
+#' @examplesIf interactive()
 #' googlesheets4::gs4_deauth()
 #' rrpp <- googlesheets4::read_sheet(
 #'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"

### 2021-06-24 tests/testthat/test-table_of_journals.R
Add tests for untested functions

@@ -1,0 +1,11 @@
+# test diversities table -------------------------------------------------------
+
+test_that("table_of_journals() returns a pander object of journals surveyed", {
+  googlesheets4::gs4_deauth()
+  rrpp <- googlesheets4::read_sheet(
+  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"
+  )
+
+  expect_type(capture.output(table_of_journals(rrpp)),
+              "character")
+})

### 2021-06-24 tests/testthat/test-workflow_dia.R

@@ -1,0 +1,6 @@
+# test diversities table -------------------------------------------------------
+
+test_that("workflow_dia() returns an rsvg_pdf object", {
+  expect_type(capture.output(workflow_dia()),
+              "character")
+          })

### 2021-06-24 analysis/paper/paper.Rmd
Adds Eckert2020 reference

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
-
-<!--# These references above are all prior 2017. We may want to update the list? I've added two using insert citation tool of the visual editor rmarkdown -->
+For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @Eckert2020; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
 

### 2021-06-24 analysis/paper/paper.Rmd
Adds Dienlin2020

@@
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @Eckert2020; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
+For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @Eckert2020; @Dienlin2020; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
 

### 2021-06-24 R/table_of_journals.R
Uses @examplesIf for all functions, cleaner doc files

@@ -10,7 +10,7 @@
 #'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"
 #')
 #' table_of_journals(rrpp)
-#' }
+#'
 #'
 table_of_journals <- function(rrpp) {
   rrpp_journals <- as.data.frame(table(rrpp[, 1]))

### 2021-06-24 R/workflow_dia.R

@@ -6,8 +6,7 @@
 #' @return PDF of workflow diagram
 #' @export workflow_dia
 #'
-#' @examples
-#'
+#' @examplesIf interactive()
 #' workflow_dia()
 #'
 

### 2021-06-24 R/import_notes.R
Fix reference to tibble

@@ -5,8 +5,8 @@
 #' reproducibility score. Also adds the 2 and 5 year impact factor values from
 #' InCites Journal Citation Reports for 2018.
 #'
-#' @return A `tibble` object of reproducibility score notes formatted for use in
-#' analysis and manuscript preparation
+#' @return A [tibble::tibble()] object of reproducibility score notes formatted
+#' for use in analysis and manuscript preparation
 #' @export import_notes
 #'
 #' @examplesIf interactive()

### 2021-07-02 analysis/paper/paper.Rmd
Corrects filepaths for figure outputs after embedding fonts

@@
    file = ("../figures/Sparks et al Figure 1.eps"),
-   outfile = ("figures/Sparks et al Figure 1.eps"),
+   outfile = ("../figures/Sparks et al Figure 1.eps"),
    options = "-dEPSCrop"
@@
    file = ("../figures/Sparks et al Figure 2.eps"),
-   outfile = ("figures/Sparks et al Figure 2eps"),
+   outfile = ("../figures/Sparks et al Figure 2.eps"),
    options = "-dEPSCrop"

### 2021-07-21 README.rmd
Update README with link to docx file and update address

@@
 
-A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document in a Docker session.
+A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the [Word document](analysis/paper/paper.docx) in a Docker session.
 
@@
 
-Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H Sparks
+Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H. Sparks
 
@@
 Department of Primary Industries and Regional Development
-Level 5, 1 Nash St Perth WA 6000
+Level 6, 1 Nash St., Perth WA 6000
 

### 2021-07-21 analysis/paper/paper.Rmd
Reknit paper with final contributions uncommented
Replace "subjective" with "objective"
Correction suggested by Dr David Ferris, Farming Systems Innovation, DPIRD

@@
 
-We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
+We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
 We have based our scoring decisions on our own experiences in the field of plant pathology.
@@
 A.H.S. wrote the manuscript in consultation with E.DP.
-<!-- All authors provided critical feedback and helped contribute to the final version of the manuscript. -->
+All authors provided critical feedback and helped contribute to the final version of the manuscript.
 

### 2021-07-27 R/import_notes.R
Remove examplesIf()

@@ -9,7 +9,7 @@
 #' for use in analysis and manuscript preparation
 #' @export import_notes
 #'
-#' @examplesIf interactive()
+#' @examples
 #' notes <- import_notes()
 #' pander::pander(head(notes))
 #'

### 2021-07-27 R/table_of_journals.R

@@ -4,7 +4,7 @@
 #' @return \CRANpkg{pander} table of journals surveyed
 #' @export table_of_journals
 #'
-#' @examplesIf interactive()
+#' @examples
 #' googlesheets4::gs4_deauth()
 #' rrpp <- googlesheets4::read_sheet(
 #'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"

### 2021-07-27 R/workflow_dia.R

@@ -6,7 +6,7 @@
 #' @return PDF of workflow diagram
 #' @export workflow_dia
 #'
-#' @examplesIf interactive()
+#' @examples
 #' workflow_dia()
 #'
 

### 2021-07-27 R/doi2bib.R
Add doi2bib function

@@ -1,0 +1,135 @@
+#' Convert DOI to Bibtex
+#'
+#' Convert a digital object identifier (\acronym{DOI}) string into a bibtex
+#' entry using the web service \url{http://www.doi2bib.org}.
+#'
+#' @param ... One or more \acronym{DOI}s, as \code{character} strings. If
+#'   arguments are named, names will replace default citekeys.
+#' @param file an optional \code{character} string. If used, the bibtex
+#'   references are sent to \code{file} rather than being returned.
+#' @param append \code{logical}. Append results to file?
+#' @param quiet \code{logical}. By default, bibtex references are printed to the
+#'   console. By setting \code{quiet} to \code{TRUE}, this behaviour will be
+#'   prevented.
+#'
+#' @note This function is take from the unrelased (on CRAN) \R package,
+#'  \pkg{doi2bib} by William Keith Morris available from GitHub under the MIT
+#'  Licence.
+#'
+#' @return a \code{list}, returned invisibly, of bibtex references as
+#'   \code{character} strings, as well as writing to file if \code{file} is
+#'   specified.
+#'
+#' @importFrom httr accept content GET
+#' @importFrom methods setGeneric setMethod signature
+#' @importFrom xml2 xml_text xml_find_all
+#' @importFrom stats setNames
+#'
+#' @examples
+#' doi2bib(Margules2000 = "10.1038/35012251")
+#' doi2bib(Margules2000 = "10.1038/35012251",
+#'         Myers2000    = "10.1038/35002501",
+#'         Moilanen     = "978-0199547777")
+#' @author William Keith Morris, \email{wkmor1@@gmail.com}
+#' @references \url{https://github.com/wkmor1/doi2bib}
+#' @export
+
+setGeneric("doi2bib",
+           function(...,
+                    file,
+                    append = TRUE,
+                    quiet = FALSE) {
+             standardGeneric("doi2bib")
+           },
+           signature = signature("..."))
+
+replace_citekeys <-
+  function(refs, nms) {
+    setNames(mapply(function(ref, nm) {
+      ifelse(nchar(nm) < 1,
+             ref,
+             sub("([^\\{]+\\{)[^,]+", paste0("\\1", nm), ref))
+    },
+    refs,
+    nms,
+    SIMPLIFY = FALSE),
+    nms)
+  }
+
+refs_to_file <-
+  function(refs, file, append) {
+    cat(paste(refs, collapse = "\n"),
+        file = file,
[…]

### 2021-07-27 analysis/paper/paper.Rmd
Acknowledge David in paper
Add visualisation references to Rmd file

@@
 The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
-Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.15.0) [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
 
@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].
 
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version 0.10.0) [@Makowski2019].
+
+Data were visualised using 'ggplot2' (version 3.3.5) [@Wickham2016], 'ggpubr' (version 0.4.0) [@Kassambara2020] and patchwork (version 1.1.1) [@Pedersen2020].
 
@@
 # Acknowledgements
+
+The authors are grateful for insightful comments from Dr. David Ferris on the final manuscript.
 

### 2021-09-01 analysis/paper/paper.Rmd
Rearrange as per CCH suggestion and correct a typo

@@
 
-## Where do we stand in regards to reproducibility?
+# Where do we stand in regards to reproducibility?
+
+## Article selection
 
@@
 We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
-The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications (see appendix for details on the methodology).
+The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+Notes regarding the selection of articles can be found in the file, "Reproducibility_in_plant_pathology_notes.ods", available in this paper's repository in `/inst/extdata'.
+The pages list was numbered from page one and went to page 150.
+This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
+
+## Scoring criteria
+
+Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)).
+
+Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
+The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
+This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
+
+Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
+This classification was based on the evaluator's judgement of the article.
+
+Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
+
+Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
+When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
+A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
+
+A total reproducibility score was calculated as the per cent of total possible for a given paper.
+However, some papers did not use specialized software therefore they were not scored for this category.
+
+We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
+We have based our scoring decisions on our own experiences in the field of plant pathology.
+While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
+Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
+The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
+
+## Statistical analysis
+
+The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
+Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.15.0) [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+
+Relatively flat priors were selected with a mean of 0 and a standard deviation of 10 for the fixed effects.
+
+The random effects were year and assignee for all models excepting the model which tested for year effects.
+In this model, the random effects were the publication title and assignee.
+
+Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data and the assumption that a zero value would only come from one process, the scoring.
+Each model was run for 3000 iterations in four chains.
+
+The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
+
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].
+
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version 0.10.0) [@Makowski2019].
+
+Data were visualised using 'ggplot2' (version 3.3.5) [@Wickham2016], 'ggpubr' (version 0.4.0) [@Kassambara2020] and patchwork (version 1.1.1) [@Pedersen2020].
+
+## Findings
 
@@
 
-However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
+However, data availability was mostly not available with 243 or 81.5% scoring '0' where the data was not available or mentioned in the article.
 However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).
@@
 
-## Are there good examples in the field?
+# Are there good examples in plant pathology?
 
@@
 
-## Best practices to enhance reproducible research
+# Best practices to enhance reproducible research
 
@@
 With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
-
-# Appendix
-
-## Article selection
-
-We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
-The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
-A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
-Notes regarding the selection of articles can be found in the file, "Reproducibility_in_plant_pathology_notes.ods", available in this paper's repository in `/inst/extdata'.
-The pages list was numbered from page one and went to page 150.
-This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
-
-## Scoring criteria
-
-Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)).
-
-Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
-The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
-
-Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
-This classification was based on the evaluator's judgement of the article.
-
-Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
-
-Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
-When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
-
-A total reproducibility score was calculated as the per cent of total possible for a given paper.
-However, some papers did not use specialized software therefore they were not scored for this category.
-
-We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
-We have based our scoring decisions on our own experiences in the field of plant pathology.
-While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
-Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
-The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
-
-## Statistical analysis
-
-The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
-Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.15.0) [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
-
-Relatively flat priors were selected with a mean of 0 and a standard deviation of 10 for the fixed effects.
-
-The random effects were year and assignee for all models excepting the model which tested for year effects.
-In this model, the random effects were the publication title and assignee.
-
-Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data and the assumption that a zero value would only come from one process, the scoring.
-Each model was run for 3000 iterations in four chains.
-
-The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
-
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].
-
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version 0.10.0) [@Makowski2019].
-
-Data were visualised using 'ggplot2' (version 3.3.5) [@Wickham2016], 'ggpubr' (version 0.4.0) [@Kassambara2020] and patchwork (version 1.1.1) [@Pedersen2020].
 

### 2021-09-01 analysis/paper/paper.Rmd
github/Github -> GitHub

@@
 A final example is provided by Carleson et al.
-[-@carleson2019population] who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on github, while providing all data on OSF.
+[-@carleson2019population] who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on GitHub, while providing all data on OSF.
 
-The third level is the use of proper data repositories such as Github, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
+The third level is the use of proper data repositories such as GitHub, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
 Sparks _et al._ [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.

### 2021-09-13 README.rmd
Update README
Update pkgdown site

@@
 
+### Licensing
+
 Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H. Sparks
@@
 
-Adam H Sparks
+Adam H. Sparks
 Senior Research Scientist
@@
 Department of Primary Industries and Regional Development
-Level 6, 1 Nash St., Perth WA 6000
+Level 6.35, 1 Nash St., Perth WA 6000
 
 <https://adamhsparks.com/>
+
+### Code of Conduct
+
+Please note that the Reproducibility.in.Plant.Pathology project is released with a [Contributor Code of Conduct](https://openplantpathology.github.io/Reproducible.Plant.Pathology/CODE_OF_CONDUCT.html).
+By contributing to this project, you agree to abide by its terms.

### 2021-09-29 analysis/paper/paper.Rmd
Remove trailing spaces
Acknowledge CCH AG in paper
Generate a preprint version of the paper

@@
      number_sections: FALSE
-     reference_docx: "../templates/template.docx" # Insert path for the DOCX file
+     reference_docx: "../templates/preprint-template.docx"
      pandoc_args:
@@
 link-citations: no
-csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
+csl: "../templates/american-phytopathological-society.csl"
 ---
@@
 
-The authors are grateful for insightful comments from Dr. David Ferris on the final manuscript.
+The authors are grateful for insightful comments from Dr. David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript.
 

### 2021-09-29 README.rmd
Update README files
Add tic badge and edit text

@@
 # Reproducibility in Plant Pathology
+<!-- badges: start -->
 ![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
+[![tic](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/tic/badge.svg?branch=main)](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/actions)
 [![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
+<!-- badges: end -->
 
-This repository contains the data and code for our paper:
+This repository contains the data and code for our letter to the editor:
 

### 2021-09-29 README.rmd
Go back to building pkgdown site locally

--- 2021-09-13 README.rmd
@@
 # Reproducibility in Plant Pathology
+<!-- badges: start -->
 ![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
@@
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
+<!-- badges: end -->
 
-This repository contains the data and code for our paper:
+This repository contains the data and code for our letter to the editor:
 

### 2021-10-13 analysis/paper/paper.Rmd
Add Emerson's middle initial
Reknit paper with Phytopath template

@@
       correspondence: true
-  - Emerson Del Ponte:
+  - Emerson M. Del Ponte:
       institute: UFV
@@
      number_sections: FALSE
-     reference_docx: "../templates/preprint-template.docx"
+     reference_docx: "../templates/phytopath_template.docx"
      pandoc_args:

### 2021-10-13 README.rmd
Add citation to preprint
Update README

@@
 
-This repository contains the data and code for our letter to the editor:
+This repository contains the data and code for our article:
 
@@
 
-Our pre-print is online here:
+Our pre-print is online on the agriRxiv preprint server:
 
-> Authors, (YYYY). _Reproducibility in plant pathology: where do we stand and a way forward_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Sparks, A.H., Del Ponte, E.M., Alves, K.
+S., Foster, Z., Grünwald, N.
+J.
+(2021).
+_Reproducibility in plant pathology: where do we stand and a way forward_.
+agriRxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`.
+Online at <https://doi.org/10.31220/agriRxiv.2021.00082>
+
+The paper is a systematic and quantitative review of articles published in 20 plant pathology journals that spans five years of publications.
+It provides a basis for identifying what has been done so far in the discipline of plant pathology's published research to ensure computational reproducibility.
+The results show that as a discipline, plant pathologists are not widely sharing data or code openly, making the works largely unreproducible.
+Based on these results and our own experiences, we offer suggestions as to how we can further improve reproducibility in the discipline of plant pathology, but which are not unique to the discipline, that would allow reviewers to make better suggestions, readers to learn more from the work and earns author more citations for their work.
 

### 2021-10-13 analysis/paper/paper.Rmd
Revise headings of sections to match Phytopath article
Use black for bars in figure 1

@@
 
-# Where do we stand in regards to reproducibility?
+# Materials and Methods
 
-## Article selection
+## Article Selection
 
@@
 
-## Scoring criteria
+## Scoring Criteria
 
@@
 
-## Statistical analysis
+## Statistical Analysis
 
@@
 
-## Findings
+# Results
 
@@
 
-# Are there good examples in plant pathology?
+# Discussion
+
+## Are There Good Examples?
 
@@
 
-# Best practices to enhance reproducible research
+## Best Practices to Enhance Reproducible Research
 
@@
 
-# Data availability statement
+# Author Recommended Internet Resources
+
+## Data
 
@@
 
-# Code availability statement
+## Code
 
@@
 
-# References
+# Literature Cited
 
@@
 A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
-  geom_bar() +
+  geom_bar(fill = "black") +
   ylab("Score") +
@@
 B <- ggplot(rrpp, aes(y = software_avail)) +
-  geom_bar() +
+  geom_bar(fill = "black") +
   xlab(NULL) +
@@
 C <- ggplot(rrpp, aes(y = software_cite)) +
-  geom_bar() +
+  geom_bar(fill = "black") +
   ylab("Score")
@@
 D <- ggplot(rrpp, aes(y = data_avail)) +
-  geom_bar() +
+  geom_bar(fill = "black") +
   ylab(NULL)

### 2021-10-14 analysis/paper/paper.Rmd
Number inline list using (i) and (ii) as per APS style

@@
 This also helps ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like GenBank, MariaDB or PostgreSQL which provide users with several benefits but two important benefits to mention here are (1) data redundancy, ensuring no records are duplicated and (2) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
+Larger data sets may warrant the use of a proper database like GenBank, MariaDB or PostgreSQL which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
 While personal databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set.

### 2021-10-14 analysis/paper/paper.Rmd
Replace _et al._ with et al. for APS style

@@
 The first level is including tables of raw data or code with the paper as a supplemental file.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden _et al._ [-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an _e-**X**tra_\* with reproducible examples for readers to refer to.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden et al.
+[-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an _e-**X**tra_\* with reproducible examples for readers to refer to.
 This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
 
-At the second level, Lehner _et al._ [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
+At the second level, Lehner et al.
+[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Likewise, Duku _et al._ [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+Likewise, Duku et al.
+[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
 A final example is provided by Carleson et al.
@@
 The third level is the use of proper data repositories such as GitHub, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
-Sparks _et al._ [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+Sparks et al.
+[-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
 Similarly, Carleson et al. [-@carleson2019population] provided all data on OSF [-@Carleson_Grünwald_2019].
 
-The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq _et al._ [@Khaliq2020] have done.
+The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
+[@Khaliq2020] have done.
 Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of _Ascochyta rabiei_ conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni _et al._ used [-@Miorini2018, [-@Miorini2019]].
-Kamvar _et al._ [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
+When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+used [-@Miorini2018, [-@Miorini2019]].
+Kamvar et al.
+[-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
 While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

### 2021-10-14 analysis/paper/paper.Rmd
Clarify the prior distributions
Clarify modifying the 'adapt_delta()' and 'max_treedepth()'

@@
 
-Relatively flat priors were selected with a mean of 0 and a standard deviation of 10 for the fixed effects.
+Relatively flat priors were selected from a normal distribution with a mean of 0 and a standard deviation of 10 for all parameters.
 
@@
 
-The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.
+The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure a good model fit to the data and that the chains mixed well.
 

### 2021-10-15 analysis/paper/paper.Rmd
Revise data and code heading
Load here and bayesplot for a new figure 1

@@
 library("janitor")
+library("here")
 library("flextable")
@@
 library("ggplot2")
+library("bayesplot")
 library("patchwork")
@@
 
-# Author Recommended Internet Resources
+# Data and Code Availability
 

### 2021-10-15 analysis/paper/paper.Rmd
Add figure 1 of posterior fits

@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()`  (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].
 
@@
 # Results
+
+None of the factors that were tested for had an effect on the reproducibility score.
 
@@
 
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (i) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
-(ii) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-(iii) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-(iv) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate the effects of factors affecting the reproducibility of papers published in 20 plant pathology journals or plant pathology focused articles from other specialised journals.
+Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws.
+Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+
+theme_set(theme_classic())
+color_scheme_set(scheme = "gray")
+
+m1 <- pp_check(readRDS(here("data/m1.Rds")))
+m2 <- pp_check(readRDS(here("data/m2.Rds")))
+m3 <- pp_check(readRDS(here("data/m3.Rds")))
+m4 <- pp_check(readRDS(here("data/m4.Rds")))
+m5 <- pp_check(readRDS(here("data/m5.Rds")))
+m6 <- pp_check(readRDS(here("data/m6.Rds")))
+
+# put them all together
+p <- (m1 | m2) / (m3 | m4) / (m5 | m6)
+
+p <- p + plot_annotation(tag_levels = "A")
+ggsave(filename = "../figures/Sparks et al Figure 1.eps",
+       plot = p,
+       width = 6,
+       height = 6,
+       units = "in",
+       device = cairo_ps)
+extrafont::embed_fonts(
+   file = ("../figures/Sparks et al Figure 1.eps"),
+   outfile = ("../figures/Sparks et al Figure 1.eps"),
+   options = "-dEPSCrop"
+)
+knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
+```
+
+\newpage
+
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
+(B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+(C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
+(D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
 a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

### 2021-10-15 analysis/paper/paper.Rmd
Move figs 1 and 2 to 2 and 3 for new posterior fig and use cairo_ps

@@
 p <- p + plot_annotation(tag_levels = "A")
-ggsave(filename = "../figures/Sparks et al Figure 1.eps",
+ggsave(filename = "../figures/Sparks et al Figure 2.eps",
        plot = p,
-       device = "eps",
        width = 6,
        height = 6,
-       units = "in")
+       units = "in",
+       device = cairo_ps)
 extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 1.eps"),
-   outfile = ("../figures/Sparks et al Figure 1.eps"),
+   file = ("../figures/Sparks et al Figure 2.eps"),
+   outfile = ("../figures/Sparks et al Figure 2.eps"),
    options = "-dEPSCrop"
 )
-knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
+knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
 ```
@@
   grViz(
-    "digraph Fig1 {
+    "digraph Fig3 {
     graph [fontsize = 8, nodesep=0.5]
@@
 ))
-rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 2.eps")
+rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 3.eps")
 extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 2.eps"),
-   outfile = ("../figures/Sparks et al Figure 2.eps"),
+   file = ("../figures/Sparks et al Figure 3.eps"),
+   outfile = ("../figures/Sparks et al Figure 3.eps"),
    options = "-dEPSCrop"
 )
-knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
+knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
 ```

### 2021-10-15 analysis/paper/paper.Rmd
Update keywords
Remove colophon for submission

@@
 
-**Keywords: open science, open data, reproducible research, FAIR data**
+**Keywords: Data Science, Computational Biology, Techniques**
 
@@
 ```
-
-\newpage
-
-# Colophon
-
-This report was generated on $`r Sys.time()`$ using the following computational environment and dependencies:
-
-```{r colophon, cache = FALSE}
-# which R packages and versions?
-sessioninfo::session_info()
-```
-
-The current Git commit details are:
-
-```{r}
-# what commit is this file at? You may need to change the path value
-# if your Rmd is not in analysis/paper/
-git2r::repository("../..")
-```

### 2022-01-18 R/doi2bib.R
add more details about doi2bib in documentation

@@ -14,7 +14,8 @@
 #'
 #' @note This function is take from the unrelased (on CRAN) \R package,
 #'  \pkg{doi2bib} by William Keith Morris available from GitHub under the MIT
-#'  Licence.
+#'  Licence.  The full package has been forked to Open Plant Pathology's
+#'  GitHub account \url{https://github.com/openplantpathology/doi2bib}.
 #'
 #' @return a \code{list}, returned invisibly, of bibtex references as
 #'   \code{character} strings, as well as writing to file if \code{file} is

### 2022-02-10 R/doi2bib.R
Delete unused function

@@ -1,136 +1,0 @@
-#' Convert DOI to Bibtex
-#'
-#' Convert a digital object identifier (\acronym{DOI}) string into a bibtex
-#' entry using the web service \url{http://www.doi2bib.org}.
-#'
-#' @param ... One or more \acronym{DOI}s, as \code{character} strings. If
-#'   arguments are named, names will replace default citekeys.
-#' @param file an optional \code{character} string. If used, the bibtex
-#'   references are sent to \code{file} rather than being returned.
-#' @param append \code{logical}. Append results to file?
-#' @param quiet \code{logical}. By default, bibtex references are printed to the
-#'   console. By setting \code{quiet} to \code{TRUE}, this behaviour will be
-#'   prevented.
-#'
-#' @note This function is take from the unrelased (on CRAN) \R package,
-#'  \pkg{doi2bib} by William Keith Morris available from GitHub under the MIT
-#'  Licence.  The full package has been forked to Open Plant Pathology's
-#'  GitHub account \url{https://github.com/openplantpathology/doi2bib}.
-#'
-#' @return a \code{list}, returned invisibly, of bibtex references as
-#'   \code{character} strings, as well as writing to file if \code{file} is
-#'   specified.
-#'
-#' @importFrom httr accept content GET
-#' @importFrom methods setGeneric setMethod signature
-#' @importFrom xml2 xml_text xml_find_all
-#' @importFrom stats setNames
-#'
-#' @examples
-#' doi2bib(Margules2000 = "10.1038/35012251")
-#' doi2bib(Margules2000 = "10.1038/35012251",
-#'         Myers2000    = "10.1038/35002501",
-#'         Moilanen     = "978-0199547777")
-#' @author William Keith Morris, \email{wkmor1@@gmail.com}
-#' @references \url{https://github.com/wkmor1/doi2bib}
-#' @export
-
-setGeneric("doi2bib",
-           function(...,
-                    file,
-                    append = TRUE,
-                    quiet = FALSE) {
-             standardGeneric("doi2bib")
-           },
-           signature = signature("..."))
-
-replace_citekeys <-
-  function(refs, nms) {
-    setNames(mapply(function(ref, nm) {
-      ifelse(nchar(nm) < 1,
-             ref,
-             sub("([^\\{]+\\{)[^,]+", paste0("\\1", nm), ref))
-    },
-    refs,
-    nms,
-    SIMPLIFY = FALSE),
-    nms)
-  }
-
[…]

### 2022-04-08 analysis/paper/paper.Rmd
Address Reviewer 1 L83 “We randomly selected 300 articles”.
Attempt to reword the article selection criteria to eliminate confusion about how the articles were randomly selected. Address reviewers thoughts on bias.

@@
 In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
-We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
-The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
-A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
-Notes regarding the selection of articles can be found in the file, "Reproducibility_in_plant_pathology_notes.ods", available in this paper's repository in `/inst/extdata'.
-The pages list was numbered from page one and went to page 150.
+We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, _e.g._ quartile range or citation index, to represent the discipline.
+The aim was to gather as complete an overview of the status of reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
+From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
+Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
+Initially there were four evaluators, later a fifth was added and the list was recreated.
+There were three evaluation events that took place to increase the yearly coverage of the evaluations.
+Each evaluator was assigned 50 articles to evaluate during an evaluation event.
+A list of randomly generated page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals.
 This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
+
+Articles were then manually selected by visiting the journals' websites and selecting the articles within which the randomly assigned page numbers fell, _i.e._, if the page number was 32, the article that started on page 28 and ended on page 35 was selected as it contained page 32.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
+All methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
 

### 2022-04-08 analysis/paper/paper.Rmd
Add more citations for brms as per the package

@@
 
-The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
-Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.15.0) [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+The statistical analysis was performed using R version 4.1.0 [@RCT2022] on an Apple MacBook Air (M1, 2020).
+Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.16.3) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
 

### 2022-04-08 analysis/paper/paper.Rmd
Update citation for the R Core Team

@@
 When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
+A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
 

### 2022-04-08 analysis/paper/paper.Rmd
Make brms version number reproducible by extracting from package in text

@@
 The statistical analysis was performed using R version 4.1.0 [@RCT2022] on an Apple MacBook Air (M1, 2020).
-Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.16.3) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
 

### 2022-04-08 analysis/paper/paper.Rmd
Refined wording around article selection section

@@
 
-In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
+In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
 We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, _e.g._ quartile range or citation index, to represent the discipline.
@@
 Each evaluator was assigned 50 articles to evaluate during an evaluation event.
-A list of randomly generated page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals.
-This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+A list of randomly generated numbers to represent page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for .
+This was done because some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.

### 2022-04-08 analysis/paper/paper.Rmd
Improve reproducibility by fetching R package versions in-text

@@
 
-The statistical analysis was performed using R version 4.1.0 [@RCT2022] on an Apple MacBook Air (M1, 2020).
+The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Air (M1, 2020).
 Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()`  (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' ((version `r packageVersion("bayesplot")`)) [@Gabry2019].
 
@@
 
-Data were visualised using 'ggplot2' (version 3.3.5) [@Wickham2016], 'ggpubr' (version 0.4.0) [@Kassambara2020] and patchwork (version 1.1.1) [@Pedersen2020].
+Data were visualised using 'ggplot2' ((version `r packageVersion("ggplot2")`)) [@Wickham2016], 'ggpubr' ((version `r packageVersion("ggpubr")`)) [@Kassambara2020] and patchwork ((version `r packageVersion("patchwork")`)) [@Pedersen2020].
+
+All methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
 

### 2022-04-08 analysis/paper/paper.Rmd
Clarify text in Article Selection and Scoring Criteria sections
Mainly in response to Reviewer 1's comments.

@@
 
-## Article Selection
+## Article Selection and Evaluation Events
 
@@
 In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
-All methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
+
+The each of the five authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)) in three different scoring events as their time allowed for their participation.
+In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.
 
@@
 
-Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)).
-
 Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
-The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
+The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
+This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.
 

### 2022-04-08 analysis/paper/paper.Rmd
Edit for clarity, remove redundant "R" from sentence

@@
 When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
+A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
 

### 2022-04-08 analysis/paper/paper.Rmd
Update authors' contributions
clean up parens around package versions

@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' ((version `r packageVersion("bayesplot")`)) [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 
@@
 A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
-N.J.G. provided five-year impact factors.
-A.H.S., E.DP., Z.F. and K.dSA. evaluated articles for scoring.
+E.DP. provided five-year impact factors.
+A.H.S., E.DP., Z.F. K.A. and N.G. evaluated articles for scoring.
 A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.

### 2022-04-08 analysis/paper/paper.Rmd
Revise figure 1 caption and add title as per Reviewer 1

@@
 
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate the effects of factors affecting the reproducibility of papers published in 20 plant pathology journals or plant pathology focused articles from other specialised journals.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of papers published in 20 plant pathology journals or plant pathology focused articles from other specialised journals.
 Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws.
@@
 
-p <- p + plot_annotation(tag_levels = "A")
+p <- p + plot_annotation(tag_levels = "A",
+                         title = "Bayesian posterior distributions of evaluation score models"
+                         )
+
 ggsave(filename = "../figures/Sparks et al Figure 1.eps",

### 2022-04-08 analysis/paper/paper.Rmd
Add figure title to Figure 2 as per Reviewer 1

@@
 p <- (A | B) / (C | D)
-p <- p + plot_annotation(tag_levels = "A")
+p <- p + plot_annotation(tag_levels = "A",
+                         title = "Aggregated article scores")
 ggsave(filename = "../figures/Sparks et al Figure 2.eps",

### 2022-04-08 analysis/paper/paper.Rmd
Add metadata & title to Figure 3 as suggested by Reviewer 1

@@
 
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
+    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
+    'An open and reproducible workflow'
+
+    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
     Question; Methodology; Data; Analysis; Manuscript;
 
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
+    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Helvetica]
     Description; Availability; Citation

### 2022-04-08 R/workflow_dia.R
Delete workflow_dia.R, this is encapsulated in Figure 3 in paper.Rmd

@@ -1,47 +1,0 @@
-
-#' Create workflow diagram figure
-#'
-#' Custom function to create a workflow diagram figure, 'Figure 1'.
-#'
-#' @return PDF of workflow diagram
-#' @export workflow_dia
-#'
-#' @examples
-#' workflow_dia()
-#'
-
-workflow_dia <- function() {
-  p <- DiagrammeRsvg::export_svg(
-    DiagrammeR::grViz(
-      "digraph Fig1 {
-    graph [fontsize = 8, nodesep=0.5]
-
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
-    Question; Methodology; Data; Analysis; Manuscript;
-
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
-    Description; Availability; Citation
-
-    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
-    'Binary Code'; 'Binary File'; Supplement
-
-    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-    'Source Code'; 'Data File'; 'Public Repository';
-
-    Question->Methodology->Data->Analysis
-    Analysis->Manuscript
-    Methodology->Description
-    Methodology->Citation
-    Methodology->Availability
-    Manuscript->Supplement
-    Data->'Data File'->'Public Repository'
-    Analysis->'Binary Code'->Supplement
-    Analysis->'Source Code'->'Public Repository'
-    Data->'Binary File'->Supplement
-  }",
-  width = 1000,
-  height = 750
-    )
-  )
-  return(rsvg::rsvg_pdf(charToRaw(p)))
-}

### 2022-04-08 analysis/paper/paper.Rmd
Update Figure 3's title and adds metadata

@@
 
+    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
+    Question
+
     node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
-    Question; Methodology; Data; Analysis; Manuscript;
+    Methodology; Data; Analysis; Manuscript;
 
@@
     node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-    'Source Code'; 'Data File'; 'Public Repository';
+    'Source Code'; 'Data File'; Metadata; 'Public Repository';
 
@@
     Data->'Data File'->'Public Repository'
+    Data->Metadata->'Public Repository'
     Analysis->'Binary Code'->Supplement

### 2022-04-08 analysis/paper/paper.Rmd
Address Reviewer 1 comments about value judgments

@@
 The use of programming or scripting languages such as R, Julia, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
+This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
 

### 2022-04-08 analysis/paper/paper.Rmd
Address Reviewer 1's comments on grammar
Address Reviewer 1's comment about citation issue

@@
 It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
-However, very often biological specimens such as strains, cultures or cultivars are often not available.
+However, biological specimens such as strains, cultures or cultivars are not available.
 These cases do constitute a lack of reproducibility but will not be covered here.
@@
 
-The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
-[@Khaliq2020] have done.
+The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as @Khaliq2020 have done.
 Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of _Ascochyta rabiei_ conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].

### 2022-04-08 analysis/paper/paper.Rmd
Add subtitles to figure 2 as per Reviewer 1's comments

@@
   ylab("Score") +
-  xlab(NULL)
+  xlab(NULL) +
+  ggtitle(label = "Computational methods availability")
 
@@
   xlab(NULL) +
-  ylab(NULL)
+  ylab(NULL) +
+  ggtitle(label = "Software availability")
 
@@
   geom_bar(fill = "black") +
-  ylab("Score")
+  ylab("Score") +
+  ggtitle(label = "Software citatations")
 
@@
   geom_bar(fill = "black") +
-  ylab(NULL)
+  ylab(NULL) +
+  ggtitle(label = "Data availability")
 

### 2022-04-08 analysis/paper/paper.Rmd
simplify citation handling

@@
 The first level is including tables of raw data or code with the paper as a supplemental file.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden et al.
-[-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an _e-**X**tra_\* with reproducible examples for readers to refer to.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an _e-**X**tra_\* with reproducible examples for readers to refer to.
 This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
 
-At the second level, Lehner et al.
-[-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
+At the second level, -@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Likewise, Duku et al.
-[-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
-A final example is provided by Carleson et al.
-[-@carleson2019population] who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on GitHub, while providing all data on OSF.
+Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+A final example is provided by @carleson2019population who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on GitHub, while providing all data on OSF.
 
@@
 [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
-Similarly, Carleson et al. [-@carleson2019population] provided all data on OSF [-@Carleson_Grünwald_2019].
+Similarly, @carleson2019population provided all data on OSF [@Carleson_Grünwald_2019].
 
@@
 used [-@Miorini2018, [-@Miorini2019]].
-Kamvar et al.
-[-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
+@Kamvar2015 took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
 While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

### 2022-04-24 analysis/paper/paper.Rmd
correct number of articles evaluated

--- 2022-04-08 analysis/paper/paper.Rmd
@@
 Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and reproducibility.
+We randomly selected 450 articles published from 2012 to 2018 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and reproducibility.
 We found that most of the articles were not following protocols for open science, and were failing to share data or code in a reproducible way.
@@
 It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
-However, biological specimens such as strains, cultures or cultivars are not available.
+However, very often biological specimens such as strains, cultures or cultivars are often not available.
 These cases do constitute a lack of reproducibility but will not be covered here.
@@
 
-## Article Selection and Evaluation Events
+## Article Selection
 
-In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
-We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, _e.g._ quartile range or citation index, to represent the discipline.
-The aim was to gather as complete an overview of the status of reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
-From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
-Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
-Initially there were four evaluators, later a fifth was added and the list was recreated.
-There were three evaluation events that took place to increase the yearly coverage of the evaluations.
-Each evaluator was assigned 50 articles to evaluate during an evaluation event.
-A list of randomly generated numbers to represent page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for .
-This was done because some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
+In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
+We randomly selected 450 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
+The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
+A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
+In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
+Notes regarding the selection of articles can be found in the file, "Reproducibility_in_plant_pathology_notes.ods", available in this paper's repository in `/inst/extdata'.
+The pages list was numbered from page one and went to page 150.
+This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
 This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
-
-Articles were then manually selected by visiting the journals' websites and selecting the articles within which the randomly assigned page numbers fell, _i.e._, if the page number was 32, the article that started on page 28 and ended on page 35 was selected as it contained page 32.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
-
-The each of the five authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)) in three different scoring events as their time allowed for their participation.
-In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.
 
@@
 
+Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)).
+
 Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
-The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.
+The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
+This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
 
@@
 When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
+A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
 
@@
 
-The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Air (M1, 2020).
-Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
+Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.15.0) [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
 
@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()`  (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].
 
@@
 
-Data were visualised using 'ggplot2' ((version `r packageVersion("ggplot2")`)) [@Wickham2016], 'ggpubr' ((version `r packageVersion("ggpubr")`)) [@Kassambara2020] and patchwork ((version `r packageVersion("patchwork")`)) [@Pedersen2020].
-
-All methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
+Data were visualised using 'ggplot2' (version 3.3.5) [@Wickham2016], 'ggpubr' (version 0.4.0) [@Kassambara2020] and patchwork (version 1.1.1) [@Pedersen2020].
 
@@
 
-The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as @Khaliq2020 have done.
+The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al.
+[@Khaliq2020] have done.
 Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of _Ascochyta rabiei_ conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
@@
 The use of programming or scripting languages such as R, Julia, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
+This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
 
@@
 A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
-E.DP. provided five-year impact factors.
-A.H.S., E.DP., Z.F. K.A. and N.G. evaluated articles for scoring.
+N.J.G. provided five-year impact factors.
+A.H.S., E.DP., Z.F. and K.dSA. evaluated articles for scoring.
 A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
@@
 
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of papers published in 20 plant pathology journals or plant pathology focused articles from other specialised journals.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate the effects of factors affecting the reproducibility of papers published in 20 plant pathology journals or plant pathology focused articles from other specialised journals.
 Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws.
@@
 
-p <- p + plot_annotation(tag_levels = "A",
-                         title = "Bayesian posterior distributions of evaluation score models"
-                         )
-
+p <- p + plot_annotation(tag_levels = "A")
 ggsave(filename = "../figures/Sparks et al Figure 1.eps",
@@
 p <- (A | B) / (C | D)
-p <- p + plot_annotation(tag_levels = "A",
-                         title = "Aggregated article scores")
+p <- p + plot_annotation(tag_levels = "A")
 ggsave(filename = "../figures/Sparks et al Figure 2.eps",
@@
 
-    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
-    'An open and reproducible workflow'
+    node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
+    Question; Methodology; Data; Analysis; Manuscript;
 
-    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
-    Question
-
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
-    Methodology; Data; Analysis; Manuscript;
-
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Helvetica]
+    node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
     Description; Availability; Citation
@@
     node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-    'Source Code'; 'Data File'; Metadata; 'Public Repository';
+    'Source Code'; 'Data File'; 'Public Repository';
 
@@
     Data->'Data File'->'Public Repository'
-    Data->Metadata->'Public Repository'
     Analysis->'Binary Code'->Supplement

### 2022-04-24 analysis/paper/paper.Rmd
use Rda files rather than Rds files for model fit vis in paper

@@
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate the effects of factors affecting the reproducibility of papers published in 20 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws.
+Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where 'y' is the data's density and 'y~rep~' are ten random posterior draws.
 Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
@@
 
-m1 <- pp_check(readRDS(here("data/m1.Rds")))
-m2 <- pp_check(readRDS(here("data/m2.Rds")))
-m3 <- pp_check(readRDS(here("data/m3.Rds")))
-m4 <- pp_check(readRDS(here("data/m4.Rds")))
-m5 <- pp_check(readRDS(here("data/m5.Rds")))
-m6 <- pp_check(readRDS(here("data/m6.Rds")))
+load(file = here("data/m1.Rda"))
+load(file = here("data/m2.Rda"))
+load(file = here("data/m3.Rda"))
+load(file = here("data/m4.Rda"))
+load(file = here("data/m5.Rda"))
+load(file = here("data/m6.Rda"))
+
+pp_m1 <- pp_check(m1)
+pp_m2 <- pp_check(m2)
+pp_m3 <- pp_check(m3)
+pp_m4 <- pp_check(m4)
+pp_m5 <- pp_check(m5)
+pp_m6 <- pp_check(m6)
 
 # put them all together
-p <- (m1 | m2) / (m3 | m4) / (m5 | m6)
+p <- (pp_m1 | pp_m2) / (pp_m3 | pp_m4) / (pp_m5 | pp_m6)
 

### 2022-04-24 tests/testthat/test-import_notes.R
Remove context and correct expected no. of cols

@@ -1,11 +1,9 @@
-context("import_notes()")
-
-# Test that import_notes() returns expected results, a tibble with 47 cols
+# Test that import_notes() returns expected results, a tibble with 49 cols
 # and columns that are set to factor are factors. All other default as read.
 test_that("import_notes returns expected results", {
   notes <- import_notes()
   expect_true(tibble::is_tibble(notes))
-  expect_equal(ncol(notes), 48)
+  expect_equal(ncol(notes), 49)
   expect_equal(class(notes$journal), "factor")
   expect_equal(class(notes$art_class), "factor")
   expect_equal(class(notes$art_class), "factor")

### 2022-04-24 analysis/paper/paper.Rmd

--- 2022-04-08 analysis/paper/paper.Rmd
@@
 
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of papers published in 20 plant pathology journals or plant pathology focused articles from other specialised journals.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
 Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws.

### 2022-04-25 analysis/paper/paper.Rmd
Move model files to inst/extdata

@@
 
-load(file = here("data/m1.Rda"))
-load(file = here("data/m2.Rda"))
-load(file = here("data/m3.Rda"))
-load(file = here("data/m4.Rda"))
-load(file = here("data/m5.Rda"))
-load(file = here("data/m6.Rda"))
+load(file = here("inst/extdata/m1.Rda"))
+load(file = here("inst/extdata/m2.Rda"))
+load(file = here("inst/extdata/m3.Rda"))
+load(file = here("inst/extdata/m4.Rda"))
+load(file = here("inst/extdata/m5.Rda"))
+load(file = here("inst/extdata/m6.Rda"))
 

### 2022-04-25 tests/testthat/test-workflow_dia.R
Remove unnecessary test

@@ -1,6 +1,0 @@
-# test diversities table -------------------------------------------------------
-
-test_that("workflow_dia() returns an rsvg_pdf object", {
-  expect_type(capture.output(workflow_dia()),
-              "character")
-          })

### 2022-04-25 analysis/paper/paper.Rmd
check installed packages before knitting and install missing

@@
 ```{r, setup, echo = FALSE, message=FALSE}
-library("officer")
-library("dplyr")
-library("janitor")
-library("here")
-library("flextable")
 library("Reproducibility.in.Plant.Pathology")
-library("tidyr")
-library("DiagrammeR")
-library("DiagrammeRsvg")
-library("rsvg")
-library("ggplot2")
-library("bayesplot")
-library("patchwork")
+
+packages <- c(
+  "officer",
+  "dplyr",
+  "janitor",
+  "here",
+  "flextable",
+  "tidyr",
+  "DiagrammeR",
+  "DiagrammeRsvg",
+  "rsvg",
+  "ggplot2",
+  "bayesplot",
+  "patchwork"
+)
+
+install.packages(setdiff(packages, rownames(installed.packages())))
 

### 2022-04-25 analysis/paper/paper.Rmd
add more missing R libs to knit

@@
 packages <- c(
+  "extrafont",
   "officer",
   "dplyr",
+  "ggpubr",
+  "ggplot2",
   "janitor",

### 2022-04-25 analysis/paper/paper.Rmd
load packages necessary to knit the paper
specify the repository so that the paper knits in RStudio
add dplyr version to paper

@@
 
-install.packages(setdiff(packages, rownames(installed.packages())))
+install.packages(setdiff(packages,
+                         rownames(installed.packages())),
+                 repos = "http://cran.us.r-project.org")
+
+invisible(
+  lapply(
+    packages,
+    library,
+    character.only = TRUE
+  )
+)
 
@@
 The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.
+This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package (version `r packageVersion("dplyr")`) [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.
 

### 2022-04-25 analysis/paper/paper.Rmd
Correct typos where there were double "(" and ")"

@@
 
-Data were visualised using 'ggplot2' ((version `r packageVersion("ggplot2")`)) [@Wickham2016], 'ggpubr' ((version `r packageVersion("ggpubr")`)) [@Kassambara2020] and patchwork ((version `r packageVersion("patchwork")`)) [@Pedersen2020].
+Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].
 

### 2022-04-25 R/table_of_journals.R
Remove table_of_journals()
This is all done on the fly in the paper.Rmd file now

@@ -1,19 +1,0 @@
-
-#' Create table of journals surveyed
-#' @param rrpp `data.frame` of article evaluations
-#' @return \CRANpkg{pander} table of journals surveyed
-#' @export table_of_journals
-#'
-#' @examples
-#' googlesheets4::gs4_deauth()
-#' rrpp <- googlesheets4::read_sheet(
-#'"https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"
-#')
-#' table_of_journals(rrpp)
-#'
-#'
-table_of_journals <- function(rrpp) {
-  rrpp_journals <- as.data.frame(table(rrpp[, 1]))
-  names(rrpp_journals) <- c("Journal", "Count")
-  return(pander::pander(rrpp_journals))
-}

### 2022-04-25 tests/testthat/test-table_of_journals.R

@@ -1,11 +1,0 @@
-# test diversities table -------------------------------------------------------
-
-test_that("table_of_journals() returns a pander object of journals surveyed", {
-  googlesheets4::gs4_deauth()
-  rrpp <- googlesheets4::read_sheet(
-  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M"
-  )
-
-  expect_type(capture.output(table_of_journals(rrpp)),
-              "character")
-})

### 2022-04-25 README.rmd
Reknit README after updating text to reflect package structure

@@
 
-This repository is organized as an R package. There are custom R functions, 
-`table_of_journals()` and `workflow_dia()` that are used in this repository, along with a bibliography file of the articles that were examined and the notes that are located in `inst/extdata` directory.
+This repository is organized as an R package.
+There is one R function, `import_notes()` that is used in the paper's figure and table making when the file, `analysis/paper/paper.Rmd` is knit.
+Additionally, a bibliography file, "references.bib", of the articles that were examined and the notes from the evaluation, "Reproducibility_in_plant_pathology_notes.ods" of the articles are both located in `inst/extdata` directory.
 We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.
@@
 
-<https://adamhsparks.com/>
+<https://adamhsparks.netlify.app>
 

### 2022-04-25 R/import_notes.R
Reformat code in function

@@ -25,24 +25,30 @@ import_notes <- function() {
     reproducibility_score <- journal <- year <- . <- NULL
 
   notes <- readODS::read_ods(
-    system.file("extdata",
-                "Reproducibility_in_plant_pathology_notes.ods",
-                package = "Reproducibility.in.Plant.Pathology"),
+    system.file(
+      "extdata",
+      "Reproducibility_in_plant_pathology_notes.ods",
+      package = "Reproducibility.in.Plant.Pathology"
+    ),
     na = "NA",
     sheet = "article_evaluations"
   )
 
   IF_5year <- readODS::read_ods(
-    system.file("extdata",
-                "Reproducibility_in_plant_pathology_notes.ods",
-                package = "Reproducibility.in.Plant.Pathology"),
+    system.file(
+      "extdata",
+      "Reproducibility_in_plant_pathology_notes.ods",
+      package = "Reproducibility.in.Plant.Pathology"
+    ),
     na = "NA",
     sheet = "5yr IF"
   )
 
   notes <-
     notes %>%
-    dplyr::left_join(x = notes, y = IF_5year, by = c("journal" = "journal")) %>%
+    dplyr::left_join(x = notes,
+                     y = IF_5year,
+                     by = c("journal" = "journal")) %>%
     dplyr::mutate(IF_5year =
                     dplyr::if_else(
                       condition = is.na(IF_5year),
@@ -62,7 +68,10 @@ import_notes <- function() {
   # calculate total possible score for a paper
   total_possible <-
     notes %>%
-    dplyr::select(comp_mthds_avail, software_avail, software_cite, data_avail) %>%
+    dplyr::select(comp_mthds_avail,
+                  software_avail,
+                  software_cite,
+                  data_avail) %>%
     dplyr::mutate(total_possible = rowSums(!is.na(.)) * 3) %>%
     dplyr::select(total_possible)
 

### 2022-04-25 analysis/paper/paper.Rmd
Move discussion on scoring methodology to Discussion section

@@
 However, some papers did not use specialized software therefore they were not scored for this category.
-
-We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
-We have based our scoring decisions on our own experiences in the field of plant pathology.
-While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
-Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
-The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
 

### 2022-04-25 analysis/paper/paper.Rmd
insert linebreak between sentences for Rmd

@@
 One article scored 100% or was classed as fully reproducible.
-No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
+No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
+The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
 

### 2022-04-25 analysis/paper/paper.Rmd
Update data availability scores and move text to discussion

@@
 
-However, data availability was mostly not available with 243 or 81.5% scoring '0' where the data was not available or mentioned in the article.
-However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).
+However, data availability was mostly not available with 361, or 80.2%, scoring '0' where the data was not available or mentioned in the article.
+However, more articles, 44 or 9.8%, scored '3' than scored '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).
 
 The most frequently cited software was SAS.
-The remainder were mostly specialised software except for Microsoft Excel, tied for 9th (Table \@ref(tab:software-used)).
+The remainder were mostly specialised software except for Microsoft Excel in a 3-way tie for 9th (Table \@ref(tab:software-used)).
 
-Unfortunately using our scoring method, most articles scored poorly for reproducibility or openness.
+Most articles, , scored poorly for reproducibility or openness.
 Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
@@
 The software availability score was better as was the citing of software and versions used.
+
+# Discussion
+
+We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
+We have based our scoring decisions on our own experiences in the field of plant pathology.
+While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have access to them.
+Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
+The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
+
 SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS.
 It is interesting to note however, that with the popularity of Python that it does not even appear in our survey results whereas R was the fourth most commonly used software.
-
-# Discussion
 

### 2022-04-25 analysis/paper/paper.Rmd
Add 'egg' and 'tidyr' to the libs used for plot construction

@@
   "extrafont",
+  "egg",
   "officer",
@@
   "bayesplot",
+  "tidyr",
   "patchwork"

### 2022-04-25 analysis/paper/paper.Rmd
import the notes once to save compilation time

@@
 ```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
+rrpp <- import_notes()
+
 rrpp_software <-
-  import_notes() %>%
+  rrpp %>% 
   transform(software_used = strsplit(software_used, ",")) %>%

### 2022-04-25 analysis/paper/paper.Rmd
clarify how many papers were evaluated in the caption for fig 1

@@
 
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
 Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws.

### 2022-04-25 analysis/paper/paper.Rmd
Add new figure of overall scores and revise aggregated scores to include NA
This addressed Reviewer 1's comments about not showing all data.

The scores for all values, including the NA values are shown and any scores not observed, e.g., computational methods didn't have any 2 values observed and this figure now shows that as being "0"

@@
 
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
-(B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-(C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-(D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
-a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
+Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a "}
+p <-
+  ggplot(data = rrpp, aes(x = reproducibility_score)) +
+  geom_histogram(binwidth = 10,
+                 fill = "black") +
+  ggtitle("Reproducibility index value")
 
-rrpp <- import_notes()
-theme_set(theme_classic())
-A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
-  geom_bar(fill = "black") +
-  ylab("Score") +
-  xlab(NULL) +
-  ggtitle(label = "Computational methods availability")
-
-B <- ggplot(rrpp, aes(y = software_avail)) +
-  geom_bar(fill = "black") +
-  xlab(NULL) +
-  ylab(NULL) +
-  ggtitle(label = "Software availability")
-
-C <- ggplot(rrpp, aes(y = software_cite)) +
-  geom_bar(fill = "black") +
-  ylab("Score") +
-  ggtitle(label = "Software citatations")
-
-D <- ggplot(rrpp, aes(y = data_avail)) +
-  geom_bar(fill = "black") +
-  ylab(NULL) +
-  ggtitle(label = "Data availability")
-
-# put them all together
-p <- (A | B) / (C | D)
-p <- p + plot_annotation(tag_levels = "A",
-                         title = "Aggregated article scores")
 ggsave(filename = "../figures/Sparks et al Figure 2.eps",
@@
 knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
+```
+
+\newpage
+
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
+(B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+(C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
+(D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
+a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+theme_set(theme_classic())
+
+rrpp_long <-
+  pivot_longer(rrpp,
+               cols = c(
+                 "comp_mthds_avail",
+                 "software_avail",
+                 "software_cite",
+                 "data_avail"
+               ))
+
+p <- ggplot(rrpp_long, aes(x = as.factor(value))) +
+  geom_bar(fill = "black") +
+  ylab("Count") +
+  xlab("Article Score") +
+  ggtitle("Aggregated article scores") +
+  facet_wrap(name ~ .)
+p <- tag_facet(p = p, tag_pool = LETTERS, x = 5, family = "Arial")
+
+ggsave(filename = "../figures/Sparks et al Figure 3.eps",
+       plot = p,
+       width = 6,
+       height = 6,
+       units = "in",
+       device = cairo_ps)
+extrafont::embed_fonts(
+   file = ("../figures/Sparks et al Figure 3.eps"),
+   outfile = ("../figures/Sparks et al Figure 3.eps"),
+   options = "-dEPSCrop"
+)
+knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
 ```
@@
 ))
-rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 3.eps")
+
+rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 4.eps")
 extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 3.eps"),
-   outfile = ("../figures/Sparks et al Figure 3.eps"),
+   file = ("../figures/Sparks et al Figure 4.eps"),
+   outfile = ("../figures/Sparks et al Figure 4.eps"),
    options = "-dEPSCrop"
 )
-knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
+
+knitr::include_graphics(path = "../figures/Sparks et al Figure 4.eps")
 ```

### 2022-04-25 analysis/paper/paper.Rmd
add english library

@@
   "egg",
+  "english",
   "officer",

### 2022-04-25 analysis/paper/paper.Rmd
Import notes to use r notation in-text for values
Text formatting in Markdown only

@@
 
+rrpp <- import_notes()
+
 knitr::opts_chunk$set(
@@
 
-# Abstract {-#abstract}
+# Abstract {#abstract .unnumbered}
 
@@
 
-In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, _e.g._, field trials that span years and locations or complex glasshouse experiments.
+In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, *e.g.*, field trials that span years and locations or complex glasshouse experiments.
 Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":
@@
 In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
-We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, _e.g._ quartile range or citation index, to represent the discipline.
+We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
 The aim was to gather as complete an overview of the status of reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
@@
 
-Articles were then manually selected by visiting the journals' websites and selecting the articles within which the randomly assigned page numbers fell, _i.e._, if the page number was 32, the article that started on page 28 and ended on page 35 was selected as it contained page 32.
-In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
+Articles were then manually selected by visiting the journals' websites and selecting the articles within which the randomly assigned page numbers fell, *i.e.*, if the page number was 32, the article that started on page 28 and ended on page 35 was selected as it contained page 32.
+In cases where an article was not suitable, *e.g.*, a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
 
@@
 The first level is including tables of raw data or code with the paper as a supplemental file.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an _e-**X**tra_\* with reproducible examples for readers to refer to.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra*\* with reproducible examples for readers to refer to.
 This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
 
-At the second level, -@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
+At the second level, -@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
-A final example is provided by @carleson2019population who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on GitHub, while providing all data on OSF.
+Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+A final example is provided by @carleson2019population who hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.
 
@@
 
-The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as @Khaliq2020 have done.
-Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of _Ascochyta rabiei_ conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+The fourth level includes packaging the analysis as a software package, *e.g.*, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as @Khaliq2020 have done.
+Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
 used [-@Miorini2018, [-@Miorini2019]].
@@
 Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, _e.g._, 'a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.'
-This allows end-users to identify what was used and identify the methods used more accurately.
+Provide a full description of all equipment used, *e.g.*, 'a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.' This allows end-users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, _e.g._, a package version, what effect it had on your research.
+This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on your research.
 
@@
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, _e.g._, comma separated (CSV) or tab separated (TSV) files.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.*, comma separated (CSV) or tab separated (TSV) files.
 This also helps ensure that the data are reusable.
@@
 To make your data the most widely discoverable and usable, ensure that it has a persistent identifier.
-A digital object identifier (DOI) is the most common ([https://www.doi.org/](https://www.doi.org/)) but the Handle.Net Registry (HNR) ([https://handle.net/](https://handle.net/)) is also an option.
+A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but the Handle.Net Registry (HNR) (<https://handle.net/>) is also an option.
 There are different options for generating a DOI for your data and other materials.
@@
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
-For more on FAIR data, visit Go-Fair [https://www.go-fair.org/fair-principles/](https://www.go-fair.org/fair-principles/).
+For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.
 
@@
 As we prepared this letter, we became more aware of the urgent need to spread and establish an open science attitude and culture among plant pathologists.
-To assist in fostering this sort of change in our discipline, Open Plant Pathology (OPP), <https://www.openplantpathology.org>, an institution-independent and non-funded initiative, was founded in January 2018 by two of this letter's co-authors, Del Ponte and Sparks, in 2018 with the following vision: “foster a diverse community culture that values openness, transparency and reproducibility of scientific research data and methods in our field”.
+To assist in fostering this sort of change in our discipline, Open Plant Pathology (OPP), <https://www.openplantpathology.org>, an institution-independent and non-funded initiative, was founded in January 2018 by two of this letter's co-authors, Del Ponte and Sparks, in 2018 with the following vision: "foster a diverse community culture that values openness, transparency and reproducibility of scientific research data and methods in our field".
 We started OPP with a minimal infrastructure and support from other enthusiastic colleagues that allows members to interact sharing and gathering ideas on how we can improve the openness and reproducibility in our discipline.

### 2022-04-25 analysis/paper/paper.Rmd
Update package citations and use inline r code to generate values
This means that when the values in the notes change, the text is updated correspondingly so we have fewer chances of mistakes in reporting values in the results, etc.

@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version 0.10.0) [@Makowski2019].
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019].
 
-Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].
+Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020], 'egg' (version `r packageVersion("egg")`) [@Auguie2019] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].
 
@@
 
-Forty-eight articles scored 0% out of a possible 100% for reproducibility.
-The mean value was 31.2% and the median value was 33.3%.
-One article scored 100% or was classed as fully reproducible.
 No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
-The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
 
-Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
-Two hundred eighty-seven articles, 96%, were classed as '0' and nine articles, 0.03%, appeared to not use any computational methods.
+Out of the `r nrow(rrpp)` articles that were evaluated, `r length(which(rrpp$reproducibility_score == 0))` articles scored 0% out of a possible 100% for reproducibility.
+The mean value was `r round(mean(rrpp$reproducibility_score), 1)`% and the median value was `r round(median(rrpp$reproducibility_score), 1)`%.
+There were `r length(which(rrpp$reproducibility_score == 100))` (`r round(length(which(rrpp$reproducibility_score == 100))/nrow(rrpp), 2) * 100`%) articles that scored 100% or were classed as fully reproducible.
 
-More articles did a good job of using software that was reasonably available to anyone with 206 scoring '2' or '3' (Figure \@ref(fig:articleScores)B).
+The majority of the articles, `r length(which(rrpp$art_class == "Fundamental"))`, were classed as fundamental, with the remaining `r length(which(rrpp$art_class != "Fundamental"))` classed as applied.
+
+Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
+`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
+
+More articles did a good job of using software that was reasonably available to anyone with `r length(which(rrpp$software_avail >= 2))` (`r round(length(which(rrpp$software_avail >= 2))/nrow(rrpp), 2) * 100`%) scoring '2' or '3' (Figure \@ref(fig:articleScores)B) for software availability.
 

### 2022-04-25 analysis/paper/paper.Rmd
Remove notes being imported for figures only, now at start of doc

@@
 ```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
-rrpp <- import_notes()
-
 rrpp_software <-

### 2022-04-25 analysis/paper/paper.Rmd
Clarifies random effects in models
Flesh out description of journal instruction for authors in results

@@
 The random effects were year and assignee for all models excepting the model which tested for year effects.
-In this model, the random effects were the publication title and assignee.
+In all models, the random effects were the publication title and assigned evaluator.
 
@@
 
+Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` scored '100' or fully reproducible.
+
 No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
+
+Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
+Only two journals, _Plant Pathology_ and _Tropical Plant Pathology_ have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
+Three had no instructions at all, _Forest Pathology_, _Phytopathologia Mediterranea_ and _Revista Mexicana de Fitopatología_, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
 

### 2022-04-25 analysis/paper/paper.Rmd
Complete the use of R to provide result values and edit results

@@
 
-Software citations were also reasonably well reported in the literature with 120 scoring '2' where the main software was cited with version numbers and 57 scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)C).
+Software citations were also reasonably well reported in the literature with `r length(which(rrpp$software_cite == 2))` (`r round(length(which(rrpp$software_cite == 2))/nrow(rrpp), 2) * 100`%) scoring '2' where the main software was cited with version numbers and `r length(which(rrpp$software_cite == 3))` (`r round(length(which(rrpp$software_cite == 3))/nrow(rrpp), 2) * 100`%) scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)C).
 
-However, data availability was mostly not available with 361, or 80.2%, scoring '0' where the data was not available or mentioned in the article.
-However, more articles, 44 or 9.8%, scored '3' than scored '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).
+However, data availability was mostly not available with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the data was not available or mentioned in the article.
+However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%) scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
 
-The most frequently cited software was SAS.
+The most frequently cited software was `r names(which.max(table(rrpp$software_used)))`.
+Other statistical software packages were frequently cited, SPSS (3rd) R (4th), GenStat and STATISTICA (7th).
 The remainder were mostly specialised software except for Microsoft Excel in a 3-way tie for 9th (Table \@ref(tab:software-used)).
 
-Most articles, , scored poorly for reproducibility or openness.
-Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
+# Discussion
 
-The software availability score was better as was the citing of software and versions used.
-
-# Discussion
+Journals can encourage authors to deposit their data and code
 

### 2022-04-25 analysis/paper/paper.Rmd
Refer to figure 2 and revise computer used for analysis

@@
 
-The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Air (M1, 2020).
+The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
 Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
@@
 None of the factors that were tested for had an effect on the reproducibility score.
-
-Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` scored '100' or fully reproducible.
+Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100' or fully reproducible (Figure \@ref(fig:reproScore)).
 

### 2022-04-26 analysis/paper/paper.Rmd
Edit software section of results and tables

@@
 
-The most frequently cited software was `r names(which.max(table(rrpp$software_used)))`.
-Other statistical software packages were frequently cited, SPSS (3rd) R (4th), GenStat and STATISTICA (7th).
-The remainder were mostly specialised software except for Microsoft Excel in a 3-way tie for 9th (Table \@ref(tab:software-used)).
+```{r softwareCited, echo=FALSE, include=FALSE}
+# tally up software used for the next paragraph
+rrpp_software <-
+  rrpp %>% 
+  transform(software_used = strsplit(software_used, ",")) %>%
+  unnest(software_used) %>%
+  mutate(software_used = trimws(software_used)) %>%
+  mutate(software_used = toupper(software_used))
+
+tab <- table(rrpp_software$software_used)
+tab_s <- as.data.frame(sort(tab))
+tab_s <-
+  tab_s %>%
+  arrange(desc(Freq)) %>%
+  filter(Freq %in% head(unique(Freq), 10)) %>% 
+  rename("Software" = "Var1", "Frequency" = "Freq")
+```
+
+The most frequently cited software was `r tab_s[1, 1]`, where different versions were not distinguished.
+The next three software packages were statistical software, `r tab_s[2, 1]`,  `r tab_s[3, 1]` and  `r tab_s[4, 1]` with two other statistical software packages frequently cited, GENSTAT and STATISTICA.
+The remainder were mostly specialised software except for Microsoft Excel (Table \@ref(tab:software-used)).
 
@@
 ```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
-rrpp_software <-
-  rrpp %>% 
-  transform(software_used = strsplit(software_used, ",")) %>%
-  unnest(software_used) %>%
-  mutate(software_used = trimws(software_used)) %>%
-  mutate(software_used = toupper(software_used)) # convert all to uppercase to standardise
-
-rrpp_software %>%
-  tabyl(software_used) %>%
-  adorn_pct_formatting() %>%
-  select(c(-percent, -valid_percent)) %>%
-  rename(`Software Used` = software_used) %>%
-  arrange(-n) %>%
-  slice(seq_len(14)) %>%
-  drop_na() %>%
+tab_s %>%
   flextable() %>%
   autofit() %>%
-  set_caption(
-    "The top ten sofware programs that were found to be used in the papers that were surveyed."
-  )
+  set_caption("The top ten sofware programs that were found to be used in the papers that were surveyed.")
 ```

### 2022-04-26 analysis/paper/paper.Rmd
Add text describing ROPE and add new results from analysis

@@
 
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019].
+Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] and the Region of Practical Equivalence (ROPE) was set to -0.1 to 0.1.
 
@@
 
-None of the factors that were tested for had an effect on the reproducibility score.
 Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100' or fully reproducible (Figure \@ref(fig:reproScore)).
 
+_Physiological and Molecular Plant Pathology_ was the only journal to show a negative effect on the reproducibility score, the analysis was unable to detect any effect of any other journal titles.
+
+There was no effect of article class found.
+
+Articles with a molecular focus tended to be more likely ranked high for reproducibility and openness but the difference was not strong enough to be detected with the analysis used.
+
+Articles published in journals with a larger five year impact factor were more likely to be more open and reproducible but the analysis was unable to detect any differences.
+
 No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
+The analysis was unable to detect any differences in the effect of access policy on the openness and reproducibility of the evaluated articles, but in journals where the policy was to allow both open and pay-for-fee access, the articles were less likely to be open and reproducible when compared to journals that were completely open.
+
+We were unable to detect any observable differences in the years that publications were submitted.
+The year 2016 appears to be have a higher score than prior and following years, but the analysis was undecided on the effect of all years on the publications' openness and reproducibility.
 

### 2022-04-26 analysis/paper/paper.Rmd
Set seed before using random draws of model runs
line breaks for sentences in Rmd
Replace "_" with "*" for italics

@@
 
-_Physiological and Molecular Plant Pathology_ was the only journal to show a negative effect on the reproducibility score, the analysis was unable to detect any effect of any other journal titles.
+*Physiological and Molecular Plant Pathology* was the only journal to show a negative effect on the reproducibility score, the analysis was unable to detect any effect of any other journal titles.
 
@@
 Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
-Only two journals, _Plant Pathology_ and _Tropical Plant Pathology_ have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
-Three had no instructions at all, _Forest Pathology_, _Phytopathologia Mediterranea_ and _Revista Mexicana de Fitopatología_, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
+Only two journals, *Plant Pathology* and *Tropical Plant Pathology* have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
+Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
 
@@
 
+set.seed(23)
 theme_set(theme_classic())

### 2022-04-29 analysis/paper/paper.Rmd
Update software citations and revise Discussion opening

@@
 
-The most frequently cited software was `r tab_s[1, 1]`, where different versions were not distinguished.
-The next three software packages were statistical software, `r tab_s[2, 1]`,  `r tab_s[3, 1]` and  `r tab_s[4, 1]` with two other statistical software packages frequently cited, GENSTAT and STATISTICA.
-The remainder were mostly specialised software except for Microsoft Excel (Table \@ref(tab:software-used)).
+In the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished.
+The next three programs were statistical software, `r tab_s[2, 1]` (2nd),  `r tab_s[3, 1]` (3rd) and  `r tab_s[4, 1]` (4th) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
+The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (5th), BLAST(6th), and BioEdit (10th) or phylogenetic analysis MrBayes (7th).
+The most general-purpose software cited in the top 10 was Excel&reg; (9th)."
+The Python programming language was cited only twice, not appearing in the top ten.
 
@@
 
-Journals can encourage authors to deposit their data and code
+MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
+The second, third and fourth, and eighth most often cited software packages were all statistical programs.
+SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
+The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel&reg;.
+It is interesting to note however, that with the popularity of Python that it only appears in the survey twice and in 2020 in both articles, not enough times to be in the top 10 most-cited.
 
-We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
-We have based our scoring decisions on our own experiences in the field of plant pathology.
-While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have access to them.
+We recognise that the scoring methods were developed by the authors specifically for this evaluation and are not entirely objective and acknowledge that we have based our scoring decisions on our own experiences in the field of plant pathology.
+However, without assigning values, it is not possible to attempt to qualify or quantify where our discipline stands in regards to computational reproducibility.
+
+In the authors' view, while many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have access to them.
 Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
-The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
-
-SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS.
-It is interesting to note however, that with the popularity of Python that it does not even appear in our survey results whereas R was the fourth most commonly used software.
+The authors believe that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible monetary cost.
 

### 2022-04-29 R/import_notes.R
Add a unique ID to the notes on import
Not all articles have a DOI. Simply create a UID (row number) to identify the article if necessary.

@@ -91,5 +91,15 @@ import_notes <- function() {
                       ) / total_possible
                     ) * 100)
 
+  # create mean assignee rating value
+  notes <-
+    notes %>%
+    dplyr::group_by(assignee) %>%
+    dplyr::summarise(mean_assignee = mean(reproducibility_score)) %>%
+    dplyr::full_join(notes, by = "assignee")
+
+  # add a unique identifier value to each article since not all have a DOI
+  notes$uid <- seq_along(1:nrow(notes))
+
   return(notes)
 }

### 2022-04-29 analysis/paper/paper.Rmd
Move statement about journals' role to workflow section
Capitalise "Contributions" to match other headings' format
Correct text on analysis findings

@@
 
-There was no effect of article class found.
+There was no effect of article class or impact factor found.
 
-Articles with a molecular focus tended to be more likely ranked high for reproducibility and openness but the difference was not strong enough to be detected with the analysis used.
-
-Articles published in journals with a larger five year impact factor were more likely to be more open and reproducible but the analysis was unable to detect any differences.
+Articles with a molecular focus skewed to a higher ranking reproducibility and openness but the difference was not strong enough to be detected with the analysis used.
 
@@
 
+Journals can encourage authors to deposit their data and code by providing instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources.
+
 A general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
@@
 
-# Authors' contributions
+# Authors' Contributions
 

### 2022-04-30 analysis/paper/paper.Rmd
replace "often" with frequently
Remove the word "often"

@@
 MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
-The second, third and fourth, and eighth most often cited software packages were all statistical programs.
+The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
 SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
@@
 Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
-This open sharing of code and data often leads to greater impact as work is cited if resources such as code or data are reused.
+This open sharing of code and data leads to greater impact as work is cited if resources such as code or data are reused.
 With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.

### 2022-04-30 analysis/paper/paper.Rmd
Response to reviewer 2, L164 comment
Respond to reviewer 2 L154 comment

@@
 It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
-However, biological specimens such as strains, cultures or cultivars are not available.
+However, frequently biological specimens such as strains, cultures or cultivars are often not available.
 These cases do constitute a lack of reproducibility but will not be covered here.
@@
 
-Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100' or fully reproducible (Figure \@ref(fig:reproScore)).
+Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100%' or fully reproducible (Figure \@ref(fig:reproScore)).
 

### 2022-04-30 analysis/paper/paper.Rmd
Respond to reviewer 2, L76-77 comment on the word "often"
Respond to R2, Line 335 (333) on 'help' > 'helps'

@@
 It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
-However, frequently biological specimens such as strains, cultures or cultivars are often not available.
+However, frequently biological specimens such as strains, cultures or cultivars are not available.
 These cases do constitute a lack of reproducibility but will not be covered here.
@@
 Second, it benefits the reviewer by aiding their understanding of the work done and gives them more materials to use to make suggestions for improvements when reviewing and the end-user or reader is better able to verify the validity of the methods used and recreate the analysis.
-Perhaps more importantly, sharing these details help with knowledge transfer by showing other interested parties how something was done rather than simply describing it.
+Perhaps more importantly, sharing these details helps with knowledge transfer by showing other interested parties how something was done rather than simply describing it.
 Lastly, openly sharing your work and making it discoverable can lead to new collaborations and synergistic ideas.

### 2022-04-30 analysis/paper/paper.Rmd
clean up typos

@@
 The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (5th), BLAST(6th), and BioEdit (10th) or phylogenetic analysis MrBayes (7th).
-The most general-purpose software cited in the top 10 was Excel&reg; (9th)."
+The most general-purpose software cited in the top 10 was Excel® (9th).
 The Python programming language was cited only twice, not appearing in the top ten.
@@
 SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
-The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel&reg;.
+The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel®.
 It is interesting to note however, that with the popularity of Python that it only appears in the survey twice and in 2020 in both articles, not enough times to be in the top 10 most-cited.

### 2022-05-01 analysis/paper/paper.Rmd
Put R libraries in alphabetical order

@@
 packages <- c(
-  "extrafont",
+  "DiagrammeR",
+  "DiagrammeRsvg",
+  "bayesplot",
+  "bayestestR",
+  "brms",
+  "dplyr",
   "egg",
   "english",
+  "extrafont",
+  "flextable",
+  "ggplot2",
+  "ggpubr",
+  "here",
+  "janitor",
+  "knitr",
   "officer",
-  "dplyr",
-  "ggpubr",
-  "ggplot2",
-  "janitor",
-  "here",
-  "flextable",
+  "patchwork",
+  "rsvg",
   "tidyr",
-  "DiagrammeR",
-  "DiagrammeRsvg",
-  "rsvg",
-  "ggplot2",
-  "bayesplot",
-  "tidyr",
-  "patchwork"
+  "tools"
 )

### 2022-05-01 analysis/paper/paper.Rmd
Load knitr, don't use namespacing

@@
 
-knitr::opts_chunk$set(
+opts_chunk$set(
   collapse = TRUE,

### 2022-05-01 analysis/paper/paper.Rmd
remove duplicate call to load extrafont lib
Remove text on overall scores to earlier section

@@
 
-library("extrafont")
 font_import()
@@
 Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
-
-Out of the `r nrow(rrpp)` articles that were evaluated, `r length(which(rrpp$reproducibility_score == 0))` articles scored 0% out of a possible 100% for reproducibility.
-The mean value was `r round(mean(rrpp$reproducibility_score), 1)`% and the median value was `r round(median(rrpp$reproducibility_score), 1)`%.
-There were `r length(which(rrpp$reproducibility_score == 100))` (`r round(length(which(rrpp$reproducibility_score == 100))/nrow(rrpp), 2) * 100`%) articles that scored 100% or were classed as fully reproducible.
 

### 2022-05-01 analysis/paper/paper.Rmd
Respond to reviewer 2 with more clarification on what Docker is

@@
 
-The fourth level includes packaging the analysis as a software package, *e.g.*, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as @Khaliq2020 have done.
-Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+The fourth level includes packaging the full analysis in a containerized software application, *e.g.*, Docker.
+Docker is an open source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyses) with the operating system required to run that analysis on any computer.
+Using an open source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
+As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package that enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
 When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.

### 2022-05-01 analysis/paper/paper.Rmd
Use 'here' and reformat code chunk

@@
 p <- p + plot_annotation(tag_levels = "A",
-                         title = "Bayesian posterior distributions of evaluation score models"
-                         )
+                         title = "Bayesian posterior distributions of evaluation score models")
 
-ggsave(filename = "../figures/Sparks et al Figure 1.eps",
+ggsave(
+  filename = here("analysis/figures/Sparks et al Figure 1.eps"),
   plot = p,
@@
   units = "in",
-       device = cairo_ps)
-extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 1.eps"),
-   outfile = ("../figures/Sparks et al Figure 1.eps"),
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks et al Figure 1.eps"),
+  outfile = here("analysis/figures/Sparks et al Figure 1.eps"),
   options = "-dEPSCrop"
 )
-knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
+include_graphics(path = here("analysis/figures/Sparks et al Figure 1.eps"))
 ```
@@
   geom_histogram(binwidth = 10,
-                 fill = "black") +
-  ggtitle("Reproducibility index value")
+                 fill = "black",
+                 colour = "black") +
+  xlab("Reproducibility score (%)")
 
-ggsave(filename = "../figures/Sparks et al Figure 2.eps",
+ggsave(
+  filename = here("analysis/figures/Sparks et al Figure 2.eps"),
   plot = p,
@@
   units = "in",
-       device = cairo_ps)
-extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 2.eps"),
-   outfile = ("../figures/Sparks et al Figure 2.eps"),
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks et al Figure 2.eps"),
+  outfile = here("analysis/figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
 )
-knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
+include_graphics(path = here("analysis/figures/Sparks et al Figure 2.eps"))
 ```
@@
 a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
-theme_set(theme_classic())
 
@@
   xlab("Article Score") +
-  ggtitle("Aggregated article scores") +
+  ggtitle("Reproducibility criteria ranks") +
   facet_wrap(name ~ .)
-p <- tag_facet(p = p, tag_pool = LETTERS, x = 5, family = "Arial")
+p <- tag_facet(
+  p = p,
+  tag_pool = LETTERS,
+  x = 5,
+  family = "Arial",
+  open = "",
+  close = ""
+)
 
-ggsave(filename = "../figures/Sparks et al Figure 3.eps",
+ggsave(
+  filename = here("analysis/figures/Sparks et al Figure 3.eps"),
   plot = p,
@@
   units = "in",
-       device = cairo_ps)
-extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 3.eps"),
-   outfile = ("../figures/Sparks et al Figure 3.eps"),
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks et al Figure 3.eps"),
+  outfile = here("analysis/figures/Sparks et al Figure 3.eps"),
   options = "-dEPSCrop"
 )
-knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
+include_graphics(path = here("analysis/figures/Sparks et al Figure 3.eps"))
 ```
@@
 
-    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
+    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
     Question
 
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
+    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
     Methodology; Data; Analysis; Manuscript;
 
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Helvetica]
+    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Arial]
     Description; Availability; Citation
@@
   height = 750
-))
+  )
+)
 
-rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 4.eps")
-extrafont::embed_fonts(
-   file = ("../figures/Sparks et al Figure 4.eps"),
-   outfile = ("../figures/Sparks et al Figure 4.eps"),
+rsvg_ps(svg = charToRaw(p),
+        file = here("analysis/figures/Sparks et al Figure 4.eps"))
+embed_fonts(
+  file = here("analysis/figures/Sparks et al Figure 4.eps"),
+  outfile = here("analysis/figures/Sparks et al Figure 4.eps"),
   options = "-dEPSCrop"
@@
 
-knitr::include_graphics(path = "../figures/Sparks et al Figure 4.eps")
+include_graphics(path = here("analysis/figures/Sparks et al Figure 4.eps"))
 ```

### 2022-05-01 analysis/paper/paper.Rmd
Revise text about results based on new analysis

@@
 
-Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100%' or fully reproducible (Figure \@ref(fig:reproScore)).
+There were `r length(which(rrpp$reproducibility_score == 100))` (`r round(length(which(rrpp$reproducibility_score == 100))/nrow(rrpp), 2) * 100`%) articles that scored 100% or were classed as fully reproducible (Figure \@ref(fig:reproScore)).
+`r toTitleCase(as.character(english::english(length(which(rrpp$reproducibility_score == 0)))))` (`r round(length(which(rrpp$reproducibility_score == 0))/nrow(rrpp), 2) * 100`%) of articles were scored at 0% out of a possible 100% for reproducibility (Figure \@ref(fig:reproScore)).
+The mean value was `r round(mean(rrpp$reproducibility_score), 1)`% and the median value was `r round(median(rrpp$reproducibility_score), 1)`%.
 
-*Physiological and Molecular Plant Pathology* was the only journal to show a negative effect on the reproducibility score, the analysis was unable to detect any effect of any other journal titles.
+The analysis was unable to detect any effect of journal titles on reproducibility scores.
 
-There was no effect of article class or impact factor found.
+There was no effect of journal title, article class or impact factor found.
 

### 2022-05-01 analysis/paper/paper.Rmd
Move library loading to later in doc

@@
 ```{r, setup, echo = FALSE, message=FALSE}
-library("Reproducibility.in.Plant.Pathology")
-
 packages <- c(
@@
 )
+
+library("Reproducibility.in.Plant.Pathology")
 

### 2022-05-01 analysis/paper/paper.Rmd
Five of us evaluated the papers

@@
   set_caption(
-    "Articles were scored in four areas for reproducibility on a scale of '0' to '3' by four independent assessors to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.")
+    "Articles were scored in four areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.")
 ```

### 2022-05-01 analysis/paper/paper.Rmd
use same terminology "index values"

@@
   xlab("Article Score") +
-  ggtitle("Reproducibility criteria ranks") +
+  ggtitle("Reproducibility criteria index values") +
   facet_wrap(name ~ .)

### 2022-05-01 analysis/paper/paper.Rmd
correct where OSF.io was used and defined first

@@
 Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
-A final example is provided by @carleson2019population who hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.
+A final example is provided by @carleson2019population who hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
 
@@
 [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
-Similarly, @carleson2019population provided all data on OSF [@Carleson_Grünwald_2019].
+Similarly, @carleson2019population provided all data on OSF.io [@Carleson_Grünwald_2019].
 
@@
 There are different options for generating a DOI for your data and other materials.
-FigShare, Zenodo and OSF all offer persistent archives along with a services to generate a DOI for your materials.
+FigShare, Zenodo and OSF.io all offer persistent archives along with a services to generate a DOI for your materials.
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
@@
 Once you have determined how to best manage your source code and the data sets for analysis the next step is to consider how to share your data.
-Providers such as FigShare, Dataverse, OSF.io (the Open Science Framework) and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
+Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
 
@@
 Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
-It is a best practice to always ensure that you have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF and generated a DOI for the materials to help ensure continued accessibility.
+It is a best practice to always ensure that you have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF.io and generated a DOI for the materials to help ensure continued accessibility.
 Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.

### 2022-05-01 analysis/paper/paper.Rmd
We evaluated the state of "computational reproducibility"

@@
 
-In this work we have evaluated the state of reproducibility in the plant pathology literature and presented suggestions for areas of improvement.
+In this work we have evaluated the state of computational reproducibility in the plant pathology literature and presented suggestions for areas of improvement.
 As we prepared this letter, we became more aware of the urgent need to spread and establish an open science attitude and culture among plant pathologists.

### 2022-05-01 analysis/paper/paper.Rmd
Evaluated articles from 2012 to 2021

@@
 Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 450 articles published from 2012 to 2018 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and reproducibility.
+We randomly selected 450 articles published from 2012 to 2021 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and reproducibility.
 We found that most of the articles were not following protocols for open science, and were failing to share data or code in a reproducible way.

### 2022-05-02 analysis/paper/paper.Rmd
Rethink title to reflect the aims of our analysis
Edit section on good examples
Include comment on the non-open nature of the RICEPEST Python scripts and correct duplicated mention of Carlson and Grünwald

@@
 ---
-title: "Reproducibility in plant pathology: where do we stand and a way forward"
+title: "Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward"
 author:
@@
 Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
-A final example is provided by @carleson2019population who hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
+However, even this example is not totally open as it requires ArcGIS, an expensive proprietary software, to run the provided Python scripts for the RICEPEST model [@Savary2014].
+This highlights the difficulty in making work completely open and reproducible, further work could be undertaken to make the Python scripts rely totally on free-open-source-software but the work as it it provided here does allow for the complete reproducibility of the paper as written provided with the proper tools.
 
@@
 [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
-Similarly, @carleson2019population provided all data on OSF.io [@Carleson_Grünwald_2019].
+Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
 

### 2022-05-04 analysis/paper/paper.Rmd
Correct Miorini in-text citation
Edit text for repro score, art class and IF

@@
 
-The analysis was unable to detect any effect of journal titles on reproducibility scores.
-
-There was no effect of journal title, article class or impact factor found.
+The analysis detected that the journal title did have an effect on the reproducibility score but there was no effect of article class or impact factor.
 
@@
 When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
-used [-@Miorini2018, [-@Miorini2019]].
+used [-@Miorini2018; -@Miorini2019].
 @Kamvar2015 took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.

### 2022-05-04 analysis/paper/paper.Rmd
Add statement on analysis of statement on instructions for sharing
Add new model for sharing instructions from journal

@@
 Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
+While the analysis did not detect an effect of the journals' instructions for sharing or depositing data and or code, the more detailed the instructions, the higher the article scored.
 
@@
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws.
+Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy, (F) Year of Publication and (G) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws.
 Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
@@
 
-load(file = here("inst/extdata/m1.Rda"))
-load(file = here("inst/extdata/m2.Rda"))
-load(file = here("inst/extdata/m3.Rda"))
-load(file = here("inst/extdata/m4.Rda"))
-load(file = here("inst/extdata/m5.Rda"))
-load(file = here("inst/extdata/m6.Rda"))
+load(file = here("inst/extdata/m_e.Rda"))
+load(file = here("inst/extdata/m_f.Rda"))
+load(file = here("inst/extdata/m_g.Rda"))
+load(file = here("inst/extdata/m_h.Rda"))
+load(file = here("inst/extdata/m_i.Rda"))
+load(file = here("inst/extdata/m_j.Rda"))
+load(file = here("inst/extdata/m_k.Rda"))
 
-pp_m1 <- pp_check(m1)
-pp_m2 <- pp_check(m2)
-pp_m3 <- pp_check(m3)
-pp_m4 <- pp_check(m4)
-pp_m5 <- pp_check(m5)
-pp_m6 <- pp_check(m6)
+pp_m_e <- pp_check(m_e)
+pp_m_f <- pp_check(m_f)
+pp_m_g <- pp_check(m_g)
+pp_m_h <- pp_check(m_h)
+pp_m_i <- pp_check(m_i)
+pp_m_j <- pp_check(m_j)
+pp_m_k <- pp_check(m_k)
 
 # put them all together
-p <- (pp_m1 | pp_m2) / (pp_m3 | pp_m4) / (pp_m5 | pp_m6)
+p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j) / pp_m_k
 

### 2022-05-05 R/import_notes.R
Fix bug where "TRUE" became "1" in the 'open' col w/ `import_notes()`

@@ -34,6 +34,8 @@ import_notes <- function() {
     sheet = "article_evaluations"
   )
 
+  notes$open <- gsub("1", "TRUE", x = notes$open)
+
   IF_5year <- readODS::read_ods(
     system.file(
       "extdata",

### 2022-05-16 analysis/paper/paper.Rmd
don't cache R output
This was causing the table of scoring criteria to not update

@@
   dev = "cairo_pdf",
-  cache = TRUE
+  cache = FALSE
 )

### 2022-05-16 analysis/paper/paper.Rmd
Wordsmith and fix citations

@@
 One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
-> Peng, R.
-> [-@Peng2009].
+> @Peng2009.
 > *Reproducible research and Biostatistics*.
@@
 
-It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
-However, frequently biological specimens such as strains, cultures or cultivars are not available.
+Plant pathologists routinely provide information on protocols and chemicals allowing for reproducibility.
+However, frequently biological specimens such as strains, cultures or cultivars are not available after publication.
 These cases do constitute a lack of reproducibility but will not be covered here.

### 2022-05-16 analysis/paper/paper.Rmd
Edit discussion including Hill et al. and fixing order of descriptions

@@
 
-While the articles that were surveyed did not score well, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.
+While the majority of the articles that were surveyed did not score well, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.
 
@@
 
-At the second level, -@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
+At the second level, in our search of the literature, we found that @Hill2019 shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
+The scripts provided used an R package, _checkpoint_ [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that are necessary to reproduce the work rather than defaulting to the latest versions.
+However, the scripts did not run unhindered, as the supplementary materials suggested that they should, without changes to the data, but with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.
+
+The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
+Sparks et al.
+[@Sparks2011; @Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
+@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
@@
 This highlights the difficulty in making work completely open and reproducible, further work could be undertaken to make the Python scripts rely totally on free-open-source-software but the work as it it provided here does allow for the complete reproducibility of the paper as written provided with the proper tools.
-
-The third level is the use of proper data repositories such as GitHub, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
-Sparks et al.
-[-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
-Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
 
@@
 When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
-used [-@Miorini2018; -@Miorini2019].
+used [@Miorini2018; @Miorini2019].
 @Kamvar2015 took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.

### 2022-05-20 R/import_inter-rater_scores.R
add import_inter-rater_scores()

@@ -1,0 +1,87 @@
+
+#' Import scoring notes checking inter-rater repeatability
+#'
+#' Imports, formats data into proper types and calculates the final
+#' reproducibility score.
+#'
+#' @return A [tibble::tibble()] object of reproducibility score notes formatted
+#' for use in analysis and manuscript preparation
+#' @export import_interrater_scores
+#'
+#' @examples
+#' notes <- import_notes()
+#' pander::pander(head(notes))
+#'
+#' @importFrom magrittr "%>%"
+#'
+
+import_interrater_scores <- function() {
+  # CRAN Note Avoidance
+  data_avail <-
+    comp_mthds_avail <-
+    software_avail <- software_avail_corrected <-
+    software_cite <-
+    IF_5year <- art_class <- repro_inst <- abbreviation <-
+    assignee <-
+    reproducibility_score <- journal <- year <- . <- NULL
+
+  notes <- readODS::read_ods(
+    system.file(
+      "extdata",
+      "Reproducibility_in_plant_pathology_notes.ods",
+      package = "Reproducibility.in.Plant.Pathology"
+    ),
+    na = "NA",
+    sheet = "inter-rater_score_check"
+  )
+
+  notes <-
+    notes %>%
+    dplyr::mutate(doi = as.factor(doi)) %>%
+    dplyr::mutate(art_class = as.factor(art_class)) %>%
+    dplyr::mutate(molecular = as.factor(molecular)) %>%
+    dplyr::mutate(assignee = as.factor(assignee))
+
+  # add reproducibility score as a percent of total possible
+  #
+  # calculate total possible score for a paper
+  total_possible <-
+    notes %>%
+    dplyr::select(
+      comp_mthds_avail,
+      software_avail,
+      software_avail_corrected,
+      software_cite,
+      data_avail
+    ) %>%
+    dplyr::mutate(total_possible = rowSums(!is.na(.)) * 3) %>%
+    dplyr::select(total_possible)
+
+  # calculate reproducibility score
+  notes <-
+    notes %>%
+    tibble::add_column(total_possible) %>%
+    dplyr::rowwise() %>%
+    dplyr::mutate(reproducibility_score =
+                    (
+                      sum(
+                        comp_mthds_avail,
+                        software_avail_corrected,
+                        software_cite,
+                        data_avail,
+                        na.rm = TRUE
+                      ) / total_possible
+                    ) * 100)
+
[…]

### 2022-05-20 analysis/paper/paper.Rmd
Add section on data cleaning

@@
 However, some papers did not use specialized software therefore they were not scored for this category.
+
+## Data Cleaning
+
+Efforts were made to standardise the scoring as much as possible.
+In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and these scores were modified after discussion to match the agreed on ratings.
+For example, a paper was rated as having a `software_avail` rating of `3`, but the evaulator noted that Excel had been used.
+Here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
+In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
+In these cases, Excel was added to the `software_used` column.
 

### 2022-05-20 analysis/paper/paper.Rmd
state that molecular focus was dropped
Revert "fixes theme_classic() set 2X, "
This reverts commit 7ec6b00c9b2200cdd4eb42436378843a70ea4150.

@@
 # Results
+
+Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was not used in the overall evaluation.
 
@@
 
-load(file = here("inst/extdata/m_e.Rda"))
 load(file = here("inst/extdata/m_f.Rda"))
@@
 
-pp_m_e <- pp_check(m_e)
 pp_m_f <- pp_check(m_f)
@@
 pp_m_j <- pp_check(m_j)
-pp_m_k <- pp_check(m_k)
+pp_m_j <- pp_check(m_k)
 
 # put them all together
-p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j) / pp_m_k
+p <- (pp_m_f | pp_m_g) / (pp_m_h | pp_m_i) / (pp_m_j | pp_m_k)
 

### 2022-05-20 analysis/paper/paper.Rmd
fixes theme_classic() set 2X,

--- 2022-05-20 analysis/paper/paper.Rmd
@@
 set.seed(23)
-theme_set(theme_classic())
 color_scheme_set(scheme = "gray")

### 2022-05-20 analysis/paper/paper.Rmd
remove extra model vis that's not used

@@
 load(file = here("inst/extdata/m_j.Rda"))
-load(file = here("inst/extdata/m_k.Rda"))
 
@@
 pp_m_j <- pp_check(m_j)
-pp_m_k <- pp_check(m_k)
 
 # put them all together
-p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j) / pp_m_k
+p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j)
 

### 2022-05-20 analysis/paper/paper.Rmd
adjust model object names for plots
Correct caption for updated models included in paper

--- 2022-05-20 analysis/paper/paper.Rmd
@@
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy, (F) Year of Publication and (G) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws.
+Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Five Year Impact Factor of Journal, (D) Journal Open Access Policy, (E) Year of Publication and (F) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws.
 Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

### 2022-05-20 analysis/paper/paper.Rmd
correct model object names
Render images in Word document
Remove spaces in filenames and tell Rmd to display output graphic

@@
 Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Five Year Impact Factor of Journal, (D) Journal Open Access Policy, (E) Year of Publication and (F) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws.
-Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}
 
@@
 pp_m_j <- pp_check(m_j)
-pp_m_j <- pp_check(m_k)
+pp_m_k <- pp_check(m_k)
 
@@
 ggsave(
-  filename = here("analysis/figures/Sparks et al Figure 1.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks et al Figure 1.eps"),
-  outfile = here("analysis/figures/Sparks et al Figure 1.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks et al Figure 1.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
 ```
@@
 ggsave(
-  filename = here("analysis/figures/Sparks et al Figure 2.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks et al Figure 2.eps"),
-  outfile = here("analysis/figures/Sparks et al Figure 2.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks et al Figure 2.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
 ```
@@
 (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
-a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+a methods paper.", cache=FALSE, fig.env='figure'}
 
@@
 ggsave(
-  filename = here("analysis/figures/Sparks et al Figure 3.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks et al Figure 3.eps"),
-  outfile = here("analysis/figures/Sparks et al Figure 3.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks et al Figure 3.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
 ```
@@
 Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
-Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
+Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}
 
@@
 rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks et al Figure 4.eps"))
+        file = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
 embed_fonts(
-  file = here("analysis/figures/Sparks et al Figure 4.eps"),
-  outfile = here("analysis/figures/Sparks et al Figure 4.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
   options = "-dEPSCrop"
@@
 
-include_graphics(path = here("analysis/figures/Sparks et al Figure 4.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
 ```

### 2022-05-20 analysis/paper/paper.Rmd
Cleanup graphic formatting
No need for DPI, using EPS files

@@
   dev = c("postscript"),
-  fig.width = 3.31,
-  fig.height = 3.31,
   out.width = "100%",
-  dpi = 300,
   comment = "#>",

### 2022-05-20 analysis/paper/paper.Rmd
Correct caption that was incomplete

@@
 ```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a "}
+Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value."}
 p <-

### 2022-05-20 analysis/paper/paper.Rmd
add a missing "," after e.g.

@@
 (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-(D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g.
-a methods paper.", cache=FALSE, fig.env='figure'}
+(D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
 

### 2022-05-20 analysis/paper/paper.Rmd
clarify dropping molecular focus as an article criteria used in evaluation

@@
 
-Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was not used in the overall evaluation.
+Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was dropped from the analysis and is not reported here.
 

### 2022-05-20 analysis/paper/paper.Rmd
Import inter-rater notes at beginning

@@
 )
+
+ir <- import_interrater_scores()
 ```

### 2022-05-20 analysis/paper/paper.Rmd
Discuss inter-rater differences in results

@@
 
-Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was dropped from the analysis and is not reported here.
+The differences between the co-authors' classifications of the article class as `applied` or `fundamental` had no differences in the five articles that were evaluated by all of the co-authors (Figure \@ref(fig:irArtClass)A).
+However, differences in evaluators' interpretations of whether or not an article had a molecular focus or not led to this scoring criteria being dropped from the analysis and is not included in this analysis (Figure \@ref(fig:irArtClass)B).
+
+There was reasonable agreement among the authors when evaluating whether software was cited properly or not and freely and openly available (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).
+All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)C, \@ref(fig:irCriteria)C).
+
+The overall reproducibility scores assigned by authors to the five articles evaluated to check for inter-rater differences showed some differences (Figure \@ref(fig:irReproScore)).
+The article that had the greatest difference, 13 to 33%, was DOI "10.1007/s12600-021-00902-2" with a standard deviation of `r ir %>% filter(doi == "10.1007/s12600-021-00902-2") %>% summarise(x = round(sd(reproducibility_score), 1))`.
+All other articles had standard deviation scores of less than 4 (Table \@ref(tab:interRaterSD)).
+However, all article scores largely agreed and fell below 50% (Figure \@ref(fig:irReproScore)).
 

### 2022-05-20 analysis/paper/paper.Rmd
include new figures for inter-rater checks

@@
 
+```{r interRaterSD, echo=FALSE, message=FALSE, warning=FALSE}
+ir %>%
+  group_by(doi) %>%
+  summarise(x = round(sd(reproducibility_score), 1)) %>%
+  rename(`Standard Deviation` = x) %>%
+  rename(DOI = doi) %>%
+  flextable() %>%
+  set_table_properties(layout = "autofit") %>%
+  set_caption(
+    "Standard deviation of reproducibility scores for five articles evaluated by all five co-authors to check for differences in article ratings.")
+```
+
+\newpage
+
 # Figures
@@
 set.seed(23)
-theme_set(theme_classic())
+
 color_scheme_set(scheme = "gray")
@@
 
-```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value."}
-p <-
-  ggplot(data = rrpp, aes(x = reproducibility_score)) +
-  geom_histogram(binwidth = 10,
-                 fill = "black",
-                 colour = "black") +
-  xlab("Reproducibility score (%)")
+```{r irArtClass, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator classifications of (A) an articles focus being molecular techniques (TRUE/FALSE) and (B) an article's class (Fundamental/Applied).
+Where all five articles were scored by all five authors to check for agreement between the evaluations.", cache=FALSE, fig.env='figure'}
+
+theme_set(theme_classic())
+a <- ggplot(ir, aes(y = doi,
+                      fill = molecular)) +
+  geom_bar() +
+  scale_fill_grey(name = "") +
+  ylab("DOI") +
+  xlab("Count") +
+  ggtitle("Molecular Focus") +
+  theme(legend.position = "top")
+
+b <- ggplot(ir, aes(y = doi,
+                      fill = art_class)) +
+  geom_bar() +
+  scale_fill_grey(name = "") +
+  xlab("Count") +
+  ylab("") +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank()
+  ) +
+  ggtitle("Article Class") +
+  theme(legend.position = "top")
+
+p <- (a | b)
+p <- p + plot_annotation(tag_levels = "A",
+                         title = "Evaluator agreement in article classifications")
 
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
   plot = p,
@@
 include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
+```
+
+\newpage
+
+```{r irCriteria, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator agreement for five articles scored for (A) software being properly cited, (B) software used being freely and openly available, (C) computational methods used, e.g.
+scripts or other self-written programs were freely and openly available and (D) data represented in the paper were freely and openly available.
+Note that one evaluator rated an article with computational methods available as 'NA', which is reflected in that article having only four evaluations for this criteria.", cache=FALSE, fig.env='figure'}
+a <- ggplot(ir,
+            aes(y = doi,
+                x = software_cite)) +
+  ylab("DOI") +
+  xlab("") +
+  xlim(c(0, 3)) +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) +
+  geom_density_ridges() +
+  ggtitle("Software Cited")
+
+b <- ggplot(ir,
+            aes(y = doi,
+                x = software_avail)) +
+  ylab("") +
+  xlab("") +
+  geom_density_ridges() +
+  theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank()
+  ) +
+  xlim(c(0, 3)) +
+  ggtitle("Software Available")
+
+c <- ggplot(ir,
+            aes(y = doi,
+                x = comp_mthds_avail)) +
+  geom_density_ridges() +
+  ylab("DOI") +
+  xlab("Score") +
+  xlim(c(0, 3)) +
+  ggtitle("Comp. Methods Available")
+
+d <- ggplot(ir,
+            aes(y = doi,
+                x = data_avail)) +
+  ylab("") +
+  xlab("Score") +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
+  xlim(c(0, 3)) +
+  geom_density_ridges() +
+  ggtitle("Data Available")
+
+p <- (a | b) / (c | d)
+p <- p + plot_annotation(tag_levels = "A",
+                         title = "Evaluator agreement in article reproducibility criteria scoring")
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+```
+
+\newpage
+
+```{r irReproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Overall reproducibility scores of five articles scored for evaluator agreement.
+Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value.", cache=FALSE, fig.env='figure'}
+p <- ggplot(ir,
+            aes(y = doi,
+                x = reproducibility_score)) +
+  geom_density_ridges() +
+  ggtitle("Inter-rater reproducibility score for five articles") +
+  ylab("DOI") +
+  xlab("Reproducibility Score (%)") +
+  xlim(c(0, 100))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+```
+
+```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
+Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value.", cache=FALSE, fig.env='figure'}
+p <-
+  ggplot(data = rrpp, aes(x = reproducibility_score)) +
+  geom_histogram(binwidth = 10,
+                 fill = "black",
+                 colour = "black") +
+  xlab("Reproducibility score (%)")
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
 ```
@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
 ```
@@
 rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+        file = here("analysis/figures/Sparks_et_al_Figure_7.eps"))
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_7.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_7.eps"),
   options = "-dEPSCrop"
@@
 
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_7.eps"))
 ```

### 2022-05-20 analysis/paper/paper.Rmd
add ggridges to used packages in paper libs

@@
   "ggplot2",
+  "ggridges",
   "ggpubr",

### 2022-05-20 analysis/paper/paper.Rmd
use "*" for italics

@@
 At the second level, in our search of the literature, we found that @Hill2019 shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
-The scripts provided used an R package, _checkpoint_ [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that are necessary to reproduce the work rather than defaulting to the latest versions.
+The scripts provided used an R package, *checkpoint* [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that are necessary to reproduce the work rather than defaulting to the latest versions.
 However, the scripts did not run unhindered, as the supplementary materials suggested that they should, without changes to the data, but with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.

### 2022-05-21 analysis/paper/paper.Rmd
Add ICC to paper

@@
   "patchwork",
+  "psych",
   "rsvg",
@@
 
-The overall reproducibility scores assigned by authors to the five articles evaluated to check for inter-rater differences showed some differences (Figure \@ref(fig:irReproScore)).
-The article that had the greatest difference, 13 to 33%, was DOI "10.1007/s12600-021-00902-2" with a standard deviation of `r ir %>% filter(doi == "10.1007/s12600-021-00902-2") %>% summarise(x = round(sd(reproducibility_score), 1))`.
-All other articles had standard deviation scores of less than 4 (Table \@ref(tab:interRaterSD)).
-However, all article scores largely agreed and fell below 50% (Figure \@ref(fig:irReproScore)).
+The overall reproducibility scores assigned by authors to the five articles evaluated to check for inter-rater differences had moderate reliability, 0.57, (Table \@ref(tab:icc), Figure \@ref(fig:irReproScore)).
 
@@
 
-```{r interRaterSD, echo=FALSE, message=FALSE, warning=FALSE}
+```{r icc, echo=FALSE, message=FALSE, warning=FALSE}
 ir %>%
-  group_by(doi) %>%
-  summarise(x = round(sd(reproducibility_score), 1)) %>%
-  rename(`Standard Deviation` = x) %>%
-  rename(DOI = doi) %>%
+  select(doi, assignee, reproducibility_score) %>%
+  pivot_wider(names_from = assignee, values_from = reproducibility_score) %>%
+  select(Adam, Emerson, Kaique, Nik, Zach) %>%
+  as.matrix() %>%
+  ICC() %>%
+  `[[`(1) %>%
   flextable() %>%
   set_table_properties(layout = "autofit") %>% 
-  set_caption(
-    "Standard deviation of reproducibility scores for five articles evaluated by all five co-authors to check for differences in article ratings.")
+  set_caption("this needs a caption")
 ```

### 2022-05-21 analysis/paper/paper.Rmd
Correct file save for figure 2

@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
   plot = p,

### 2022-05-29 R/import_notes.R
Don't calculate reproducibility score

@@ -57,48 +57,21 @@ import_notes <- function() {
                       true = 0,
                       false = IF_5year
                     )) %>%
-    dplyr::mutate(journal = as.factor(journal)) %>%
-    dplyr::mutate(year = as.factor(year)) %>%
-    dplyr::mutate(art_class = as.factor(art_class)) %>%
-    dplyr::mutate(repro_inst = as.factor(repro_inst)) %>%
-    dplyr::mutate(open = as.factor(open)) %>%
-    dplyr::mutate(abbreviation = as.factor(abbreviation)) %>%
-    dplyr::mutate(assignee = as.factor(assignee))
-
-  # add reproducibility score as a percent of total possible
-  #
-  # calculate total possible score for a paper
-  total_possible <-
-    notes %>%
-    dplyr::select(comp_mthds_avail,
-                  software_avail,
-                  software_cite,
-                  data_avail) %>%
-    dplyr::mutate(total_possible = rowSums(!is.na(.)) * 3) %>%
-    dplyr::select(total_possible)
-
-  # calculate reproducibility score
-  notes <-
-    notes %>%
-    tibble::add_column(total_possible) %>%
-    dplyr::rowwise() %>%
-    dplyr::mutate(reproducibility_score =
-                    (
-                      sum(
-                        comp_mthds_avail,
-                        software_avail,
-                        software_cite,
-                        data_avail,
-                        na.rm = TRUE
-                      ) / total_possible
-                    ) * 100)
-
-  # create mean assignee rating value
-  notes <-
-    notes %>%
-    dplyr::group_by(assignee) %>%
-    dplyr::summarise(mean_assignee = mean(reproducibility_score)) %>%
-    dplyr::full_join(notes, by = "assignee")
+    dplyr::mutate(
+      software_cite = software_cite + 1,
+      software_avail = software_avail + 1,
+      comp_mthds_avail = comp_mthds_avail + 1,
+      data_avail = data_avail + 1
+    ) %>%
+    dplyr::mutate(
+      journal = as.factor(journal),
+      year = as.factor(year),
+      art_class = as.factor(art_class),
+      repro_inst = as.factor(repro_inst),
+      open = as.factor(open),
+      abbreviation = as.factor(abbreviation),
+      assignee = as.factor(assignee)
+    )
 
   # add a unique identifier value to each article since not all have a DOI
   notes$uid <- seq_along(1:nrow(notes))

### 2022-05-29 R/import_inter-rater_scores.R
Don't calculate reproducibility score on import

@@ -57,30 +57,7 @@ import_interrater_scores <- function() {
     dplyr::mutate(total_possible = rowSums(!is.na(.)) * 3) %>%
     dplyr::select(total_possible)
 
-  # calculate reproducibility score
-  notes <-
-    notes %>%
-    tibble::add_column(total_possible) %>%
-    dplyr::rowwise() %>%
-    dplyr::mutate(reproducibility_score =
-                    (
-                      sum(
-                        comp_mthds_avail,
-                        software_avail_corrected,
-                        software_cite,
-                        data_avail,
-                        na.rm = TRUE
-                      ) / total_possible
-                    ) * 100)
-
-  # create mean assignee rating value
-  notes <-
-    notes %>%
-    dplyr::group_by(assignee) %>%
-    dplyr::summarise(mean_assignee = mean(reproducibility_score)) %>%
-    dplyr::full_join(notes, by = "assignee")
-
-  # add a unique identifier value to each article since not all have a DOI
+    # add a unique identifier value to each article since not all have a DOI
   notes$uid <- seq_along(1:nrow(notes))
 
   return(notes)

### 2022-05-30 R/import_inter-rater_scores.R
Convert values from 0-3 to 1-4, remove total possible

@@ -37,27 +37,20 @@ import_interrater_scores <- function() {
 
   notes <-
     notes %>%
-    dplyr::mutate(doi = as.factor(doi)) %>%
-    dplyr::mutate(art_class = as.factor(art_class)) %>%
-    dplyr::mutate(molecular = as.factor(molecular)) %>%
-    dplyr::mutate(assignee = as.factor(assignee))
-
-  # add reproducibility score as a percent of total possible
-  #
-  # calculate total possible score for a paper
-  total_possible <-
-    notes %>%
-    dplyr::select(
-      comp_mthds_avail,
-      software_avail,
-      software_avail_corrected,
-      software_cite,
-      data_avail
+    dplyr::mutate(
+      software_cite = software_cite + 1,
+      software_avail = software_avail + 1,
+      comp_mthds_avail = comp_mthds_avail + 1,
+      data_avail = data_avail + 1
     ) %>%
-    dplyr::mutate(total_possible = rowSums(!is.na(.)) * 3) %>%
-    dplyr::select(total_possible)
+    dplyr::mutate(
+      doi = as.factor(doi),
+      art_class = as.factor(art_class),
+      molecular = as.factor(molecular),
+      assignee = as.factor(assignee)
+    )
 
-    # add a unique identifier value to each article since not all have a DOI
+  # add a unique identifier value to each article since not all have a DOI
   notes$uid <- seq_along(1:nrow(notes))
 
   return(notes)

### 2022-06-02 R/import_inter-rater_scores_paper.R
Add functions to import data for paper
Don't add 1 to scores as done for analysis.

@@ -1,0 +1,51 @@
+
+#' Import scoring notes checking inter-rater repeatability for paper publication
+#'
+#' Imports, formats data into proper types and calculates the final
+#' reproducibility score.
+#'
+#' @return A [tibble::tibble()] object of reproducibility score notes formatted
+#' for use in analysis and manuscript preparation
+#' @export import_interrater_scores_paper
+#'
+#' @examples
+#' notes <- import_notes()
+#' pander::pander(head(notes))
+#'
+#' @importFrom magrittr "%>%"
+#'
+
+import_interrater_scores_paper <- function() {
+  # CRAN Note Avoidance
+  data_avail <-
+    comp_mthds_avail <-
+    software_avail <- software_avail_corrected <-
+    software_cite <-
+    IF_5year <- art_class <- repro_inst <- abbreviation <-
+    assignee <-
+    reproducibility_score <- journal <- year <- . <- NULL
+
+  notes <- readODS::read_ods(
+    system.file(
+      "extdata",
+      "Reproducibility_in_plant_pathology_notes.ods",
+      package = "Reproducibility.in.Plant.Pathology"
+    ),
+    na = "NA",
+    sheet = "inter-rater_score_check"
+  )
+
+  notes <-
+    notes %>%
+    dplyr::mutate(
+      doi = as.factor(doi),
+      art_class = as.factor(art_class),
+      molecular = as.factor(molecular),
+      assignee = as.factor(assignee)
+    )
+
+  # add a unique identifier value to each article since not all have a DOI
+  notes$uid <- seq_along(1:nrow(notes))
+
+  return(notes)
+}

### 2022-06-02 R/import_notes_paper.R

@@ -1,0 +1,74 @@
+
+#' Import reproducibility score notes for inclusion in paper
+#'
+#' Imports, formats data into proper types and calculates the final
+#' reproducibility score. Also adds the 2 and 5 year impact factor values from
+#' InCites Journal Citation Reports for 2018.
+#'
+#' @return A [tibble::tibble()] object of reproducibility score notes formatted
+#' for use in analysis and manuscript preparation
+#' @export import_notes_paper
+#'
+#' @examples
+#' notes <- import_notes()
+#' pander::pander(head(notes))
+#'
+#' @importFrom magrittr "%>%"
+#'
+
+import_notes_paper <- function() {
+  # CRAN Note Avoidance
+  data_avail <-
+    comp_mthds_avail <- software_avail <- software_cite <-
+    IF_5year <-
+    art_class <- repro_inst <- abbreviation <- assignee <-
+    reproducibility_score <- journal <- year <- . <- NULL
+
+  notes <- readODS::read_ods(
+    system.file(
+      "extdata",
+      "Reproducibility_in_plant_pathology_notes.ods",
+      package = "Reproducibility.in.Plant.Pathology"
+    ),
+    na = "NA",
+    sheet = "article_evaluations"
+  )
+
+  notes$open <- gsub("1", "TRUE", x = notes$open)
+
+  IF_5year <- readODS::read_ods(
+    system.file(
+      "extdata",
+      "Reproducibility_in_plant_pathology_notes.ods",
+      package = "Reproducibility.in.Plant.Pathology"
+    ),
+    na = "NA",
+    sheet = "5yr IF"
+  )
+
+  notes <-
+    notes %>%
+    dplyr::left_join(x = notes,
+                     y = IF_5year,
+                     by = c("journal" = "journal")) %>%
+    dplyr::mutate(IF_5year =
+                    dplyr::if_else(
+                      condition = is.na(IF_5year),
+                      true = 0,
+                      false = IF_5year
+                    )) %>%
+    dplyr::mutate(
+      journal = as.factor(journal),
+      year = as.factor(year),
+      art_class = as.factor(art_class),
+      repro_inst = as.factor(repro_inst),
+      open = as.factor(open),
+      abbreviation = as.factor(abbreviation),
+      assignee = as.factor(assignee)
+    )
+
+  # add a unique identifier value to each article since not all have a DOI
+  notes$uid <- seq_along(1:nrow(notes))
+
+  return(notes)
+}

### 2022-06-02 analysis/paper/paper.Rmd
Insert missing \newpage in figure section
Revise figures

@@
 
-load(file = here("inst/extdata/m_f.Rda"))
-load(file = here("inst/extdata/m_g.Rda"))
-load(file = here("inst/extdata/m_h.Rda"))
-load(file = here("inst/extdata/m_i.Rda"))
-load(file = here("inst/extdata/m_j.Rda"))
-load(file = here("inst/extdata/m_k.Rda"))
+load(file = here("inst/extdata/m_f1.Rda"))
+load(file = here("inst/extdata/m_f2.Rda"))
+load(file = here("inst/extdata/m_f3.Rda"))
+load(file = here("inst/extdata/m_g1.Rda"))
+load(file = here("inst/extdata/m_g2.Rda"))
+load(file = here("inst/extdata/m_g3.Rda"))
+load(file = here("inst/extdata/m_h1.Rda"))
+load(file = here("inst/extdata/m_h2.Rda"))
+load(file = here("inst/extdata/m_h3.Rda"))
+load(file = here("inst/extdata/m_i1.Rda"))
+load(file = here("inst/extdata/m_i2.Rda"))
+load(file = here("inst/extdata/m_i3.Rda"))
+load(file = here("inst/extdata/m_j1.Rda"))
+load(file = here("inst/extdata/m_j2.Rda"))
+load(file = here("inst/extdata/m_j3.Rda"))
 
-pp_m_f <- pp_check(m_f)
-pp_m_g <- pp_check(m_g)
-pp_m_h <- pp_check(m_h)
-pp_m_i <- pp_check(m_i)
-pp_m_j <- pp_check(m_j)
-pp_m_k <- pp_check(m_k)
+mod_list <- list(
+  pp_check(m_f1) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_f2) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_f3) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_g1) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_g2) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_g3) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_h1) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_h2) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_h3) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_i1),
+  pp_check(m_i2),
+  pp_check(m_i3)
+)
 
-# put them all together
-p <- (pp_m_f | pp_m_g) / (pp_m_h | pp_m_i) / (pp_m_j | pp_m_k)
-
-p <- p + plot_annotation(tag_levels = "A",
+p <- wrap_plots(mod_list, nrow = 4) +
+  plot_layout(guides = "collect") +
+  plot_annotation(tag_levels = "A",
                   title = "Bayesian posterior distributions of evaluation score models")
@@
 
-```{r irCriteria, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator agreement for five articles scored for (A) software being properly cited, (B) software used being freely and openly available, (C) computational methods used, e.g.
-scripts or other self-written programs were freely and openly available and (D) data represented in the paper were freely and openly available.
+```{r irCriteria, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator agreement for five articles scored for (A) computational methods (code) used, e.g.
+scripts or other self-written programs were freely and openly available and (B) data represented in the paper were freely and openly available.
 Note that one evaluator rated an article with computational methods available as 'NA', which is reflected in that article having only four evaluations for this criteria.", cache=FALSE, fig.env='figure'}
 a <- ggplot(ir,
-            aes(y = doi,
-                x = software_cite)) +
-  ylab("DOI") +
-  xlab("") +
-  xlim(c(0, 3)) +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) +
-  geom_density_ridges() +
-  ggtitle("Software Cited")
-
-b <- ggplot(ir,
-            aes(y = doi,
-                x = software_avail)) +
-  ylab("") +
-  xlab("") +
-  geom_density_ridges() +
-  theme(
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank()
-  ) +
-  xlim(c(0, 3)) +
-  ggtitle("Software Available")
-
-c <- ggplot(ir,
             aes(y = doi,
@@
   xlim(c(0, 3)) +
-  ggtitle("Comp. Methods Available")
+  ggtitle("Code Available")
 
-d <- ggplot(ir,
+b <- ggplot(ir,
             aes(y = doi,
@@
 
-p <- (a | b) / (c | d)
+p <- a + b
 p <- p + plot_annotation(tag_levels = "A",
@@
 
-```{r irReproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Overall reproducibility scores of five articles scored for evaluator agreement.
-Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value.", cache=FALSE, fig.env='figure'}
-p <- ggplot(ir,
-            aes(y = doi,
-                x = reproducibility_score)) +
-  geom_density_ridges() +
-  ggtitle("Inter-rater reproducibility score for five articles") +
-  ylab("DOI") +
-  xlab("Reproducibility Score (%)") +
-  xlim(c(0, 100))
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the three categories evaluated, (A) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+(B) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+(C) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
+
+a <- ggplot(rrpp, aes(x = as.factor(software_avail))) +
+  geom_bar(fill = "black") +
+  ylab("Count") +
+  xlab("Article Score") +
+  ggtitle("Software")
+
+b <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
+  geom_bar(fill = "black") +
+  ylab("Count") +
+  xlab("Article Score") +
+  ggtitle("Code")
+
+c <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
+  geom_bar(fill = "black") +
+  ylab("Count") +
+  xlab("Article Score") +
+  ggtitle("Data")
+
+p <- a + b + c
+p <- p +
+  plot_annotation(tag_levels = "A")
 
@@
 include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
-```
-
-```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value.", cache=FALSE, fig.env='figure'}
-p <-
-  ggplot(data = rrpp, aes(x = reproducibility_score)) +
-  geom_histogram(binwidth = 10,
-                 fill = "black",
-                 colour = "black") +
-  xlab("Reproducibility score (%)")
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
-```
-
-\newpage
-
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users.
-(B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-(C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used.
-(D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
-
-rrpp_long <-
-  pivot_longer(rrpp,
-               cols = c(
-                 "comp_mthds_avail",
-                 "software_avail",
-                 "software_cite",
-                 "data_avail"
-               ))
-
-p <- ggplot(rrpp_long, aes(x = as.factor(value))) +
-  geom_bar(fill = "black") +
-  ylab("Count") +
-  xlab("Article Score") +
-  ggtitle("Reproducibility criteria index values") +
-  facet_wrap(name ~ .)
-p <- tag_facet(
-  p = p,
-  tag_pool = LETTERS,
-  x = 5,
-  family = "Arial",
-  open = "",
-  close = ""
-)
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
 ```
@@
 rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_7.eps"))
+        file = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_7.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_7.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
   options = "-dEPSCrop"
@@
 
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_7.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
 ```

### 2022-06-02 analysis/paper/paper.Rmd
Use new functions to import notes

@@
 
-rrpp <- import_notes()
+rrpp <- import_notes_paper()
+ir <- import_interrater_scores_paper()
 
@@
 )
-
-ir <- import_interrater_scores()
 ```

### 2022-06-02 analysis/paper/paper.Rmd
Text edits and clarifications to fit new analysis

@@
 
-Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.
+Where possible, the software used in conducting the research behind the publication was recorded in the notes if it was cited or otherwise specified in the article text.
 
@@
 
-A total reproducibility score was calculated as the per cent of total possible for a given paper.
-However, some papers did not use specialized software therefore they were not scored for this category.
-
 ## Data Cleaning
@@
 Efforts were made to standardise the scoring as much as possible.
-In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and these scores were modified after discussion to match the agreed on ratings.
-For example, a paper was rated as having a `software_avail` rating of `3`, but the evaulator noted that Excel had been used.
-Here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
+In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and these scores were modified after discussion to match the agreed on ratings based on the record of the software that was used in each respective paper.
+For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
 In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
-In these cases, Excel was added to the `software_used` column.
+Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
 
@@
 The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
-Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
+Inter-rater differences were evaluated using percent agreement and Fliess' Kappa [ZZZZ cite emerson here]
+The software availability, computational methods availability and data availability scores were converted from 0-3 to 1-4 ordinal score values and Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, journal open access policy, journal data and code deposition instructions.
+The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, publication analysis where the 'journal' was a fixed effect and five-year impact factor where correlations between the journal title and impact factor affected the software availability model.
 
-Relatively flat priors were selected from a normal distribution with a mean of 0 and a standard deviation of 10 for all parameters.
+Non-informative priors were selected from a normal distribution with a mean of 0 and a standard deviation of 1.5 were selected for all models.
 
@@
 
-Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data and the assumption that a zero value would only come from one process, the scoring.
-Each model was run for 3000 iterations in four chains.
+Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
+Each model was run for 4000 iterations in four chains.
 
@@
 
-Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020], 'egg' (version `r packageVersion("egg")`) [@Auguie2019] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].
+Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].
 
@@
 The differences between the co-authors' classifications of the article class as `applied` or `fundamental` had no differences in the five articles that were evaluated by all of the co-authors (Figure \@ref(fig:irArtClass)A).
-However, differences in evaluators' interpretations of whether or not an article had a molecular focus or not led to this scoring criteria being dropped from the analysis and is not included in this analysis (Figure \@ref(fig:irArtClass)B).
-
-There was reasonable agreement among the authors when evaluating whether software was cited properly or not and freely and openly available (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).
-All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)C, \@ref(fig:irCriteria)C).
-
-The overall reproducibility scores assigned by authors to the five articles evaluated to check for inter-rater differences had moderate reliability, 0.57, (Table \@ref(tab:icc), Figure \@ref(fig:irReproScore)).
-
-There were `r length(which(rrpp$reproducibility_score == 100))` (`r round(length(which(rrpp$reproducibility_score == 100))/nrow(rrpp), 2) * 100`%) articles that scored 100% or were classed as fully reproducible (Figure \@ref(fig:reproScore)).
-`r toTitleCase(as.character(english::english(length(which(rrpp$reproducibility_score == 0)))))` (`r round(length(which(rrpp$reproducibility_score == 0))/nrow(rrpp), 2) * 100`%) of articles were scored at 0% out of a possible 100% for reproducibility (Figure \@ref(fig:reproScore)).
-The mean value was `r round(mean(rrpp$reproducibility_score), 1)`% and the median value was `r round(median(rrpp$reproducibility_score), 1)`%.
+However, there were several differences in evaluators' interpretations of whether or not an article had a molecular focus (Figure \@ref(fig:irArtClass)B).
+All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).
 
 The analysis detected that the journal title did have an effect on the reproducibility score but there was no effect of article class or impact factor.
-
-Articles with a molecular focus skewed to a higher ranking reproducibility and openness but the difference was not strong enough to be detected with the analysis used.
 
@@
 Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
-`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
+`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail + -1 == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail+ -1 == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
 
@@
     "Articles were scored in four areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.")
-```
-
-\newpage
-
-```{r icc, echo=FALSE, message=FALSE, warning=FALSE}
-ir %>%
-  select(doi, assignee, reproducibility_score) %>%
-  pivot_wider(names_from = assignee, values_from = reproducibility_score) %>%
-  select(Adam, Emerson, Kaique, Nik, Zach) %>%
-  as.matrix() %>%
-  ICC() %>%
-  `[[`(1) %>%
-  flextable() %>%
-  set_table_properties(layout = "autofit") %>% 
-  set_caption("this needs a caption")
 ```

### 2022-06-02 analysis/paper/paper.Rmd
Clarify writing

@@
 Each evaluator was assigned 50 articles to evaluate during an evaluation event.
-A list of randomly generated numbers to represent page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for .
+A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for each sampling event.
 This was done because some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
@@
 
-The each of the five authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)) in three different scoring events as their time allowed for their participation.
+Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)) in each of the three different scoring events as their time allowed for their participation.
 In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.

### 2022-06-02 analysis/paper/paper.Rmd
Better descriptions of scoring and cite Emerson inter-rater tests

@@
 Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
-This classification was based on the evaluator's judgement of the article.
+These classifications were based on the individual evaluator's judgement of the article.
 
-Where possible, the software used in conducting the research behind the publication was recorded in the notes if it was cited or otherwise specified in the article text.
+Each article was rated on a 0 -- 3 scale for its software, data and code availability.
+'Software availability' was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+'Code availability' scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+Lastly, the 'Data availability' was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 
-Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
-When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
+Where possible, the software used in conducting the research behind the publication was recorded in the notes when it was cited or otherwise specified in the article text.
 
@@
 Efforts were made to standardise the scoring as much as possible.
-In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and these scores were modified after discussion to match the agreed on ratings based on the record of the software that was used in each respective paper.
+A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
+Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
+When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
+In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
 For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
@@
 Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
+The software availability, computational methods availability and data availability scores were converted from 0 -- 3 to 1 -- 4 ordinal score values for analysis.
 
@@
 The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
-Inter-rater differences were evaluated using percent agreement and Fliess' Kappa [ZZZZ cite emerson here]
-The software availability, computational methods availability and data availability scores were converted from 0-3 to 1-4 ordinal score values and Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, journal open access policy, journal data and code deposition instructions.
+
+Inter-rater differences were evaluated using percent agreement and Fliess' Kappa [@DelPonte2019].
+
+The articles' computational reproducibility were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, journal open access policy, journal data and code deposition instructions on three factors, data and code availability how open and available the software used were.
 The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, publication analysis where the 'journal' was a fixed effect and five-year impact factor where correlations between the journal title and impact factor affected the software availability model.
@@
 Non-informative priors were selected from a normal distribution with a mean of 0 and a standard deviation of 1.5 were selected for all models.
-
-The random effects were year and assignee for all models excepting the model which tested for year effects.
-In all models, the random effects were the publication title and assigned evaluator.
 
@@
 
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model fitnesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 

### 2022-06-02 analysis/paper/paper.Rmd
Clarify scoring factors

@@
 
-The articles' computational reproducibility were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, journal open access policy, journal data and code deposition instructions on three factors, data and code availability how open and available the software used were.
+The articles' computational reproducibility were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, journal open access policy, journal data and code deposition instructions on three factors, data, code and software availability.
 The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, publication analysis where the 'journal' was a fixed effect and five-year impact factor where correlations between the journal title and impact factor affected the software availability model.

### 2022-06-02 analysis/paper/paper.Rmd
Spelling correction

@@
 
-Model fitnesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 

### 2022-06-03 analysis/paper/paper.Rmd
clarify number of chains run and warmup
Add details of thinning in the models
Remove references to article class (Fundamental/Applied)

@@
 
-Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
-These classifications were based on the individual evaluator's judgement of the article.
-
 Each article was rated on a 0 -- 3 scale for its software, data and code availability.
@@
 Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
-Each model was run for 4000 iterations in four chains.
+Each model was run for 6000 iterations in four chains with a warmup of 3000 iterations and thinning set to 1.
 
@@
 
-The differences between the co-authors' classifications of the article class as `applied` or `fundamental` had no differences in the five articles that were evaluated by all of the co-authors (Figure \@ref(fig:irArtClass)A).
-However, there were several differences in evaluators' interpretations of whether or not an article had a molecular focus (Figure \@ref(fig:irArtClass)B).
 All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).
@@
 # Figures
-
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Five Year Impact Factor of Journal, (D) Journal Open Access Policy, (E) Year of Publication and (F) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws.
-Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}
-
-set.seed(23)
-
-color_scheme_set(scheme = "gray")
-
-load(file = here("inst/extdata/m_f1.Rda"))
-load(file = here("inst/extdata/m_f2.Rda"))
-load(file = here("inst/extdata/m_f3.Rda"))
-load(file = here("inst/extdata/m_g1.Rda"))
-load(file = here("inst/extdata/m_g2.Rda"))
-load(file = here("inst/extdata/m_g3.Rda"))
-load(file = here("inst/extdata/m_h1.Rda"))
-load(file = here("inst/extdata/m_h2.Rda"))
-load(file = here("inst/extdata/m_h3.Rda"))
-load(file = here("inst/extdata/m_i1.Rda"))
-load(file = here("inst/extdata/m_i2.Rda"))
-load(file = here("inst/extdata/m_i3.Rda"))
-load(file = here("inst/extdata/m_j1.Rda"))
-load(file = here("inst/extdata/m_j2.Rda"))
-load(file = here("inst/extdata/m_j3.Rda"))
-
-mod_list <- list(
-  pp_check(m_f1) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_f2) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_f3) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_g1) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_g2) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_g3) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_h1) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_h2) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_h3) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_i1),
-  pp_check(m_i2),
-  pp_check(m_i3)
-)
-
-p <- wrap_plots(mod_list, nrow = 4) +
-  plot_layout(guides = "collect") +
-  plot_annotation(tag_levels = "A",
-                  title = "Bayesian posterior distributions of evaluation score models")
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
-```
-
-\newpage
-
-```{r irArtClass, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator classifications of (A) an articles focus being molecular techniques (TRUE/FALSE) and (B) an article's class (Fundamental/Applied).
-Where all five articles were scored by all five authors to check for agreement between the evaluations.", cache=FALSE, fig.env='figure'}
-
-theme_set(theme_classic())
-a <- ggplot(ir, aes(y = doi,
-                      fill = molecular)) +
-  geom_bar() +
-  scale_fill_grey(name = "") +
-  ylab("DOI") +
-  xlab("Count") +
-  ggtitle("Molecular Focus") +
-  theme(legend.position = "top")
-
-b <- ggplot(ir, aes(y = doi,
-                      fill = art_class)) +
-  geom_bar() +
-  scale_fill_grey(name = "") +
-  xlab("Count") +
-  ylab("") +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank()
-  ) +
-  ggtitle("Article Class") +
-  theme(legend.position = "top")
-
-p <- (a | b)
-p <- p + plot_annotation(tag_levels = "A",
-                         title = "Evaluator agreement in article classifications")
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
-```
-
 \newpage
@@
 p <- p + plot_annotation(tag_levels = "A",
-                         title = "Evaluator agreement in article reproducibility criteria scoring")
+                         title = "Evaluator agreement in article reproducibility criteria scoring") &
+  theme(text = element_text("Arial"))
 
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
+```
+
+\newpage
+
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
+Six factors were evaluated, (A, B, C) Publication (Journal Title), (D, E, F) Article Class, (G, H, I) Five Year Impact Factor of Journal, (J, K, L) Journal Open Access Policy, (M, N, O) Year of Publication and (P, Q) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws.
+Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}
+
+set.seed(23)
+
+color_scheme_set(scheme = "gray")
+
+load(file = here("inst/extdata/m_f1.Rda"))
+load(file = here("inst/extdata/m_f2.Rda"))
+load(file = here("inst/extdata/m_f3.Rda"))
+load(file = here("inst/extdata/m_g1.Rda"))
+load(file = here("inst/extdata/m_g2.Rda"))
+load(file = here("inst/extdata/m_g3.Rda"))
+load(file = here("inst/extdata/m_h1.Rda"))
+load(file = here("inst/extdata/m_h2.Rda"))
+load(file = here("inst/extdata/m_h3.Rda"))
+load(file = here("inst/extdata/m_i1.Rda"))
+load(file = here("inst/extdata/m_i2.Rda"))
+load(file = here("inst/extdata/m_i3.Rda"))
+load(file = here("inst/extdata/m_j1.Rda"))
+load(file = here("inst/extdata/m_j2.Rda"))
+load(file = here("inst/extdata/m_j3.Rda"))
+load(file = here("inst/extdata/m_k1.Rda"))
+load(file = here("inst/extdata/m_k2.Rda"))
+
+mod_list <- list(
+  pp_check(m_f1) +
+    ggtitle("Code") +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank(),
+      plot.title = element_text(hjust = 0.5)
+    ) +
+    ylab("Journal"),
+  pp_check(m_f2) +
+    ggtitle("Data") +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank(),
+      plot.title = element_text(hjust = 0.5)
+    ),
+  pp_check(m_f3) +
+    ggtitle("Software") +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank(),
+      plot.title = element_text(hjust = 0.5)
+    ),
+  pp_check(m_g1) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ) +
+    ylab("5 Y IF"),
+  pp_check(m_g2) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_g3) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_h1) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ) +
+    ylab("Year"),
+  pp_check(m_h2) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_h3) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank(),
+    ),
+  pp_check(m_i1) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ) +
+    ylab("Access"),
+  pp_check(m_i2) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_i3) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_j1) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ) +
+    ylab("Instructions"),
+  pp_check(m_j2) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_j3),
+  pp_check(m_k1) +
+    ylab("Software"),
+  pp_check(m_k2)
+)
+
+p <- wrap_plots(mod_list, ncol = 3) +
+  plot_layout(guides = "collect") &
+  plot_annotation(title = "Bayesian posterior distributions of evaluation score models") &
+  theme(text = element_text("Arial"))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
 ```
@@
 p <- p +
-  plot_annotation(tag_levels = "A")
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
 
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
 ```
@@
 rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
+        file = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
   options = "-dEPSCrop"
@@
 
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
 ```

### 2022-06-04 analysis/paper/paper.Rmd
Specify the ggplot2 theme to be used

@@
 )
+
+theme_set(theme_classic())
 ```

### 2022-06-04 analysis/paper/paper.Rmd
Minor edits for clarity

@@
 
-In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
+In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our collective status.
 We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
-The aim was to gather as complete an overview of the status of reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
+The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
 From those 21 journals we randomly selected 450 articles published from 2012 to 2021.

### 2022-06-04 analysis/paper/paper.Rmd
Edits to the methods

@@
 Each article was rated on a 0 -- 3 scale for its software, data and code availability.
-'Software availability' was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-'Code availability' scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-Lastly, the 'Data availability' was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+'Software availability' rated how freely and openly available the software used was.
+It was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+'Code availability' rated how easily and openly available the computational methods used in the article were.
+Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+Lastly, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
+This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 
@@
 
-Efforts were made to standardise the scoring as much as possible.
 A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].

### 2022-06-04 analysis/paper/paper.Rmd
Edits to interrater repeatability differences analysis

@@
 
-The articles' computational reproducibility were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, journal open access policy, journal data and code deposition instructions on three factors, data, code and software availability.
-The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, publication analysis where the 'journal' was a fixed effect and five-year impact factor where correlations between the journal title and impact factor affected the software availability model.
+The articles' scores for data, code and software availability were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, year of publication, journal open access policy, and the effect of the availability of the software used, `software_avail` on the code and data availability.
+The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, journal title analysis where the 'journal' was a fixed effect and the five-year impact factor model where correlations between the journal title and impact factor affected the software availability model.
 

### 2022-06-04 analysis/paper/paper.Rmd
Edit the results section to match new analyses

@@
 
-All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).
+Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
+`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail + -1 == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail+ -1 == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
 
-The analysis detected that the journal title did have an effect on the reproducibility score but there was no effect of article class or impact factor.
+However, data was mostly not available with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the data was not available or mentioned in the article.
+However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%) scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
+
+More articles did a good job of using software that was reasonably available to anyone with `r length(which(rrpp$software_avail >= 2))` (`r round(length(which(rrpp$software_avail >= 2))/nrow(rrpp), 2) * 100`%) scoring '2' or '3' (Figure \@ref(fig:articleScores)B) for software availability.
+
+## Interrater Agreement
+
+All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the interrater percent agreement a score of 100% with the `NA value dropped from the code availability.
+Fleiss' Kappa was not able to be calculated for code or data availability due to 100% agreement of a score of '0', converted to '1' for the analysis.
+
+## Effect of Journal Title
+
+The analysis found that publications in Phytopathology were more likely to share their code but was unable to detect differences in any other journal titles.
+Publications in Crop Protection and Plant Disease were less likely to share their data but no effects were detectable in any other journal title.
+The analysis was unable to detect any effect of journal title on the software used, though articles in Plant Disease, Nematology and Tropical Plant Pathology tended to be more open and available.
+
+## Effect of Impact Factor
+
+There were no detectable effects of the five-year impact factor on code or data availability.
+However, there was no effect of the five-year impact factor on the availability of the software that was used.
+
+## Effect of Year
+
+We were unable to detect any observable differences as a result of the year that an article was published for code, data or software availability.
+
+## Effect of Access Policy
 
@@
 
-We were unable to detect any observable differences in the years that publications were submitted.
-The year 2016 appears to be have a higher score than prior and following years, but the analysis was undecided on the effect of all years on the publications' openness and reproducibility.
+## Effect of Reproducibility Instructions
 
@@
 Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
-While the analysis did not detect an effect of the journals' instructions for sharing or depositing data and or code, the more detailed the instructions, the higher the article scored.
+There were no detectable effects of the instructions on any of the three scores that were evaluated.
 
-The majority of the articles, `r length(which(rrpp$art_class == "Fundamental"))`, were classed as fundamental, with the remaining `r length(which(rrpp$art_class != "Fundamental"))` classed as applied.
+## Effect of Software Used
 
-Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
-`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail + -1 == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail+ -1 == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
-
-More articles did a good job of using software that was reasonably available to anyone with `r length(which(rrpp$software_avail >= 2))` (`r round(length(which(rrpp$software_avail >= 2))/nrow(rrpp), 2) * 100`%) scoring '2' or '3' (Figure \@ref(fig:articleScores)B) for software availability.
-
-Software citations were also reasonably well reported in the literature with `r length(which(rrpp$software_cite == 2))` (`r round(length(which(rrpp$software_cite == 2))/nrow(rrpp), 2) * 100`%) scoring '2' where the main software was cited with version numbers and `r length(which(rrpp$software_cite == 3))` (`r round(length(which(rrpp$software_cite == 3))/nrow(rrpp), 2) * 100`%) scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)C).
-
-However, data availability was mostly not available with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the data was not available or mentioned in the article.
-However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%) scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
+The availability of the software used had no effect on the availability of the code, i.e., the use of free, open-source software (FOSS), did not have the effect of making the code more available.
+Conversely, the use of closed or restrictive software did not cause code to be less available. 
+There was no detectable effect of the software's availability on the availability of data.
+However, both of these scores tended to be higher when the software used was more available.
 

### 2022-06-04 analysis/paper/paper.Rmd
Don't use here::here() to load data from package

@@
 
-load(file = here("inst/extdata/m_f1.Rda"))
-load(file = here("inst/extdata/m_f2.Rda"))
-load(file = here("inst/extdata/m_f3.Rda"))
-load(file = here("inst/extdata/m_g1.Rda"))
-load(file = here("inst/extdata/m_g2.Rda"))
-load(file = here("inst/extdata/m_g3.Rda"))
-load(file = here("inst/extdata/m_h1.Rda"))
-load(file = here("inst/extdata/m_h2.Rda"))
-load(file = here("inst/extdata/m_h3.Rda"))
-load(file = here("inst/extdata/m_i1.Rda"))
-load(file = here("inst/extdata/m_i2.Rda"))
-load(file = here("inst/extdata/m_i3.Rda"))
-load(file = here("inst/extdata/m_j1.Rda"))
-load(file = here("inst/extdata/m_j2.Rda"))
-load(file = here("inst/extdata/m_j3.Rda"))
-load(file = here("inst/extdata/m_k1.Rda"))
-load(file = here("inst/extdata/m_k2.Rda"))
+load(system.file("extdata",
+            "m_f1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_f2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_f3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_g1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_g2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_g3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_h1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_h2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_h3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_i1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_i2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_i3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_j1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_j2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_j3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_k1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_k2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
 

### 2022-06-04 analysis/paper/paper.Rmd
Correct filename when saving figure 4

@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
   plot = p,

### 2022-06-04 analysis/paper/paper.Rmd
Replace interrater with inter-rater and acknowledge A. Hepworth

@@
 
-## Interrater Agreement
+## Inter-rater Agreement
 
-All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the interrater percent agreement a score of 100% with the `NA value dropped from the code availability.
+All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the inter-rater percent agreement a score of 100% with the `NA value dropped from the code availability.
 Fleiss' Kappa was not able to be calculated for code or data availability due to 100% agreement of a score of '0', converted to '1' for the analysis.
@@
 
-The authors are grateful for insightful comments from Dr. David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript.
+The authors are grateful for insightful comments from Dr.
+David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript and from Ms.
+Anna Hepworth for statistical guidance on evaluating inter-rater scores.
 

### 2022-06-04 R/data.R
Move scoring criteria to ODS file

@@ -1,12 +1,0 @@
-#' Scoring criteria
-#'
-#' The scoring criteria used for scoring articles on reproducibility.
-#'
-#' @format A data frame with 19 rows and three variables:
-#' \describe{
-#'   \item{Category}{Scoring criterion category}
-#'   \item{Index.Value}{The index score assigned}
-#'   \item{Definition}{Definition of the criteria used to assign an index value
-#'    score for an article in each category}
-#' }
-"scoring_criteria"

### 2022-06-04 analysis/paper/paper.Rmd
Use scoring criteria from ODS file and remove citation details

@@
 ```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
-scoring_criteria %>%
+readODS::read_ods(
+    system.file(
+      "extdata",
+      "Reproducibility_in_plant_pathology_notes.ods",
+      package = "Reproducibility.in.Plant.Pathology"
+    ),
+    na = "NA",
+    sheet = "scoring_criteria_paper"
+  ) %>% 
   rename(`Index Value` = Index.Value) %>%
@@
   set_caption(
-    "Articles were scored in four areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.")
+    "Articles were three in four areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
 ```

### 2022-06-04 analysis/paper/paper.Rmd
Escape `NA` in text

@@
 
-All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the inter-rater percent agreement a score of 100% with the `NA value dropped from the code availability.
+All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
 Fleiss' Kappa was not able to be calculated for code or data availability due to 100% agreement of a score of '0', converted to '1' for the analysis.

### 2022-06-04 analysis/paper/paper.Rmd
Remove trailing space
Clarify discussion

@@
 However, the scripts did not run unhindered, as the supplementary materials suggested that they should, without changes to the data, but with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.
+One drawback to this approach is that journals are often not equipped to handle code, e.g., script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them.
+Though this should be possible given some effort from the publishing journal to share simple text files rather than binary formats along with the proper instructions and handling of these file formats rather than a one-size-fits all approach that we commonly see for supplementary materials.
 
 The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
-Sparks et al.
-[@Sparks2011; @Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+As an example, Sparks et al.
+[-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
 Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
@@
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
+Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania [@Sparks2022a].
 However, even this example is not totally open as it requires ArcGIS, an expensive proprietary software, to run the provided Python scripts for the RICEPEST model [@Savary2014].
 This highlights the difficulty in making work completely open and reproducible, further work could be undertaken to make the Python scripts rely totally on free-open-source-software but the work as it it provided here does allow for the complete reproducibility of the paper as written provided with the proper tools.
+Using a repository resource like GitHub allows readers to easily contact the authors by opening "Issues" and report bugs or ask questions in an open forum that are not as straightforward when the data are provided as supplementary material.
 

### 2022-06-04 analysis/paper/paper.Rmd
No new pages at start of figures
No need to rename columns for table now

@@
   ) %>% 
-  rename(`Index Value` = Index.Value) %>%
   flextable() %>%
@@
 # Figures
-\newpage
 

### 2022-06-04 analysis/paper/paper.Rmd
Break at full stops
Flesh out Docker description and refer to Nuest et al.

@@
 The fourth level includes packaging the full analysis in a containerized software application, *e.g.*, Docker.
-Docker is an open source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyses) with the operating system required to run that analysis on any computer.
-Using an open source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
+Docker is an open source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyses) with the operating system required to run that analysis on a user's computer.
+However, there are drawbacks to using Docker.
+It can be difficult to understand for a new user and new platforms, like the Apple M1 chip, may not be fully supported, which hinder the ability to share the container.
+But, in most cases using an open source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
+For more on using Docker for reproducible research, we would refer readers to @Nuest2020.
 As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package that enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].

### 2022-06-04 analysis/paper/paper.Rmd
Add statement on journal instruction
use double quotes and linebreak for full stop

@@
 Journals can encourage authors to deposit their data and code by providing instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources.
+While our analysis was unable to detect any differences in journals providing such instruction and journals that did not, the trend did indicate that journals that provided such instruction had better scores for data and code availability.
 
@@
 Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, *e.g.*, 'a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.' This allows end-users to identify what was used and identify the methods used more accurately.
+Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
+This allows end-users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.

### 2022-06-06 R/import_inter-rater_scores.R
Convert scores to ordered factors for analysis

@@ -38,16 +38,25 @@ import_interrater_scores <- function() {
   notes <-
     notes %>%
     dplyr::mutate(
-      software_cite = software_cite + 1,
-      software_avail = software_avail + 1,
-      comp_mthds_avail = comp_mthds_avail + 1,
-      data_avail = data_avail + 1
-    ) %>%
-    dplyr::mutate(
       doi = as.factor(doi),
       art_class = as.factor(art_class),
       molecular = as.factor(molecular),
-      assignee = as.factor(assignee)
+      assignee = as.factor(assignee),
+      software_avail = factor(
+        software_avail,
+        levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      ),
+      comp_mthds_avail = factor(
+        comp_mthds_avail,
+        levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      ),
+      data_avail = factor(
+        data_avail,
+        levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      )
     )
 
   # add a unique identifier value to each article since not all have a DOI

### 2022-06-06 R/import_notes.R

@@ -46,6 +46,7 @@ import_notes <- function() {
     sheet = "5yr IF"
   )
 
+
   notes <-
     notes %>%
     dplyr::left_join(x = notes,
@@ -58,19 +59,28 @@ import_notes <- function() {
                       false = IF_5year
                     )) %>%
     dplyr::mutate(
-      software_cite = software_cite + 1,
-      software_avail = software_avail + 1,
-      comp_mthds_avail = comp_mthds_avail + 1,
-      data_avail = data_avail + 1
-    ) %>%
-    dplyr::mutate(
       journal = as.factor(journal),
       year = as.factor(year),
       art_class = as.factor(art_class),
       repro_inst = as.factor(repro_inst),
       open = as.factor(open),
       abbreviation = as.factor(abbreviation),
-      assignee = as.factor(assignee)
+      assignee = as.factor(assignee),
+      software_avail = factor(
+        software_avail,
+        levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      ),
+      comp_mthds_avail = factor(
+        comp_mthds_avail,
+        levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      ),
+      data_avail = factor(
+        data_avail,
+        levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      )
     )
 
   # add a unique identifier value to each article since not all have a DOI

### 2022-06-06 R/import_inter-rater_scores_paper.R
Remove import_paper functions

@@ -1,51 +1,0 @@
-
-#' Import scoring notes checking inter-rater repeatability for paper publication
-#'
-#' Imports, formats data into proper types and calculates the final
-#' reproducibility score.
-#'
-#' @return A [tibble::tibble()] object of reproducibility score notes formatted
-#' for use in analysis and manuscript preparation
-#' @export import_interrater_scores_paper
-#'
-#' @examples
-#' notes <- import_notes()
-#' pander::pander(head(notes))
-#'
-#' @importFrom magrittr "%>%"
-#'
-
-import_interrater_scores_paper <- function() {
-  # CRAN Note Avoidance
-  data_avail <-
-    comp_mthds_avail <-
-    software_avail <- software_avail_corrected <-
-    software_cite <-
-    IF_5year <- art_class <- repro_inst <- abbreviation <-
-    assignee <-
-    reproducibility_score <- journal <- year <- . <- NULL
-
-  notes <- readODS::read_ods(
-    system.file(
-      "extdata",
-      "Reproducibility_in_plant_pathology_notes.ods",
-      package = "Reproducibility.in.Plant.Pathology"
-    ),
-    na = "NA",
-    sheet = "inter-rater_score_check"
-  )
-
-  notes <-
-    notes %>%
-    dplyr::mutate(
-      doi = as.factor(doi),
-      art_class = as.factor(art_class),
-      molecular = as.factor(molecular),
-      assignee = as.factor(assignee)
-    )
-
-  # add a unique identifier value to each article since not all have a DOI
-  notes$uid <- seq_along(1:nrow(notes))
-
-  return(notes)
-}

### 2022-06-06 R/import_notes_paper.R

@@ -1,74 +1,0 @@
-
-#' Import reproducibility score notes for inclusion in paper
-#'
-#' Imports, formats data into proper types and calculates the final
-#' reproducibility score. Also adds the 2 and 5 year impact factor values from
-#' InCites Journal Citation Reports for 2018.
-#'
-#' @return A [tibble::tibble()] object of reproducibility score notes formatted
-#' for use in analysis and manuscript preparation
-#' @export import_notes_paper
-#'
-#' @examples
-#' notes <- import_notes()
-#' pander::pander(head(notes))
-#'
-#' @importFrom magrittr "%>%"
-#'
-
-import_notes_paper <- function() {
-  # CRAN Note Avoidance
-  data_avail <-
-    comp_mthds_avail <- software_avail <- software_cite <-
-    IF_5year <-
-    art_class <- repro_inst <- abbreviation <- assignee <-
-    reproducibility_score <- journal <- year <- . <- NULL
-
-  notes <- readODS::read_ods(
-    system.file(
-      "extdata",
-      "Reproducibility_in_plant_pathology_notes.ods",
-      package = "Reproducibility.in.Plant.Pathology"
-    ),
-    na = "NA",
-    sheet = "article_evaluations"
-  )
-
-  notes$open <- gsub("1", "TRUE", x = notes$open)
-
-  IF_5year <- readODS::read_ods(
-    system.file(
-      "extdata",
-      "Reproducibility_in_plant_pathology_notes.ods",
-      package = "Reproducibility.in.Plant.Pathology"
-    ),
-    na = "NA",
-    sheet = "5yr IF"
-  )
-
-  notes <-
-    notes %>%
-    dplyr::left_join(x = notes,
-                     y = IF_5year,
-                     by = c("journal" = "journal")) %>%
-    dplyr::mutate(IF_5year =
-                    dplyr::if_else(
-                      condition = is.na(IF_5year),
-                      true = 0,
-                      false = IF_5year
-                    )) %>%
-    dplyr::mutate(
-      journal = as.factor(journal),
-      year = as.factor(year),
-      art_class = as.factor(art_class),
-      repro_inst = as.factor(repro_inst),
-      open = as.factor(open),
-      abbreviation = as.factor(abbreviation),
-      assignee = as.factor(assignee)
-    )
-
-  # add a unique identifier value to each article since not all have a DOI
-  notes$uid <- seq_along(1:nrow(notes))
-
-  return(notes)
-}

### 2022-06-06 analysis/paper/paper.Rmd
Remove import_paper functions
We only looked at three areas of reproducibility in the paper, not four

@@
 
-rrpp <- import_notes_paper()
-ir <- import_interrater_scores_paper()
+rrpp <- import_notes()
+ir <- import_interrater_scores()
 
@@
   set_caption(
-    "Articles were three in four areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
+    "Articles were three in three areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
 ```

### 2022-06-06 analysis/paper/paper.Rmd
Move the loading of the model objects

@@
 theme_set(theme_classic())
+
+load(system.file("extdata",
+            "m_f1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_f2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_f3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_g1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_g2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_g3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_h1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_h2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_h3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_i1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_i2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_i3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_j1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_j2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_j3.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+
+load(system.file("extdata",
+            "m_k1.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
+load(system.file("extdata",
+            "m_k2.Rda",
+            package = "Reproducibility.in.Plant.Pathology",
+            mustWork = TRUE))
 ```
@@
 
-load(system.file("extdata",
-            "m_f1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_f2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_f3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
-load(system.file("extdata",
-            "m_g1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_g2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_g3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
-load(system.file("extdata",
-            "m_h1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_h2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_h3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
-load(system.file("extdata",
-            "m_i1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_i2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_i3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
-load(system.file("extdata",
-            "m_j1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_j2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_j3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
-load(system.file("extdata",
-            "m_k1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_k2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
 mod_list <- list(

### 2022-06-06 analysis/paper/paper.Rmd
add an equivalence test figure, not complete

@@
 
+```{r equivalence-tests, echo=FALSE, warning=FALSE, message=FALSE}
+a <- plot(equivalence_test(m_f1), rope_color = "grey70") +
+  scale_y_discrete(
+    label = function(x) {
+      x %>% gsub("b_abbreviation", "", .)
+    }
+  ) +
+  scale_fill_grey()
+b <-
+  plot(equivalence_test(m_f2), rope_color = "grey70") +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  scale_fill_grey()
+c <-
+  plot(equivalence_test(m_f3), rope_color = "grey70") +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  scale_fill_grey()
+
+p <- a + b + c
+p <- p +
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+
+```
+
+\newpage
+
 ```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.

### 2022-06-08 analysis/paper/paper.Rmd
Remove unused model objects

@@
             mustWork = TRUE))
-load(system.file("extdata",
-            "m_f3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
 
@@
             "m_g2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_g3.Rda",
             package = "Reproducibility.in.Plant.Pathology",
@@
             mustWork = TRUE))
-load(system.file("extdata",
-            "m_h3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
 
@@
             "m_i2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_i3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
-load(system.file("extdata",
-            "m_j1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_j2.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_j3.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-
-load(system.file("extdata",
-            "m_k1.Rda",
-            package = "Reproducibility.in.Plant.Pathology",
-            mustWork = TRUE))
-load(system.file("extdata",
-            "m_k2.Rda",
             package = "Reproducibility.in.Plant.Pathology",

### 2022-06-08 analysis/paper/paper.Rmd
Fix printing values

@@
 Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
-`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail + -1 == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail+ -1 == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
+`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
 
@@
     ),
-  pp_check(m_f3) +
-    ggtitle("Software") +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank(),
-      plot.title = element_text(hjust = 0.5)
-    ),
   pp_check(m_g1) +
@@
   pp_check(m_g2) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_g3) +
     theme(
@@
     ),
-  pp_check(m_h3) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank(),
-    ),
-  pp_check(m_i1) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ) +
-    ylab("Access"),
-  pp_check(m_i2) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_i3) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_j1) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ) +
-    ylab("Instructions"),
-  pp_check(m_j2) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_j3),
-  pp_check(m_k1) +
-    ylab("Software"),
-  pp_check(m_k2)
+  pp_check(m_i1),
+  pp_check(m_i2)
+    )
 )

### 2022-06-08 analysis/paper/paper.Rmd
Remove reference to figure that was removed

@@
 
-All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
+All authors agreed on the evaluation of the data availability of all five articles that were scored by each author but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
 Fleiss' Kappa was not able to be calculated for code or data availability due to 100% agreement of a score of '0', converted to '1' for the analysis.

### 2022-06-08 analysis/paper/paper.Rmd
Clean up figures

@@
 
-```{r irCriteria, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator agreement for five articles scored for (A) computational methods (code) used, e.g.
-scripts or other self-written programs were freely and openly available and (B) data represented in the paper were freely and openly available.
-Note that one evaluator rated an article with computational methods available as 'NA', which is reflected in that article having only four evaluations for this criteria.", cache=FALSE, fig.env='figure'}
-a <- ggplot(ir,
-            aes(y = doi,
-                x = comp_mthds_avail)) +
-  geom_density_ridges() +
-  ylab("DOI") +
-  xlab("Score") +
-  xlim(c(0, 3)) +
-  ggtitle("Code Available")
-
-b <- ggplot(ir,
-            aes(y = doi,
-                x = data_avail)) +
-  ylab("") +
-  xlab("Score") +
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) +
-  xlim(c(0, 3)) +
-  geom_density_ridges() +
-  ggtitle("Data Available")
-
-p <- a + b
-p <- p + plot_annotation(tag_levels = "A",
-                         title = "Evaluator agreement in article reproducibility criteria scoring") &
-  theme(text = element_text("Arial"))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
-```
-
-\newpage
-
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A, B, C) Publication (Journal Title), (D, E, F) Article Class, (G, H, I) Five Year Impact Factor of Journal, (J, K, L) Journal Open Access Policy, (M, N, O) Year of Publication and (P, Q) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws.
+Six factors were evaluated, (A, B) Publication (Journal Title), (D, E) Year of Publication, (G, H) Five Year Impact Factor of Journal, and (J, K) Journal Open Access Policy where y is the data's density and y~rep~ are ten random posterior draws.
 Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}
@@
     ) +
-    ylab("5 Y IF"),
+    ylab("Year"),
   pp_check(m_g2) +
@@
     ) +
-    ylab("Year"),
+    ylab("5 Y IF"),
   pp_check(m_h2) +
@@
     ),
-  pp_check(m_i1),
+  pp_check(m_i1) +
+    ylab("Access\nPolicy"),
   pp_check(m_i2)
     )
-)
 
-p <- wrap_plots(mod_list, ncol = 3) +
+p <- wrap_plots(mod_list, ncol = 2) +
   plot_layout(guides = "collect") &
-  plot_annotation(title = "Bayesian posterior distributions of evaluation score models") &
+  plot_annotation(title = "Bayesian posterior distributions of evaluation score models",
+                  tag_levels = "A") &
   theme(text = element_text("Arial"))
@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
 ```
@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
 ```
@@
   scale_fill_grey()
-c <-
-  plot(equivalence_test(m_f3), rope_color = "grey70") +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  scale_fill_grey()
 
-p <- a + b + c
+p <- a + b
 p <- p +

### 2022-06-08 analysis/paper/paper.Rmd
Clean up libs being used

@@
   "dplyr",
-  "egg",
   "english",
@@
   "flextable",
-  "ggplot2",
   "ggridges",
@@
   "patchwork",
-  "psych",
   "rsvg",

### 2022-06-08 analysis/paper/paper.Rmd
clarify results

@@
 
-All authors agreed on the evaluation of the data availability of all five articles that were scored by each author but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
-Fleiss' Kappa was not able to be calculated for code or data availability due to 100% agreement of a score of '0', converted to '1' for the analysis.
+All authors agreed on the inter-rater article evaluations for the data availability, '0', not available, but one of the authors rated one article as `NA` or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
 
@@
 Publications in Crop Protection and Plant Disease were less likely to share their data but no effects were detectable in any other journal title.
-The analysis was unable to detect any effect of journal title on the software used, though articles in Plant Disease, Nematology and Tropical Plant Pathology tended to be more open and available.
+
+## Effect of Year
+
+We were unable to detect any observable differences as a result of the year that an article was published for code availability.
+However, of the articles surveyed those published in 2016 were more likely to have shared data than the other years.
 
@@
 There were no detectable effects of the five-year impact factor on code or data availability.
-However, there was no effect of the five-year impact factor on the availability of the software that was used.
-
-## Effect of Year
-
-We were unable to detect any observable differences as a result of the year that an article was published for code, data or software availability.
 
@@
 
-No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
-The analysis was unable to detect any differences in the effect of access policy on the openness and reproducibility of the evaluated articles, but in journals where the policy was to allow both open and pay-for-fee access, the articles were less likely to be open and reproducible when compared to journals that were completely open.
+No journals surveyed were completely closed, all offered at least an option for open access articles but some were completely open.
+The analysis was unable to detect any differences in the effect of access policy on the availability of code or data.
+But in those journals where the policy was fully open access, the articles were more likely to share code.
 
-## Effect of Reproducibility Instructions
-
-Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
-Only two journals, *Plant Pathology* and *Tropical Plant Pathology* have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
-Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
-There were no detectable effects of the instructions on any of the three scores that were evaluated.
-
-## Effect of Software Used
-
-The availability of the software used had no effect on the availability of the code, i.e., the use of free, open-source software (FOSS), did not have the effect of making the code more available.
-Conversely, the use of closed or restrictive software did not cause code to be less available.
-There was no detectable effect of the software's availability on the availability of data.
-However, both of these scores tended to be higher when the software used was more available.
+## Software Used
 
@@
 ```
-
-In the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished.
-The next three programs were statistical software, `r tab_s[2, 1]` (2nd), `r tab_s[3, 1]` (3rd) and `r tab_s[4, 1]` (4th) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
-The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (5th), BLAST(6th), and BioEdit (10th) or phylogenetic analysis MrBayes (7th).
-The most general-purpose software cited in the top 10 was Excel® (9th).
-The Python programming language was cited only twice, not appearing in the top ten.
+Two-hundred fifty three unique software applications were recorded as having been used in the articles that were evalutated.
+These included desktop programs, web-based software and databases.
+From the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished.
+The next three programs were statistical software, SAS (`r scales::ordinal(which(tab_s == "SAS"))`), SPSS (`r scales::ordinal(which(tab_s == "SPSS"))`) and R (`r scales::ordinal(which(tab_s == "R"))`) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
+The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST ((`r scales::ordinal(which(tab_s == "BLAST"))`)), and BioEdit ((`r scales::ordinal(which(tab_s == "BIOEDIT"))`)) or phylogenetic analysis MrBayes ((`r scales::ordinal(which(tab_s == "MRBAYS"))`)).
+The most general-purpose software cited in the top 10 was Excel® (`r scales::ordinal(which(tab_s == "EXCEL"))`).
+The Python programming language was cited only twice.
 

### 2022-06-09 analysis/paper/paper.Rmd
Use posterior package to extract median values of parameters

@@
   "patchwork",
+  "posterior",
   "rsvg",

### 2022-06-09 analysis/paper/paper.Rmd
Edits to results section

@@
 
-Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] and the Region of Practical Equivalence (ROPE) was set to -0.1 to 0.1.
+A test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] with the Region of Practical Equivalence (ROPE) set to -0.1 to 0.1.
 
@@
 # Results
+
+## Inter-rater Agreement
+
+All authors agreed on the inter-rater article evaluations for the data availability, '0', not available, but one of the authors rated one article as `NA` or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
+
+## Code and Data Sharing Classification Scores
 
@@
 
-## Inter-rater Agreement
+## Analysis of Effects
 
-All authors agreed on the inter-rater article evaluations for the data availability, '0', not available, but one of the authors rated one article as `NA` or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
-
-## Effect of Journal Title
-
-The analysis found that publications in Phytopathology were more likely to share their code but was unable to detect differences in any other journal titles.
+The analysis found that publications in Phytopathology were more likely to share their code but undecided on any effects of any other journal titles (Median = `summarise_draws(m_f1) %>% filter(variable == "b_abbreviationPhytopathology") %>% select(median)`, 95% CI [0.78, 4.21] and can be considered as significant (0% in ROPE).
 Publications in Crop Protection and Plant Disease were less likely to share their data but no effects were detectable in any other journal title.
-
-## Effect of Year
 
@@
 
-## Effect of Impact Factor
-
 There were no detectable effects of the five-year impact factor on code or data availability.
-
-## Effect of Access Policy
 

### 2022-06-09 analysis/paper/paper.Rmd
Edits to discussion

@@
 ```
-Two-hundred fifty three unique software applications were recorded as having been used in the articles that were evalutated.
+
+There were `r as.character(english(length(unique(rrpp_software$software_used))))` unique software applications recorded being used in the articles that were evaluated.
 These included desktop programs, web-based software and databases.
-From the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished.
+From the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished for this work.
 The next three programs were statistical software, SAS (`r scales::ordinal(which(tab_s == "SAS"))`), SPSS (`r scales::ordinal(which(tab_s == "SPSS"))`) and R (`r scales::ordinal(which(tab_s == "R"))`) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
@@
 
+Except for a few isolated cases, most papers were not fully computationally reproducible.
+Very few authors choose to share both data and code.
+More authors shared data due to journal requirements to share sequence data, but other types of data related to field experiments or other laboratory studies were not likely to be shared.
+Code sharing was extremely rare, but in cases where it was shared, most were included as a part of the journal article's publication as extra materials rather than through data repositories.
+The reasons for not sharing code or data were not clearly available from the papers themselves and so this work was unable to determine possible reasons for this situation.
+We recognise that in some cases there may be commercial or intellectual property (IP) reasons for not sharing data or code, but these reasons should be clearly stated.
+However, in most cases, the data are collected with public funding and the code was developed using similar funding and there are no commercial or IP issues that preclude sharing and in fact the funding agency may have guidelines in place for sharing these materials.
+
+Much of the software used are Free Open Source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
+However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.
 MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
 The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
-SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
+SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
 The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel®.
-It is interesting to note however, that with the popularity of Python that it only appears in the survey twice and in 2020 in both articles, not enough times to be in the top 10 most-cited.
-
-We recognise that the scoring methods were developed by the authors specifically for this evaluation and are not entirely objective and acknowledge that we have based our scoring decisions on our own experiences in the field of plant pathology.
-However, without assigning values, it is not possible to attempt to qualify or quantify where our discipline stands in regards to computational reproducibility.
-
-In the authors' view, while many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have access to them.
-Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
-The authors believe that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible monetary cost.
+It is interesting to note however, that even with the popularity of Python in scientific programming, it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
 
@@
 
-While the majority of the articles that were surveyed did not score well, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.
+While the majority of the articles that were surveyed did not score well for sharing data and code, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.
 

### 2022-06-09 analysis/paper/paper.Rmd
Edits to closing

@@
 
+Without the data underlying the paper, we as a community cannot adequately evaluate the work as it is presented.
+Without the code that was used to analyse the data, we as a community cannot adequately evaluate the work as it is presented.
+That is, while we may be standing on the shoulders of giants doing our work, we cannot see where they've been to do our work, which hinders our efforts.
+
 # Authors' Contributions

### 2022-06-09 analysis/paper/paper.Rmd
Add tables of ROPE

@@
 
+```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_f1) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>% 
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit() %>%
+  set_caption(
+    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
+  )
+```
+
+\newpage
+
+```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_f2) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>%
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit()
+```
+
+\newpage
+
+```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_g1) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>%
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit()
+```
+
+\newpage
+
+```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_g2) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>%
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit()
+```
+
+\newpage
+
+```{r if-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_h1) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>%
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit()
+```
+
+\newpage
+
+```{r if-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_h2) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>%
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit()
+```
+
+\newpage
+
+```{r access-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_i1) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>%
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit()
+```
+
+\newpage
+
+```{r access-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+equivalence_test(m_i2) %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename(
+    "ROPE\nlow" = "ROPE_low",
+    "ROPE\nhigh" = "ROPE_high",
+    "ROPE %" = "ROPE_Percentage",
+    "ROPE Equivalence" = "ROPE_Equivalence",
+    "HDI\nLow" = "HDI_low",
+    "HDI\nHigh" = "HDI_high"
+  ) %>%
+  select(-Effects, -Component) %>%
+  flextable() %>%
+  colformat_num(na_str = "NA") %>%
+  set_formatter_type(fmt_double = "%.01f") %>%
+  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  autofit()
+```
+
+\newpage
+
 ```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A, B) Publication (Journal Title), (D, E) Year of Publication, (G, H) Five Year Impact Factor of Journal, and (J, K) Journal Open Access Policy where y is the data's density and y~rep~ are ten random posterior draws.
+Six factors were evaluated, (A, B) Publication (Journal Title), (C, D) Year of Publication, (E, F) Five Year Impact Factor of Journal, and (G, H) Journal Open Access Policy where y is the data's density and y~rep~ are ten random posterior draws.
 Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}
@@
 
-```{r equivalence-tests, echo=FALSE, warning=FALSE, message=FALSE}
-a <- plot(equivalence_test(m_f1), rope_color = "grey70") +
-  scale_y_discrete(
-    label = function(x) {
-      x %>% gsub("b_abbreviation", "", .)
-    }
-  ) +
-  scale_fill_grey()
-b <-
-  plot(equivalence_test(m_f2), rope_color = "grey70") +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  scale_fill_grey()
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
-
-```
-
-\newpage
-
 ```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
@@
 rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+        file = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
   options = "-dEPSCrop"
@@
 
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
 ```

### 2022-06-10 analysis/paper/paper.Rmd
specify iterations and confidence intervals

@@
 Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
-Each model was run for 6000 iterations in four chains with a warmup of 3000 iterations and thinning set to 1.
+Each model was run for 10,000 iterations in four chains with a warmup of 3000 iterations and thinning set to 1.
 
@@
 
-A test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] with the Region of Practical Equivalence (ROPE) set to -0.1 to 0.1.
+A test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] with the Region of Practical Equivalence (ROPE) set to -0.1 to 0.1 and confidence interval of 0.95.
 

### 2022-06-10 analysis/paper/paper.Rmd
Add to analysis results

@@
 Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
-`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
+`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2)`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2)`%) appeared to not use any computational methods.
 
-However, data was mostly not available with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the data was not available or mentioned in the article.
-However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%) scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
-
-More articles did a good job of using software that was reasonably available to anyone with `r length(which(rrpp$software_avail >= 2))` (`r round(length(which(rrpp$software_avail >= 2))/nrow(rrpp), 2) * 100`%) scoring '2' or '3' (Figure \@ref(fig:articleScores)B) for software availability.
+However, data was mostly not available with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2)`%) scoring '0' where the data was not available or mentioned in the article.
+However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2)`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2)`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
 
@@
 
-The analysis found that publications in Phytopathology were more likely to share their code but undecided on any effects of any other journal titles (Median = `summarise_draws(m_f1) %>% filter(variable == "b_abbreviationPhytopathology") %>% select(median)`, 95% CI [0.78, 4.21] and can be considered as significant (0% in ROPE).
-Publications in Crop Protection and Plant Disease were less likely to share their data but no effects were detectable in any other journal title.
+```{r code-data-analysis, message=FALSE, warning=FALSE, echo=FALSE}
+f1_draws <- summarise_draws(m_f1)
+f1_equivalence <- equivalence_test(m_f1)
+
+f2_draws <- summarise_draws(m_f2)
+f2_equivalence <- equivalence_test(m_f2)
+
+g2_draws <- summarise_draws(m_g2)
+g2_equivalence <- equivalence_test(m_g2)
+
+i2_draws <- summarise_draws(m_i2)
+i2_equivalence <- equivalence_test(m_i2)
+
+phytopath_draws_f1 <-
+  filter(f1_draws, variable == "b_abbreviationPhytopathology")
+phytopath_equiv_f1 <-
+  as_tibble(f1_equivalence) %>% filter(Parameter == "b_abbreviationPhytopathology")
+
+cropProt_draws_f2 <-
+  filter(f2_draws, variable == "b_abbreviationCropProt")
+plantDis_draws_f2 <-
+  filter(f2_draws, variable == "b_abbreviationPlantDis")
+revMexFitopatol_draws_f2 <-
+  filter(f2_draws, variable == "b_abbreviationRevMexFitopatol")
+
+year2016_draws_g2 <-
+  as_tibble(g2_draws) %>% filter(variable == "b_year2016")
+
+access_i2 <-
+  filter(f2_draws, variable == "b_openTRUE")
+
+access_draws_i2 <-
+  as_tibble(i2_draws) %>% filter(variable == "b_openTRUE")
+
+cropProt_equiv_f2 <-
+  as_tibble(f1_equivalence) %>% filter(Parameter == "b_abbreviationCropProt")
+plantDis_equiv_f2 <-
+  as_tibble(f1_equivalence) %>% filter(Parameter == "b_abbreviationPlantDis")
+revMexFitopatol_equiv_f2 <-
+  as_tibble(f2_equivalence) %>% filter(Parameter == "b_abbreviationRevMexFitopatol")
+
+year2016_equiv_g2 <-
+  as_tibble(g2_equivalence) %>% filter(Parameter == "b_year2016")
+
+access_equiv_i2 <-
+  as_tibble(i2_equivalence) %>% filter(Parameter == "b_openTRUE")
+```
+
+The analysis found that publications in Phytopathology were more likely to share their code but undecided on any effects of any other journal titles (Median = `r round(phytopath_draws_f1$median, digits = 2)`, 95% CI [`r round(phytopath_equiv_f1$HDI_low, digits = 2)`, `r round(phytopath_equiv_f1$HDI_high, digits = 2)`] and can be considered as significant (`r round(phytopath_equiv_f1$ROPE_Percentage, digits = 2)`% in ROPE)).
+Publications in three journals, Crop Protection, Plant Disease and Revista Mexicana de Fitopatología were not likely to share their data (Median = `r round(cropProt_draws_f2$median, digits = 2)`, 95% CI [`r round(cropProt_equiv_f2$HDI_low, digits = 2)`, `r round(cropProt_equiv_f2$HDI_high, digits = 2)`] with (`r round(cropProt_equiv_f2$ROPE_Percentage, digits = 2)`% in ROPE), Median = `r round(plantDis_draws_f2$median, digits = 2)`, 95% CI [`r round(plantDis_equiv_f2$HDI_low, digits = 2)`, `r round(plantDis_equiv_f2$HDI_high, digits = 2)`] with (`r round(plantDis_equiv_f2$ROPE_Percentage, digits = 2)`% in ROPE) and Median = `r round(revMexFitopatol_draws_f2$median, digits = 2)`, 95% CI [`r round(revMexFitopatol_equiv_f2$HDI_low, digits = 2)`, `r round(revMexFitopatol_equiv_f2$HDI_high, digits = 2)`] (`r round(revMexFitopatol_equiv_f2$ROPE_Percentage, digits = 2)`% in ROPE), respectively, and so can be considered significant but no effects were detectable in any other journal titles.
 
 We were unable to detect any observable differences as a result of the year that an article was published for code availability.
-However, of the articles surveyed those published in 2016 were more likely to have shared data than the other years.
+However, of the articles surveyed those published in 2016 did share more code than in other years (Median = `r round(year2016_draws_g2$median, digits = 2)`, 95% CI [`r round(year2016_equiv_g2$HDI_low, digits = 2)`, `r round(year2016_equiv_g2$HDI_high, digits = 2)`] and can be considered as significant (`r round(year2016_equiv_g2$ROPE_Percentage, digits = 2) * 100 `% in ROPE)), but no discernible pattern was found across years.
 
@@
 The analysis was unable to detect any differences in the effect of access policy on the availability of code or data.
-But in those journals where the policy was fully open access, the articles were more likely to share code.
+But in those journals where the policy was fully open access, the articles tended to be more likely to share code (Median = `r round(access_draws_i2$median, digits = 2)`, 95% CI [`r round(access_equiv_i2$HDI_low, digits = 2)`, `r round(access_equiv_i2$HDI_high, digits = 2)`]).
 

### 2022-06-10 analysis/paper/paper.Rmd
Fix double "(" and typo for MRBAYES

@@
 The next three programs were statistical software, SAS (`r scales::ordinal(which(tab_s == "SAS"))`), SPSS (`r scales::ordinal(which(tab_s == "SPSS"))`) and R (`r scales::ordinal(which(tab_s == "R"))`) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
-The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST ((`r scales::ordinal(which(tab_s == "BLAST"))`)), and BioEdit ((`r scales::ordinal(which(tab_s == "BIOEDIT"))`)) or phylogenetic analysis MrBayes ((`r scales::ordinal(which(tab_s == "MRBAYS"))`)).
+The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST (`r scales::ordinal(which(tab_s == "BLAST"))`), and BioEdit (`r scales::ordinal(which(tab_s == "BIOEDIT"))`) or phylogenetic analysis MrBayes (`r scales::ordinal(which(tab_s == "MRBAYES"))`).
 The most general-purpose software cited in the top 10 was Excel® (`r scales::ordinal(which(tab_s == "EXCEL"))`).

### 2022-06-10 analysis/paper/paper.Rmd
fix typo in col name

@@
   rename(
-    "ROPE\nlow" = "ROPE_low",
-    "ROPE\nhigh" = "ROPE_high",
+    "ROPE\nLow" = "ROPE_low",
+    "ROPE\nHigh" = "ROPE_high",
     "ROPE %" = "ROPE_Percentage",

### 2022-06-10 analysis/paper/paper.Rmd
fix column formatting in tables

@@
   colformat_num(na_str = "NA") %>%
-  set_formatter_type(fmt_double = "%.01f") %>% 
-  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
+  colformat_double(
+    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
+    digits = 2
+  ) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      sprintf("%1.f%%", x * 100)
+  ) %>%
   autofit() %>%
@@
   colformat_num(na_str = "NA") %>%
-  set_formatter_type(fmt_double = "%.01f") %>%
-  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
-  autofit()
+  colformat_double(
+    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
+    digits = 2
+  ) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      sprintf("%1.f%%", x * 100)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
+  )
 ```
@@
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
   rename(
-    "ROPE\nlow" = "ROPE_low",
-    "ROPE\nhigh" = "ROPE_high",
+    "ROPE\nLow" = "ROPE_low",
+    "ROPE\nHigh" = "ROPE_high",
     "ROPE %" = "ROPE_Percentage",

### 2022-06-10 analysis/paper/paper.Rmd
Name medians, hdi low/high, etc. for clarity

@@
   as_tibble(i2_equivalence) %>% filter(Parameter == "b_openTRUE")
-```
-
-The analysis found that publications in Phytopathology were more likely to share their code but undecided on any effects of any other journal titles (Median = `r round(phytopath_draws_f1$median, digits = 2)`, 95% CI [`r round(phytopath_equiv_f1$HDI_low, digits = 2)`, `r round(phytopath_equiv_f1$HDI_high, digits = 2)`] and can be considered as significant (`r round(phytopath_equiv_f1$ROPE_Percentage, digits = 2)`% in ROPE)).
-Publications in three journals, Crop Protection, Plant Disease and Revista Mexicana de Fitopatología were not likely to share their data (Median = `r round(cropProt_draws_f2$median, digits = 2)`, 95% CI [`r round(cropProt_equiv_f2$HDI_low, digits = 2)`, `r round(cropProt_equiv_f2$HDI_high, digits = 2)`] with (`r round(cropProt_equiv_f2$ROPE_Percentage, digits = 2)`% in ROPE), Median = `r round(plantDis_draws_f2$median, digits = 2)`, 95% CI [`r round(plantDis_equiv_f2$HDI_low, digits = 2)`, `r round(plantDis_equiv_f2$HDI_high, digits = 2)`] with (`r round(plantDis_equiv_f2$ROPE_Percentage, digits = 2)`% in ROPE) and Median = `r round(revMexFitopatol_draws_f2$median, digits = 2)`, 95% CI [`r round(revMexFitopatol_equiv_f2$HDI_low, digits = 2)`, `r round(revMexFitopatol_equiv_f2$HDI_high, digits = 2)`] (`r round(revMexFitopatol_equiv_f2$ROPE_Percentage, digits = 2)`% in ROPE), respectively, and so can be considered significant but no effects were detectable in any other journal titles.
+
+phytopath_median <- round(phytopath_draws_f1$median, digits = 2)
+phytopath_hdi_low <- round(phytopath_equiv_f1$HDI_low, digits = 2)
+phytopath_hdi_high <- round(phytopath_equiv_f1$HDI_high, digits = 2)
+phytopath_perc_rope <-
+  round(phytopath_equiv_f1$ROPE_Percentage, digits = 2)
+
+cropProt_median <- round(cropProt_draws_f2$median, digits = 2)
+cropProt_hdi_low <- round(cropProt_equiv_f2$HDI_low, digits = 2)
+cropProt_hdi_high <- round(cropProt_equiv_f2$HDI_high, digits = 2)
+cropProt_perc_rope <-
+  round(cropProt_equiv_f2$ROPE_Percentage, digits = 2)
+
+plantDis_median <- round(plantDis_draws_f2$median, digits = 2)
+plantDis_hdi_low <- round(plantDis_equiv_f2$HDI_low, digits = 2)
+plantDis_hdi_high <- round(plantDis_equiv_f2$HDI_high, digits = 2)
+plantDis_perc_rope <-
+  round(plantDis_equiv_f2$ROPE_Percentage, digits = 2)
+
+revMexFitopatol_median <-
+  round(revMexFitopatol_draws_f2$median, digits = 2)
+revMexFitopatol_hdi_low <-
+  round(revMexFitopatol_equiv_f2$HDI_low, digits = 2)
+revMexFitopatol_hdi_high <-
+  round(revMexFitopatol_equiv_f2$HDI_high, digits = 2)
+revMexFitopatol_perc_rope <-
+  round(revMexFitopatol_equiv_f2$ROPE_Percentage, digits = 2)
+
+year2016_median <- round(year2016_draws_g2$median, digits = 2)
+year2016_hdi_low <- round(year2016_equiv_g2$HDI_low, digits = 2)
+year2016_hdi_high <- round(year2016_equiv_g2$HDI_high, digits = 2)
+year2016_perc_rope <- round(year2016_equiv_g2$ROPE_Percentage, digits = 2)
+
+access_median <- round(access_draws_i2$median, digits = 2)
+access_hdi_low <- round(access_equiv_i2$HDI_low, digits = 2)
+access_hdi_high <- round(access_equiv_i2$HDI_high, digits = 2)
+```
+
+The analysis found that publications in Phytopathology were more likely to share their code but undecided on any effects of any other journal titles (Median = `r phytopath_median`, 95% CI [`r phytopath_hdi_low`, `r phytopath_hdi_high`] and can be considered as significant (`r phytopath_perc_rope`% in ROPE)).
+Publications in three journals, Crop Protection, Plant Disease and Revista Mexicana de Fitopatología were not likely to share their data (Median = `r cropProt_median`, 95% CI [`r cropProt_hdi_low`, `r cropProt_hdi_high`] with (`r cropProt_perc_rope`% in ROPE), Median = `r plantDis_median`, 95% CI [`r plantDis_hdi_low`, `r plantDis_hdi_high`] with (`r plantDis_perc_rope`% in ROPE) and Median = `r revMexFitopatol_median`, 95% CI [`r revMexFitopatol_hdi_low`, `r revMexFitopatol_hdi_high`] (`r revMexFitopatol_perc_rope`% in ROPE), respectively, and so can be considered significant but no effects were detectable in any other journal titles.
 
 We were unable to detect any observable differences as a result of the year that an article was published for code availability.
-However, of the articles surveyed those published in 2016 did share more code than in other years (Median = `r round(year2016_draws_g2$median, digits = 2)`, 95% CI [`r round(year2016_equiv_g2$HDI_low, digits = 2)`, `r round(year2016_equiv_g2$HDI_high, digits = 2)`] and can be considered as significant (`r round(year2016_equiv_g2$ROPE_Percentage, digits = 2) * 100 `% in ROPE)), but no discernible pattern was found across years.
+However, of the articles surveyed those published in 2016 did share more code than in other years (Median = `r year2016_median`, 95% CI [`r year2016_hdi_low`, `r year2016_hdi_high`] and can be considered as significant (`r year2016_perc_rope`% in ROPE)), but no discernible pattern was found across years.
 
@@
 The analysis was unable to detect any differences in the effect of access policy on the availability of code or data.
-But in those journals where the policy was fully open access, the articles tended to be more likely to share code (Median = `r round(access_draws_i2$median, digits = 2)`, 95% CI [`r round(access_equiv_i2$HDI_low, digits = 2)`, `r round(access_equiv_i2$HDI_high, digits = 2)`]).
+But in those journals where the policy was fully open access, the articles tended to be more likely to share code (Median = `r access_median`, 95% CI [`r access_hdi_low`, `r access_hdi_high`]).
 

### 2022-06-10 analysis/paper/paper.Rmd
Update software ranking text

@@
 The next three programs were statistical software, SAS (`r scales::ordinal(which(tab_s == "SAS"))`), SPSS (`r scales::ordinal(which(tab_s == "SPSS"))`) and R (`r scales::ordinal(which(tab_s == "R"))`) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
-The remainder of the top ten programs we found were related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST (`r scales::ordinal(which(tab_s == "BLAST"))`), and BioEdit (`r scales::ordinal(which(tab_s == "BIOEDIT"))`) or phylogenetic analysis MrBayes (`r scales::ordinal(which(tab_s == "MRBAYES"))`).
-The most general-purpose software cited in the top 10 was Excel® (`r scales::ordinal(which(tab_s == "EXCEL"))`).
+The remainder of the top ten programs we found were mostly related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST (`r scales::ordinal(which(tab_s == "BLAST"))`), and BioEdit (9th) or phylogenetic analysis MrBayes (8th), tied with the most general-purpose software cited in the top 10, Excel®.
+In tenth place was FigTree, used for phylogenetic trees.
 The Python programming language was cited only twice.

### 2022-06-10 analysis/paper/paper.Rmd
clean up wording about software used in discussion
remove an errant "*"

@@
 SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
-The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel®.
 It is interesting to note however, that even with the popularity of Python in scientific programming, it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
@@
 The first level is including tables of raw data or code with the paper as a supplemental file.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra*\* with reproducible examples for readers to refer to.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
 This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.

### 2022-06-10 analysis/paper/paper.Rmd
Fix capitalisation in title
clarify "computational" reproducibility in the abstract

@@
 ---
-title: "Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward"
+title: "Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward"
 author:
@@
 Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 450 articles published from 2012 to 2021 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and reproducibility.
+We randomly selected 450 articles published from 2012 to 2021 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and computational reproducibility.
 We found that most of the articles were not following protocols for open science, and were failing to share data or code in a reproducible way.
-We also propose that use of open-source tools facilitates reproducible work and analyses benefitting not just readers, but the authors as well.
-Finally, we also provide ideas and tools to promote open, reproducible research practices among plant pathologists.
+We also propose that use of open-source tools facilitates computationally reproducible work and analyses benefitting not just readers, but the authors as well.
+Finally, we also provide ideas and tools to promote open, reproducible computational research practices among plant pathologists.
 

### 2022-06-11 analysis/paper/paper.Rmd
Add effect size objects

@@
 load(system.file("extdata",
+                 "m_f1_effectsize.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
+load(system.file("extdata",
                  "m_f2.Rda",
@@
                  mustWork = TRUE))
+load(system.file("extdata",
+                 "m_f2_effectsize.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
 
@@
 load(system.file("extdata",
+                 "m_g1_effectsize.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
+load(system.file("extdata",
                  "m_g2.Rda",
@@
                  mustWork = TRUE))
+load(system.file("extdata",
+                 "m_g2_effectsize.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
 
@@
 load(system.file("extdata",
+                 "m_h1_effectsize.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
+load(system.file("extdata",
                  "m_h2.Rda",
@@
                  mustWork = TRUE))
+load(system.file("extdata",
+                 "m_h2_effectsize.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
 
@@
 load(system.file("extdata",
+                 "m_i1_effectsize.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
+load(system.file("extdata",
                  "m_i2.Rda",
+                 package = "Reproducibility.in.Plant.Pathology",
+                 mustWork = TRUE))
+load(system.file("extdata",
+                 "m_i2_effectsize.Rda",
                  package = "Reproducibility.in.Plant.Pathology",

### 2022-06-11 analysis/paper/paper.Rmd
Filter Intercepts from tables

@@
 equivalence_test(m_f1) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
@@
 equivalence_test(m_f2) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
@@
 equivalence_test(m_g1) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
@@
 equivalence_test(m_g2) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
@@
 equivalence_test(m_h1) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
@@
 equivalence_test(m_h2) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
@@
 equivalence_test(m_i1) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
@@
 equivalence_test(m_i2) %>%
+  filter(!grepl("Intercept", Parameter)) %>% 
   mutate(Parameter = gsub("b_", "", .$Parameter)) %>%

### 2022-06-11 analysis/paper/paper.Rmd
replace effect size with report object

@@
 load(system.file("extdata",
-                 "m_f1_effectsize.Rda",
+                 "m_f1_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",
@@
 load(system.file("extdata",
-                 "m_f2_effectsize.Rda",
+                 "m_f2_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",
@@
 load(system.file("extdata",
-                 "m_g1_effectsize.Rda",
+                 "m_g1_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",
@@
 load(system.file("extdata",
-                 "m_g2_effectsize.Rda",
+                 "m_g2_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",
@@
 load(system.file("extdata",
-                 "m_h1_effectsize.Rda",
+                 "m_h1_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",
@@
 load(system.file("extdata",
-                 "m_h2_effectsize.Rda",
+                 "m_h2_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",
@@
 load(system.file("extdata",
-                 "m_i1_effectsize.Rda",
+                 "m_i1_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",
@@
 load(system.file("extdata",
-                 "m_i2_effectsize.Rda",
+                 "m_i2_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",

### 2022-06-12 analysis/paper/paper.Rmd
start adding description of models using "report"

@@
 
-The articles' scores for data, code and software availability were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, year of publication, journal open access policy, and the effect of the availability of the software used, `software_avail` on the code and data availability.
-The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, journal title analysis where the 'journal' was a fixed effect and the five-year impact factor model where correlations between the journal title and impact factor affected the software availability model.
-
-Non-informative priors were selected from a normal distribution with a mean of 0 and a standard deviation of 1.5 were selected for all models.
-
-Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
-Each model was run for 10,000 iterations in four chains with a warmup of 3000 iterations and thinning set to 1.
+We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "logit")` family function for ordinal scale data using using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
+Priors over all parameters were set as normal (mean = 0.00, SD = 1.50), student_t (location = 0.00, scale = 2.50) distributions.
+
+The models' were structured as follows to predict two responses, computational methods and data availability.
+For the the publishing journal (abbreviation was used throughout) (formula: response ~ abbreviation) and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
+The effects of year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
 

### 2022-06-12 analysis/paper/paper.Rmd
Add model methods

@@
 The models' were structured as follows to predict two responses, computational methods and data availability.
-For the the publishing journal (abbreviation was used throughout) (formula: response ~ abbreviation) and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
-The effects of year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
+To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
+To predict the responses with the journals' open access policies the formula took the form response ~ open and included abbreviation, assignee and year as random effects (formula: list(~1 | abbreviation, ~1 | assignee, ~1 | year)).
 

### 2022-06-12 analysis/paper/paper.Rmd
Add reporting on parameters with detectable differences

@@
 
-## Analysis of Effects
+## Statistical Analysis
 
@@
 ```
+
+For brevity, only journals where the 95% CI fell outside the Region of Practical Equivalence (ROPE) are reported here.
+For a full description of all parameters see (XXXXXX).
+When predicting the availability of computational methods (code) availability, the effect of *Phytopathology* (Median = 2.55, 95% CI [0.73, 4.24]) had a 99.59% probability of being positive (> 0), 99.57% of being significant (> 0.05), and 99.12% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24803).
+When predicting the availability of data availability, three journals were less likely to share data, with the others being unable to detect any effect.
+The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
+The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
+The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
+The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).
+
+There was no effect detected for year when predicting the availability of computational methods (code) availability.
+However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
+There was no detectable pattern in increasing or decreasing availability of data in the years examined.
+
+There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.
+
+The effect of the open access policy, open being TRUE, (Median = 0.08, 95% CI [-2.13, 2.26]) had a 52.95% probability of being positive (> 0), 51.12% of being significant (> 0.05), and 41.96% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22528).
+
+Following the Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework, we report the median of the posterior distribution and its 95% CI (Highest Density Interval), along the probability of direction (pd), the probability of significance and the probability of being large.
+The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are |0.05| and |0.30|.
+Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 (Vehtari et al., 2019), and Effective Sample Size (ESS), which should be greater than 1000 (Burkner, 2017).
 

### 2022-06-13 analysis/paper/paper.Rmd
Remove code chunk that's not needed
Values are included from "report"

@@
 
-```{r code-data-analysis, message=FALSE, warning=FALSE, echo=FALSE}
-f1_draws <- summarise_draws(m_f1)
-f1_equivalence <- equivalence_test(m_f1)
-
-f2_draws <- summarise_draws(m_f2)
-f2_equivalence <- equivalence_test(m_f2)
-
-g2_draws <- summarise_draws(m_g2)
-g2_equivalence <- equivalence_test(m_g2)
-
-i2_draws <- summarise_draws(m_i2)
-i2_equivalence <- equivalence_test(m_i2)
-
-phytopath_draws_f1 <-
-  filter(f1_draws, variable == "b_abbreviationPhytopathology")
-phytopath_equiv_f1 <-
-  as_tibble(f1_equivalence) %>% filter(Parameter == "b_abbreviationPhytopathology")
-
-cropProt_draws_f2 <-
-  filter(f2_draws, variable == "b_abbreviationCropProt")
-plantDis_draws_f2 <-
-  filter(f2_draws, variable == "b_abbreviationPlantDis")
-revMexFitopatol_draws_f2 <-
-  filter(f2_draws, variable == "b_abbreviationRevMexFitopatol")
-
-year2016_draws_g2 <-
-  as_tibble(g2_draws) %>% filter(variable == "b_year2016")
-
-access_i2 <-
-  filter(f2_draws, variable == "b_openTRUE")
-
-access_draws_i2 <-
-  as_tibble(i2_draws) %>% filter(variable == "b_openTRUE")
-
-cropProt_equiv_f2 <-
-  as_tibble(f1_equivalence) %>% filter(Parameter == "b_abbreviationCropProt")
-plantDis_equiv_f2 <-
-  as_tibble(f1_equivalence) %>% filter(Parameter == "b_abbreviationPlantDis")
-revMexFitopatol_equiv_f2 <-
-  as_tibble(f2_equivalence) %>% filter(Parameter == "b_abbreviationRevMexFitopatol")
-
-year2016_equiv_g2 <-
-  as_tibble(g2_equivalence) %>% filter(Parameter == "b_year2016")
-
-access_equiv_i2 <-
-  as_tibble(i2_equivalence) %>% filter(Parameter == "b_openTRUE")
-
-phytopath_median <- round(phytopath_draws_f1$median, digits = 2)
-phytopath_hdi_low <- round(phytopath_equiv_f1$HDI_low, digits = 2)
-phytopath_hdi_high <- round(phytopath_equiv_f1$HDI_high, digits = 2)
-phytopath_perc_rope <-
-  round(phytopath_equiv_f1$ROPE_Percentage, digits = 2)
-
-cropProt_median <- round(cropProt_draws_f2$median, digits = 2)
-cropProt_hdi_low <- round(cropProt_equiv_f2$HDI_low, digits = 2)
-cropProt_hdi_high <- round(cropProt_equiv_f2$HDI_high, digits = 2)
-cropProt_perc_rope <-
-  round(cropProt_equiv_f2$ROPE_Percentage, digits = 2)
-
-plantDis_median <- round(plantDis_draws_f2$median, digits = 2)
-plantDis_hdi_low <- round(plantDis_equiv_f2$HDI_low, digits = 2)
-plantDis_hdi_high <- round(plantDis_equiv_f2$HDI_high, digits = 2)
-plantDis_perc_rope <-
-  round(plantDis_equiv_f2$ROPE_Percentage, digits = 2)
-
-revMexFitopatol_median <-
-  round(revMexFitopatol_draws_f2$median, digits = 2)
-revMexFitopatol_hdi_low <-
-  round(revMexFitopatol_equiv_f2$HDI_low, digits = 2)
-revMexFitopatol_hdi_high <-
-  round(revMexFitopatol_equiv_f2$HDI_high, digits = 2)
-revMexFitopatol_perc_rope <-
-  round(revMexFitopatol_equiv_f2$ROPE_Percentage, digits = 2)
-
-year2016_median <- round(year2016_draws_g2$median, digits = 2)
-year2016_hdi_low <- round(year2016_equiv_g2$HDI_low, digits = 2)
-year2016_hdi_high <- round(year2016_equiv_g2$HDI_high, digits = 2)
-year2016_perc_rope <- round(year2016_equiv_g2$ROPE_Percentage, digits = 2)
-
-access_median <- round(access_draws_i2$median, digits = 2)
-access_hdi_low <- round(access_equiv_i2$HDI_low, digits = 2)
-access_hdi_high <- round(access_equiv_i2$HDI_high, digits = 2)
-```
-
 For brevity, only journals where the 95% CI fell outside the Region of Practical Equivalence (ROPE) are reported here.
-For a full description of all parameters see (XXXXXX).
+For a full description of all parameters details see (XXXXXX).
 When predicting the availability of computational methods (code) availability, the effect of *Phytopathology* (Median = 2.55, 95% CI [0.73, 4.24]) had a 99.59% probability of being positive (> 0), 99.57% of being significant (> 0.05), and 99.12% of being large (> 0.30).
@@
 When predicting the availability of data availability, three journals were less likely to share data, with the others being unable to detect any effect.
+Publications in three journals, Crop Protection, Plant Disease and Revista Mexicana de Fitopatología were not likely to share their data and so can be considered significant but no effects were detectable in any other journal titles.
 The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).

### 2022-06-13 analysis/paper/paper.Rmd
clean up results

@@
 
+No journals surveyed were completely closed, all offered at least an option for open access articles but some were completely open.
 The effect of the open access policy, open being TRUE, (Median = 0.08, 95% CI [-2.13, 2.26]) had a 52.95% probability of being positive (> 0), 51.12% of being significant (> 0.05), and 41.96% of being large (> 0.30).
@@
 Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 (Vehtari et al., 2019), and Effective Sample Size (ESS), which should be greater than 1000 (Burkner, 2017).
-
-The analysis found that publications in Phytopathology were more likely to share their code but undecided on any effects of any other journal titles (Median = `r phytopath_median`, 95% CI [`r phytopath_hdi_low`, `r phytopath_hdi_high`] and can be considered as significant (`r phytopath_perc_rope`% in ROPE)).
-Publications in three journals, Crop Protection, Plant Disease and Revista Mexicana de Fitopatología were not likely to share their data (Median = `r cropProt_median`, 95% CI [`r cropProt_hdi_low`, `r cropProt_hdi_high`] with (`r cropProt_perc_rope`% in ROPE), Median = `r plantDis_median`, 95% CI [`r plantDis_hdi_low`, `r plantDis_hdi_high`] with (`r plantDis_perc_rope`% in ROPE) and Median = `r revMexFitopatol_median`, 95% CI [`r revMexFitopatol_hdi_low`, `r revMexFitopatol_hdi_high`] (`r revMexFitopatol_perc_rope`% in ROPE), respectively, and so can be considered significant but no effects were detectable in any other journal titles.
-
-We were unable to detect any observable differences as a result of the year that an article was published for code availability.
-However, of the articles surveyed those published in 2016 did share more code than in other years (Median = `r year2016_median`, 95% CI [`r year2016_hdi_low`, `r year2016_hdi_high`] and can be considered as significant (`r year2016_perc_rope`% in ROPE)), but no discernible pattern was found across years.
-
-There were no detectable effects of the five-year impact factor on code or data availability.
-
-No journals surveyed were completely closed, all offered at least an option for open access articles but some were completely open.
-The analysis was unable to detect any differences in the effect of access policy on the availability of code or data.
-But in those journals where the policy was fully open access, the articles tended to be more likely to share code (Median = `r access_median`, 95% CI [`r access_hdi_low`, `r access_hdi_high`]).
 

### 2022-06-13 analysis/paper/paper.Rmd
clarify results section
quantify how many journals were "open" vs "both"

@@
 
-For brevity, only journals where the 95% CI fell outside the Region of Practical Equivalence (ROPE) are reported here.
+For brevity, only details of parameter where the 95% CI fell outside the Region of Practical Equivalence (ROPE) are reported here.
 For a full description of all parameters details see (XXXXXX).
+
 When predicting the availability of computational methods (code) availability, the effect of *Phytopathology* (Median = 2.55, 95% CI [0.73, 4.24]) had a 99.59% probability of being positive (> 0), 99.57% of being significant (> 0.05), and 99.12% of being large (> 0.30).
@@
 
-No journals surveyed were completely closed, all offered at least an option for open access articles but some were completely open.
+No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.
 The effect of the open access policy, open being TRUE, (Median = 0.08, 95% CI [-2.13, 2.26]) had a 52.95% probability of being positive (> 0), 51.12% of being significant (> 0.05), and 41.96% of being large (> 0.30).

### 2022-06-14 analysis/paper/paper.Rmd
Flesh out description of priors

@@
 
-We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "logit")` family function for ordinal scale data using using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
-Priors over all parameters were set as normal (mean = 0.00, SD = 1.50), student_t (location = 0.00, scale = 2.50) distributions.
+We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal scale data using using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
+Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
+Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random intercepts.
 

### 2022-06-14 analysis/paper/paper.Rmd
wordsmith the paper's text

@@
 For brevity, only details of parameter where the 95% CI fell outside the Region of Practical Equivalence (ROPE) are reported here.
-For a full description of all parameters details see (XXXXXX).
-
-When predicting the availability of computational methods (code) availability, the effect of *Phytopathology* (Median = 2.55, 95% CI [0.73, 4.24]) had a 99.59% probability of being positive (> 0), 99.57% of being significant (> 0.05), and 99.12% of being large (> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24803).
-When predicting the availability of data availability, three journals were less likely to share data, with the others being unable to detect any effect.
+For a full description of all models' parameter details see (XXXXXX).
+
+When predicting the availability of computational methods (code) availability, all journals were compared with *Phytopathology*
+There were no clear differences found between any of the journals as compared with *Phytopathology* for the sharing of computational materials, the effects of all parameters were undecided.
+
+When predicting the availability of data availability as compared with *Phytopathology* two journals were not likely to share data, with the others being unable to detect any effect.
 Publications in three journals, Crop Protection, Plant Disease and Revista Mexicana de Fitopatología were not likely to share their data and so can be considered significant but no effects were detectable in any other journal titles.

### 2022-06-15 analysis/paper/paper.Rmd
load report and parameters

@@
   "officer",
+  "parameters",
   "patchwork",
   "posterior",
+  "report",
   "rsvg",

### 2022-06-15 analysis/paper/paper.Rmd
remove open access policy figures

@@
                  "m_h2_report.Rda",
-                 package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-
-load(system.file("extdata",
-                 "m_i1.Rda",
-                 package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
-                 "m_i1_report.Rda",
-                 package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
-                 "m_i2.Rda",
-                 package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
-                 "m_i2_report.Rda",
                  package = "Reproducibility.in.Plant.Pathology",

### 2022-06-15 analysis/paper/paper.Rmd
clean up description of methods

@@
 The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package (version `r packageVersion("dplyr")`) [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.
+This was downloaded, saved as an Open Document Spreadsheet (ODS) file for analysis.
 

### 2022-06-15 analysis/paper/paper.Rmd
Remove sentence describing work that wasn't done.

@@
 Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
-The software availability, computational methods availability and data availability scores were converted from 0 -- 3 to 1 -- 4 ordinal score values for analysis.
 
@@
 The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
+Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages.
+The full reproducible code is available in Supplementary Materials.
 

### 2022-06-15 analysis/paper/paper.Rmd
Remove sentence referring to open access policies
wordsmithing results

@@
 To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
-To predict the responses with the journals' open access policies the formula took the form response ~ open and included abbreviation, assignee and year as random effects (formula: list(~1 | abbreviation, ~1 | assignee, ~1 | year)).
 
@@
 
-However, data was mostly not available with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2)`%) scoring '0' where the data was not available or mentioned in the article.
+Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2)`%) scoring '0' where the data was not available or mentioned in the article.
 However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2)`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2)`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
@@
 
-For brevity, only details of parameter where the 95% CI fell outside the Region of Practical Equivalence (ROPE) are reported here.
-For a full description of all models' parameter details see (XXXXXX).
-
-When predicting the availability of computational methods (code) availability, all journals were compared with *Phytopathology*
-There were no clear differences found between any of the journals as compared with *Phytopathology* for the sharing of computational materials, the effects of all parameters were undecided.
+When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores with a mean of zero.
+
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A).
 
 When predicting the availability of data availability as compared with *Phytopathology* two journals were not likely to share data, with the others being unable to detect any effect.
-Publications in three journals, Crop Protection, Plant Disease and Revista Mexicana de Fitopatología were not likely to share their data and so can be considered significant but no effects were detectable in any other journal titles.
+Publications in three journals, *Crop Protection*, *Plant Disease* and *Revista Mexicana de Fitopatología*, can be considered clearly less likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
 The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).

### 2022-06-15 analysis/paper/paper.Rmd
Remove sentence on open access policy effects

@@
 No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.
-The effect of the open access policy, open being TRUE, (Median = 0.08, 95% CI [-2.13, 2.26]) had a 52.95% probability of being positive (> 0), 51.12% of being significant (> 0.05), and 41.96% of being large (> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22528).
 

### 2022-06-15 analysis/paper/paper.Rmd
Move parameter descriptions from tables to figures and supplementary mats

@@
 
-```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_f1) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
-```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_f2) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
-```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_g1) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
-```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_g2) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
-```{r if-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_h1) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
-```{r if-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_h2) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
-```{r access-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_i1) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
-```{r access-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-equivalence_test(m_i2) %>%
-  filter(!grepl("Intercept", Parameter)) %>% 
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename(
-    "ROPE\nLow" = "ROPE_low",
-    "ROPE\nHigh" = "ROPE_high",
-    "ROPE %" = "ROPE_Percentage",
-    "ROPE Equivalence" = "ROPE_Equivalence",
-    "HDI\nLow" = "HDI_low",
-    "HDI\nHigh" = "HDI_high"
-  ) %>%
-  select(-Effects, -Component) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  colformat_double(
-    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
-    digits = 2
-  ) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
-  )
-```
-
-\newpage
-
 ```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}

### 2022-06-15 analysis/paper/paper.Rmd
clean up posterior check figure

@@
 Six factors were evaluated, (A, B) Publication (Journal Title), (C, D) Year of Publication, (E, F) Five Year Impact Factor of Journal, and (G, H) Journal Open Access Policy where y is the data's density and y~rep~ are ten random posterior draws.
-Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}
+Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
 
@@
 mod_list <- list(
-  pp_check(m_f1) +
+  pp_check(m_f1, type = "bars", ndraws = 50) +
     ggtitle("Code") +
@@
     ylab("Journal"),
-  pp_check(m_f2) +
+  pp_check(m_f2, type = "bars", ndraws = 50) +
     ggtitle("Data") +
@@
     ),
-  pp_check(m_g1) +
+  pp_check(m_g1, type = "bars", ndraws = 50) +
     theme(
@@
     ylab("Year"),
-  pp_check(m_g2) +
+  pp_check(m_g2, type = "bars", ndraws = 50) +
     theme(
@@
     ),
-  pp_check(m_h1) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ) +
+  pp_check(m_h1, type = "bars", ndraws = 50) +
     ylab("5 Y IF"),
-  pp_check(m_h2) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_i1) +
-    ylab("Access\nPolicy"),
-  pp_check(m_i2)
+  pp_check(m_h2, type = "bars", ndraws = 50)
 )

### 2022-06-15 analysis/paper/paper.Rmd
add figures for parameters

@@
 
+```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
+a <- plot(parameters(m_f1)) + 
+  scale_colour_grey() +
+  ggtitle("Code")
+
+b <- plot(parameters(m_f2)) + 
+  scale_colour_grey() +
+   theme(
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.y = element_blank()
+    ) +
+  ggtitle("Data")
+
+p <- a + b
+p <- p +
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+```
+
+\newpage
+
+```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
+a <- plot(parameters(m_g1), show_lables = TRUE) + 
+  scale_colour_grey() +
+  ggtitle("Code")
+
+b <- plot(parameters(m_g2), show_lables = TRUE) + 
+  scale_colour_grey() +
+   theme(
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.y = element_blank()
+    ) +
+  ggtitle("Data")
+
+p <- a + b
+p <- p +
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+```
+
+\newpage
+
+```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
+a <- plot(parameters(m_h1), show_lables = TRUE) + 
+  scale_colour_grey() +
+  ggtitle("Code")
+
+b <- plot(parameters(m_h2), show_lables = TRUE) + 
+  scale_colour_grey() +
+   theme(
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.y = element_blank()
+    ) +
+  ggtitle("Data")
+
+p <- a + b
+p <- p +
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
+```
+
+\newpage
+
 ```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.

### 2022-06-15 analysis/paper/paper.Rmd
add supplementary materials section

@@
 rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
   options = "-dEPSCrop"
@@
 
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
 ```
+
+\newpage
+
+# Supplementary Materials
+
+## Tables
+
+\newpage
+
+```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+parameters(m_f1) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  as_tibble() %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      sprintf("%1.f%%", x * 100)
+  ) %>%
+  autofit()
+```
+
+\newpage
+
+```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+parameters(m_f2) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  as_tibble() %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      sprintf("%1.f%%", x * 100)
+  ) %>%
+  autofit()
+```
+
+\newpage
+
+```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+parameters(m_h1) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  as_tibble() %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      sprintf("%1.f%%", x * 100)
+  ) %>%
+  autofit()
+```
+
+\newpage
+
+```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+parameters(m_h2) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  as_tibble() %>%
+  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      sprintf("%1.f%%", x * 100)
+  ) %>%
+  autofit()
+```

### 2022-06-16 analysis/paper/paper.Rmd
format code chunk

@@
 
-invisible(
-  lapply(
-    packages,
+invisible(lapply(packages,
                  library,
-    character.only = TRUE
-  )
-)
+                 character.only = TRUE))
 
@@
 
-load(system.file("extdata",
+load(
+  system.file(
+    "extdata",
     "m_f1.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_f1_report.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_f2.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_f2_report.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
+    mustWork = TRUE
+  )
+)
 
-load(system.file("extdata",
+load(
+  system.file(
+    "extdata",
     "m_g1.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_g1_report.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_g2.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_g2_report.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
+    mustWork = TRUE
+  )
+)
 
-load(system.file("extdata",
+load(
+  system.file(
+    "extdata",
     "m_h1.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_h1_report.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_h2.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
-load(system.file("extdata",
+    mustWork = TRUE
+  )
+)
+load(
+  system.file(
+    "extdata",
     "m_h2_report.Rda",
     package = "Reproducibility.in.Plant.Pathology",
-                 mustWork = TRUE))
+    mustWork = TRUE
+  )
+)
 ```

### 2022-06-16 analysis/paper/paper.Rmd
wordsmithing

@@
 
-We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal scale data using using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
+We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
 Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).

### 2022-06-16 analysis/paper/paper.Rmd
Revise methods section

@@
 
-Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].
-
-All methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
+Using the Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework, the median of the posterior distribution and its 95% CI (Highest Density Interval), along the probability of direction (pd), the probability of significance and the probability of being large are reported.
+The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are 0.05 and 0.3 as suggested by @Makowski2019.
+Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 [@VVehtari2021] and Effective Sample Size (ESS), which should be greater than 1000 [@Burkner2017].
+
+A full report of all parameters and model details are available in the Supplementary Materials.
+Additionally, all methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
 

### 2022-06-16 analysis/paper/paper.Rmd
Move to Methods section

@@
 
-Following the Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework, we report the median of the posterior distribution and its 95% CI (Highest Density Interval), along the probability of direction (pd), the probability of significance and the probability of being large.
-The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are |0.05| and |0.30|.
-Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 (Vehtari et al., 2019), and Effective Sample Size (ESS), which should be greater than 1000 (Burkner, 2017).
-
 ## Software Used

### 2022-06-16 analysis/paper/paper.Rmd
Use autofit()

@@
   colformat_num(na_str = "NA") %>%
-  set_table_properties(layout = "autofit") %>%
+  autofit() %>%
   set_caption(

### 2022-06-16 analysis/paper/paper.Rmd
Move supplementary materials to own file

@@
 ```
-
-\newpage
-
-# Supplementary Materials
-
-## Tables
-
-\newpage
-
-```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-parameters(m_f1) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  as_tibble() %>%
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit()
-```
-
-\newpage
-
-```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-parameters(m_f2) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  as_tibble() %>%
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit()
-```
-
-\newpage
-
-```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-parameters(m_h1) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  as_tibble() %>%
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit()
-```
-
-\newpage
-
-```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-parameters(m_h2) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  as_tibble() %>%
-  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      sprintf("%1.f%%", x * 100)
-  ) %>%
-  autofit()
-```

### 2022-06-16 analysis/supplementary materials/Supplementary Materials.Rmd
create supplementary materials files

--- 2022-06-16 analysis/paper/paper.Rmd
@@
 ---
-title: "Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward"
+title: "Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward"
 author:
@@
 output: 
-  bookdown::word_document2:
+  officedown::rdocx_document:
+     pandoc_args:
+       - '--lua-filter=pagebreak.lua'
      fig_caption: yes
@@
      reference_docx: "../templates/phytopath_template.docx"
-     pandoc_args:
-       - '--lua-filter=scholarly-metadata.lua'
-       - '--lua-filter=author-info-blocks.lua'
-       - '--lua-filter=pagebreak.lua'
-bibliography: references.bib
-link-citations: no
-csl: "../templates/american-phytopathological-society.csl"
 ---
@@
 ```{r, setup, echo = FALSE, message=FALSE}
-packages <- c(
-  "DiagrammeR",
-  "DiagrammeRsvg",
-  "bayesplot",
-  "bayestestR",
-  "brms",
-  "dplyr",
-  "english",
-  "extrafont",
-  "flextable",
-  "ggridges",
-  "ggpubr",
-  "here",
-  "janitor",
-  "knitr",
-  "officer",
-  "parameters",
-  "patchwork",
-  "posterior",
-  "report",
-  "rsvg",
-  "tidyr",
-  "tools"
-)
-
-install.packages(setdiff(packages,
-                         rownames(installed.packages())),
-                 repos = "http://cran.us.r-project.org")
-
-invisible(lapply(packages,
-                 library,
-                 character.only = TRUE))
 
 library("Reproducibility.in.Plant.Pathology")
+library("tidyverse")
+library("pander")
+library("report")
+library("flextable")
 
@@
 ir <- import_interrater_scores()
-
-opts_chunk$set(
-  collapse = TRUE,
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  dev = c("postscript"),
-  out.width = "100%",
-  comment = "#>",
-  dev = "cairo_pdf",
-  cache = FALSE
-)
-
-theme_set(theme_classic())
 
@@
 
-**Keywords: Data Science, Computational Biology, Techniques**
+# Supplementary Materials
 
-\newpage
+## Journal Publication Model Reports
 
-# Abstract {#abstract .unnumbered}
+### Computational Methods
 
-Open research practices have been highlighted extensively during the last ten years in many fields of scientific study as essential standards needed to promote transparency and reproducibility of scientific results.
-Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and, analyses were conducted.
-Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
-We randomly selected 450 articles published from 2012 to 2021 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and computational reproducibility.
-We found that most of the articles were not following protocols for open science, and were failing to share data or code in a reproducible way.
-We also propose that use of open-source tools facilitates computationally reproducible work and analyses benefitting not just readers, but the authors as well.
-Finally, we also provide ideas and tools to promote open, reproducible computational research practices among plant pathologists.
-
-\newpage
-
-# Introduction
-
-Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
-Collectively, they contribute to increasing our basic and applied knowledge of several aspects of pathogen biology and disease development to ultimately improve plant disease management.
-Scientific research in the field varies from the purely observational or descriptive nature to inferential, based on experimental or simulation-derived data sets.
-Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of the methods and results.
-These research findings include biological materials (host and pathogen genotypes), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated during the course of the research.
-
-Recently, open science has been highlighted with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
-
-Reproducibility is one component under the umbrella of open science.
-By proactively practising open science, the work increases the chance to become more reproducible through the availability of data and code.
-That is, open science leads to reproducibility and replicability.
-
-For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
-Many of the terms used in this area have varying definitions that may or may not agree with each other.
-For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @Eckert2020; @Dienlin2020; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
-
-In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, *e.g.*, field trials that span years and locations or complex glasshouse experiments.
-Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":
-
-> "The replication of scientific findings using independent investigators, methods, data, equipment, and protocols has long been, and will continue to be, the standard by which scientific claims are evaluated.
-However, in many fields of study there are examples of scientific investigations that cannot be fully replicated because of a lack of time or resources.
-In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing.
-One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
-> @Peng2009.
-> *Reproducible research and Biostatistics*.
-> Biostatistics, 10 (3): 405-408.
-
-Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes.
-And that the software used are also easily obtained and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
-
-Plant pathologists routinely provide information on protocols and chemicals allowing for reproducibility.
-However, frequently biological specimens such as strains, cultures or cultivars are not available after publication.
-These cases do constitute a lack of reproducibility but will not be covered here.
-
-# Materials and Methods
-
-## Article Selection and Evaluation Events
-
-In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our collective status.
-We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
-The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
-From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
-Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
-Initially there were four evaluators, later a fifth was added and the list was recreated.
-There were three evaluation events that took place to increase the yearly coverage of the evaluations.
-Each evaluator was assigned 50 articles to evaluate during an evaluation event.
-A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for each sampling event.
-This was done because some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
-
-Articles were then manually selected by visiting the journals' websites and selecting the articles within which the randomly assigned page numbers fell, *i.e.*, if the page number was 32, the article that started on page 28 and ended on page 35 was selected as it contained page 32.
-In cases where an article was not suitable, *e.g.*, a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
-
-Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)) in each of the three different scoring events as their time allowed for their participation.
-In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.
-
-## Scoring Criteria
-
-Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
-The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as an Open Document Spreadsheet (ODS) file for analysis.
-
-Each article was rated on a 0 -- 3 scale for its software, data and code availability.
-'Software availability' rated how freely and openly available the software used was.
-It was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-'Code availability' rated how easily and openly available the computational methods used in the article were.
-Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-Lastly, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
-This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
-
-Where possible, the software used in conducting the research behind the publication was recorded in the notes when it was cited or otherwise specified in the article text.
-
-## Data Cleaning
-
-A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
-Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
-When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
-For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
-In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
-Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
-
-## Statistical Analysis
-
-The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
-Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages.
-The full reproducible code is available in Supplementary Materials.
-
-Inter-rater differences were evaluated using percent agreement and Fliess' Kappa [@DelPonte2019].
-
-We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
-Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
-Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random intercepts.
-
-The models' were structured as follows to predict two responses, computational methods and data availability.
-To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
-To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
-
-The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure a good model fit to the data and that the chains mixed well.
-
-Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
-
-A test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] with the Region of Practical Equivalence (ROPE) set to -0.1 to 0.1 and confidence interval of 0.95.
-
-Using the Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework, the median of the posterior distribution and its 95% CI (Highest Density Interval), along the probability of direction (pd), the probability of significance and the probability of being large are reported.
-The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are 0.05 and 0.3 as suggested by @Makowski2019.
-Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 [@VVehtari2021] and Effective Sample Size (ESS), which should be greater than 1000 [@Burkner2017].
-
-A full report of all parameters and model details are available in the Supplementary Materials.
-Additionally, all methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
-
-# Results
-
-## Inter-rater Agreement
-
-All authors agreed on the inter-rater article evaluations for the data availability, '0', not available, but one of the authors rated one article as `NA` or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
-
-## Code and Data Sharing Classification Scores
-
-Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
-`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2)`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2)`%) appeared to not use any computational methods.
-
-Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2)`%) scoring '0' where the data was not available or mentioned in the article.
-However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2)`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2)`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
-
-## Statistical Analysis
-
-When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores with a mean of zero.
-
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A).
-
-When predicting the availability of data availability as compared with *Phytopathology* two journals were not likely to share data, with the others being unable to detect any effect.
-Publications in three journals, *Crop Protection*, *Plant Disease* and *Revista Mexicana de Fitopatología*, can be considered clearly less likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
-The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
-The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
-The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).
-
-There was no effect detected for year when predicting the availability of computational methods (code) availability.
-However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
-There was no detectable pattern in increasing or decreasing availability of data in the years examined.
-
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.
-
-No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.
-
-## Software Used
-
-```{r softwareCited, echo=FALSE, include=FALSE}
-# tally up software used for the next paragraph
-rrpp_software <-
-  rrpp %>% 
-  transform(software_used = strsplit(software_used, ",")) %>%
-  unnest(software_used) %>%
-  mutate(software_used = trimws(software_used)) %>%
-  mutate(software_used = toupper(software_used))
-
-tab <- table(rrpp_software$software_used)
-tab_s <- as.data.frame(sort(tab))
-tab_s <-
-  tab_s %>%
-  arrange(desc(Freq)) %>%
-  filter(Freq %in% head(unique(Freq), 10)) %>% 
-  rename("Software" = "Var1", "Frequency" = "Freq")
+```{r journal-code, echo=FALSE}
+m_f1_report %>% 
+  pander()
 ```
 
-There were `r as.character(english(length(unique(rrpp_software$software_used))))` unique software applications recorded being used in the articles that were evaluated.
-These included desktop programs, web-based software and databases.
-From the top ten most frequently cited software, the most frequently cited program was `r tab_s[1, 1]`, where different versions were not distinguished for this work.
-The next three programs were statistical software, SAS (`r scales::ordinal(which(tab_s == "SAS"))`), SPSS (`r scales::ordinal(which(tab_s == "SPSS"))`) and R (`r scales::ordinal(which(tab_s == "R"))`) with two other statistical programs also frequently cited, GenStat and Statistica (tied 8th).
-The remainder of the top ten programs we found were mostly related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST (`r scales::ordinal(which(tab_s == "BLAST"))`), and BioEdit (9th) or phylogenetic analysis MrBayes (8th), tied with the most general-purpose software cited in the top 10, Excel®.
-In tenth place was FigTree, used for phylogenetic trees.
-The Python programming language was cited only twice.
+### Data
 
-# Discussion
-
-Except for a few isolated cases, most papers were not fully computationally reproducible.
-Very few authors choose to share both data and code.
-More authors shared data due to journal requirements to share sequence data, but other types of data related to field experiments or other laboratory studies were not likely to be shared.
-Code sharing was extremely rare, but in cases where it was shared, most were included as a part of the journal article's publication as extra materials rather than through data repositories.
-The reasons for not sharing code or data were not clearly available from the papers themselves and so this work was unable to determine possible reasons for this situation.
-We recognise that in some cases there may be commercial or intellectual property (IP) reasons for not sharing data or code, but these reasons should be clearly stated.
-However, in most cases, the data are collected with public funding and the code was developed using similar funding and there are no commercial or IP issues that preclude sharing and in fact the funding agency may have guidelines in place for sharing these materials.
-
-Much of the software used are Free Open Source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
-However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.
-MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
-The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
-SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
-It is interesting to note however, that even with the popularity of Python in scientific programming, it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
-
-## Are There Good Examples?
-
-While the majority of the articles that were surveyed did not score well for sharing data and code, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.
-
-There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
-The first level is including tables of raw data or code with the paper as a supplemental file.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
-This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
-
-At the second level, in our search of the literature, we found that @Hill2019 shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
-The scripts provided used an R package, *checkpoint* [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that are necessary to reproduce the work rather than defaulting to the latest versions.
-However, the scripts did not run unhindered, as the supplementary materials suggested that they should, without changes to the data, but with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.
-One drawback to this approach is that journals are often not equipped to handle code, e.g., script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them.
-Though this should be possible given some effort from the publishing journal to share simple text files rather than binary formats along with the proper instructions and handling of these file formats rather than a one-size-fits all approach that we commonly see for supplementary materials.
-
-The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
-As an example, Sparks et al.
-[-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
-Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
-@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
-The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania [@Sparks2022a].
-However, even this example is not totally open as it requires ArcGIS, an expensive proprietary software, to run the provided Python scripts for the RICEPEST model [@Savary2014].
-This highlights the difficulty in making work completely open and reproducible, further work could be undertaken to make the Python scripts rely totally on free-open-source-software but the work as it it provided here does allow for the complete reproducibility of the paper as written provided with the proper tools.
-Using a repository resource like GitHub allows readers to easily contact the authors by opening "Issues" and report bugs or ask questions in an open forum that are not as straightforward when the data are provided as supplementary material.
-
-The fourth level includes packaging the full analysis in a containerized software application, *e.g.*, Docker.
-Docker is an open source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyses) with the operating system required to run that analysis on a user's computer.
-However, there are drawbacks to using Docker.
-It can be difficult to understand for a new user and new platforms, like the Apple M1 chip, may not be fully supported, which hinder the ability to share the container.
-But, in most cases using an open source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
-For more on using Docker for reproducible research, we would refer readers to @Nuest2020.
-As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package that enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
-used [@Miorini2018; @Miorini2019].
-@Kamvar2015 took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
-While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
-
-## Best Practices to Enhance Reproducible Research
-
-Journals can encourage authors to deposit their data and code by providing instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources.
-While our analysis was unable to detect any differences in journals providing such instruction and journals that did not, the trend did indicate that journals that provided such instruction had better scores for data and code availability.
-
-A general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
-
-The first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
-A second level involves providing raw data and code as binary files (PDF or other non-text files) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a paywall.
-The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
-The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-In the next section we present standards and tools that can be used to ensure reproducibility.
-
-When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
-Deposit and annotate biological materials with an herbarium or other repository.
-Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
-This allows end-users to identify what was used and identify the methods used more accurately.
-Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on your research.
-
-The use of programming or scripting languages such as R, Julia, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
-
-Text files for saving small sets of data are preferable.
-Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.*, comma separated (CSV) or tab separated (TSV) files.
-This also helps ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like GenBank, MariaDB or PostgreSQL which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
-While personal databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set.
-Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
-
-Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
-It should be noted, that the use of a database management system also allows for both of these at the expense of added complexity.
-Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
-Unexpected changes to values in the data [@Ziemann2016] may also occur when using proprietary formats.
-
-If steps are followed to make the data FAIR then it will be readable by humans and machines alike and this will help support discoveries and support further research.
-In turn, sharing data will lead to new citations for your work as others discover and use it.
-To make your data the most widely discoverable and usable, ensure that it has a persistent identifier.
-A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but the Handle.Net Registry (HNR) (<https://handle.net/>) is also an option.
-There are different options for generating a DOI for your data and other materials.
-FigShare, Zenodo and OSF.io all offer persistent archives along with a services to generate a DOI for your materials.
-The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
-For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.
-
-Once you have determined how to best manage your source code and the data sets for analysis the next step is to consider how to share your data.
-Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
-
-Other providers exist that allow for you to not only track changes but also to share the data openly, these include GitHub, Gitlab and Bitbucket.
-GitHub is arguably the most popular and widely used software development platform currently.
-Data that is encoded in CSV or other plain text formats can easily be deposited in a repository along with code for analysis to enable tracking of changes and other users to download and replicate the work.
-
-We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only as these are not an optimal way to preserve and share your work over the long term.
-Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
-It is a best practice to always ensure that you have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF.io and generated a DOI for the materials to help ensure continued accessibility.
-Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
-If readers are uncertain, we suggest to also consult with local librarians about possible resources.
-Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
-The important aspect is that data once deposited cannot be modified any more.
-
-In this work we have evaluated the state of computational reproducibility in the plant pathology literature and presented suggestions for areas of improvement.
-As we prepared this letter, we became more aware of the urgent need to spread and establish an open science attitude and culture among plant pathologists.
-To assist in fostering this sort of change in our discipline, Open Plant Pathology (OPP), <https://www.openplantpathology.org>, an institution-independent and non-funded initiative, was founded in January 2018 by two of this letter's co-authors, Del Ponte and Sparks, in 2018 with the following vision: "foster a diverse community culture that values openness, transparency and reproducibility of scientific research data and methods in our field".
-We started OPP with a minimal infrastructure and support from other enthusiastic colleagues that allows members to interact sharing and gathering ideas on how we can improve the openness and reproducibility in our discipline.
-
-We believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
-For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
-This letter was drafted over the course of several years as the authors had time to devote to it.
-Having everything in a reproducible framework made it easy to resume work and set-aside as necessary without losing information and having everything well-documented made it more simple to do this.
-Second, it benefits the reviewer by aiding their understanding of the work done and gives them more materials to use to make suggestions for improvements when reviewing and the end-user or reader is better able to verify the validity of the methods used and recreate the analysis.
-Perhaps more importantly, sharing these details helps with knowledge transfer by showing other interested parties how something was done rather than simply describing it.
-Lastly, openly sharing your work and making it discoverable can lead to new collaborations and synergistic ideas.
-One of the most important messages that we would like to share is that there is more to the work than just the paper.
-Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
-This open sharing of code and data leads to greater impact as work is cited if resources such as code or data are reused.
-With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
-
-Without the data underlying the paper, we as a community cannot adequately evaluate the work as it is presented.
-Without the code that was used to analyse the data, we as a community cannot adequately evaluate the work as it is presented.
-That is, while we may be standing on the shoulders of giants doing our work, we cannot see where they've been to do our work, which hinders our efforts.
-
-# Authors' Contributions
-
-A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
-E.DP. provided five-year impact factors.
-A.H.S., E.DP., Z.F. K.A. and N.G. evaluated articles for scoring.
-A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
-A.H.S. wrote the manuscript in consultation with E.DP.
-All authors provided critical feedback and helped contribute to the final version of the manuscript.
-
-# Data and Code Availability
-
-## Data
-
-The raw data for this work are documented and available from DOI [https://doi.org/10.5281/zenodo.4941722](10.5281/zenodo.4941722).
-
-## Code
-
-All code used in the analyses and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
-A webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.
-
-# Acknowledgements
-
-The authors are grateful for insightful comments from Dr.
-David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript and from Ms.
-Anna Hepworth for statistical guidance on evaluating inter-rater scores.
-
-\newpage
-
-# Literature Cited
-
-<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
-
-::: {#refs}
-:::
-
-\newpage
-
-# Tables
-
-```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
-import_notes() %>%
-  tabyl(journal) %>%
-  select(-percent) %>%
-  rename(Journal = journal) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  autofit() %>%
-  set_caption(
-    "Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
-  )
+```{r journal-data, echo=FALSE}
+m_f2_report %>% 
+  pander()
 ```
@@
 
-```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
-tab_s %>%
-  flextable() %>%
-  autofit() %>%
-  set_caption("The top ten sofware programs that were found to be used in the papers that were surveyed.")
+## Year
+
+### Computational Methods
+
+```{r year-code, echo=FALSE}
+m_g1_report %>% 
+  pander()
+```
+
+### Data
+
+```{r year-data, echo=FALSE}
+m_g2_report %>% 
+  pander()
 ```
@@
 
-```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
-readODS::read_ods(
-    system.file(
-      "extdata",
-      "Reproducibility_in_plant_pathology_notes.ods",
-      package = "Reproducibility.in.Plant.Pathology"
-    ),
-    na = "NA",
-    sheet = "scoring_criteria_paper"
+## Five-year Impact Factor
+
+### Computational Methods
+
+```{r if5yr-code, echo=FALSE}
+m_h1_report %>% 
+  pander()
+```
+
+### Data
+
+```{r if5yr-data, echo=FALSE}
+m_h2_report %>% 
+  pander()
+```
+
+## Tables
+
+\newpage
+
+```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_f1_report) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>% 
+  colformat_double(digits = 2) %>% 
+    set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
   ) %>%
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
   autofit() %>%
-  set_caption(
-    "Articles were three in three areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
+  set_caption("")
 ```
@@
 
-# Figures
-
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A, B) Publication (Journal Title), (C, D) Year of Publication, (E, F) Five Year Impact Factor of Journal, and (G, H) Journal Open Access Policy where y is the data's density and y~rep~ are ten random posterior draws.
-Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
-
-set.seed(23)
-
-color_scheme_set(scheme = "gray")
-
-mod_list <- list(
-  pp_check(m_f1, type = "bars", ndraws = 50) +
-    ggtitle("Code") +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank(),
-      plot.title = element_text(hjust = 0.5)
-    ) +
-    ylab("Journal"),
-  pp_check(m_f2, type = "bars", ndraws = 50) +
-    ggtitle("Data") +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank(),
-      plot.title = element_text(hjust = 0.5)
-    ),
-  pp_check(m_g1, type = "bars", ndraws = 50) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ) +
-    ylab("Year"),
-  pp_check(m_g2, type = "bars", ndraws = 50) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ),
-  pp_check(m_h1, type = "bars", ndraws = 50) +
-    ylab("5 Y IF"),
-  pp_check(m_h2, type = "bars", ndraws = 50)
-)
-
-p <- wrap_plots(mod_list, ncol = 2) +
-  plot_layout(guides = "collect") &
-  plot_annotation(title = "Bayesian posterior distributions of evaluation score models",
-                  tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
+```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_f2_report) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>% 
+  colformat_double(digits = 2) %>% 
+    set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption("")
 ```
@@
 
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the three categories evaluated, (A) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-(B) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-(C) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
-
-a <- ggplot(rrpp, aes(x = as.factor(software_avail))) +
-  geom_bar(fill = "black") +
-  ylab("Count") +
-  xlab("Article Score") +
-  ggtitle("Software")
-
-b <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
-  geom_bar(fill = "black") +
-  ylab("Count") +
-  xlab("Article Score") +
-  ggtitle("Code")
-
-c <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
-  geom_bar(fill = "black") +
-  ylab("Count") +
-  xlab("Article Score") +
-  ggtitle("Data")
-
-p <- a + b + c
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
+```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_g1_report) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>% 
+  colformat_double(digits = 2) %>% 
+    set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption("")
 ```
@@
 
-```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_f1)) + 
-  scale_colour_grey() +
-  ggtitle("Code")
-
-b <- plot(parameters(m_f2)) + 
-  scale_colour_grey() +
-   theme(
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.title.y = element_blank()
-    ) +
-  ggtitle("Data")
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
+```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_g2_report) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>% 
+  colformat_double(digits = 2) %>% 
+    set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption("")
 ```
@@
 
-```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_g1), show_lables = TRUE) + 
-  scale_colour_grey() +
-  ggtitle("Code")
-
-b <- plot(parameters(m_g2), show_lables = TRUE) + 
-  scale_colour_grey() +
-   theme(
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.title.y = element_blank()
-    ) +
-  ggtitle("Data")
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
+```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_h1_report) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>% 
+  colformat_double(digits = 2) %>% 
+    set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption("")
 ```
@@
 
-```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_h1), show_lables = TRUE) + 
-  scale_colour_grey() +
-  ggtitle("Code")
-
-b <- plot(parameters(m_h2), show_lables = TRUE) + 
-  scale_colour_grey() +
-   theme(
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.title.y = element_blank()
-    ) +
-  ggtitle("Data")
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
+```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_h2_report) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>% 
+  colformat_double(digits = 2) %>% 
+    set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption("")
 ```
-
-\newpage
-
-```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
-Starting with the question, determine the methodology, describe it, make it available and cite it.
-Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
-Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}
-
-p <- export_svg(
-  grViz(
-    "digraph Fig3 {
-    graph [fontsize = 8, nodesep=0.5]
-
-    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
-    'An open and reproducible workflow'
-
-    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
-    Question
-
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
-    Methodology; Data; Analysis; Manuscript;
-
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Arial]
-    Description; Availability; Citation
-
-    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
-    'Binary Code'; 'Binary File'; Supplement
-
-    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-    'Source Code'; 'Data File'; Metadata; 'Public Repository';
-
-    Question->Methodology->Data->Analysis
-    Analysis->Manuscript
-    Methodology->Description
-    Methodology->Citation
-    Methodology->Availability
-    Manuscript->Supplement
-    Data->'Data File'->'Public Repository'
-    Data->Metadata->'Public Repository'
-    Analysis->'Binary Code'->Supplement
-    Analysis->'Source Code'->'Public Repository'
-    Data->'Binary File'->Supplement
-  }",
-  width = 1000,
-  height = 750
-  )
-)
-
-rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
-  options = "-dEPSCrop"
-)
-
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
-```

### 2022-06-16 analysis/paper/paper.Rmd
Wordsmithing and spelling corrections

@@
 
-We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
-Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
-Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random intercepts.
+We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
+The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
+Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
+Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
 
-The models' were structured as follows to predict two responses, computational methods and data availability.
+The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
 To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).

### 2022-06-16 analysis/paper/paper.Rmd
Wordsmithing and clean up statistical analysis

@@
 
-All authors agreed on the inter-rater article evaluations for the data availability, '0', not available, but one of the authors rated one article as `NA` or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
+All authors agreed on the five inter-rater article evaluations for the data availability, '0', not available for a inter-rater score of 100%.
+However, one of the authors rated one article as 'NA' or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the 'NA' value dropped from the code availability.
 
-## Code and Data Sharing Classification Scores
+## Code and Data Sharing Findings
 
@@
 However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2)`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2)`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
-
-## Statistical Analysis
-
-When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores with a mean of zero.
-
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A).
-
-When predicting the availability of data availability as compared with *Phytopathology* two journals were not likely to share data, with the others being unable to detect any effect.
-Publications in three journals, *Crop Protection*, *Plant Disease* and *Revista Mexicana de Fitopatología*, can be considered clearly less likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
-The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
-The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
-The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).
-
-There was no effect detected for year when predicting the availability of computational methods (code) availability.
-However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
-There was no detectable pattern in increasing or decreasing availability of data in the years examined.
-
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.
-
-No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.
 

### 2022-06-16 analysis/paper/paper.Rmd
Move statistical analysis

--- 2022-06-16 analysis/paper/paper.Rmd
@@
 The Python programming language was cited only twice.
+
+## Statistical Analysis
+
+When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores with a mean of zero.
+
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A).
+
+When predicting the availability of data availability as compared with *Phytopathology*, publications in three journals, *Crop Protection*, *Plant Disease* and *Revista Mexicana de Fitopatología*, can be considered clearly less likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
+The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
+The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
+The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
+The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).
+
+There was no effect detected for year when predicting the availability of computational methods (code) availability.
+However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
+There was no detectable pattern in increasing or decreasing availability of data in the years examined.
+
+There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.
+
+No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.
 

### 2022-06-16 analysis/paper/paper.Rmd
Add captions to figures

@@
 
-```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
+```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
+Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
+Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_f1)) +
@@
 
-```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
+```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_g1), show_lables = TRUE) + 
@@
 
-```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
+```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_h1), show_lables = TRUE) + 

### 2022-06-17 analysis/scripts/check_abbreviation_model_fit.R
Add model checks for abbrevation
compare logit and probit models for best fit

@@ -1,0 +1,102 @@
+library(tidyverse)
+library(brms)
+library(Reproducibility.in.Plant.Pathology)
+library(bayestestR)
+
+options(mc.cores = parallel::detectCores())
+
+rrpp <- import_notes()
+
+rrpp <-
+  within(rrpp,
+         abbreviation <-
+           relevel(abbreviation, ref = "Phytopathology"))
+
+rrpp <- drop_na(rrpp, comp_mthds_avail)
+
+priors <- c(prior(normal(0, 1), class = "b"),
+            prior(normal(0, 1), class = "Intercept"))
+
+prior_i_only <- c(prior(normal(0, 1), class = "Intercept"))
+
+m_f1_logit_intercept <-
+  brm(formula = data_avail ~ 1 +
+        (1 | assignee) +
+        (1 | year),
+      data = rrpp,
+      seed = 27,
+      prior = prior_i_only,
+      family = cumulative(link = "logit"),
+      iter = 20000,
+      control = list(adapt_delta = 0.999),
+      save_pars = save_pars(all = TRUE)
+  )
+loo_f1_logit_intercept <- loo(m_f1_logit_intercept, save_psis = TRUE)
+
+m_f1_logit <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee) +
+      (1 | year),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "logit"),
+    iter = 20000,
+    control = list(adapt_delta = 0.999),
+    save_pars = save_pars(all = TRUE)
+  )
+loo_f1_logit <- loo(m_f1_logit, save_psis = TRUE)
+
+m_f2_logit <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee) +
+      (1 | year),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "logit"),
+    iter = 20000,
+    control = list(adapt_delta = 0.999),
+    save_pars = save_pars(all = TRUE)
+  )
+loo_f2_logit <- loo(m_f2_logit, save_psis = TRUE)
+
+m_f1_probit <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee) +
+      (1 | year),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "probit"),
[…]

### 2022-06-17 analysis/scripts/check_year_model_fit.R
Add model checks for year
Check for best model fit between logit and probit

@@ -1,0 +1,87 @@
+library(tidyverse)
+library(brms)
+library(Reproducibility.in.Plant.Pathology)
+library(bayestestR)
+
+options(mc.cores = parallel::detectCores())
+
+rrpp <- import_notes()
+
+rrpp <-
+  within(rrpp,
+         abbreviation <-
+           relevel(abbreviation, ref = "Phytopathology"))
+
+rrpp <- drop_na(rrpp, comp_mthds_avail)
+
+priors <- c(prior(normal(0, 1), class = "b"),
+            prior(normal(0, 1), class = "Intercept"))
+
+prior_i_only <- c(prior(normal(0, 1), class = "Intercept"))
+
+m_g1_logit_intercept <-
+  brm(formula = data_avail ~ 1 +
+        (1 | assignee),
+      data = rrpp,
+      seed = 27,
+      prior = prior_i_only,
+      family = cumulative(link = "logit"),
+      iter = 20000,
+      control = list(adapt_delta = 0.999),
+      save_pars = save_pars(all = TRUE)
+  )
+
+m_g1_logit <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "logit"),
+    iter = 20000,
+    control = list(adapt_delta = 0.999),
+    save_pars = save_pars(all = TRUE)
+  )
+
+m_g2_logit <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "logit"),
+    iter = 20000,
+    control = list(adapt_delta = 0.999),
+    save_pars = save_pars(all = TRUE)
+  )
+
+m_g1_probit <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "probit"),
+    iter = 20000,
+    control = list(adapt_delta = 0.99),
+    save_pars = save_pars(all = TRUE)
+  )
+
+m_g2_probit <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "probit"),
+    iter = 20000,
[…]

### 2022-06-17 analysis/paper/paper.Rmd
Add statement on how models were selected
Remove software score from figure

@@
 Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages.
-The full reproducible code is available in Supplementary Materials.
+The full reproducible code is available in @Sparks2022.
 
@@
 Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
+The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log pointwise predictive density via `loo_compare()`.
 
@@
 
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the three categories evaluated, (A) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
-(B) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-(C) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the two categories evaluated, (A) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+(B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
 
-a <- ggplot(rrpp, aes(x = as.factor(software_avail))) +
-  geom_bar(fill = "black") +
-  ylab("Count") +
-  xlab("Article Score") +
-  ggtitle("Software")
-
-b <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
+a <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
   geom_bar(fill = "black") +
@@
 
-c <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
+b <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
   geom_bar(fill = "black") +
@@
 
-p <- a + b + c
+p <- a + b
 p <- p +

### 2022-06-17 analysis/paper/paper.Rmd
Strip out more references to software availability

@@
 
-Each article was rated on a 0 -- 3 scale for its software, data and code availability.
-'Software availability' rated how freely and openly available the software used was.
-It was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
+Each article was rated on a 0 -- 3 scale for its data and code availability.
 'Code availability' rated how easily and openly available the computational methods used in the article were.
@@
   set_caption(
-    "Articles were three in three areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
+    "Articles were three in two areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of two areas, 'Computational Methods Availability' and 'Data Availability'.")
 ```

### 2022-06-17 analysis/paper/paper.Rmd
Remove table 3, redundant with text

@@
 
-Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)) in each of the three different scoring events as their time allowed for their participation.
+Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research in each of the three different scoring events as their time allowed for their participation.
 In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.
@@
 
-```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
-readODS::read_ods(
-    system.file(
-      "extdata",
-      "Reproducibility_in_plant_pathology_notes.ods",
-      package = "Reproducibility.in.Plant.Pathology"
-    ),
-    na = "NA",
-    sheet = "scoring_criteria_paper"
-  ) %>% 
-  flextable() %>%
-  colformat_num(na_str = "NA") %>%
-  autofit() %>%
-  set_caption(
-    "Articles were three in two areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of two areas, 'Computational Methods Availability' and 'Data Availability'.")
-```
-
-\newpage
-
 # Figures

### 2022-06-17 analysis/paper/paper.Rmd
specify link function used, logit, in methods

@@
 
-We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
+We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
 The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.

### 2022-06-17 analysis/paper/paper.Rmd
Clarify captions for figures

@@
 ```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials.
+However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
 Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
@@
 
-```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.', cache=FALSE, fig.env='figure'}
+```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for practical equivalence was undecided in any detectable effects of year of publication on computational materials or data being shared.
+Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_g1), show_lables = TRUE) + 
@@
 
-```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.', cache=FALSE, fig.env='figure'}
+```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for practical equivalence was undecided on any detectable effects of impact factor.
+Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_h1), show_lables = TRUE) + 

### 2022-06-17 analysis/scripts/check_abbreviation_model_fit.R
Add models without year for comparison

@@ -20,18 +20,21 @@ priors <- c(prior(normal(0, 1), class = "b"),
 prior_i_only <- c(prior(normal(0, 1), class = "Intercept"))
 
 m_f1_logit_intercept <-
-  brm(formula = data_avail ~ 1 +
-        (1 | assignee) +
-        (1 | year),
-      data = rrpp,
-      seed = 27,
-      prior = prior_i_only,
-      family = cumulative(link = "logit"),
-      iter = 20000,
-      control = list(adapt_delta = 0.999),
-      save_pars = save_pars(all = TRUE)
+  brm(
+    formula = data_avail ~ 1 +
+      (1 | assignee) +
+      (1 | year),
+    data = rrpp,
+    seed = 27,
+    prior = prior_i_only,
+    family = cumulative(link = "logit"),
+    iter = 20000,
+    control = list(adapt_delta = 0.999,
+                   max_treedepth = 15),
+    save_pars = save_pars(all = TRUE)
   )
-loo_f1_logit_intercept <- loo(m_f1_logit_intercept, save_psis = TRUE)
+loo_f1_logit_intercept <-
+  loo(m_f1_logit_intercept, save_psis = TRUE)
 
 m_f1_logit <-
   brm(
@@ -48,6 +51,21 @@ m_f1_logit <-
   )
 loo_f1_logit <- loo(m_f1_logit, save_psis = TRUE)
 
+m_f1_logit_no_year <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "logit"),
+    iter = 20000,
+    control = list(adapt_delta = 0.999),
+    save_pars = save_pars(all = TRUE)
+  )
+loo_f1_logit_no_year <- loo(m_f1_logit_no_year, save_psis = TRUE)
+
+
 m_f2_logit <-
   brm(
     formula = data_avail ~ year +
@@ -62,6 +80,20 @@ m_f2_logit <-
     save_pars = save_pars(all = TRUE)
   )
 loo_f2_logit <- loo(m_f2_logit, save_psis = TRUE)
+
+m_f2_logit_no_year <-
+  brm(
+    formula = data_avail ~ year +
+      (1 | assignee),
+    data = rrpp,
+    seed = 27,
+    prior = priors,
+    family = cumulative(link = "logit"),
[…]

### 2022-06-17 analysis/scripts/check_abbreviation_model_fit.R
Use waic for model checks

@@ -125,13 +125,12 @@ m_f2_probit <-
   )
 loo_f2_probit <- loo(m_f2_probit, save_psis = TRUE)
 
-# compare with AIC
+# compare with waic
 waic(m_f1_logit_intercept,
      m_f1_logit,
      m_f1_probit,
      m_f1_logit_no_year)
-waic(m_f2_logit_intercept,
-     m_f2_logit,
+waic(m_f2_logit,
      m_f2_probit,
      m_f2_logit_no_year)
 
@@ -140,7 +139,6 @@ loo_compare(loo_f1_logit_intercept,
             loo_f1_logit,
             loo_f1_probit,
             loo_f1_logit_no_year)
-loo_compare(loo_f2_logit_intercept,
-            loo_f2_logit,
+loo_compare(loo_f2_logit,
             loo_f2_probit,
             loo_f2_logit_no_year)

### 2022-06-17 analysis/scripts/check_year_model_fit.R
check year models for fit with waic and loo_compare

@@ -19,18 +19,6 @@ priors <- c(prior(normal(0, 1), class = "b"),
 
 prior_i_only <- c(prior(normal(0, 1), class = "Intercept"))
 
-m_g1_logit_intercept <-
-  brm(formula = data_avail ~ 1 +
-        (1 | assignee),
-      data = rrpp,
-      seed = 27,
-      prior = prior_i_only,
-      family = cumulative(link = "logit"),
-      iter = 20000,
-      control = list(adapt_delta = 0.999),
-      save_pars = save_pars(all = TRUE)
-  )
-
 m_g1_logit <-
   brm(
     formula = data_avail ~ year +
@@ -85,3 +73,17 @@ m_g2_probit <-
 
 m_g1_comparison <- bayesfactor_models(m_g1_logit, m_g1_probit)
 m_g2_comparison <- bayesfactor_models(m_g2_logit, m_g2_probit)
+
+
+# compare with waic
+waic(m_g1_logit,
+     m_g1_probit)
+waic(m_g2_logit,
+     m_g2_probit)
+
+# compare with LOO
+loo_compare(loo_f1_logit,
+            loo_f1_probit)
+loo_compare(loo_f2_logit,
+            loo_f2_probit)
+

### 2022-06-17 analysis/paper/paper.Rmd
Update random effects, didn't use year

@@
 The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
-To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
+To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee as a random effect (formula: ~1 | assignee).
 To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).

### 2022-06-17 analysis/paper/paper.Rmd
Install package dependencies to knit paper
spelling/punctuation correction

@@
                          rownames(installed.packages())),
-                 repos = "http://cran.us.r-project.org")
+                 repos = "http://cran.us.r-project.org",
+                 dependencies = TRUE)
 
@@
 
-Model fitnesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model fitness's were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 

### 2022-06-17 analysis/paper/paper.Rmd
Clean up methods removing redundant text

@@
 
-The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
-Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages.
-The full reproducible code is available in @Sparks2022.
+The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020) using R 4.1.0 (R Core Team, 2021).
 

### 2022-06-17 analysis/paper/paper.Rmd
Fix citation

@@
 The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are 0.05 and 0.3 as suggested by @Makowski2019.
-Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 [@VVehtari2021] and Effective Sample Size (ESS), which should be greater than 1000 [@Burkner2017].
+Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 [@Vehtari2021] and Effective Sample Size (ESS), which should be greater than 1000 [@Burkner2017].
 

### 2022-06-18 analysis/scripts/check_abbreviation_model_fit.R
tighten up and clarify model fit check scripts

@@ -32,6 +32,14 @@ m_f1_logit <-
     save_pars = save_pars(all = TRUE)
   )
 
+m_f1_logit_fit <-
+  add_criterion(
+    m_f1_logit,
+    criterion = "loo",
+    moment_match = TRUE,
+    reloo = TRUE
+  )
+
 m_f1_logit_no_year <-
   brm(
     formula = comp_mthds_avail ~ abbreviation +
@@ -43,6 +51,13 @@ m_f1_logit_no_year <-
     iter = 20000,
     control = list(adapt_delta = 0.99),
     save_pars = save_pars(all = TRUE)
+  )
+m_f1_logit_no_year_fit <-
+  add_criterion(
+    m_f1_logit_no_year,
+    criterion = "loo",
+    moment_match = TRUE,
+    reloo = TRUE
   )
 
 m_f2_logit <-
@@ -58,6 +73,7 @@ m_f2_logit <-
     control = list(adapt_delta = 0.9),
     save_pars = save_pars(all = TRUE)
   )
+loo_f2_logit <- loo(m_f2_logit, save_psis = TRUE)
 
 m_f2_logit_no_year <-
   brm(
@@ -71,6 +87,7 @@ m_f2_logit_no_year <-
     control = list(adapt_delta = 0.9),
     save_pars = save_pars(all = TRUE)
   )
+loo_f2_logit_no_year <- loo(m_f2_logit_no_year, save_psis = TRUE)
 
 m_f1_probit <-
   brm(
@@ -85,6 +102,8 @@ m_f1_probit <-
     control = list(adapt_delta = 0.995),
     save_pars = save_pars(all = TRUE)
   )
+loo_f1_probit <- loo(m_f1_probit, save_psis = TRUE)
+
 
 m_f2_probit <-
   brm(
@@ -99,11 +118,113 @@ m_f2_probit <-
     control = list(adapt_delta = 0.99),
     save_pars = save_pars(all = TRUE)
   )
+loo_f2_probit <- loo(m_f2_probit, save_psis = TRUE)
 
 # compare with waic
 waic(m_f1_logit,
      m_f1_probit,
      m_f1_logit_no_year)
+# Output of model 'm_f1_logit':
+#
+#   Computed from 40000 by 440 log-likelihood matrix
+#
+# Estimate   SE
+# elpd_waic    -33.7 12.3
+# p_waic         8.1  3.7
+# waic          67.3 24.7
+#
[…]

### 2022-06-18 analysis/scripts/check_IF_5year_fit.R
tighten up and clarify model fit check scripts

@@ -19,69 +19,64 @@ priors <- c(prior(normal(0, 1), class = "b"),
 
 prior_i_only <- c(prior(normal(0, 1), class = "Intercept"))
 
-m_g1_logit_intercept <-
-  brm(formula = data_avail ~ 1 +
-        (1 | assignee),
-      data = rrpp,
-      seed = 27,
-      prior = prior_i_only,
-      family = cumulative(link = "logit"),
-      iter = 20000,
-      control = list(adapt_delta = 0.999),
-      save_pars = save_pars(all = TRUE)
-  )
-
-m_g1_logit <-
+cat("m_h1_logit model ")
+m_h1_logit <-
   brm(
-    formula = data_avail ~ year +
+    formula = data_avail ~ IF_5year +
       (1 | assignee),
     data = rrpp,
     seed = 27,
     prior = priors,
     family = cumulative(link = "logit"),
+    control = list(adapt_delta = 0.99),
     iter = 20000,
-    control = list(adapt_delta = 0.999),
     save_pars = save_pars(all = TRUE)
   )
 
-m_g2_logit <-
+cat("m_h2_logit model ")
+m_h2_logit <-
   brm(
-    formula = data_avail ~ year +
+    formula = data_avail ~ IF_5year +
       (1 | assignee),
     data = rrpp,
     seed = 27,
     prior = priors,
     family = cumulative(link = "logit"),
+    control = list(adapt_delta = 0.9),
     iter = 20000,
-    control = list(adapt_delta = 0.999),
     save_pars = save_pars(all = TRUE)
   )
 
-m_g1_probit <-
+cat("m_h1_probit model ")
+m_h1_probit <-
   brm(
-    formula = data_avail ~ year +
+    formula = data_avail ~ IF_5year +
       (1 | assignee),
     data = rrpp,
     seed = 27,
     prior = priors,
     family = cumulative(link = "probit"),
-    iter = 20000,
     control = list(adapt_delta = 0.99),
+    iter = 25000,
     save_pars = save_pars(all = TRUE)
   )
 
-m_g2_probit <-
+cat("m_h2_probit model ")
+m_h2_probit <-
   brm(
-    formula = data_avail ~ year +
+    formula = data_avail ~ IF_5year +
       (1 | assignee),
     data = rrpp,
     seed = 27,
     prior = priors,
     family = cumulative(link = "probit"),
-    iter = 20000,
[…]

### 2022-06-18 analysis/scripts/check_abbreviation_model_fit.R

@@ -12,110 +12,86 @@ rrpp <-
          abbreviation <-
            relevel(abbreviation, ref = "Phytopathology"))
 
-rrpp <- drop_na(rrpp, comp_mthds_avail)
+rrpp_code <- drop_na(rrpp, comp_mthds_avail)
+rrpp_data <- drop_na(rrpp, data_avail)
 
 priors <- c(prior(normal(0, 1), class = "b"),
             prior(normal(0, 1), class = "Intercept"))
 
-prior_i_only <- c(prior(normal(0, 1), class = "Intercept"))
-
-m_f1_logit_intercept <-
-  brm(
-    formula = data_avail ~ 1 +
-      (1 | assignee) +
-      (1 | year),
-    data = rrpp,
-    seed = 27,
-    prior = prior_i_only,
-    family = cumulative(link = "logit"),
-    iter = 20000,
-    control = list(adapt_delta = 0.999,
-                   max_treedepth = 15),
-    save_pars = save_pars(all = TRUE)
-  )
-loo_f1_logit_intercept <-
-  loo(m_f1_logit_intercept, save_psis = TRUE)
-
 m_f1_logit <-
   brm(
-    formula = data_avail ~ year +
+    formula = comp_mthds_avail ~ abbreviation +
       (1 | assignee) +
       (1 | year),
-    data = rrpp,
+    data = rrpp_code,
     seed = 27,
     prior = priors,
     family = cumulative(link = "logit"),
     iter = 20000,
-    control = list(adapt_delta = 0.999),
+    control = list(adapt_delta = 0.995),
     save_pars = save_pars(all = TRUE)
   )
-loo_f1_logit <- loo(m_f1_logit, save_psis = TRUE)
 
 m_f1_logit_no_year <-
   brm(
-    formula = data_avail ~ year +
+    formula = comp_mthds_avail ~ abbreviation +
       (1 | assignee),
-    data = rrpp,
+    data = rrpp_code,
     seed = 27,
     prior = priors,
     family = cumulative(link = "logit"),
     iter = 20000,
-    control = list(adapt_delta = 0.999),
+    control = list(adapt_delta = 0.99),
     save_pars = save_pars(all = TRUE)
   )
-loo_f1_logit_no_year <- loo(m_f1_logit_no_year, save_psis = TRUE)
-
 
 m_f2_logit <-
   brm(
-    formula = data_avail ~ year +
+    formula = data_avail ~ abbreviation +
       (1 | assignee) +
[…]

### 2022-06-18 analysis/scripts/check_year_model_fit.R

@@ -28,7 +28,6 @@ m_g1_logit <-
     prior = priors,
     family = cumulative(link = "logit"),
     iter = 20000,
-    control = list(adapt_delta = 0.999),
     save_pars = save_pars(all = TRUE)
   )
 
@@ -41,7 +40,6 @@ m_g2_logit <-
     prior = priors,
     family = cumulative(link = "logit"),
     iter = 20000,
-    control = list(adapt_delta = 0.999),
     save_pars = save_pars(all = TRUE)
   )
 
@@ -71,19 +69,10 @@ m_g2_probit <-
     save_pars = save_pars(all = TRUE)
   )
 
-m_g1_comparison <- bayesfactor_models(m_g1_logit, m_g1_probit)
-m_g2_comparison <- bayesfactor_models(m_g2_logit, m_g2_probit)
-
-
 # compare with waic
 waic(m_g1_logit,
      m_g1_probit)
 waic(m_g2_logit,
      m_g2_probit)
 
-# compare with LOO
-loo_compare(loo_f1_logit,
-            loo_f1_probit)
-loo_compare(loo_f2_logit,
-            loo_f2_probit)
 

### 2022-06-20 analysis/supplementary materials/Supplementary Materials.Rmd
Add plots to supplementary materials

@@
 
-```{r, setup, echo = FALSE, message=FALSE}
+```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}
 
@@
 library("flextable")
+library("bayestestR")
+
+options(mc.cores = parallel::detectCores())
+theme_set(theme_classic())
 
@@
 
+```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+plot(equivalence_test(m_f1))
+```
+
 ```{r journal-code, echo=FALSE}
@@
 ### Data
+
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+plot(equivalence_test(m_f2))
+```
 
@@
 
+```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+plot(equivalence_test(m_g1))
+```
+
 ```{r year-code, echo=FALSE}
@@
 ### Data
+
+```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+plot(equivalence_test(m_g2))
+```
 
@@
 
+```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+plot(equivalence_test(m_h1))
+```
+
 ```{r if5yr-code, echo=FALSE}
@@
 ### Data
+
+```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+plot(equivalence_test(m_h2))
+```
 

### 2022-06-20 analysis/paper/paper.Rmd
Update findings of analysis

@@
 
-When predicting the availability of data availability as compared with *Phytopathology*, publications in three journals, *Crop Protection*, *Plant Disease* and *Revista Mexicana de Fitopatología*, can be considered clearly less likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
-The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
-The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
-The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
-The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).
+When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterrania* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
+The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (> 0), 90.61% of being significant (> 0.05), and 78.94% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 25478).
+The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (> 0), 99.42% of being significant (> 0.05), and 97.73% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24986).
 
-There was no effect detected for year when predicting the availability of computational methods (code) availability.
-However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
-There was no detectable pattern in increasing or decreasing availability of data in the years examined.
+There was no effect detected for year when predicting the availability of computational methods (code) or data availability.
 
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.
-
-No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.
+There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data.
 

### 2022-06-22 analysis/paper/paper.Rmd
clarify caption
replace broad with wide

@@
 
-In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our collective status.
+In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
 We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
@@
 ```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials.
+A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code).
 However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.

### 2022-06-22 analysis/paper/paper.Rmd
Remove reference to unused analysis

@@
 
-Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
 The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
@@
 Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-Lastly, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
+Second, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
 This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
@@
 
-A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
+A custom function, `import_notes()`, was written to import the data and format the columns properly R [@RCT2022].
 Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
 When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
-In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
-For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
-In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
-Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
 
@@
 
-The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020) using R 4.1.0 (R Core Team, 2021).
+The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
 

### 2022-06-22 analysis/paper/paper.Rmd
clarify writing and remove double citation

@@
 The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
-To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee as a random effect (formula: ~1 | assignee).
+To predict the responses with publishing journal, as the journals' abbreviation, the formula took the form: response ~ abbreviation and the models included assignee as a random effect (formula: ~1 | assignee).
 To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
@@
 
-Model fitness's were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model fitness's were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 

### 2022-06-22 analysis/paper/paper.Rmd
Clarify writing

@@
 
-When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores with a mean of zero.
+When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores having a mean of zero.
 

### 2022-06-22 analysis/paper/paper.Rmd
Revise discussion section
Combine two subsections into examples and best practices and edit for clarity

@@
 
-## Are There Good Examples?
-
-While the majority of the articles that were surveyed did not score well for sharing data and code, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.
+## Examples of Different Levels of Reproducibility
 
 There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
-The first level is including tables of raw data or code with the paper as a supplemental file.
+A general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
+Here we defined three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
+
+The first level is including tables of raw data or code with the paper as a supplemental file or even within the paper as tables where possible.
 This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
-This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
-
-At the second level, in our search of the literature, we found that @Hill2019 shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
+@Hill2019 also shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
 The scripts provided used an R package, *checkpoint* [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that are necessary to reproduce the work rather than defaulting to the latest versions.
 However, the scripts did not run unhindered, as the supplementary materials suggested that they should, without changes to the data, but with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.
-One drawback to this approach is that journals are often not equipped to handle code, e.g., script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them.
+One drawback to this approach is that journals are often not equipped to handle code, e.g., script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them or if they are provided in a native text format, they do not render via the web properly.
 Though this should be possible given some effort from the publishing journal to share simple text files rather than binary formats along with the proper instructions and handling of these file formats rather than a one-size-fits all approach that we commonly see for supplementary materials.
+For example, the R scripts for @Hill2019 were provided as supplementary materials but do not actually appear in the browser window when requested, which may confuse readers and makes downloading them more difficult.
+While this allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself, the data or code are not readily findable and accessible. 
+Furthermore, in many cases this does not allow prompt access to the data and running the code because of a journal paywall.
 
-The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
+The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or other long-term repository as provided by a library, Zenodo, FigShare, etc.
+Fewer authors choose to follow this method, but in one instance that we found, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provide the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI to refer to these materials.
+
+The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
 As an example, Sparks et al.
@@
 
-The fourth level includes packaging the full analysis in a containerized software application, *e.g.*, Docker.
+Taking this approach even further, packaging the full analysis in a containerized software application, *e.g.*, Docker is a way to help ensure computational reproducibility but at the expense of added complexity.
 Docker is an open source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyses) with the operating system required to run that analysis on a user's computer.
@@
 
-## Best Practices to Enhance Reproducible Research
-
-Journals can encourage authors to deposit their data and code by providing instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources.
-While our analysis was unable to detect any differences in journals providing such instruction and journals that did not, the trend did indicate that journals that provided such instruction had better scores for data and code availability.
-
-A general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
-
-The first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
-A second level involves providing raw data and code as binary files (PDF or other non-text files) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a paywall.
-The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
+Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
 The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-In the next section we present standards and tools that can be used to ensure reproducibility.
-
 When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
@@
 
+## Final Thoughts
+
 In this work we have evaluated the state of computational reproducibility in the plant pathology literature and presented suggestions for areas of improvement.
@@
 For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
-This letter was drafted over the course of several years as the authors had time to devote to it.
+This manuscript was drafted over the course of several years as the authors had time to devote to it.
 Having everything in a reproducible framework made it easy to resume work and set-aside as necessary without losing information and having everything well-documented made it more simple to do this.
@@
 This open sharing of code and data leads to greater impact as work is cited if resources such as code or data are reused.
+But it is not just up to the authors to ensure that their work is reproducible.
+Journals can and should provide clear instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources to encourage authors to share the data and code that support the manuscript.
 With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
@@
 Without the code that was used to analyse the data, we as a community cannot adequately evaluate the work as it is presented.
-That is, while we may be standing on the shoulders of giants doing our work, we cannot see where they've been to do our work, which hinders our efforts.
+That is, while we may be standing on the shoulders of giants doing our work, we cannot see where they have been to do our work, which hinders our efforts.
 

### 2022-06-22 analysis/paper/paper.Rmd
edit for grammar

@@
 SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
-It is interesting to note however, that even with the popularity of Python in scientific programming, it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
+It is interesting to note however, that even with the popularity of Python in scientific programming it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
 

### 2022-06-23 analysis/paper/paper.Rmd
Move workflow description to introduction

@@
 These cases do constitute a lack of reproducibility but will not be covered here.
+
+In this paper we will assume that a general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript and depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 
@@
 
+```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
+Starting with the question, determine the methodology, describe it, make it available and cite it.
+Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
+Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}
+
+p <- export_svg(
+  grViz(
+    "digraph Fig3 {
+    graph [fontsize = 8, nodesep=0.5]
+
+    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
+    'An open and reproducible workflow'
+
+    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
+    Question
+
+    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
+    Methodology; Data; Analysis; Manuscript;
+
+    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Arial]
+    Description; Availability; Citation
+
+    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
+    'Binary Code'; 'Binary File'; Supplement
+
+    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
+    'Source Code'; 'Data File'; Metadata; 'Public Repository';
+
+    Question->Methodology->Data->Analysis
+    Analysis->Manuscript
+    Methodology->Description
+    Methodology->Citation
+    Methodology->Availability
+    Manuscript->Supplement
+    Data->'Data File'->'Public Repository'
+    Data->Metadata->'Public Repository'
+    Analysis->'Binary Code'->Supplement
+    Analysis->'Source Code'->'Public Repository'
+    Data->'Binary File'->Supplement
+  }",
+  width = 1000,
+  height = 750
+  )
+)
+
+rsvg_ps(svg = charToRaw(p),
+        file = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  options = "-dEPSCrop"
+)
+
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
+```
+
+\newpage
+
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
 ```
@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
-```
-
-\newpage
-
-```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code).
-However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
-Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
-Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_f1)) +
-  scale_colour_grey() +
-  ggtitle("Code")
-
-b <- plot(parameters(m_f2)) +
-  scale_colour_grey() +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  ggtitle("Data")
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
   filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
@@
 
-```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for practical equivalence was undecided in any detectable effects of year of publication on computational materials or data being shared.
-Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_g1), show_lables = TRUE) + 
+```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code).
+However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
+Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
+Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
+a <- plot(parameters(m_f1)) +
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_g2), show_lables = TRUE) + 
+b <- plot(parameters(m_f2)) +
   scale_colour_grey() +
@@
 
-```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for practical equivalence was undecided on any detectable effects of impact factor.
+```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for practical equivalence was undecided in any detectable effects of year of publication on computational materials or data being shared.
 Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_h1), show_lables = TRUE) + 
+a <- plot(parameters(m_g1), show_lables = TRUE) + 
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_h2), show_lables = TRUE) + 
+b <- plot(parameters(m_g2), show_lables = TRUE) + 
   scale_colour_grey() +
@@
 
-```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
-Starting with the question, determine the methodology, describe it, make it available and cite it.
-Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
-Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}
+```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for practical equivalence was undecided on any detectable effects of impact factor.
+Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
+a <- plot(parameters(m_h1), show_lables = TRUE) + 
+  scale_colour_grey() +
+  ggtitle("Code")
 
-p <- export_svg(
-  grViz(
-    "digraph Fig3 {
-    graph [fontsize = 8, nodesep=0.5]
+b <- plot(parameters(m_h2), show_lables = TRUE) + 
+  scale_colour_grey() +
+   theme(
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.y = element_blank()
+    ) +
+  ggtitle("Data")
 
-    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
-    'An open and reproducible workflow'
+p <- a + b
+p <- p +
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
 
-    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
-    Question
-
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
-    Methodology; Data; Analysis; Manuscript;
-
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Arial]
-    Description; Availability; Citation
-
-    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
-    'Binary Code'; 'Binary File'; Supplement
-
-    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-    'Source Code'; 'Data File'; Metadata; 'Public Repository';
-
-    Question->Methodology->Data->Analysis
-    Analysis->Manuscript
-    Methodology->Description
-    Methodology->Citation
-    Methodology->Availability
-    Manuscript->Supplement
-    Data->'Data File'->'Public Repository'
-    Data->Metadata->'Public Repository'
-    Analysis->'Binary Code'->Supplement
-    Analysis->'Source Code'->'Public Repository'
-    Data->'Binary File'->Supplement
-  }",
-  width = 1000,
-  height = 750
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
 )
-)
-
-rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
 embed_fonts(
@@
 )
-
 include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))

### 2022-06-23 analysis/paper/paper.Rmd
Revert "Move workflow description to introduction"
This reverts commit 30f07044e4b3fb012969aae21815ec0914ee0200.

--- 2022-06-22 analysis/paper/paper.Rmd
@@
 The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are 0.05 and 0.3 as suggested by @Makowski2019.
-Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 [@Vehtari2021] and Effective Sample Size (ESS), which should be greater than 1000 [@Burkner2017].
+Convergence and stability of the Bayesian sampling was assessed using R-hat, which should be below 1.01 [@Vehtari2021] and Effective Sample Size (ESS), which should be greater than 1000 [@Burkner2017].
 
@@
 
-All authors agreed on the five inter-rater article evaluations for the data availability, '0', not available for a inter-rater score of 100%.
+All authors agreed on the five inter-rater article evaluations for the data availability, '0', not available for an inter-rater score of 100%.
 However, one of the authors rated one article as 'NA' or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the 'NA' value dropped from the code availability.
@@
 
-Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
-`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2)`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2)`%) appeared to not use any computational methods.
+Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3) * 100`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
+`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 3) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.
 
-Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2)`%) scoring '0' where the data was not available or mentioned in the article.
-However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2)`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2)`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
+Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the data was not available or mentioned in the article.
+However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
 
@@
 There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
-A general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
-Here we defined three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).
+Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
 
@@
 The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or other long-term repository as provided by a library, Zenodo, FigShare, etc.
-Fewer authors choose to follow this method, but in one instance that we found, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provide the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI to refer to these materials.
+Fewer authors choose to follow this method, but in one instance that we found, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
 
-The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
+The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
 As an example, Sparks et al.
@@
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania [@Sparks2022a].
+Likewise, @Duku2016 provide R and Python scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania [@Sparks2022a].
 However, even this example is not totally open as it requires ArcGIS, an expensive proprietary software, to run the provided Python scripts for the RICEPEST model [@Savary2014].
@@
 When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
-used [@Miorini2018; @Miorini2019].
+used [-@Miorini2018; -@Miorini2019].
 @Kamvar2015 took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
@@
 When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
-Deposit and annotate biological materials with an herbarium or other repository.
 Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
@@
 This also helps ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like GenBank, MariaDB or PostgreSQL which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
-While personal databases may offer many advantages, the trade-off is that they are more complex to set up and administer, especially for a small data set.
+Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g.
+SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialised database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
 Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
+While databases may offer many advantages for speed and data integrity, the trade-off is that they are more complex to set up and administer, especially for a small data set.
 
@@
 If readers are uncertain, we suggest to also consult with local librarians about possible resources.
-Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development repositories as well.
+Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development or data repositories as well.
 The important aspect is that data once deposited cannot be modified any more.
@@
 
-Without the data underlying the paper, we as a community cannot adequately evaluate the work as it is presented.
-Without the code that was used to analyse the data, we as a community cannot adequately evaluate the work as it is presented.
-That is, while we may be standing on the shoulders of giants doing our work, we cannot see where they have been to do our work, which hinders our efforts.
+Without the code used to generate the paper and the data that were gathered for the paper, we as a community cannot adequately evaluate the work as it is presented.
+That is, while we may be standing on the shoulders of giants in doing our work, we cannot see where they have been to do our work, which hinders our efforts to be able to see farther ahead.
 

### 2022-06-23 analysis/paper/paper.Rmd
Remove reference to Duku et al.

@@
 
-In this paper we will assume that a general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript and depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
-
 # Materials and Methods
@@
 There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
+Assuming that a general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
@@
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Likewise, @Duku2016 provide R and Python scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania [@Sparks2022a].
-However, even this example is not totally open as it requires ArcGIS, an expensive proprietary software, to run the provided Python scripts for the RICEPEST model [@Savary2014].
-This highlights the difficulty in making work completely open and reproducible, further work could be undertaken to make the Python scripts rely totally on free-open-source-software but the work as it it provided here does allow for the complete reproducibility of the paper as written provided with the proper tools.
-Using a repository resource like GitHub allows readers to easily contact the authors by opening "Issues" and report bugs or ask questions in an open forum that are not as straightforward when the data are provided as supplementary material.
+Using a public code repository resource like GitHub allows readers to easily contact the authors by opening "Issues" and report bugs or ask questions in an open forum that are not as straightforward when the data are provided as supplementary material.
 
@@
 
-```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
-Starting with the question, determine the methodology, describe it, make it available and cite it.
-Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
-Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}
-
-p <- export_svg(
-  grViz(
-    "digraph Fig3 {
-    graph [fontsize = 8, nodesep=0.5]
-
-    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
-    'An open and reproducible workflow'
-
-    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
-    Question
-
-    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
-    Methodology; Data; Analysis; Manuscript;
-
-    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Arial]
-    Description; Availability; Citation
-
-    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
-    'Binary Code'; 'Binary File'; Supplement
-
-    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
-    'Source Code'; 'Data File'; Metadata; 'Public Repository';
-
-    Question->Methodology->Data->Analysis
-    Analysis->Manuscript
-    Methodology->Description
-    Methodology->Citation
-    Methodology->Availability
-    Manuscript->Supplement
-    Data->'Data File'->'Public Repository'
-    Data->Metadata->'Public Repository'
-    Analysis->'Binary Code'->Supplement
-    Analysis->'Source Code'->'Public Repository'
-    Data->'Binary File'->Supplement
-  }",
-  width = 1000,
-  height = 750
-  )
-)
-
-rsvg_ps(svg = charToRaw(p),
-        file = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  options = "-dEPSCrop"
-)
-
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
-```
-
-\newpage
-
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
@@
 ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
+```
+
+\newpage
+
+```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code).
+However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
+Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
+Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
+a <- plot(parameters(m_f1)) +
+  scale_colour_grey() +
+  ggtitle("Code")
+
+b <- plot(parameters(m_f2)) +
+  scale_colour_grey() +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  ggtitle("Data")
+
+p <- a + b
+p <- p +
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
+
+ggsave(
   filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
@@
 
-```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code).
-However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
-Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
-Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_f1)) +
+```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for practical equivalence was undecided in any detectable effects of year of publication on computational materials or data being shared.
+Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
+a <- plot(parameters(m_g1), show_lables = TRUE) + 
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_f2)) +
+b <- plot(parameters(m_g2), show_lables = TRUE) + 
   scale_colour_grey() +
@@
 
-```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for practical equivalence was undecided in any detectable effects of year of publication on computational materials or data being shared.
+```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.
+A test for practical equivalence was undecided on any detectable effects of impact factor.
 Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_g1), show_lables = TRUE) + 
+a <- plot(parameters(m_h1), show_lables = TRUE) + 
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_g2), show_lables = TRUE) + 
+b <- plot(parameters(m_h2), show_lables = TRUE) + 
   scale_colour_grey() +
@@
 
-```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for practical equivalence was undecided on any detectable effects of impact factor.
-Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_h1), show_lables = TRUE) + 
-  scale_colour_grey() +
-  ggtitle("Code")
+```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow.
+Starting with the question, determine the methodology, describe it, make it available and cite it.
+Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
+Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}
 
-b <- plot(parameters(m_h2), show_lables = TRUE) + 
-  scale_colour_grey() +
-   theme(
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.title.y = element_blank()
-    ) +
-  ggtitle("Data")
+p <- export_svg(
+  grViz(
+    "digraph Fig3 {
+    graph [fontsize = 8, nodesep=0.5]
 
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
+    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
+    'An open and reproducible workflow'
 
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
+    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
+    Question
+
+    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
+    Methodology; Data; Analysis; Manuscript;
+
+    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Arial]
+    Description; Availability; Citation
+
+    node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
+    'Binary Code'; 'Binary File'; Supplement
+
+    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
+    'Source Code'; 'Data File'; Metadata; 'Public Repository';
+
+    Question->Methodology->Data->Analysis
+    Analysis->Manuscript
+    Methodology->Description
+    Methodology->Citation
+    Methodology->Availability
+    Manuscript->Supplement
+    Data->'Data File'->'Public Repository'
+    Data->Metadata->'Public Repository'
+    Analysis->'Binary Code'->Supplement
+    Analysis->'Source Code'->'Public Repository'
+    Data->'Binary File'->Supplement
+  }",
+  width = 1000,
+  height = 750
   )
+)
+
+rsvg_ps(svg = charToRaw(p),
+        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
 embed_fonts(
@@
 )
+
 include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))

### 2022-06-23 analysis/paper/paper.Rmd
Clarify that this manuscript was not a part of the analysis

@@
 The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or other long-term repository as provided by a library, Zenodo, FigShare, etc.
-Fewer authors choose to follow this method, but in one instance that we found, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
+Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
 

### 2022-06-23 analysis/paper/paper.Rmd
Add 5 year impact factor to journal table

@@
 ```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
-import_notes() %>%
-  tabyl(journal) %>%
-  select(-percent) %>%
-  rename(Journal = journal) %>%
+journal <-
+  tabyl(rrpp, journal) %>%
+  select(-percent)
+
+distinct(rrpp, journal, IF_5year) %>%
+  left_join(journal, by = "journal") %>% 
+  rename(Journal = journal,
+         `5 Year IF` = IF_5year) %>%
   flextable() %>%
@@
   set_caption(
-    "Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
+    "Journal titles selected for inclusion, their respective five year impact factors as of 2022 and the number (n) of articles from each journal that were evaluated."
   )

### 2022-06-23 analysis/paper/paper.Rmd
Clarify table 1's caption

@@
   set_caption(
-    "Journal titles selected for inclusion, their respective five year impact factors as of 2022 and the number (n) of articles from each journal that were evaluated."
+    "Journal titles selected for inclusion, their respective five year impact factors as of 2022 (5 Year IF) and the number (n) of articles from each journal that were evaluated."
   )

### 2022-06-23 analysis/paper/paper.Rmd
State that journals should be requiring code/data deposited

@@
 But it is not just up to the authors to ensure that their work is reproducible.
-Journals can and should provide clear instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources to encourage authors to share the data and code that support the manuscript.
-With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
+At the very least, journals can and should provide clear instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources to encourage authors to share the data and code that support the manuscript.
+Ideally, with mandates for openly sharing data becoming more common with funding agencies, journals should also be mandating this practice as well.
+We can and should embrace this and move the discipline forward and have a greater impact with our work.
 

### 2022-06-24 analysis/supplementary materials/Supplementary Materials.Rmd
Save supplementary figures outside of document

--- 2022-06-16 analysis/supplementary materials/Supplementary Materials.Rmd
@@
 
-```{r, setup, echo = FALSE, message=FALSE}
+```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}
 
 library("Reproducibility.in.Plant.Pathology")
-library("tidyverse")
-library("pander")
-library("report")
-library("flextable")
+packages <- c(
+  "tidyverse",
+  "bayesplot",
+  "bayestestR",
+  "brms",
+  "extrafont",
+  "flextable",
+  "ggpubr",
+  "here",
+  "knitr",
+  "officer",
+  "pander",
+  "posterior",
+  "report",
+  "tools"
+)
+
+install.packages(setdiff(packages,
+                         rownames(installed.packages())),
+                 repos = "http://cran.us.r-project.org",
+                 dependencies = TRUE)
+
+invisible(lapply(packages,
+                 library,
+                 character.only = TRUE))
+
+options(mc.cores = parallel::detectCores())
+theme_set(theme_classic())
 
@@
 
+```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+p <- plot(equivalence_test(m_f1))
+
+ggsave(
+  filename = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+  ),
+  outfile = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+))
+```
+
 ```{r journal-code, echo=FALSE}
@@
 ### Data
+
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+p <- plot(equivalence_test(m_f2))
+
+ggsave(
+  filename = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+  ),
+  outfile = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+))
+```
 
@@
 
+```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+p <- plot(equivalence_test(m_g1))
+
+ggsave(
+  filename = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+  ),
+  outfile = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+))
+```
+
 ```{r year-code, echo=FALSE}
@@
 ### Data
+
+```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+p <- plot(equivalence_test(m_g2))
+
+ggsave(
+  filename = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+  ),
+  outfile = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+))
+```
 
@@
 
+```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+p <- plot(equivalence_test(m_h1))
+
+ggsave(
+  filename = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+  ),
+  outfile = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+))
+```
+
 ```{r if5yr-code, echo=FALSE}
@@
 ### Data
+
+```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+p <- plot(equivalence_test(m_h2))
+
+ggsave(
+  filename = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+  ),
+  outfile = here(
+    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+))
+```
 

### 2022-06-24 analysis/paper/paper.Rmd
cite 'report' package
reknit manuscript and supplementary materials

@@
   "flextable",
-  "ggridges",
   "ggpubr",
@@
 
-A full report of all parameters and model details are available in the Supplementary Materials.
+A full report of all parameters and model details are available in the Supplementary Materials generated using the contributed package 'report' (version `r packageVersion("report")`) [@Makowski2021].
 Additionally, all methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.

### 2022-06-24 analysis/supplementary materials/Supplementary Materials.Rmd
Update supplementary materials, remove figures, update tables

--- 2022-06-16 analysis/supplementary materials/Supplementary Materials.Rmd
@@
 
-```{r, setup, echo = FALSE, message=FALSE}
+```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}
 
 library("Reproducibility.in.Plant.Pathology")
-library("tidyverse")
-library("pander")
-library("report")
-library("flextable")
+packages <- c(
+  "bayesplot",
+  "bayestestR",
+  "brms",
+  "dplyr",
+  "extrafont",
+  "flextable",
+  "ggpubr",
+  "here",
+  "knitr",
+  "officer",
+  "officedown",
+  "pander",
+  "posterior",
+  "report",
+  "tools"
+)
+
+install.packages(setdiff(packages,
+                         rownames(installed.packages())),
+                 repos = "http://cran.us.r-project.org",
+                 dependencies = TRUE)
+
+invisible(lapply(packages,
+                 library,
+                 character.only = TRUE))
+
+options(mc.cores = parallel::detectCores())
+theme_set(theme_classic())
 
@@
 )
+
+knitr::opts_chunk$set(
+  fig.cap.pre = "Figure S",
+  tab.cap.pre = "Table S"
+)
 ```
@@
 
+<!---BLOCK_LANDSCAPE_START--->
+
 # Supplementary Materials
 
-## Journal Publication Model Reports
-
-### Computational Methods
-
-```{r journal-code, echo=FALSE}
-m_f1_report %>% 
-  pander()
-```
-
-### Data
-
-```{r journal-data, echo=FALSE}
-m_f2_report %>% 
-  pander()
-```
-
-\newpage
-
-## Year
-
-### Computational Methods
-
-```{r year-code, echo=FALSE}
-m_g1_report %>% 
-  pander()
-```
-
-### Data
-
-```{r year-data, echo=FALSE}
-m_g2_report %>% 
-  pander()
-```
-
-\newpage
-
-## Five-year Impact Factor
-
-### Computational Methods
-
-```{r if5yr-code, echo=FALSE}
-m_h1_report %>% 
-  pander()
-```
-
-### Data
-
-```{r if5yr-data, echo=FALSE}
-m_h2_report %>% 
-  pander()
-```
-
 ## Tables
-
-\newpage
 
@@
   autofit() %>%
-  set_caption("")
+  set_caption("Full description of model fit for the effect of journal title on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
 ```
@@
   autofit() %>%
-  set_caption("")
+  set_caption("Full description of model fit for the effect of journal title on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
 ```
@@
   autofit() %>%
-  set_caption("")
+  set_caption("Full description of model fit for the effect of year of publication on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.")
 ```
@@
   autofit() %>%
-  set_caption("")
+    set_caption("Full description of model fit for the effect of year of publication on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.")
 ```
@@
   autofit() %>%
-  set_caption("")
+  set_caption("Full description of model fit for the effect of five year impact factor on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.
+")
 ```
@@
   autofit() %>%
-  set_caption("")
+  set_caption("Full description of model fit for the effect of five year impact factor on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.
+")
 ```
+
+<!---BLOCK_LANDSCAPE_STOP--->

### 2022-06-24 analysis/paper/paper.Rmd
Update figure 1 and fix caption

@@
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-Six factors were evaluated, (A, B) Publication (Journal Title), (C, D) Year of Publication, (E, F) Five Year Impact Factor of Journal, and (G, H) Journal Open Access Policy where y is the data's density and y~rep~ are ten random posterior draws.
+The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (A) and data availability (B), and Five Year Impact Factor of Journal was tested for effect on code availability (A) and data availability (B).
 Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
@@
 mod_list <- list(
-  pp_check(m_f1, type = "bars", ndraws = 50) +
-    ggtitle("Code") +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank(),
-      plot.title = element_text(hjust = 0.5)
-    ) +
-    ylab("Journal"),
-  pp_check(m_f2, type = "bars", ndraws = 50) +
-    ggtitle("Data") +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank(),
-      plot.title = element_text(hjust = 0.5)
-    ),
-  pp_check(m_g1, type = "bars", ndraws = 50) +
-    theme(
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.title.x = element_blank()
-    ) +
-    ylab("Year"),
-  pp_check(m_g2, type = "bars", ndraws = 50) +
+  pp_check(m_f1, type = "rootogram", ndraws = 50) +
     theme(
@@
     ),
-  pp_check(m_h1, type = "bars", ndraws = 50) +
-    ylab("5 Y IF"),
-  pp_check(m_h2, type = "bars", ndraws = 50)
+  pp_check(m_f2, type = "rootogram", ndraws = 50) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank(),
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.y = element_blank()
+    ),
+  pp_check(m_g1, type = "rootogram", ndraws = 50) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank()
+    ),
+  pp_check(m_g2, type = "rootogram", ndraws = 50) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      axis.title.x = element_blank(),
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.y = element_blank()
+    ),
+  pp_check(m_h1, type = "rootogram", ndraws = 50),
+  pp_check(m_h2, type = "rootogram", ndraws = 50) +
+    theme(
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.y = element_blank()
+    )
 )

### 2022-06-24 analysis/supplementary materials/Supplementary Materials.Rmd
include equivalence test plots in supplementary materials

--- 2022-06-24 analysis/supplementary materials/Supplementary Materials.Rmd
@@
 )
+
+knitr::opts_chunk$set(
+  fig.cap.pre = "Figure S",
+  tab.cap.pre = "Table S"
+)
+
 ```
@@
 
-```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
 p <- plot(equivalence_test(m_f1))
@@
 
-```{r journal-code, echo=FALSE}
-m_f1_report %>% 
-  pander()
-```
-
 ### Data
 
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
 p <- plot(equivalence_test(m_f2))
@@
 
-```{r journal-data, echo=FALSE}
-m_f2_report %>% 
-  pander()
-```
-
 \newpage
@@
 
-```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
 p <- plot(equivalence_test(m_g1))
@@
 
-```{r year-code, echo=FALSE}
-m_g1_report %>% 
-  pander()
-```
-
 ### Data
 
-```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
 p <- plot(equivalence_test(m_g2))
@@
 
-```{r year-data, echo=FALSE}
-m_g2_report %>% 
-  pander()
-```
-
 \newpage
@@
 
-```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE}
+```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
 p <- plot(equivalence_test(m_h1))
@@
 
-```{r if5yr-code, echo=FALSE}
-m_h1_report %>% 
-  pander()
-```
-
 ### Data
 
-```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE}
+```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
 p <- plot(equivalence_test(m_h2))
@@
 
-```{r if5yr-data, echo=FALSE}
-m_h2_report %>% 
-  pander()
-```
-
 ## Tables
@@
   autofit() %>%
-  set_caption("")
+  set_caption("Full description of model fit for the effect of journal title on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
+
 ```
@@
   autofit() %>%
-  set_caption("")
+    set_caption("Full description of model fit for the effect of journal title on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
+
 ```
@@
   autofit() %>%
-  set_caption("")
+  set_caption(
+    "Full description of model fit for the effect of year of publication on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
 ```
@@
   autofit() %>%
-  set_caption("")
+    set_caption("Full description of model fit for the effect of year of publication on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.")
+
 ```
@@
   autofit() %>%
-  set_caption("")
+  set_caption(
+    "Full description of model fit for the effect of five-year impact factor on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+
 ```
@@
   autofit() %>%
-  set_caption("")
+  set_caption(
+    "Full description of model fit for the effect of five year impact factor on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
 ```

### 2022-06-24 analysis/paper/paper.Rmd
reknit and recreate docs and figures

@@
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A) (Supplementary Figures .
 

### 2022-06-24 analysis/paper/paper.Rmd
Reference supplementary figures and tables

--- 2022-06-24 analysis/paper/paper.Rmd
@@
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Figure S1, Table S1).
 
-When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterrania* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
+When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterrania* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
 The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (> 0), 90.61% of being significant (> 0.05), and 78.94% of being large (> 0.30).
@@
 
-There was no effect detected for year when predicting the availability of computational methods (code) or data availability.
+There was no effect detected for year when predicting the availability of computational methods (code) or data availability (Figures S3, S4; Tables S3, S4).
 
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data.
+There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures S5, S6, Tables S5, S6).
 

### 2022-06-27 analysis/paper/paper.Rmd
comment code chunk

@@
 
+# install packages if needed
 install.packages(setdiff(packages,
@@
 
+# load packages for use in knitting Rmd
 invisible(lapply(packages,

### 2022-07-01 analysis/paper/paper.Rmd
acknowledge Bec!

@@
 The authors are grateful for insightful comments from Dr.
-David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript and from Ms.
-Anna Hepworth for statistical guidance on evaluating inter-rater scores.
+David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript, from Ms.
+Anna Hepworth for statistical guidance on evaluating inter-rater scores and Dr Rebecca O'Leary for her insightful comments that helped improve the paper.
 

### 2022-07-01 analysis/paper/paper.Rmd
Add years to table two, top 10 software used

@@
 ```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
-tab_s %>%
+tab_t <- tabyl(rrpp_software, software_used, year)
+
+tab_t <- tab_t[tab_t$software_used %in% tab_s$Software ,]
+
+tab_t %>%
+  rowwise() %>%
+  mutate(Total = sum(c_across(where(is.numeric)), na.rm = T)) %>%
+  arrange(desc(Total)) %>%
+  rename(Software = software_used) %>% 
   flextable() %>%
   autofit() %>%
-  set_caption("The top ten sofware programs that were found to be used in the papers that were surveyed.")
+  set_caption(
+    "The frequency of use of top ten sofware programs by year of publication that were found to be used in the papers that were surveyed."
+  )
 ```

### 2022-07-01 analysis/scripts/statistical_software_use_over_time.R
Add script to plot software use over time

@@ -1,0 +1,49 @@
+
+library(Reproducibility.in.Plant.Pathology)
+library(tidyverse)
+
+rrpp <- import_notes()
+
+# tally up software used
+rrpp_software <-
+  rrpp %>%
+  transform(software_used = strsplit(software_used, ",")) %>%
+  unnest(software_used) %>%
+  mutate(software_used = trimws(software_used)) %>%
+  mutate(software_used = toupper(software_used))
+
+tab <- table(rrpp_software$software_used)
+tab_s <- as.data.frame(sort(tab))
+tab_s <-
+  tab_s %>%
+  arrange(desc(Freq)) %>%
+  filter(Freq %in% head(unique(Freq), 10)) %>%
+  rename("Software" = "Var1", "Frequency" = "Freq")
+
+tab_t <- tabyl(rrpp_software, software_used, year)
+
+tab_t <- tab_t[tab_t$software_used %in% tab_s$Software , ]
+
+tab_t %>%
+  rowwise() %>%
+  mutate(sumnumeric = sum(c_across(where(is.numeric)), na.rm = T)) %>%
+  arrange(sumnumeric) %>%
+  select(-sumnumeric) %>%
+  filter(
+    software_used == "R" |
+      software_used == "SAS" |
+      software_used == "GENSTAT" |
+      software_used == "SPSS" |
+      software_used == "STATISTICA"
+  ) %>%
+  mutate(software_used = factor(software_used)) %>%
+  pivot_longer(!software_used, names_to = "year", values_to = "count") %>%
+  ggplot(aes(
+    x = year,
+    y = count,
+    group = software_used,
+    colour = software_used
+  )) +
+  geom_line() +
+  geom_point(size = 4, aes(shape = software_used)) +
+  scale_color_brewer(type = "qual", palette = "Dark2")

### 2022-07-01 analysis/figures/eps2pdf.sh
Add script to convert eps files to PDF and resulting PDF files

@@ -1,0 +1,2 @@
+#/bin/bash
+for f in *.eps; do epstopdf $f; done

### 2022-07-01 analysis/paper/paper.Rmd
Remove duplicated "R version" in text
Fix caption lettering for sub-figures

@@
 
-The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
+The statistical analysis was performed using `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
 
@@
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
-The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (A) and data availability (B), and Five Year Impact Factor of Journal was tested for effect on code availability (A) and data availability (B).
+The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and Five Year Impact Factor of Journal was tested for effect on code availability (E) and data availability (F).
 Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}

### 2022-07-01 analysis/paper/paper.Rmd
Remove "abbreviation" and "year" from y-axis-tick-marks

@@
 Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
+
+a_y_labs <- rev(gsub("b_abbreviation", "", parameters(m_f1)$Parameter)[-c(1:2)])
 a <- plot(parameters(m_f1)) +
+  scale_y_discrete(labels = a_y_labs) +
   scale_colour_grey() +

### 2022-07-01 analysis/supplementary materials/Supplementary Materials.Rmd
Remove "abbreviation" and "year" from y-axis-tick-marks

@@
   "pander",
+  "parameters",
   "posterior",
@@
 ```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
-p <- plot(equivalence_test(m_f1))
+y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
+y_labs <- rev(gsub("b_", "", y_labs))
+y_labs <- y_labs[c(21:22, 1:20)]
+
+p <- plot(equivalence_test(m_f1)) +
+    scale_y_discrete(labels = y_labs)
 
@@
 ```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
-p <- plot(equivalence_test(m_f2))
+y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
+y_labs <- rev(gsub("b_", "", y_labs))
+y_labs <- y_labs[c(21:23, 1:20)]
+
+p <- plot(equivalence_test(m_f2)) +
+    scale_y_discrete(labels = y_labs)
 
@@
 ```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
-p <- plot(equivalence_test(m_g1))
+y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
+y_labs <- rev(gsub("b_", "", y_labs))
+y_labs <- y_labs[c(10:11, 1:9)]
+
+p <- plot(equivalence_test(m_g1)) +
+  scale_y_discrete(labels = y_labs)
 
@@
 ```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
-p <- plot(equivalence_test(m_g2))
+p <- plot(equivalence_test(m_g2)) +
+  scale_y_discrete(labels = y_labs)
 

### 2022-07-01 analysis/supplementary materials/Supplementary Materials.Rmd
Correct caption for figure S2

@@
 
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
 y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)

### 2022-07-01 analysis/supplementary materials/Supplementary Materials.Rmd
Reformat code chunks in supplementary materials

@@
   autofit() %>%
-  set_caption("Full description of model fit for the effect of journal title on code availability.
+  set_caption(
+    "Full description of model fit for the effect of journal title on code availability.
 We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
 The model included assignee as random effect (formula: ~1 | assignee).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
-
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
 ```
@@
   autofit() %>%
-    set_caption("Full description of model fit for the effect of journal title on data availability.
+  set_caption(
+    "Full description of model fit for the effect of journal title on data availability.
 We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
 The model included assignee as random effect (formula: ~1 | assignee).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
-
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
 ```
@@
   autofit() %>%
-    set_caption("Full description of model fit for the effect of year of publication on data availability.
+  set_caption(
+    "Full description of model fit for the effect of year of publication on data availability.
 We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
 The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.")
-
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
 ```
@@
   )
-
 ```

### 2022-07-01 analysis/paper/paper.Rmd
Address Bec's comment about randomly assigning articles to evaluators

@@
 There were three evaluation events that took place to increase the yearly coverage of the evaluations.
-Each evaluator was assigned 50 articles to evaluate during an evaluation event.
+During each scoring event, each evaluator was randomly assigned 50 unique articles to evaluate during an evaluation event.
+
 A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for each sampling event.
@@
 Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research in each of the three different scoring events as their time allowed for their participation.
-In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.
+In the first event, three authors (AS, EDP, and ZF) evaluated a total of 200 unique articles, in the second event two authors evaluated a total of 100 unique articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated a total of 150 unique articles for a total of 450 articles.
+Each article was evaluated by only one evaluator save five articles randomly selected for inter-rater repeatability analysis from the third and final evaluation event.
 

### 2022-07-01 analysis/paper/paper.Rmd
Apply Bec's suggestion for model description paragraph for clarity

@@
 
-The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
-To predict the responses with publishing journal, as the journals' abbreviation, the formula took the form: response ~ abbreviation and the models included assignee as a random effect (formula: ~1 | assignee).
-To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
+Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
+Models 1 and 2 to predict two responses with publishing journal, as the journals’ abbreviation, the formula took the form: response ~ abbreviation (model 1: code_availability ~ abbreviation and model 2: data_availability ~ abbreviation) and the models included assignee as a random effect (formula: ~1 | assignee).
+Models 3 and 4 to predict the two responses with year (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). 
+Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
 

### 2022-07-02 analysis/supplementary materials/Supplementary Materials.Rmd
Use bookdown rather than officedown for Word out

@@
 output: 
-  officedown::rdocx_document:
-     pandoc_args:
-       - '--lua-filter=pagebreak.lua'
+  bookdown::word_document2:
      fig_caption: yes
@@
      reference_docx: "../templates/phytopath_template.docx"
+     pandoc_args:
+       - '--lua-filter=scholarly-metadata.lua'
+       - '--lua-filter=author-info-blocks.lua'
+       - '--lua-filter=pagebreak.lua'
 ---

### 2022-07-02 analysis/supplementary materials/supplementary materials.Rmd
rename files to use lower case

--- 2022-07-02 analysis/supplementary materials/Supplementary Materials.Rmd
@@
 
-## Journal Publication Model Reports
+## Tables
 
-### Computational Methods
+```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_f1_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of journal title on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_f2_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of journal title on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_g1_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of year of publication on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_g2_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of year of publication on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_h1_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of five-year impact factor on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_h2_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of five year impact factor on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+## Figures
 
@@
 
-### Data
+\newpage
 
@@
 
-## Year
-
-### Computational Methods
-
 ```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
@@
 
-## Five-year Impact Factor
-
-### Computational Methods
-
 ```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
@@
 ```
-
-## Tables
-
-\newpage
-
-```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_f1_report) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of journal title on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
-The model included assignee as random effect (formula: ~1 | assignee).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_f2_report) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of journal title on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
-The model included assignee as random effect (formula: ~1 | assignee).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_g1_report) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of year of publication on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_g2_report) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of year of publication on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_h1_report) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of five-year impact factor on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_h2_report) %>%
-  filter(!grepl("Intercept", Parameter)) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of five year impact factor on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```

### 2022-07-02 analysis/supplementary materials/knit_supplementary_materials.R
Add script to knit supplementary materials

@@ -1,0 +1,7 @@
+# knits the paper using knitr
+
+library("rmarkdown")
+
+# Knit Rmd file
+render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary materials.Rmd",
+       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary-materials.docx")

### 2022-07-02 analysis/paper/paper.Rmd
Spellcheck and reknit

@@
 
-We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
+We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
 The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
@@
 Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
-The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log pointwise predictive density via `loo_compare()`.
+The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log point-wise predictive density via `loo_compare()`.
 
@@
 David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript, from Ms.
-Anna Hepworth for statistical guidance on evaluating inter-rater scores and Dr Rebecca O'Leary for her insightful comments that helped improve the paper.
+Anna Hepworth for statistical guidance on evaluating inter-rater scores and Dr.
+Rebecca O'Leary for her insightful comments that helped improve the paper.
 
@@
   set_caption(
-    "The frequency of use of top ten sofware programs by year of publication that were found to be used in the papers that were surveyed."
+    "The frequency of use of top ten software programs by year of publication that were found to be used in the papers that were surveyed."
   )

### 2022-07-02 analysis/paper/paper.Rmd
Grammar corrections
Reword acknowledgements

@@
 We randomly selected 450 articles published from 2012 to 2021 across 21 journals representative of the plant pathology discipline and assigned them scores reflecting their openness and computational reproducibility.
-We found that most of the articles were not following protocols for open science, and were failing to share data or code in a reproducible way.
+We found that most of the articles were not following protocols for open science and were failing to share data or code in a reproducible way.
 We also propose that use of open-source tools facilitates computationally reproducible work and analyses benefitting not just readers, but the authors as well.
@@
 
-The authors are grateful for insightful comments from Dr.
-David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript, from Ms.
-Anna Hepworth for statistical guidance on evaluating inter-rater scores and Dr.
-Rebecca O'Leary for her insightful comments that helped improve the paper.
+The authors are grateful for insightful comments from Drs.
+David Ferris and Rebecca O'Leary the USQ Centre for Crop Health Advisory Group on the final manuscript that helped improve the paper and from Ms.
+Anna Hepworth for statistical guidance on evaluating inter-rater scores.
 

### 2022-07-02 analysis/paper/paper.Rmd
More grammar corrections

@@
 Open research practices have been highlighted extensively during the last ten years in many fields of scientific study as essential standards needed to promote transparency and reproducibility of scientific results.
-Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and, analyses were conducted.
+Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyzes were conducted.
 Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
@@
 We found that most of the articles were not following protocols for open science and were failing to share data or code in a reproducible way.
-We also propose that use of open-source tools facilitates computationally reproducible work and analyses benefitting not just readers, but the authors as well.
+We also propose that use of open-source tools facilitates computationally reproducible work and analyzes benefitting not just readers, but the authors as well.
 Finally, we also provide ideas and tools to promote open, reproducible computational research practices among plant pathologists.
@@
 Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of the methods and results.
-These research findings include biological materials (host and pathogen genotypes), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated during the course of the research.
+These research findings include biological materials (host and pathogen genotypes), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated during the research activities.
 
@@
 In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing.
-One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
+One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyzes".
 > @Peng2009.
@@
 
-Therefore our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes.
-And that the software used are also easily obtained and preferably open source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
+Therefore, our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyzes or for use in instructional purposes.
+And that the software used are also easily obtained and preferably open-source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
 
@@
 
-In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
+In an effort to understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
 We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
@@
 
-Model fitness's were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model fitness' were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 
@@
 
-Much of the software used are Free Open Source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
+Much of the software used are Free open-source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
 However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.
-MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
+MEGA was the most widely cited software in this evaluation reflecting the widespread use of sequence analysis in the field of plant pathology.
 The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
@@
 There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
-Assuming that a general work flow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
+Assuming that a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
@@
 The first level is including tables of raw data or code with the paper as a supplemental file or even within the paper as tables where possible.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyzes where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
 @Hill2019 also shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
@@
 
-The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or other long-term repository as provided by a library, Zenodo, FigShare, etc.
+The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or some other long-term repository as provided by a library, Zenodo, FigShare, etc.
 Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
@@
 Taking this approach even further, packaging the full analysis in a containerized software application, *e.g.*, Docker is a way to help ensure computational reproducibility but at the expense of added complexity.
-Docker is an open source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyses) with the operating system required to run that analysis on a user's computer.
+Docker is an open-source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyzes) with the operating system required to run that analysis on a user's computer.
 However, there are drawbacks to using Docker.
 It can be difficult to understand for a new user and new platforms, like the Apple M1 chip, may not be fully supported, which hinder the ability to share the container.
-But, in most cases using an open source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
+But, in most cases using an open-source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
 For more on using Docker for reproducible research, we would refer readers to @Nuest2020.
@@
 
-Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
+Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
 The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
@@
 The use of programming or scripting languages such as R, Julia, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.
+This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyzes and visualization or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualize and analyze data.
 
@@
 This also helps ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g.
-SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialised database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
+Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialised database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
 Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
@@
 Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
-It should be noted, that the use of a database management system also allows for both of these at the expense of added complexity.
+It should be noted that the use of a database management system also allows for both of these at the expense of added complexity.
 Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
@@
 There are different options for generating a DOI for your data and other materials.
-FigShare, Zenodo and OSF.io all offer persistent archives along with a services to generate a DOI for your materials.
+FigShare, Zenodo and OSF.io all offer persistent archives along with a service to generate a DOI for your materials.
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
@@
 We believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
-For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
+For example, between complicated analyzes, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
 This manuscript was drafted over the course of several years as the authors had time to devote to it.
-Having everything in a reproducible framework made it easy to resume work and set-aside as necessary without losing information and having everything well-documented made it more simple to do this.
+Having everything in a reproducible framework made it easy to resume work and set-aside as necessary without losing information and having everything well-documented made it simpler to do this.
 Second, it benefits the reviewer by aiding their understanding of the work done and gives them more materials to use to make suggestions for improvements when reviewing and the end-user or reader is better able to verify the validity of the methods used and recreate the analysis.
@@
 
-All code used in the analyses and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
+All code used in the analyzes and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
 A webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.

### 2022-07-02 analysis/paper/paper.Rmd
Further edits for grammar corrections

@@
 There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
-Assuming that a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
+If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
@@
 Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
-It should be noted that the use of a database management system also allows for both of these at the expense of added complexity.
+It should be noted that the use of a database management system also allows for both at the expense of added complexity.
 Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.

### 2022-07-02 analysis/paper/paper.Rmd
visualisations to visualizations

@@
 
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and Five Year Impact Factor of Journal was tested for effect on code availability (E) and data availability (F).

### 2022-07-02 analysis/paper/paper.Rmd
specialised to specialized

@@
 This also helps ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialised database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
+Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
 Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
@@
 
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and Five Year Impact Factor of Journal was tested for effect on code availability (E) and data availability (F).

### 2022-07-04 analysis/paper/paper.Rmd
Correct title capitalisation
Edit paper for grammar and spelling

@@
 ---
-title: "Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward"
+title: "Openness and computational reproducibility in plant pathology: where do we stand and a way forward"
 author:
@@
 Reproducibility is one component under the umbrella of open science.
-By proactively practising open science, the work increases the chance to become more reproducible through the availability of data and code.
+By proactively practicing open science, the work increases the chance to become more reproducible through the availability of data and code.
 That is, open science leads to reproducibility and replicability.
@@
 
-In an effort to understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
-We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
+To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
+We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.*, quartile range or citation index, to represent the discipline.
 The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
@@
 
-Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research in each of the three different scoring events as their time allowed for their participation.
+Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomized list of journal articles using scoring criteria devised for the purposes of this research in each of the three different scoring events as their time allowed for their participation.
 In the first event, three authors (AS, EDP, and ZF) evaluated a total of 200 unique articles, in the second event two authors evaluated a total of 100 unique articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated a total of 150 unique articles for a total of 450 articles.
@@
 Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
-When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
+When working with these data in R, all strings of software character values were converted to fully upper-case to standardize the capitalization and alleviate any issues with capitalization used between evaluators.
 
@@
 
-When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterrania* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
+When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterranea* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
 The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (> 0), 90.61% of being significant (> 0.05), and 78.94% of being large (> 0.30).
@@
 The reasons for not sharing code or data were not clearly available from the papers themselves and so this work was unable to determine possible reasons for this situation.
-We recognise that in some cases there may be commercial or intellectual property (IP) reasons for not sharing data or code, but these reasons should be clearly stated.
+We recognize that in some cases there may be commercial or intellectual property (IP) reasons for not sharing data or code, but these reasons should be clearly stated.
 However, in most cases, the data are collected with public funding and the code was developed using similar funding and there are no commercial or IP issues that preclude sharing and in fact the funding agency may have guidelines in place for sharing these materials.
@@
 There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
-If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
+If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
@@
 Taking this approach even further, packaging the full analysis in a containerized software application, *e.g.*, Docker is a way to help ensure computational reproducibility but at the expense of added complexity.
-Docker is an open-source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyzes) with the operating system required to run that analysis on a user's computer.
+Docker is an open-source containerization platform that enables users to package several applications and an operating system into containers, thereby standardizing the executable components by combining application source code (or analyzes) with the operating system required to run that analysis on a user's computer.
 However, there are drawbacks to using Docker.
@@
 
-If steps are followed to make the data FAIR then it will be readable by humans and machines alike and this will help support discoveries and support further research.
+If steps are followed to make the data FAIR, then it will be readable by humans and machines alike and this will help support discoveries and support further research.
 In turn, sharing data will lead to new citations for your work as others discover and use it.
@@
   set_caption(
-    "Journal titles selected for inclusion, their respective five year impact factors as of 2022 (5 Year IF) and the number (n) of articles from each journal that were evaluated."
+    "Journal titles selected for inclusion, their respective five-year impact factors as of 2022 (5 Year IF) and the number (n) of articles from each journal that were evaluated."
   )
@@
 ```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
-The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and Five Year Impact Factor of Journal was tested for effect on code availability (E) and data availability (F).
+The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F).
 Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
@@
 Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
-Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
+Intervals in black have a median value that is greater than that of *Phytopathology*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
 

### 2022-07-04 tests/testthat/test-import_notes.R
Update tests for changes in functionality

@@ -2,8 +2,7 @@
 # and columns that are set to factor are factors. All other default as read.
 test_that("import_notes returns expected results", {
   notes <- import_notes()
-  expect_true(tibble::is_tibble(notes))
-  expect_equal(ncol(notes), 49)
+  expect_equal(ncol(notes), 21)
   expect_equal(class(notes$journal), "factor")
   expect_equal(class(notes$art_class), "factor")
   expect_equal(class(notes$art_class), "factor")

### 2022-07-04 tests/testthat/test-import_notes.R
Update tests

@@ -1,4 +1,4 @@
-# Test that import_notes() returns expected results, a tibble with 49 cols
+# Test that import_notes() returns expected results, a tibble with 21 cols
 # and columns that are set to factor are factors. All other default as read.
 test_that("import_notes returns expected results", {
   notes <- import_notes()

### 2022-07-04 tests/testthat/test-import_inter-rater_scores.R
add tests for import_interrater_scores()

@@ -1,0 +1,5 @@
+# Test that import_interrater_scores() returns expected results, a df with 12 cols
+test_that("import_inter-rater_scores returns expected results", {
+  scores <- import_interrater_scores()
+  expect_equal(ncol(scores), 12)
+})

### 2022-07-04 R/import_inter-rater_scores.R
Address no global bindings message when checking pkg build

@@ -23,7 +23,7 @@ import_interrater_scores <- function() {
     software_cite <-
     IF_5year <- art_class <- repro_inst <- abbreviation <-
     assignee <-
-    reproducibility_score <- journal <- year <- . <- NULL
+    reproducibility_score <- journal <- year <- doi <- molecular <- . <- NULL
 
   notes <- readODS::read_ods(
     system.file(
@@ -42,6 +42,11 @@ import_interrater_scores <- function() {
       art_class = as.factor(art_class),
       molecular = as.factor(molecular),
       assignee = as.factor(assignee),
+      software_cite = factor(
+        software_cite,
+        levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      ),
       software_avail = factor(
         software_avail,
         levels = c("0", "1", "2", "3"),
@@ -55,6 +60,11 @@ import_interrater_scores <- function() {
       data_avail = factor(
         data_avail,
         levels = c("0", "1", "2", "3"),
+        ordered = TRUE
+      ),
+      software_avail_corrected = factor(
+        software_avail_corrected,
+        levels =  c("0", "1", "2", "3"),
         ordered = TRUE
       )
     )

### 2022-07-04 README.rmd
Update paper's title in README
Correct "20" to "21" journals in README

@@
 (YYYY).
-_Reproducibility in plant pathology: where do we stand and a way forward_.
+_Openness and computational reproducibility in plant pathology: where do we stand and a way forward_.
 Name of journal/book <https://doi.org/xxx/xxx>
@@
 (2021).
-_Reproducibility in plant pathology: where do we stand and a way forward_.
+_Openness and computational reproducibility in plant pathology: where do we stand and a way forward_.
 agriRxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`.
@@
 
-The paper is a systematic and quantitative review of articles published in 20 plant pathology journals that spans five years of publications.
+The paper is a systematic and quantitative review of articles published in 21 plant pathology journals that spans five years of publications.
 It provides a basis for identifying what has been done so far in the discipline of plant pathology's published research to ensure computational reproducibility.

### 2022-07-04 analysis/paper/paper.Rmd
Add grDevices to libraries in Rmd files

@@
   "ggpubr",
+  "grDevices",
   "here",
@@
   echo = FALSE,
-  dev = c("postscript"),
   out.width = "100%",
   comment = "#>",
-  dev = "cairo_pdf",
+  dev = "cairo_ps",
   cache = FALSE

### 2022-07-04 analysis/supplementary materials/supplementary materials.Rmd
Add grDevices to libraries in Rmd files

@@
   "flextable",
+  "grDevices",
   "ggpubr",
@@
 theme_set(theme_classic())
+
+opts_chunk$set(
+  collapse = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  echo = FALSE,
+  dev = "cairo_ps"
+)
 

### 2022-07-04 README.rmd
Correct preprint year
Reknit README and paper and supplementary materials

@@
 J.
-(2021).
+(2022).
 _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_.
@@
 
-A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the [Word document](analysis/paper/paper.docx) in a Docker session.
+A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the [manuscript](analysis/paper/paper.docx) and the [supplementary materials](analysis/supplementary-materials.docx) in a Docker session.
 

### 2022-07-05 analysis/paper/paper.Rmd
delete a few unnecessary spaces

@@
 
-```{r, setup, echo = FALSE, message=FALSE}
+```{r, setup, echo=FALSE, message=FALSE}
 packages <- c(

### 2022-07-05 analysis/supplementary materials/supplementary materials.Rmd
Correct title in supplementary materials

@@
 ---
-title: "Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward"
+title: "Supplementary Materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward'"
 author:

### 2022-07-05 analysis/supplementary materials/supplementary materials.Rmd
Delete unnecessary spaces
Try loading this library to knit supplementary materials

@@
 
-```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}
+```{r, setup, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-options(mc.cores = parallel::detectCores())
-theme_set(theme_classic())
+library("Reproducibility.in.Plant.Pathology")
+
+rrpp <- import_notes()
+ir <- import_interrater_scores()
 
@@
   echo = FALSE,
-  dev = "cairo_ps"
+  out.width = "100%",
+  comment = "#>",
+  dev = "cairo_ps",
+  cache = FALSE
 )
 
-rrpp <- import_notes()
-ir <- import_interrater_scores()
+theme_set(theme_classic())
 

### 2022-07-05 analysis/supplementary materials/supplementary materials.Rmd
move sup figures to analysis/figures

@@
   filename = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
   ),
@@
   file = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
   ),
   outfile = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
   ),
@@
 include_graphics(path = here(
-  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
 ))
@@
   filename = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
   ),
@@
   file = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
   ),
   outfile = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
   ),
@@
 include_graphics(path = here(
-  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
 ))
@@
   filename = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
   ),
@@
   file = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
   ),
   outfile = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
   ),
@@
 include_graphics(path = here(
-  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
 ))
@@
   filename = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
   ),
@@
   file = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
   ),
   outfile = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
   ),
@@
 include_graphics(path = here(
-  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
 ))
@@
   filename = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
   ),
@@
   file = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
   ),
   outfile = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
   ),
@@
 include_graphics(path = here(
-  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
 ))
@@
   filename = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
   ),
@@
   file = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
   ),
   outfile = here(
-    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
   ),
@@
 include_graphics(path = here(
-  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
 ))

### 2022-07-07 analysis/paper/knit_paper.R
Move supplementary materials to paper directoryUtmost-Unclothed-Annex7

@@ -2,6 +2,11 @@
 
 library("rmarkdown")
 
-# Knit Rmd file
+# Knit Rmd file for manuscript
 render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.Rmd",
        output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
+
+# Knit Rmd file for supplementary materials
+render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary materials.Rmd",
+       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary-materials.docx")
+

### 2022-07-07 analysis/supplementary materials/knit_supplementary_materials.R

@@ -1,7 +1,0 @@
-# knits the paper using knitr
-
-library("rmarkdown")
-
-# Knit Rmd file
-render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary materials.Rmd",
-       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary-materials.docx")

### 2022-07-07 analysis/paper/knit_paper.R
Correct file-path

@@ -7,6 +7,6 @@ render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/
        output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
 
 # Knit Rmd file for supplementary materials
-render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary materials.Rmd",
-       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/supplementary materials/supplementary-materials.docx")
+render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary materials.Rmd",
+       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary-materials.docx")
 

### 2022-07-07 analysis/paper/paper.Rmd
Change "levels" to "layers" as suggested in review

@@
 
-## Examples of Different Levels of Reproducibility
+## Examples of Different Layers of Reproducibility
 
-There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
+There are different ways to make research more open and reproducible, which can be thought of as layers of reproducibility.
 If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
-Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
+Here we define three layers of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
 
-The first level is including tables of raw data or code with the paper as a supplemental file or even within the paper as tables where possible.
+The first layer is including tables of raw data or code with the paper as a supplemental file or even within the paper as tables where possible.
 This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyzes where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
@@
 
-The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or some other long-term repository as provided by a library, Zenodo, FigShare, etc.
+The second layer is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or some other long-term repository as provided by a library, Zenodo, FigShare, etc.
 Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
 
-The third level is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
+The third layer is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
 As an example, Sparks et al.
@@
 As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package that enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+When this layer is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
 used [-@Miorini2018; -@Miorini2019].
@@
 Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
-The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
+The first layer, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
 When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.

### 2022-07-07 analysis/paper/knit_paper.R
Correct filepath to supplementary-materials.Rmd

@@ -7,6 +7,6 @@ render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/
        output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
 
 # Knit Rmd file for supplementary materials
-render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary materials.Rmd",
+render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary-materials.Rmd",
        output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary-materials.docx")
 

### 2022-07-07 analysis/paper/paper.Rmd
Note that supplementary materials are not data in searchable databases per se

@@
 For example, the R scripts for @Hill2019 were provided as supplementary materials but do not actually appear in the browser window when requested, which may confuse readers and makes downloading them more difficult.
-While this allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself, the data or code are not readily findable and accessible. 
+While this allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself, the data or code are not readily findable and accessible through a searchable database.
 Furthermore, in many cases this does not allow prompt access to the data and running the code because of a journal paywall.

### 2022-07-07 analysis/paper/paper.Rmd
Use bars for model fit and relabel xaxis to follow ordinal scoring

@@
 mod_list <- list(
-  pp_check(m_f1, type = "rootogram", ndraws = 50) +
+  pp_check(m_f1, type = "bars", ndraws = 50) +
     theme(
@@
     ),
-  pp_check(m_f2, type = "rootogram", ndraws = 50) +
+  pp_check(m_f2, type = "bars", ndraws = 50) +
     theme(
@@
     ),
-  pp_check(m_g1, type = "rootogram", ndraws = 50) +
+  pp_check(m_g1, type = "bars", ndraws = 50) +
     theme(
@@
     ),
-  pp_check(m_g2, type = "rootogram", ndraws = 50) +
+  pp_check(m_g2, type = "bars", ndraws = 50) +
     theme(
@@
     ),
-  pp_check(m_h1, type = "rootogram", ndraws = 50),
-  pp_check(m_h2, type = "rootogram", ndraws = 50) +
+  pp_check(m_h1, type = "bars", ndraws = 50) +
+    scale_x_continuous(labels = c("0", "1", "2", "3"),
+                       breaks = 1:4),
+  pp_check(m_h2, type = "bars", ndraws = 50) +
+    scale_x_continuous(labels = c("0", "1", "2", "3"),
+                       breaks = 1:4) +
     theme(

### 2022-07-07 analysis/paper/paper.Rmd
Remove "final thoughts" and add paragraph on implementing layers

@@
 
-## Final Thoughts
+These layers provide increasing openness and reproducibility so Layer 1 should not be viewed as the starting point before moving on to Layer 2 and then Layer 3.
+Rather the layers are provided to give the reader some idea of how much benefit end-users of the computational materials and data will derive at the expense of the increasing complexity.
+Authors need not start with Level 1 before moving to Level 2 and then Level 3.
+If they have the ability to start with depositing the computational materials and data and generating DOIs all parties will benefit from it.
+However, we recognise that these steps may not be appropriate or attractive for various reasons and so have detailed other layers that improve openness and reproducibility.
 

### 2022-07-07 analysis/paper/paper.Rmd
Describe figure 1 more clearly
Add x-axis labels to figure 1

@@
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F).
+Where yrep indicate 50 random draws for model predictions and y are the observed values.
 Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
@@
     scale_x_continuous(labels = c("0", "1", "2", "3"),
-                       breaks = 1:4),
+                       breaks = 1:4) +
+  xlab("Score (0 to 3)"),
   pp_check(m_h2, type = "bars", ndraws = 50) +
@@
                        breaks = 1:4) +
+    xlab("Score (0 to 3)") +
     theme(

### 2022-07-07 analysis/paper/paper.Rmd
Put supplementary materials in paper document
Try to get them to knit in the Docker this way

@@
 ```
+
+\newpage
+
+# Supplementary Materials
+
+## Tables
+
+```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_f1_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of journal title on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_f2_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of journal title on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_g1_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of year of publication on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_g2_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of year of publication on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_h1_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of five-year impact factor on code availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+as_tibble(m_h2_report) %>%
+  filter(!grepl("R2", Parameter)) %>%
+  filter(!is.na(Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
+         "CI\nHigh" = "CI_high") %>%
+  flextable() %>%
+  fontsize(size = 8, part = "all") %>%
+  colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
+  autofit() %>%
+  set_caption(
+    "Full description of model fit for the effect of five year impact factor on data availability.
+We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+  )
+```
+
+\newpage
+
+## Figures
+
+```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
+y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
+y_labs <- rev(gsub("b_", "", y_labs))
+y_labs <- y_labs[c(21:22, 1:20)]
+
+p <- plot(equivalence_test(m_f1)) +
+  scale_y_discrete(labels = y_labs)
+
+ggsave(
+  filename = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
+  ),
+  outfile = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
+))
+```
+
+\newpage
+
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
+y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
+y_labs <- rev(gsub("b_", "", y_labs))
+y_labs <- y_labs[c(21:23, 1:20)]
+
+p <- plot(equivalence_test(m_f2)) +
+  scale_y_discrete(labels = y_labs)
+
+ggsave(
+  filename = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
+  ),
+  outfile = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
+))
+```
+
+\newpage
+
+```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
+y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
+y_labs <- rev(gsub("b_", "", y_labs))
+y_labs <- y_labs[c(10:11, 1:9)]
+
+p <- plot(equivalence_test(m_g1)) +
+  scale_y_discrete(labels = y_labs)
+
+ggsave(
+  filename = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
+  ),
+  outfile = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
+))
+```
+
+\newpage
+
+```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
+p <- plot(equivalence_test(m_g2)) +
+  scale_y_discrete(labels = y_labs)
+
+ggsave(
+  filename = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
+  ),
+  outfile = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
+))
+```
+
+\newpage
+
+```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
+p <- plot(equivalence_test(m_h1))
+
+ggsave(
+  filename = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
+  ),
+  outfile = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
+))
+```
+
+\newpage
+
+```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
+p <- plot(equivalence_test(m_h2))
+
+ggsave(
+  filename = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
+  ),
+  outfile = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
+))
+```

### 2022-07-07 analysis/paper/knit_paper.R

@@ -5,8 +5,3 @@ library("rmarkdown")
 # Knit Rmd file for manuscript
 render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.Rmd",
        output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
-
-# Knit Rmd file for supplementary materials
-render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary-materials.Rmd",
-       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary-materials.docx")
-

### 2022-07-08 analysis/paper/paper.Rmd
Revise this sentence for clarity as per reviewer 2

@@
 
-Recently, open science has been highlighted with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
+Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010].
 

### 2022-07-08 analysis/paper/paper.Rmd
Add more detail on inter-rater repeatability including sup figure

@@
 
+Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure \@ref(fig:evaluator-differences)).
+However, the analyses did account for different raters for each article by including this as a random effect.
+
 ## Code and Data Sharing Findings
@@
 # Discussion
+
+Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
+Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
 
@@
 
-## Figures
-
-```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
-y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:22, 1:20)]
-
-p <- plot(equivalence_test(m_f1)) +
-  scale_y_discrete(labels = y_labs)
+## Supplementary Figures
+
+```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data avaialbility for each of the five evaluators.
+Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators."}
+p <- import_notes() %>%
+  mutate(
+    comp_mthds_avail = as.numeric(as.character(comp_mthds_avail)),
+    data_avail =  as.numeric(as.character(data_avail))
+  ) %>%
+  pivot_longer(cols = c("comp_mthds_avail",
+                        "data_avail")) %>%
+  ggplot(aes(y = as.factor(value), x = assignee)) +
+  geom_count() +
+  ylab("Criteria Score") +
+  xlab("Evaluator") +
+  ggtitle("Criteria scores by evaluator") +
+  facet_wrap(name ~ .,
+             labeller = labeller(name =
+                                   c(
+                                     "comp_mthds_avail" = "Code",
+                                     "data_avail" = "Data"
+                                   )))
 
 ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-  ),
+  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-  ),
+  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-))
-```
-
-\newpage
-
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
-y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"))
+```
+
+\newpage
+
+```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
+y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
 y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:23, 1:20)]
-
-p <- plot(equivalence_test(m_f2)) +
+y_labs <- y_labs[c(21:22, 1:20)]
+
+p <- plot(equivalence_test(m_f1)) +
   scale_y_discrete(labels = y_labs)
@@
 
-```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
-y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
+y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
 y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(10:11, 1:9)]
-
-p <- plot(equivalence_test(m_g1)) +
+y_labs <- y_labs[c(21:23, 1:20)]
+
+p <- plot(equivalence_test(m_f2)) +
   scale_y_discrete(labels = y_labs)
@@
 
-```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
-p <- plot(equivalence_test(m_g2)) +
+```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
+y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
+y_labs <- rev(gsub("b_", "", y_labs))
+y_labs <- y_labs[c(10:11, 1:9)]
+
+p <- plot(equivalence_test(m_g1)) +
   scale_y_discrete(labels = y_labs)
@@
 
-```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
-p <- plot(equivalence_test(m_h1))
+```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
+p <- plot(equivalence_test(m_g2)) +
+  scale_y_discrete(labels = y_labs)
 
@@
 
-```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
-p <- plot(equivalence_test(m_h2))
+```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
+p <- plot(equivalence_test(m_h1))
 
@@
 ```
+
+\newpage
+
+```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
+p <- plot(equivalence_test(m_h2))
+
+ggsave(
+  filename = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
+  ),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
+  ),
+  outfile = here(
+    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
+  ),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here(
+  "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
+))
+```

### 2022-07-08 analysis/paper/paper.Rmd
Label subheading "Supplementary Tables"
Escape special characters

@@
 Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
-Models 1 and 2 to predict two responses with publishing journal, as the journals’ abbreviation, the formula took the form: response ~ abbreviation (model 1: code_availability ~ abbreviation and model 2: data_availability ~ abbreviation) and the models included assignee as a random effect (formula: ~1 | assignee).
-Models 3 and 4 to predict the two responses with year (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). 
-Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
+Models 1 and 2 to predict two responses with publishing journal, as the journals' abbreviation, the formula took the form: response \~ abbreviation (model 1: code_availability \~ abbreviation and model 2: data_availability \~ abbreviation) and the models included assignee as a random effect (formula: \~1 \| assignee).
+Models 3 and 4 to predict the two responses with year (formula: response \~ year) and the models included abbreviation and assignee as random effects (formula: list(\~1 \| abbreviation, \~1 \| assignee)).
+Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response \~ IF_5year and included assignee as random effect (formula: \~1 \| assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
 
@@
 When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterranea* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
-The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (> 0), 90.61% of being significant (> 0.05), and 78.94% of being large (> 0.30).
+The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (\> 0), 90.61% of being significant (\> 0.05), and 78.94% of being large (\> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 25478).
-The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (> 0), 99.42% of being significant (> 0.05), and 97.73% of being large (> 0.30).
+The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (\> 0), 99.42% of being significant (\> 0.05), and 97.73% of being large (\> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24986).
@@
 
-## Tables
+## Supplementary Tables
 

### 2022-07-08 analysis/paper/paper.Rmd
Define/reference Jupyter and replace you/your with we/our

@@
 As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package that enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
-When this layer is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al.
+When this layer is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks, a "web application for creating and sharing computational documents" [@jupyter2022], as Mioroni et al.
 used [-@Miorini2018; -@Miorini2019].
@@
 The first layer, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
+When making our science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
 Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
 This allows end-users to identify what was used and identify the methods used more accurately.
-Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
-This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on your research.
-
-The use of programming or scripting languages such as R, Julia, SAS or Python enables you as a scientist to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyzes and visualization or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualize and analyze data.
+Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
+This also helps to ensure that we researchers can reconstruct what we have done since we will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on our research.
+
+The use of programming or scripting languages such as R, Julia, SAS or Python enables us scientists to keep very detailed records of what was computationally performed.
+This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyzes and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
 
@@
 In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.*, comma separated (CSV) or tab separated (TSV) files.
-This also helps ensure that the data are reusable.
+This also helps to ensure that the data are reusable.
 Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
@@
 
-Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
+Ideally, once the data are complete, best practices for keeping our data as we perform our work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
 It should be noted that the use of a database management system also allows for both at the expense of added complexity.
@@
 If steps are followed to make the data FAIR, then it will be readable by humans and machines alike and this will help support discoveries and support further research.
-In turn, sharing data will lead to new citations for your work as others discover and use it.
-To make your data the most widely discoverable and usable, ensure that it has a persistent identifier.
+In turn, sharing data will lead to new citations for our work as others discover and use it.
+To make our data the most widely discoverable and usable, ensure that it has a persistent identifier.
 A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but the Handle.Net Registry (HNR) (<https://handle.net/>) is also an option.
-There are different options for generating a DOI for your data and other materials.
-FigShare, Zenodo and OSF.io all offer persistent archives along with a service to generate a DOI for your materials.
+There are different options for generating a DOI for our data and other materials.
+FigShare, Zenodo and OSF.io all offer persistent archives along with a service to generate a DOI for our materials.
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
@@
 
-Once you have determined how to best manage your source code and the data sets for analysis the next step is to consider how to share your data.
-Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for you to deposit your data and generate a DOI for sharing your project once you are finished with it.
-
-Other providers exist that allow for you to not only track changes but also to share the data openly, these include GitHub, Gitlab and Bitbucket.
+Once it has been determined how to best manage the source code and the data sets for analysis, the next step is to consider how to share the data.
+Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and generate a DOI for sharing the project once it is finished.
+
+Other providers exist that allow for us to not only track changes but also to share the data openly, these include GitHub, Gitlab and Bitbucket.
 GitHub is arguably the most popular and widely used software development platform currently.
@@
 
-We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only as these are not an optimal way to preserve and share your work over the long term.
+We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only as these are not an optimal way to preserve and share our work over the long term.
 Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
-It is a best practice to always ensure that you have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF.io and generated a DOI for the materials to help ensure continued accessibility.
+It is a best practice to always ensure that we have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF.io and generated a DOI for the materials to help ensure continued accessibility.
 Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
@@
 We believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
-For example, between complicated analyzes, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
+For example, between complicated analyzes, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce our work quickly and easily.
 This manuscript was drafted over the course of several years as the authors had time to devote to it.
@@
 Perhaps more importantly, sharing these details helps with knowledge transfer by showing other interested parties how something was done rather than simply describing it.
-Lastly, openly sharing your work and making it discoverable can lead to new collaborations and synergistic ideas.
+Lastly, openly sharing our work and making it discoverable can lead to new collaborations and synergistic ideas.
 One of the most important messages that we would like to share is that there is more to the work than just the paper.

### 2022-07-08 analysis/paper/paper.Rmd
Update acknowledgements

@@
 
-The authors are grateful for insightful comments from Drs.
-David Ferris and Rebecca O'Leary the USQ Centre for Crop Health Advisory Group on the final manuscript that helped improve the paper and from Ms.
-Anna Hepworth for statistical guidance on evaluating inter-rater scores.
+The authors are grateful for insightful comments from Dr David Ferris and Dr Rebecca O'Leary the USQ Centre for Crop Health Advisory Group on the final manuscript that helped improve the paper and from Ms Anna Hepworth for statistical guidance on evaluating inter-rater scores and for the comments from the anonymous reviewers and Dr Nian Wang that greatly improved the quality of this manuscript.
 

### 2022-07-08 analysis/paper/paper.Rmd
quote 'yrep' and 'y' in caption describing figure 1
Clarify scoring and data cleaning

@@
 
+In cases where partial computational materials or data were made available, the score was assigned the lowest score reflecting the completeness of the availability, all or nothing.
+That is, in cases where some data such as sequences were deposited in a database, *e.g.*, GenBank, but other data that was collected and used were not made available, the score assigned was '0'.
+
 Where possible, the software used in conducting the research behind the publication was recorded in the notes when it was cited or otherwise specified in the article text.
@@
 ## Data Cleaning
+
+The criteria scores were checked for inconsistencies using the evaluators' comments in the spreadsheet and based on the software used.
+In some cases these comments were used to adjust the criteria score to align with the scoring definitions.
+This was not possible in all cases but only in cases where the evaluator had left comments that could be checked and acted upon.
+For example, a reviewer noted that all data were deposited in GenBank but the data score was '0', this was changed to '3' to align with the definition.
+Or in other cases, some software packages used were Excel add-ins but Excel was not recorded as being used; Excel was added to the list of software used to rectify this.
 
@@
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F).
-Where yrep indicate 50 random draws for model predictions and y are the observed values.
+Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values.
 Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}

### 2022-07-08 analysis/paper/paper.Rmd
Correct reference to supplementary figure

@@
 
-Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure \@ref(fig:evaluator-differences)).
+Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure S1).
 However, the analyses did account for different raters for each article by including this as a random effect.

### 2022-07-08 analysis/paper/paper.Rmd
Cross reference Table 2

@@
 
-There were `r as.character(english(length(unique(rrpp_software$software_used))))` unique software applications recorded being used in the articles that were evaluated.
+There were `r as.character(english(length(unique(rrpp_software$software_used))))` unique software applications recorded being used in the articles that were evaluated (Table \@ref(tab:software-used)).
 These included desktop programs, web-based software and databases.

### 2022-07-08 analysis/paper/paper.Rmd
Edit text to reflect analysis results

@@
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Figure S1, Table S1).
-
-When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterranea* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
-The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (\> 0), 90.61% of being significant (\> 0.05), and 78.94% of being large (\> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 25478).
-The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (\> 0), 99.42% of being significant (\> 0.05), and 97.73% of being large (\> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24986).
-
-There was no effect detected for year when predicting the availability of computational methods (code) or data availability (Figures S3, S4; Tables S3, S4).
-
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures S5, S6, Tables S5, S6).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
+
+When predicting the availability of data availability as compared with *Phytopathology*, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).
+
+The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) has a 99.99% probability of being positive (> 0), 99.98% of being significant (> 0.05), and 99.83% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19017).
+
+There was no effect detected for year when predicting the availability of computational methods (Table S3, Figure S4).
+However, 2018 was clearly different with more data being made available than all other years (Table S4; Figure S5).
+
+There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Tables S5, S6 and Figures S6, S7).
 

### 2022-07-08 analysis/paper/paper.Rmd
Discuss why PM may have more data available than Phytopath

@@
 Code sharing was extremely rare, but in cases where it was shared, most were included as a part of the journal article's publication as extra materials rather than through data repositories.
+Authors publishing in *Phytopathologia Mediterranea* were more likely than articles published in *Phytopathology* to share data.
+Several articles published in this journal either made the data available through GenBank or it was noted that all data were available through the article and associated supplementary materials.
+The journal ranking highest for sharing data, *Phytopathologia Mediterranea*, did not have any articles that were sampled in 2018 (Table \@ref(tab:journals)).
+There is no clear reason for the year 2018 to have more data shared than other years other than random chance that we found.
 The reasons for not sharing code or data were not clearly available from the papers themselves and so this work was unable to determine possible reasons for this situation.

### 2022-07-08 analysis/paper/paper.Rmd
Add discussion on the necessity and use of metadata

@@
 Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
+Making the raw data FAIR means providing proper metadata for the resource.
+The metadata define the resource that has been made available allowing for discovery and use by other interested parties.
+That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
+Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
+Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
+That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.
+
 The first layer, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
@@
 Once it has been determined how to best manage the source code and the data sets for analysis, the next step is to consider how to share the data.
-Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and generate a DOI for sharing the project once it is finished.
+Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and provide metadata and generate a DOI for sharing the project once it is finished.
 

### 2022-07-08 analysis/paper/paper.Rmd
Include year in Table 1 and fit on page

@@
 journal <-
-  tabyl(rrpp, journal) %>%
-  select(-percent)
+  tabyl(rrpp, journal, year) %>%
+  rowwise() %>%
+  mutate(n = sum(c_across(where(is.numeric)), na.rm = T))
 
@@
   rename(Journal = journal,
-         `5 Year IF` = IF_5year) %>%
+         `IF` = IF_5year) %>%
   flextable() %>%
   colformat_num(na_str = "NA") %>%
-  autofit() %>%
+  fontsize(size = 10, part = "body") %>%
+  set_table_properties(layout = "autofit", width = 1) %>%
   set_caption(
-    "Journal titles selected for inclusion, their respective five-year impact factors as of 2022 (5 Year IF) and the number (n) of articles from each journal that were evaluated."
+    "Journal titles selected for inclusion, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
   )

### 2022-07-08 analysis/paper/paper.Rmd
wrap text in table for better fit

@@
   flextable() %>%
-  autofit() %>%
+  set_table_properties(layout = "autofit", width = 1) %>% 
+  fontsize(size = 10) %>% 
   set_caption(

### 2022-07-08 analysis/paper/paper.Rmd
Remove reference to Molecular Plant Path

@@
 A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code).
-However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
+However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
 Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.

### 2022-07-08 analysis/paper/paper.Rmd
Remove supplementary materials and put in own file for item numbering

@@
 ```
-
-\newpage
-
-# Supplementary Materials
-
-## Supplementary Tables
-
-```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_f1_report) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of journal title on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
-The model included assignee as random effect (formula: ~1 | assignee).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_f2_report) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of journal title on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
-The model included assignee as random effect (formula: ~1 | assignee).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_g1_report) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of year of publication on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_g2_report) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of year of publication on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_h1_report) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of five-year impact factor on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_h2_report) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>%
-  set_caption(
-    "Full description of model fit for the effect of five year impact factor on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-## Supplementary Figures
-
-```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data avaialbility for each of the five evaluators.
-Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators."}
-p <- import_notes() %>%
-  mutate(
-    comp_mthds_avail = as.numeric(as.character(comp_mthds_avail)),
-    data_avail =  as.numeric(as.character(data_avail))
-  ) %>%
-  pivot_longer(cols = c("comp_mthds_avail",
-                        "data_avail")) %>%
-  ggplot(aes(y = as.factor(value), x = assignee)) +
-  geom_count() +
-  ylab("Criteria Score") +
-  xlab("Evaluator") +
-  ggtitle("Criteria scores by evaluator") +
-  facet_wrap(name ~ .,
-             labeller = labeller(name =
-                                   c(
-                                     "comp_mthds_avail" = "Code",
-                                     "data_avail" = "Data"
-                                   )))
-
-ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"))
-```
-
-\newpage
-
-```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
-y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:22, 1:20)]
-
-p <- plot(equivalence_test(m_f1)) +
-  scale_y_discrete(labels = y_labs)
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-))
-```
-
-\newpage
-
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
-y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:23, 1:20)]
-
-p <- plot(equivalence_test(m_f2)) +
-  scale_y_discrete(labels = y_labs)
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-))
-```
-
-\newpage
-
-```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
-y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(10:11, 1:9)]
-
-p <- plot(equivalence_test(m_g1)) +
-  scale_y_discrete(labels = y_labs)
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-))
-```
-
-\newpage
-
-```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
-p <- plot(equivalence_test(m_g2)) +
-  scale_y_discrete(labels = y_labs)
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-))
-```
-
-\newpage
-
-```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
-p <- plot(equivalence_test(m_h1))
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-))
-```
-
-\newpage
-
-```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
-p <- plot(equivalence_test(m_h2))
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-))
-```

### 2022-07-08 analysis/paper/supplementary_materials.Rmd
Remove supplementary materials and put in own file for item numbering

--- 2022-07-05 analysis/supplementary materials/supplementary materials.Rmd
@@
 ---
-title: "Supplementary Materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward'"
+title: "Supplementary materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward'"
 author:
@@
        - '--lua-filter=pagebreak.lua'
+bibliography: references.bib
+link-citations: no
+csl: "../templates/american-phytopathological-society.csl"
 ---
 
-```{r, setup, echo=FALSE, message=FALSE, warning=FALSE}
-
-library("Reproducibility.in.Plant.Pathology")
+```{r, setup, echo=FALSE, message=FALSE}
 packages <- c(
-  "tidyverse",
+  "DiagrammeR",
+  "DiagrammeRsvg",
   "bayesplot",
@@
   "brms",
+  "dplyr",
+  "english",
   "extrafont",
   "flextable",
+  "ggpubr",
   "grDevices",
-  "ggpubr",
   "here",
+  "janitor",
   "knitr",
   "officer",
-  "pander",
   "parameters",
+  "patchwork",
   "posterior",
   "report",
+  "rsvg",
+  "tidyr",
   "tools"
@@
   dev = "cairo_ps",
-  cache = FALSE
+  cache = FALSE,
+  fig.cap.pre = "Figure S",
+  tab.cap.pre = "Table S"
 )
@@
 )
-
-knitr::opts_chunk$set(
-  fig.cap.pre = "Figure S",
-  tab.cap.pre = "Table S"
-)
-
 ```
@@
 ```
+``
 
@@
 
-## Figures
+## Supplementary Figures
+
+```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data avaialbility for each of the five evaluators.
+Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators."}
+p <- import_notes() %>%
+  mutate(
+    comp_mthds_avail = as.numeric(as.character(comp_mthds_avail)),
+    data_avail =  as.numeric(as.character(data_avail))
+  ) %>%
+  pivot_longer(cols = c("comp_mthds_avail",
+                        "data_avail")) %>%
+  ggplot(aes(y = as.factor(value), x = assignee)) +
+  geom_count() +
+  ylab("Criteria Score") +
+  xlab("Evaluator") +
+  ggtitle("Criteria scores by evaluator") +
+  facet_wrap(name ~ .,
+             labeller = labeller(name =
+                                   c(
+                                     "comp_mthds_avail" = "Code",
+                                     "data_avail" = "Data"
+                                   )))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"))
+```
+
+\newpage
 
@@
 p <- plot(equivalence_test(m_f1)) +
-  scale_y_discrete(labels = y_labs)
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
-))
-```
-
-\newpage
-
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
-y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:23, 1:20)]
-
-p <- plot(equivalence_test(m_f2)) +
   scale_y_discrete(labels = y_labs)
@@
 
-```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
-y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
+y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
 y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(10:11, 1:9)]
+y_labs <- y_labs[c(21:23, 1:20)]
 
-p <- plot(equivalence_test(m_g1)) +
+p <- plot(equivalence_test(m_f2)) +
   scale_y_discrete(labels = y_labs)

### 2022-07-08 analysis/paper/knit_paper.R
add lines to knit supp materials

@@ -5,3 +5,6 @@ library("rmarkdown")
 # Knit Rmd file for manuscript
 render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.Rmd",
        output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/paper.docx")
+
+render(input = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary_materials.Rmd",
+       output_file = "/home/rstudio/Reproducibility_in_Plant_Pathology/analysis/paper/supplementary_materials.docx")

### 2022-07-08 analysis/paper/paper.Rmd
Further clarify raw data and metadata

@@
 Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
-Making the raw data FAIR means providing proper metadata for the resource.
-The metadata define the resource that has been made available allowing for discovery and use by other interested parties.
+Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
+The metadata further define the resource that has been made available allowing for discovery and use by other interested parties.
 That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.

### 2022-08-22 analysis/paper/paper.Rmd
Address Reviewer 1 Comment #1

@@
 Reproducibility is one component under the umbrella of open science.
-By proactively practicing open science, the work increases the chance to become more reproducible through the availability of data and code.
-That is, open science leads to reproducibility and replicability.
+By proactively practising open science, the work increases the chance to become more reproducible through the availability of data and code.
+That is, open science enables reproducibility and replicability.
 

### 2022-08-22 analysis/paper/paper.Rmd
Address Reviewer #1 comment #2
Address Reviewer #1's comment re:figure 1

@@
 
-Plant pathologists routinely provide information on protocols and chemicals allowing for reproducibility.
+Plant pathologists often provide information on protocols and chemicals allowing for reproducibility.
 However, frequently biological specimens such as strains, cultures or cultivars are not available after publication.
@@
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F).
+Scoring for 'Code Availability' was scored 1 -- 3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+And the scoring for 'Data Availability' was scored 1 -- 3 as follows, shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values.

### 2022-08-22 analysis/paper/paper.Rmd
Address Reviewer #1 Comment on removing "also"

--- 2022-07-08 analysis/paper/paper.Rmd
@@
 We found that most of the articles were not following protocols for open science and were failing to share data or code in a reproducible way.
-We also propose that use of open-source tools facilitates computationally reproducible work and analyzes benefitting not just readers, but the authors as well.
-Finally, we also provide ideas and tools to promote open, reproducible computational research practices among plant pathologists.
+We propose that use of open-source tools facilitates computationally reproducible work and analyzes benefitting not just readers, but the authors as well.
+Finally, we provide ideas and tools to promote open, reproducible computational research practices among plant pathologists.
 

### 2022-08-22 analysis/paper/paper.Rmd
Address Reviewer #1's comment to delete "etc."

@@
 Therefore, our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyzes or for use in instructional purposes.
-And that the software used are also easily obtained and preferably open-source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats, etc.
+And that the software used are also easily obtained and preferably open-source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats.
 

### 2022-08-22 analysis/paper/paper.Rmd
Address Reviewer #1's comment, sentence clarity
First pass at addressing clarity issues as per Reviewer #1 comments

@@
 
-A custom function, `import_notes()`, was written to import the data and format the columns properly R [@RCT2022].
+A custom function, `import_notes()`, was written to import the data and format the columns properly in R [@RCT2022].
 Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
@@
 We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
-The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
-Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
+The cumulative logit family is often used for ordinal data as it uses cumulative probabilities up to a threshold, making all of the of ordinal categories binary at that threshold.
+Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
 Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
@@
 Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
-Models 1 and 2 to predict two responses with publishing journal, as the journals' abbreviation, the formula took the form: response \~ abbreviation (model 1: code_availability \~ abbreviation and model 2: data_availability \~ abbreviation) and the models included assignee as a random effect (formula: \~1 \| assignee).
-Models 3 and 4 to predict the two responses with year (formula: response \~ year) and the models included abbreviation and assignee as random effects (formula: list(\~1 \| abbreviation, \~1 \| assignee)).
-Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response \~ IF_5year and included assignee as random effect (formula: \~1 \| assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
+Models 1 and 2 were used to predict responses with publishing journal, using the journals' abbreviation as the predictor the formula took the form: response \~ abbreviation (model 1: code_availability \~ abbreviation and model 2: data_availability \~ abbreviation) and the models included assignee as a random effect (formula: \~1 \| assignee).
+Models 3 and 4 were used to predict the two responses with year as the predictor (formula: response \~ year) and the models included abbreviation and assignee as random effects (formula: list(\~1 \| abbreviation, \~1 \| assignee)).
+Models 5 and 6 were used to predict the responses using IF_5year as the predictor the formula took the form: response \~ IF_5year and included assignee as random effect (formula: \~1 \| assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
 

### 2022-08-25 analysis/paper/paper.Rmd
Finalise response to reviewer 1's comments

@@
 
-Model fitness' were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model fitness was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 
@@
 
-Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the data was not available or mentioned in the article.
+Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the original data were not available or mentioned in the article.
 However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
@@
 As an example, Sparks et al.
-[-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+[-@Sparks2011; -@Sparks2014, @Sparks2016] used FigShare to provide models, data and code necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
 Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
@@
 For more on using Docker for reproducible research, we would refer readers to @Nuest2020.
-As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package that enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package.
+This enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected.
+It also allows for more in-depth investigation by stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
 When this layer is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks, a "web application for creating and sharing computational documents" [@jupyter2022], as Mioroni et al.
@@
 The first layer, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-When making our science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
+When making science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
 Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
@@
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
-This also helps to ensure that we researchers can reconstruct what we have done since we will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on our research.
+This also helps to ensure that researchers can reconstruct what they did more easily since good notes exist and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on the research.
 
@@
 Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values.
-Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
+Model fitness was found to be good for all models.", cache=FALSE, fig.env='figure'}
 

### 2022-08-25 analysis/paper/supplementary_materials.Rmd
Finalise response to reviewer 1's comments

@@
 
-```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data avaialbility for each of the five evaluators.
+```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data availability for each of the five evaluators.
 Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators."}
@@
 
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability."}
 y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)

### 2022-08-25 analysis/paper/paper.Rmd
Add more funders requiring open data per Reviewer #1

@@
 
-Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010].
+Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010].
 

### 2022-08-25 analysis/paper/paper.Rmd

@@
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F).
+Scoring for 'Code Availability' was scored 1 -- 3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+And the scoring for 'Data Availability' was scored 1 -- 3 as follows, shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values.
-Model fitness was found to be good for all models.", cache=FALSE, fig.env='figure'}
+Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
 

### 2022-08-25 analysis/paper/paper.Rmd
Remove statement about grey intervals as they don't appear in figure

@@
 A test for practical equivalence was undecided on any detectable effects of impact factor.
-Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
+Intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_h1), show_lables = TRUE) + 

### 2022-08-25 analysis/paper/paper.Rmd
Define "code" and "data" in "code/data availability"
State that "code" includes ANY materials used in the analysis pipeline or model code, etc.

@@
 This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+
+For the purposes of this research paper, the word "code" in "code availability" was defined as including any materials that were used in the data import, cleaning, analysis, genome assembly or manuscript preparation or in the case of modelling papers, the model's software code itself.
+The word "data" in "data availability" was defined as including any data created or collected and presented in the research manuscript.
 

### 2022-08-31 analysis/paper/paper.Rmd
Add Barton 2022 reference

@@
 
-Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010].
+Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@barton2022].
 

### 2022-10-07 analysis/paper/paper.Rmd
Correct spelling of "label"

@@
 We found that most of the articles were not following protocols for open science and were failing to share data or code in a reproducible way.
-We propose that use of open-source tools facilitates computationally reproducible work and analyzes benefitting not just readers, but the authors as well.
+We propose that use of open-source tools facilitates computationally reproducible work and analyses benefitting not just readers, but the authors as well.
 Finally, we provide ideas and tools to promote open, reproducible computational research practices among plant pathologists.
@@
 Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_g1), show_lables = TRUE) + 
+a <- plot(parameters(m_g1), show_labels = TRUE) + 
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_g2), show_lables = TRUE) + 
+b <- plot(parameters(m_g2), show_labels = TRUE) + 
   scale_colour_grey() +
@@
 Intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_h1), show_lables = TRUE) + 
+a <- plot(parameters(m_h1), show_labels = TRUE) + 
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_h2), show_lables = TRUE) + 
+b <- plot(parameters(m_h2), show_labels = TRUE) + 
   scale_colour_grey() +

### 2022-10-13 analysis/paper/paper.Rmd
Fix Barton reference

@@
 
-Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@barton2022].
+Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@Barton2022].
 

### 2022-10-13 analysis/paper/paper.Rmd
Address R2's comments Re: random page numbers and bias

@@
 A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for each sampling event.
-This was done because some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
-This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.
+This was done to ensure that the the randomly generated number had a corresponding number in the journal.
 
@@
 Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
+
+The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
+This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, _e.g._, _Phytopathology_(R) have focus issues with invited authors.
+In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct.
 

### 2022-10-13 analysis/paper/paper.Rmd
Use "Phytopathology&reg;" throughout

@@
 
-When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores having a mean of zero.
+When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology*&reg; as the reference with latent scores having a mean of zero.
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*&reg; for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
 
-When predicting the availability of data availability as compared with *Phytopathology*, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).
+When predicting the availability of data availability as compared with *Phytopathology*&reg;, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*&reg;, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).
 
@@
 The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
-This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, _e.g._, _Phytopathology_(R) have focus issues with invited authors.
+This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, _e.g._, *Phytopathology*&reg;&reg; have focus issues with invited authors.
 In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct.
@@
 Code sharing was extremely rare, but in cases where it was shared, most were included as a part of the journal article's publication as extra materials rather than through data repositories.
-Authors publishing in *Phytopathologia Mediterranea* were more likely than articles published in *Phytopathology* to share data.
+Authors publishing in *Phytopathologia Mediterranea* were more likely than articles published in *Phytopathology*&reg; to share data.
 Several articles published in this journal either made the data available through GenBank or it was noted that all data were available through the article and associated supplementary materials.
@@
 ```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code).
-However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*.
-Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*.
-Intervals in black have a median value that is greater than that of *Phytopathology*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
+A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code).
+However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*&reg;.
+Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;.
+Intervals in black have a median value that is greater than that of *Phytopathology*&reg;, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*&reg;.', cache=FALSE, fig.env='figure'}
 

### 2022-10-13 analysis/paper/paper.Rmd
Address R2's comment Re: Order of statistical analysis
Clarify model structures

@@
 
-The statistical analysis was performed using `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
+Inter-rater differences were evaluated using percent agreement and Fliess' Kappa [@DelPonte2019].
 
-Inter-rater differences were evaluated using percent agreement and Fliess' Kappa [@DelPonte2019].
+Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
+Models 1 and 2 were used to predict responses with publishing journal, using the journals' abbreviation as the predictor (formula: response \~ abbreviation).
+Models 3 and 4 were used to predict the two responses with year as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)).
+Models 5 and 6 were used to predict the responses using IF_5year as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) and included assignee as random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
+All models included the assigned article evaluator as a random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) to address inter-rater effects on scoring.
 
@@
 The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log point-wise predictive density via `loo_compare()`.
-
-Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
-Models 1 and 2 were used to predict responses with publishing journal, using the journals' abbreviation as the predictor the formula took the form: response \~ abbreviation (model 1: code_availability \~ abbreviation and model 2: data_availability \~ abbreviation) and the models included assignee as a random effect (formula: \~1 \| assignee).
-Models 3 and 4 were used to predict the two responses with year as the predictor (formula: response \~ year) and the models included abbreviation and assignee as random effects (formula: list(\~1 \| abbreviation, \~1 \| assignee)).
-Models 5 and 6 were used to predict the responses using IF_5year as the predictor the formula took the form: response \~ IF_5year and included assignee as random effect (formula: \~1 \| assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
 
@@
 Additionally, all methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
+
+All statistical analysis was performed using `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
 
@@
 
-When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology*&reg; as the reference with latent scores having a mean of zero.
+When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology*® as the reference with latent scores having a mean of zero.
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*&reg; for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
 
-When predicting the availability of data availability as compared with *Phytopathology*&reg;, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*&reg;, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).
+When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).
 
-The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) has a 99.99% probability of being positive (> 0), 99.98% of being significant (> 0.05), and 99.83% of being large (> 0.30).
+The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) has a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83% of being large (\> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19017).
@@
 The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
-This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, _e.g._, *Phytopathology*&reg;&reg; have focus issues with invited authors.
+This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, *e.g.*, *Phytopathology*®® have focus issues with invited authors.
 In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct.
@@
 Code sharing was extremely rare, but in cases where it was shared, most were included as a part of the journal article's publication as extra materials rather than through data repositories.
-Authors publishing in *Phytopathologia Mediterranea* were more likely than articles published in *Phytopathology*&reg; to share data.
+Authors publishing in *Phytopathologia Mediterranea* were more likely than articles published in *Phytopathology*® to share data.
 Several articles published in this journal either made the data available through GenBank or it was noted that all data were available through the article and associated supplementary materials.
@@
 
-A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
-E.DP. provided five-year impact factors.
-A.H.S., E.DP., Z.F. K.A. and N.G. evaluated articles for scoring.
-A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
+A.H.S, E.DP., Z.F.
+and N.J.G. conceived of the presented idea and scoring system.
+E.DP.
+provided five-year impact factors.
+A.H.S., E.DP., Z.F. K.A.
+and N.G.
+evaluated articles for scoring.
+A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP.
+and Z.F.
 A.H.S. wrote the manuscript in consultation with E.DP.

### 2022-10-13 analysis/paper/paper.Rmd
Add section and references on related discipline efforts

@@
 It is interesting to note however, that even with the popularity of Python in scientific programming it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
+
+## Efforts and Examples from Related Disciplines
+
+Plant pathology is not alone in the lack of reproducibility and with the close-nature of data and code.
+In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
+Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
+@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
+@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
+More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture, [@Smith2018; @Arnaud2020; @Stacey2022].
+However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
 

### 2022-10-13 analysis/paper/paper.Rmd
Fix linebreaks in Author contributions

@@
 @Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
-More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture, [@Smith2018; @Arnaud2020; @Stacey2022].
+More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
 However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
@@
 
-Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
+Efforts to annotate structured raw data, make it FAIR (Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
 Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
@@
 
-A.H.S, E.DP., Z.F.
-and N.J.G. conceived of the presented idea and scoring system.
-E.DP.
-provided five-year impact factors.
-A.H.S., E.DP., Z.F. K.A.
-and N.G.
-evaluated articles for scoring.
-A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP.
-and Z.F.
+A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
+E.DP. provided five-year impact factors.
+A.H.S., E.DP., Z.F. K.A. and N.G. evaluated articles for scoring.
+A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
 A.H.S. wrote the manuscript in consultation with E.DP.

### 2022-10-13 analysis/paper/paper.Rmd
Reword section heading for related disciplines
Reentitle section on reproducility layers
Replace e.g. with *e.g.* throughout

@@
 
-Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@Barton2022].
+Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [*e.g.*, @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@Barton2022].
 
@@
 'Code availability' rated how easily and openly available the computational methods used in the article were.
-Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
 Second, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
-This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, *e.g.*, a methods paper.
 
@@
 
-## Efforts and Examples from Related Disciplines
+## Examples and Efforts from Related Disciplines
 
@@
 
-## Examples of Different Layers of Reproducibility
+## Examples of Different Layers for Improving Reproducibility
 
-There are different ways to make research more open and reproducible, which can be thought of as layers of reproducibility.
-If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
+There are different ways to make research more open and reproducible.
+These can be thought of as layers of reproducibility.
+If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, writing the manuscript then the next logical steps are depositing any code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 Here we define three layers of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
@@
 @Hill2019 also shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
-The scripts provided used an R package, *checkpoint* [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that are necessary to reproduce the work rather than defaulting to the latest versions.
-However, the scripts did not run unhindered, as the supplementary materials suggested that they should, without changes to the data, but with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.
-One drawback to this approach is that journals are often not equipped to handle code, e.g., script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them or if they are provided in a native text format, they do not render via the web properly.
+The scripts provided used an R package, *checkpoint* [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that were necessary to reproduce the work rather than defaulting to the latest versions, which may cause failures due to changes in the package code-bases.
+However, the scripts did not run unhindered as the supplementary materials suggested without changes to the data.
+But with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.
+One drawback to this approach is that journals are often not equipped to handle code, *e.g.*, script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them or if they are provided in a native text format, they do not render via the web properly.
 Though this should be possible given some effort from the publishing journal to share simple text files rather than binary formats along with the proper instructions and handling of these file formats rather than a one-size-fits all approach that we commonly see for supplementary materials.
@@
 
-The second layer is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or some other long-term repository as provided by a library, Zenodo, FigShare, etc.
+The second layer is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or some other long-term repository as provided by an institutional library, Zenodo, FigShare, etc.
 Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
 
-The third layer is the use of proper code repositories such as GitHub and data repositories like FigShare, Zenodo or OSF.io among others, allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
+The third layer is the use of proper code repositories such as a library resource, or code repository (*e.g.* GitHub or GitLab) and data repositories (*e.g.*, FigShare, Zenodo or OSF.io), allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
 As an example, Sparks et al.
@@
 The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
-Using a public code repository resource like GitHub allows readers to easily contact the authors by opening "Issues" and report bugs or ask questions in an open forum that are not as straightforward when the data are provided as supplementary material.
+Using a public code repository resource allows other researchers to easily contact the authors by opening "Issues" and report bugs or ask questions in an open forum that are not as straightforward when the data are provided as supplementary material.
 
@@
 
-Efforts to annotate structured raw data, make it FAIR (Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
+Simply depositing code and data in repositories is not enough.
+Efforts must be made to annotate and structure the raw data to make it FAIR (Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016].
 Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
-The metadata further define the resource that has been made available allowing for discovery and use by other interested parties.
-That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
+Further, fully documenting the code used for the analysis is necessary for other researchers to fully use and understand.
+
+Proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
 Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
@@
 The use of programming or scripting languages such as R, Julia, SAS or Python enables us scientists to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyzes and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
+This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
 
@@
 This also helps to ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
+Larger data sets may warrant the use of a proper database like lightweight personal databases, *e.g.*, SQLite or DuckDB, larger more robust databases, *e.g.*, MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
 Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.

### 2022-10-13 analysis/paper/paper.Rmd
Replace a double ®

@@
 The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
-This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, *e.g.*, *Phytopathology*®® have focus issues with invited authors.
+This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, *e.g.*, *Phytopathology*® have focus issues with invited authors.
 In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct.

### 2022-10-13 analysis/paper/paper.Rmd
Fix figure cross-references

@@
 Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure S1).
-However, the analyses did account for different raters for each article by including this as a random effect.
+However, the analyses did account for different raters (assignees) for each article by including this as a random effect.
 
@@
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
 
-When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).
+When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B, Table S2, Figure S3).
 
@@
 
-There was no effect detected for year when predicting the availability of computational methods (Table S3, Figure S4).
-However, 2018 was clearly different with more data being made available than all other years (Table S4; Figure S5).
+There was no effect detected for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
+However, 2018 was clearly different with more data being made available than all other years (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
 
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Tables S5, S6 and Figures S6, S7).
+There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6; Figures S6, S7).
 

### 2022-10-13 analysis/paper/paper.Rmd
Correct spelling of "Swath"

@@
 
-To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
+To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swath of publications to evaluate our collective status.
 We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.*, quartile range or citation index, to represent the discipline.

### 2022-10-13 analysis/paper/paper.Rmd
Fix typo, "Figure Figure"

@@
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
 

### 2022-10-13 analysis/paper/paper.Rmd
Move ref to Fig 1 to results

@@
 
-Model fitness was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+Model fitness was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 
@@
 ## Statistical Analysis
+
+All models' diagnostic plots indicated good chain mixing and all were deemed suitable for the data by the checking posterior fits (Figure \@ref(fig:posteriors)).
 

### 2022-10-13 analysis/paper/paper.Rmd
replace *e.g.* with e.g. throughout

@@
 
-Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [*e.g.*, @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@Barton2022].
+Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@Barton2022].
 
@@
 
-In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, *e.g.*, field trials that span years and locations or complex glasshouse experiments.
+In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, e.g., field trials that span years and locations or complex glasshouse experiments.
 Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":
@@
 To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swath of publications to evaluate our collective status.
-We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.*, quartile range or citation index, to represent the discipline.
+We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, e.g., quartile range or citation index, to represent the discipline.
 The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
@@
 Articles were then manually selected by visiting the journals' websites and selecting the articles within which the randomly assigned page numbers fell, *i.e.*, if the page number was 32, the article that started on page 28 and ended on page 35 was selected as it contained page 32.
-In cases where an article was not suitable, *e.g.*, a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
+In cases where an article was not suitable, e.g., a review or otherwise not related to plant pathology or the randomly assigned numbers for that journal and year fell within the same article, the next article in that journal was selected until a suitable article was found.
 
@@
 'Code availability' rated how easily and openly available the computational methods used in the article were.
-Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
 Second, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
-This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (*e.g.*, login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, *e.g.*, a methods paper.
+This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 
@@
 In cases where partial computational materials or data were made available, the score was assigned the lowest score reflecting the completeness of the availability, all or nothing.
-That is, in cases where some data such as sequences were deposited in a database, *e.g.*, GenBank, but other data that was collected and used were not made available, the score assigned was '0'.
+That is, in cases where some data such as sequences were deposited in a database, e.g., GenBank, but other data that was collected and used were not made available, the score assigned was '0'.
 
@@
 The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
-This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, *e.g.*, *Phytopathology*® have focus issues with invited authors.
+This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
 In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct.
@@
 But with some modifications to the data, and file name changes, the scripts ran allowing examples of the research to be reproduced using the definition of @Peng2009.
-One drawback to this approach is that journals are often not equipped to handle code, *e.g.*, script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them or if they are provided in a native text format, they do not render via the web properly.
+One drawback to this approach is that journals are often not equipped to handle code, e.g., script files, that may be developed as a part of the research process and so they are often archived as PDF or Word documents which hinder the ability to easily ingest and start working with them or if they are provided in a native text format, they do not render via the web properly.
 Though this should be possible given some effort from the publishing journal to share simple text files rather than binary formats along with the proper instructions and handling of these file formats rather than a one-size-fits all approach that we commonly see for supplementary materials.
@@
 
-The third layer is the use of proper code repositories such as a library resource, or code repository (*e.g.* GitHub or GitLab) and data repositories (*e.g.*, FigShare, Zenodo or OSF.io), allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
+The third layer is the use of proper code repositories such as a library resource, or code repository (e.g.
+GitHub or GitLab) and data repositories (e.g., FigShare, Zenodo or OSF.io), allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
 As an example, Sparks et al.
@@
 
-Taking this approach even further, packaging the full analysis in a containerized software application, *e.g.*, Docker is a way to help ensure computational reproducibility but at the expense of added complexity.
+Taking this approach even further, packaging the full analysis in a containerized software application, e.g., Docker is a way to help ensure computational reproducibility but at the expense of added complexity.
 Docker is an open-source containerization platform that enables users to package several applications and an operating system into containers, thereby standardizing the executable components by combining application source code (or analyzes) with the operating system required to run that analysis on a user's computer.
@@
 When making science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
-Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
+Provide a full description of all equipment used, e.g., "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
 This allows end-users to identify what was used and identify the methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
-This also helps to ensure that researchers can reconstruct what they did more easily since good notes exist and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on the research.
+This also helps to ensure that researchers can reconstruct what they did more easily since good notes exist and documentation and be able to identify if something changes, e.g., a package version, what effect it had on the research.
 
@@
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, *e.g.*, comma separated (CSV) or tab separated (TSV) files.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, e.g., comma separated (CSV) or tab separated (TSV) files.
 This also helps to ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like lightweight personal databases, *e.g.*, SQLite or DuckDB, larger more robust databases, *e.g.*, MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
+Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
 Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.

### 2022-10-13 R/import_notes.R
Treat years as a continous variable not a discrete factor

@@ -60,7 +60,6 @@ import_notes <- function() {
                     )) %>%
     dplyr::mutate(
       journal = as.factor(journal),
-      year = as.factor(year),
       art_class = as.factor(art_class),
       repro_inst = as.factor(repro_inst),
       open = as.factor(open),

### 2022-10-14 analysis/paper/paper.Rmd
Reorder affiliation

@@
 institute:
-  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
+  - DPIRD: Farming Systems Innovation, Department of Primary Industries and Regional Development, Perth WA 6000, Australia
   - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia

### 2022-10-14 analysis/paper/paper.Rmd
clean up inclusions in output

@@
 
-```{r, setup, echo=FALSE, message=FALSE}
+```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
 packages <- c(
@@
   "rsvg",
+  "rstan",
   "tidyr",
@@
                  dependencies = TRUE)
-
 # load packages for use in knitting Rmd
@@
                  character.only = TRUE))
-
 library("Reproducibility.in.Plant.Pathology")

### 2022-10-14 analysis/paper/paper.Rmd
Use here to load files

@@
 
-load(
-  system.file(
-    "extdata",
-    "m_f1.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_f1_report.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_f2.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_f2_report.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
+load(here("inst/extdata/m_f1.Rda"))
+load(here("inst/extdata/m_f1_report.Rda"))
+load(here("inst/extdata/m_f2.Rda"))
+load(here("inst/extdata/m_f2_report.Rda"))
 
-load(
-  system.file(
-    "extdata",
-    "m_g1.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_g1_report.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_g2.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_g2_report.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
+load(here("inst/extdata/m_g1.Rda"))
+load(here("inst/extdata/m_g1_report.Rda"))
 
-load(
-  system.file(
-    "extdata",
-    "m_h1.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_h1_report.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_h2.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
-load(
-  system.file(
-    "extdata",
-    "m_h2_report.Rda",
-    package = "Reproducibility.in.Plant.Pathology",
-    mustWork = TRUE
-  )
-)
+load(here("inst/extdata/m_g2.Rda"))
+load(here("inst/extdata/m_g2_report.Rda"))
+
+load(here("inst/extdata/m_h1.Rda"))
+load(here("inst/extdata/m_h1_report.Rda"))
+load(here("inst/extdata/m_h2.Rda"))
+load(here("inst/extdata/m_h2_report.Rda"))
 ```

### 2022-10-14 analysis/paper/supplementary_materials.Rmd
Clean up output and code chunks

@@
   "report",
+  "rope",
   "rsvg",

### 2022-10-14 analysis/paper/supplementary_materials.Rmd
Remove "Rope Percentage" from table

@@
 ```
-``
 
@@
   mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
+  rename("CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%
@@
   mutate(Parameter = gsub("year", "", .$Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
+  rename("CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%
@@
   mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
+  rename("CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%
@@
   filter(!is.na(Parameter)) %>%
-  rename("ROPE %" = "ROPE_Percentage",
-         "CI\nLow" = "CI_low",
+  rename("CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%

### 2022-10-14 analysis/paper/supplementary_materials.Rmd
Revert "Remove ROPE from tables"
This reverts commit f5634093aff3d80c0da49a7f3597a2462e1cbc0e.

@@
   set_caption(
-    "Full description of model fit for the effect of journal title on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
 The model included assignee as random effect (formula: ~1 | assignee).
@@
   set_caption(
-    "Full description of model fit for the effect of journal title on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
 The model included assignee as random effect (formula: ~1 | assignee).
@@
   filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
   rename("CI\nLow" = "CI_low",
@@
   set_caption(
-    "Full description of model fit for the effect of year of publication on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
 The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
   )
@@
   filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
   rename("CI\nLow" = "CI_low",
@@
   set_caption(
-    "Full description of model fit for the effect of year of publication on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict data_avail with year (formula: data_avail ~ year).
 The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.
+"
   )
@@
   set_caption(
-    "Full description of model fit for the effect of five-year impact factor on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of five-year impact factor on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
 The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
@@
   set_caption(
-    "Full description of model fit for the effect of five year impact factor on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+    "Full description of model fit for the effect of five-year impact factor on data availability.
+Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
 The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
@@
 ```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data availability for each of the five evaluators.
-Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators."}
+Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators.
+Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+And the scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
 p <- import_notes() %>%
@@
 
-```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
+```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability.
+Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
 y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
@@
 
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability."}
+```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.
+Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
 y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
@@
 
-```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
-y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(10:11, 1:9)]
-
-p <- plot(equivalence_test(m_g1)) +
-  scale_y_discrete(labels = y_labs)
+```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability.
+Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
+p <- plot(equivalence_test(m_g1))
 
@@
 
-```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
-p <- plot(equivalence_test(m_g2)) +
-  scale_y_discrete(labels = y_labs)
+```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability.
+Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
+p <- plot(equivalence_test(m_g2))
 
@@
 
-```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
+```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability.
+Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
 p <- plot(equivalence_test(m_h1))
@@
 
-```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
+```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability.
+Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
 p <- plot(equivalence_test(m_h2))

### 2022-10-14 analysis/paper/supplementary_materials.Rmd
Remove ROPE from tables

--- 2022-10-14 analysis/paper/supplementary_materials.Rmd
@@
   "report",
-  "rope",
   "rsvg",
@@
   colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
   autofit() %>%

### 2022-10-14 analysis/paper/paper.Rmd
Add statement on inter-rater repeatability to discussion

@@
 
+We acknowledge that the number of article that are cross-scored is low.
+However, our aim was not to test inter-rater reproducibility, this is covered at length in the plant pathology literature.
 Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
 Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
+Therefore, we concluded that the inter-rater agreement was good enough for this paper to illustrate that code and data are not being widely shared with peer-reviewed publications.
 

### 2022-10-14 analysis/paper/paper.Rmd
Flesh out idea more about invited articles being no different

@@
 This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
-In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct.
+In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.
 

### 2022-10-14 analysis/paper/paper.Rmd
Reorder and create section on limitations to approach taken
Edits for clarity

@@
 
-We acknowledge that the number of article that are cross-scored is low.
-However, our aim was not to test inter-rater reproducibility, this is covered at length in the plant pathology literature.
-Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
-Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
-Therefore, we concluded that the inter-rater agreement was good enough for this paper to illustrate that code and data are not being widely shared with peer-reviewed publications.
-
-The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
-This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
-In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.
-
 Except for a few isolated cases, most papers were not fully computationally reproducible.
@@
 
+## Limitations to Our Approach
+
+We acknowledge that the number of article that are cross-scored is low.
+However, our aim was not to test inter-rater reproducibility, this is covered at length in the plant pathology literature.
+Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
+Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
+Therefore, we concluded that the inter-rater agreement was good enough for this paper to illustrate that code and data are not being widely shared with peer-reviewed publications.
+
+Furthermore, the methods for selecting articles meant that only page numbers between 1 and 150 were selected.
+This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
+In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.
+
 ## Examples and Efforts from Related Disciplines
 
-Plant pathology is not alone in the lack of reproducibility and with the close-nature of data and code.
+Plant pathology is not alone in the lack of reproducibility and the closed-nature of data and code.
 In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.

### 2022-10-14 analysis/paper/paper.Rmd
Update statement on year effect on code and data w/ new analysis

@@
 
-There was no effect detected for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
-However, 2018 was clearly different with more data being made available than all other years (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
+There was no detectable effect or non-effect for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
+However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
 

### 2022-10-14 analysis/paper/paper.Rmd
Remove spaces around emdashes

@@
 
-Each article was rated on a 0 -- 3 scale for its data and code availability.
+Each article was rated on a 0--3 scale for its data and code availability.
 'Code availability' rated how easily and openly available the computational methods used in the article were.
@@
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F).
-Scoring for 'Code Availability' was scored 1 -- 3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-And the scoring for 'Data Availability' was scored 1 -- 3 as follows, shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+And the scoring for 'Data Availability' was scored 1--3 as follows, shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values.

### 2022-10-14 analysis/paper/paper.Rmd
Reword results of analysis

@@
 
-There was no detectable effect or non-effect for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
+There was no clear effect for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
 However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).

### 2022-10-14 analysis/paper/paper.Rmd
Update paper Rmd to reflect new analysis results

@@
 
-The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) has a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83% of being large (\> 0.30).
+The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) had a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83% of being large (\> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19017).
 
-There was no clear effect for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
-However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
+There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
+
+However, the null hypothesis that the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
+The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 21692)
 

### 2022-10-14 analysis/paper/supplementary_materials.Rmd
Update paper Rmd to reflect new analysis results

@@
   set_caption(
-    "Full description of model fit for the effect of year of publication on code availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+    "We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
 The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
   )
@@
   set_caption(
-    "Full description of model fit for the effect of year of publication on data availability.
-We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
+    "We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict data_avail with year (formula: data_avail ~ year).
 The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.
+"
   )
@@
 ```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
-y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(10:11, 1:9)]
-
-p <- plot(equivalence_test(m_g1)) +
-  scale_y_discrete(labels = y_labs)
+p <- plot(equivalence_test(m_g1))
 
@@
 ```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
-p <- plot(equivalence_test(m_g2)) +
-  scale_y_discrete(labels = y_labs)
+p <- plot(equivalence_test(m_g2))
 

### 2022-10-15 analysis/paper/paper.Rmd
Fix typos in captions and display 0-3 values in all graphs
Fixes x-axis in pp_check plots where there were no values for 3. The axis now reads 0-3 for both code and data subfigures in the same plot.

@@
 Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-And the scoring for 'Data Availability' was scored 1--3 as follows, shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+And the scoring for 'Data Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values.
@@
   pp_check(m_f1, type = "bars", ndraws = 50) +
+    scale_x_continuous(,
+                       breaks = c(1, 2, 3, 4),
+                       limits = c(0.5, 4.5)) +
     theme(
@@
   pp_check(m_g1, type = "bars", ndraws = 50) +
+    scale_x_continuous(,
+                       breaks = c(1, 2, 3, 4),
+                       limits = c(0.5, 4.5)) +
     theme(
@@
   pp_check(m_h1, type = "bars", ndraws = 50) +
-    scale_x_continuous(labels = c("0", "1", "2", "3"),
-                       breaks = 1:4) +
+    scale_x_continuous(
+      labels = c("0", "1", "2", "3"),
+      breaks = c(1, 2, 3, 4),
+      limits = c(0.5, 4.5)
+    ) +
     xlab("Score (0 to 3)"),
@@
     scale_x_continuous(labels = c("0", "1", "2", "3"),
-                       breaks = 1:4) +
+                       breaks = c(1, 2, 3, 4),
+                       limits = c(0.5, 4.5)) +
     xlab("Score (0 to 3)") +

### 2022-10-15 analysis/paper/paper.Rmd
Clean up top 10 software table caption

@@
   set_caption(
-    "The frequency of use of top ten software programs by year of publication that were found to be used in the papers that were surveyed."
+    "The frequency of use of top ten most used software programs that were found in 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals by year of publication."
   )

### 2022-10-15 analysis/paper/paper.Rmd
Clean up/clarify journal titles included table caption

@@
   set_caption(
-    "Journal titles selected for inclusion, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
+    "Journal titles selected for inclusion representing 21 plant pathology journals or specialised journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
   )

### 2022-10-15 analysis/paper/paper.Rmd
Replace "fitted" with "fit"

@@
 
-We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
+We fit Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
 The cumulative logit family is often used for ordinal data as it uses cumulative probabilities up to a threshold, making all of the of ordinal categories binary at that threshold.
@@
 
-```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fit to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F).

### 2022-10-15 analysis/paper/paper.Rmd
Add missing full stop on line 342
Clarify no article scored 3 for data in figure 1
Clarify year effect on score in figure 4

@@
 The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 21692)
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 21692).
 
@@
 Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values.
+No article scored 3 for data availability.
 Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
@@
 A test for practical equivalence was undecided in any detectable effects of year of publication on computational materials or data being shared.
-Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
+Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_g1), show_labels = TRUE) + 

### 2022-10-15 analysis/paper/paper.Rmd
Clarify caption for figure 5

@@
 A test for practical equivalence was undecided on any detectable effects of impact factor.
-Intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
+Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the impact factor of the publication increases, the likelyhood of sharing code or data may increase', cache=FALSE, fig.env='figure'}
 a <- plot(parameters(m_h1), show_labels = TRUE) + 

### 2022-10-16 analysis/paper/paper.Rmd
Correct caption for fig 4

@@
 ```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for practical equivalence was undecided in any detectable effects of year of publication on computational materials or data being shared.
+A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared.
+A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared.
 Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}

### 2022-10-16 analysis/paper/paper.Rmd
Correct terminology

@@
 
-However, the null hypothesis that the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
+However, the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
 The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).

### 2022-10-20 analysis/paper/paper.Rmd
Revert "Remove "Rope Percentage" from table"
This reverts commit a7c2c1803f5d6bfa3685daa81cef8a1b6f57b5e3.

Conflicts:
	analysis/paper/supplementary_materials.Rmd

@@
 
-## Examples and Efforts from Related Disciplines
+## Examples and Efforts from Other Disciplines
 
@@
 However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
+
+@Seibold2021 investigated the types of methods and software used in PLOS ONE articles and whether the were able to reproduce the data analysis using open source software for papers that dealt with longitudinal data and used mixed effect models or generalized estimating equations for analysis and provided the data.
+They found that most articles provided tables and visualisations only.
+However, unlike our analysis, even with the data being supplied they found that only one article used open source software, whereas R prominently featured in the articles we examined along with other free open-source software packages.
+Not surprisingly they found that replication was mostly difficult and required the results to be reverse engineered or contacting the authors.
+They were unable to reproduce the results for for three articles and only parts of another two.
+They needed to contact the articles' authors for all articles save two.
+Their main conclusion was that reproducing papers is difficult if no code is provided and puts an undue burden on those interested in reproducing the work.
 
@@
 a_y_labs <- rev(gsub("b_abbreviation", "", parameters(m_f1)$Parameter)[-c(1:2)])
-a <- plot(parameters(m_f1)) +
+a <- plot(equivalence_test(m_f1)) +
   scale_y_discrete(labels = a_y_labs) +
-  scale_colour_grey() +
+  scale_fill_grey() +
   ggtitle("Code")
 
-b <- plot(parameters(m_f2)) +
-  scale_colour_grey() +
+b <- plot(equivalence_test(m_f2)) +
+  scale_fill_grey() +
   theme(
@@
 Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_g1), show_labels = TRUE) + 
+a <- plot(equivalence_test(m_g1), show_labels = TRUE) + 
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_g2), show_labels = TRUE) + 
+b <- plot(equivalence_test(m_g2), show_labels = TRUE) + 
   scale_colour_grey() +
@@
 Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the impact factor of the publication increases, the likelyhood of sharing code or data may increase', cache=FALSE, fig.env='figure'}
-a <- plot(parameters(m_h1), show_labels = TRUE) + 
+a <- plot(equivalence_test(m_h1), show_labels = TRUE) + 
   scale_colour_grey() +
@@
 
-b <- plot(parameters(m_h2), show_labels = TRUE) + 
+b <- plot(equivalence_test(m_h2), show_labels = TRUE) + 
   scale_colour_grey() +

### 2022-10-20 analysis/paper/supplementary_materials.Rmd
Revert "Remove "Rope Percentage" from table"
This reverts commit a7c2c1803f5d6bfa3685daa81cef8a1b6f57b5e3.

Conflicts:
	analysis/paper/supplementary_materials.Rmd

@@
   mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
-  rename("CI\nLow" = "CI_low",
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%
@@
   colformat_double(digits = 2) %>%
+  set_formatter(
+    `ROPE %` = function(x)
+      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
+  ) %>%
   autofit() %>%
@@
   filter(!is.na(Parameter)) %>%
-  rename("CI\nLow" = "CI_low",
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%
@@
   filter(!is.na(Parameter)) %>%
-  rename("CI\nLow" = "CI_low",
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%
@@
   filter(!is.na(Parameter)) %>%
-  rename("CI\nLow" = "CI_low",
+  rename("ROPE %" = "ROPE_Percentage",
+         "CI\nLow" = "CI_low",
          "CI\nHigh" = "CI_high") %>%

### 2022-10-20 analysis/paper/supplementary_materials.Rmd
Remove "ROPE" from supplementary tables

--- 2022-10-15 analysis/paper/supplementary_materials.Rmd
@@
   filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
   rename("CI\nLow" = "CI_low",
@@
   filter(!is.na(Parameter)) %>%
+  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
   rename("CI\nLow" = "CI_low",

### 2022-10-22 analysis/paper/paper.Rmd
Update figures 4 & 5 to display equivalence tests

@@
 Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}
-a <- plot(equivalence_test(m_g1), show_labels = TRUE) + 
-  scale_colour_grey() +
-  ggtitle("Code")
 
-b <- plot(equivalence_test(m_g2), show_labels = TRUE) + 
-  scale_colour_grey() +
+m_g1_eq <- equivalence_test(m_g1)
+m_g2_eq <- equivalence_test(m_g2)
+
+m_g1_eq <-
+  filter(m_g1_eq,
+         Parameter != "b_Intercept[1]" &
+           Parameter != "b_Intercept[2]")
+m_g2_eq <-
+  filter(
+    m_g2_eq,
+    Parameter != "b_Intercept[1]" &
+      Parameter != "b_Intercept[2]" &
+      Parameter != "b_Intercept[3]"
+  )
+
+a <- plot(m_g1_eq,
+          show_labels = TRUE,
+          rope_color = "grey10") +
+  ggtitle("Code") +
+  xlim(-0.3, 0.6) +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) +
+  coord_flip()
+
+b <-
+  plot(m_g2_eq,
+       show_labels = TRUE,
+       rope_color = "grey10") +
   theme(
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank(),
     axis.text.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.title.y = element_blank()
+    axis.ticks.x = element_blank(),
+    axis.text.x = element_blank(),
   ) +
-  ggtitle("Data")
+  ggtitle("Data") +
+  xlim(-0.3, 0.6) +
+  coord_flip()
 
@@
 Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the impact factor of the publication increases, the likelyhood of sharing code or data may increase', cache=FALSE, fig.env='figure'}
-a <- plot(equivalence_test(m_h1), show_labels = TRUE) + 
-  scale_colour_grey() +
-  ggtitle("Code")
+m_h1_eq <- equivalence_test(m_h1)
+m_h2_eq <- equivalence_test(m_h2)
 
-b <- plot(equivalence_test(m_h2), show_labels = TRUE) + 
-  scale_colour_grey() +
+m_h1_eq <-
+  filter(m_h1_eq,
+         Parameter != "b_Intercept[1]" &
+           Parameter != "b_Intercept[2]")
+m_h2_eq <-
+  filter(
+    m_h2_eq,
+    Parameter != "b_Intercept[1]" &
+      Parameter != "b_Intercept[2]" &
+      Parameter != "b_Intercept[3]"
+  )
+
+a <- plot(m_h1_eq,
+          show_labels = TRUE,
+          rope_color = "grey10") +
+  ggtitle("Code") +
+  xlim(-0.2, 1.1) +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) +
+  coord_flip()
+
+b <-
+  plot(m_h2_eq,
+       show_labels = TRUE,
+       rope_color = "grey10") +
   theme(
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank(),
     axis.text.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.title.y = element_blank()
+    axis.ticks.x = element_blank(),
+    axis.text.x = element_blank(),
+    legend.position = "none"
   ) +
-  ggtitle("Data")
+  ggtitle("Data") +
+  xlim(-0.2, 1.1) +
+  coord_flip()
 

### 2022-10-22 analysis/paper/paper.Rmd
Edit Fernandez et al. bit

@@
 @Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
+Fernandez2022 provide an R package, 'cndcR', that supports the manuscript: "Dataset characteristics for the determination of critical nitrogen dilution curves: from the past to new guidelines", [Fernandez2022a].
+The package contains source data and R code that @Fernandez2022a used for their sensitivity analyses when fitting critical N dilution curves in crop species using Bayesian models. 
+The package allows the user to recreate the figures in the manuscript and includes the all of the data files required to produce all results and figures presented in the manuscript.
 More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].

### 2022-10-23 analysis/paper/paper.Rmd
Use greyscale and standardise ROPE figures

@@
   "brms",
+  "cowplot",
   "dplyr",
@@
 
-```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
+```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
 A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code).
@@
 Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;.
-Intervals in black have a median value that is greater than that of *Phytopathology*&reg;, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*&reg;.', cache=FALSE, fig.env='figure'}
-
-a_y_labs <- rev(gsub("b_abbreviation", "", parameters(m_f1)$Parameter)[-c(1:2)])
-a <- plot(equivalence_test(m_f1)) +
-  scale_y_discrete(labels = a_y_labs) +
-  scale_fill_grey() +
-  ggtitle("Code")
-
-b <- plot(equivalence_test(m_f2)) +
-  scale_fill_grey() +
+The region of practical equivalence (ROPE) is shown between two dotted lines.
+If the entire distribution falls within the ROPE, the hypothesis is accepted.
+If the entire distribution falls outside the ROPE, the hypothesis is rejected.
+In some cases the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
+m_f1_eq <- equivalence_test(m_f1)
+m_f2_eq <- equivalence_test(m_f2)
+
+m_f1_eq <-
+  filter(m_f1_eq,
+         Parameter != "b_Intercept[1]" &
+           Parameter != "b_Intercept[2]")
+
+m_f2_eq <-
+  filter(
+    m_f2_eq,
+    Parameter != "b_Intercept[1]" &
+      Parameter != "b_Intercept[2]" &
+      Parameter != "b_Intercept[3]"
+  )
+
+ylabs <- gsub("b_abbreviation", "", m_f1_eq$Parameter)
+
+a <- plot(m_f1_eq,
+          show_labels = TRUE,
+          rope_color = "grey50") +
+  ggtitle("Code") +
+  scale_y_discrete(labels = rev(ylabs)) +
+  scale_fill_manual(
+    values =  "grey70"
+  ) +
+  theme(legend.position = "none") +
+  xlim(-3.5, 3.5) +
+  xlab("") +
+  ylab("Journal Abbreviation")
+
+b <-
+  plot(m_f2_eq,
+       show_labels = TRUE,
+       rope_color = "grey70") +
   theme(
-    axis.text.y = element_blank(),
     axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
+    axis.title.y = element_blank(),
+    axis.text.y = element_blank()
   ) +
-  ggtitle("Data")
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
+  scale_fill_manual(values = c("grey100", "grey70")) +
+  ggtitle("Data") +
+  xlab("") +
+  xlim(-3.5, 3.5)
+
+# get legend
+legend_b <- get_legend(b)
+
+b <- b + theme(legend.position = "none")
+
+p <- plot_grid(a, b,
+               ncol = 2,
+               rel_widths = c(1, 0.675),
+               labels = c("A", "B"),
+               label_x = 0.85,
+               label_y = 0.9)
+p <-
+  add_sub(
+    p,
+    "95% Highest Density Region of Posterior Samples",
+    y = 2,
+    x = 0.6,
+    vpadding = grid::unit(0, "lines")
+  )
+
+p <- plot_grid(p, legend_b, nrow = 2, rel_heights = c(1, 0.1))
 
@@
   filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
-  plot = p,
+  plot = ggdraw(p),
   width = 6,
@@
 
-```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
+```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
 A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared.
 A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared.
-Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}
+The region of practical equivalence (ROPE) is shown between two dotted lines.
+If the entire distribution falls within the ROPE, the hypothesis is accepted.
+If the entire distribution falls outside the ROPE, the hypothesis is rejected.
+In some cases the data do not provide a definitive answer and the decision on H0 is undecided.
+Here, year is treated as a continous variable to determine if there are changes over time in the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
 
@@
           rope_color = "grey10") +
+  theme(
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank(),
+    axis.text.y = element_blank(),
+    axis.title.x = element_blank(),
+    legend.box.spacing = unit(40, "pt")
+  ) +
+  xlim(-0.3, 0.7) +
+  scale_fill_manual(values = "grey70") +
   ggtitle("Code") +
-  xlim(-0.3, 0.6) +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) +
-  coord_flip()
+  coord_cartesian(ylim = c(0.9, 6), expand = FALSE)
 
@@
     axis.text.y = element_blank(),
-    axis.ticks.x = element_blank(),
-    axis.text.x = element_blank(),
+    axis.title.x = element_blank(),
+    legend.title = element_blank(),
+    legend.box.spacing = unit(40, "pt")
   ) +
+  xlim(-0.3, 0.7) +
+  scale_fill_manual(values = "black") +
   ggtitle("Data") +
-  xlim(-0.3, 0.6) +
-  coord_flip()
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
+  coord_cartesian(ylim = c(0.8, 20), expand = FALSE)
+
+p <- plot_grid(
+  a,
+  b,
+  ncol = 2,
+  rel_widths = c(1, 1),
+  labels = c("A", "B"),
+  label_x = 0.85,
+  label_y = 0.9
+)
+
+p <-
+  add_sub(
+    p,
+    "95% Highest Density Region of Posterior Samples",
+    y = 6,
+    x = 0.6,
+    vpadding = grid::unit(0, "lines")
+  )
 
@@
   filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
-  plot = p,
+  plot = ggdraw(p),
   width = 6,
@@
 
-```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.
+```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.
 A test for practical equivalence was undecided on any detectable effects of impact factor.
-Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the impact factor of the publication increases, the likelyhood of sharing code or data may increase', cache=FALSE, fig.env='figure'}
+The region of practical equivalence (ROPE) is shown between two dotted lines.
+If the entire distribution falls within the ROPE, the hypothesis is accepted.
+If the entire distribution falls outside the ROPE, the hypothesis is rejected.
+In some cases the data do not provide a definitive answer and the decision on H0 is undecided.
+Here, impact factor is a continous variable to determine if greater or lesser impact factor values affect the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
 m_h1_eq <- equivalence_test(m_h1)
@@
           rope_color = "grey10") +
+  theme(
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank(),
+    axis.text.y = element_blank(),
+    axis.title.x = element_blank(),
+    legend.position = "none"
+  ) +
+  xlim(-0.2, 1.1) +
+  scale_fill_manual(values = "grey70") +
   ggtitle("Code") +
-  xlim(-0.2, 1.1) +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) +
-  coord_flip()
+  coord_cartesian(ylim = c(0.9, 4.5), expand = FALSE)
 
 b <-
-  plot(m_h2_eq,
+  plot(m_g1_eq,
        show_labels = TRUE,
@@
     axis.text.y = element_blank(),
-    axis.ticks.x = element_blank(),
-    axis.text.x = element_blank(),
-    legend.position = "none"
+    axis.title.x = element_blank()
   ) +
+  xlim(-0.2, 1.1) +
+  scale_fill_manual(values = "grey70") +
   ggtitle("Data") +
-  xlim(-0.2, 1.1) +
-  coord_flip()
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
+  coord_cartesian(ylim = c(0.9, 6), expand = FALSE)
+
+# get legend
+legend_b <- get_legend(b)
+
+b <- b + theme(legend.position = "none")
+
+p <- plot_grid(
+  a,
+  b,
+  ncol = 2,
+  rel_widths = c(1, 1),
+  labels = c("A", "B"),
+  label_x = 0.85,
+  label_y = 0.9
+)
+
+p <-
+  add_sub(
+    p,
+    "95% Highest Density Region of Posterior Samples",
+    y = 1,
+    x = 0.6,
+    vpadding = grid::unit(0, "lines")
+  )
+
+p <- plot_grid(p, legend_b, nrow = 2, rel_heights = c(1, 0.1))
 
@@
   filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
-  plot = p,
+  plot = ggdraw(p),
   width = 6,

### 2022-10-23 analysis/paper/paper.Rmd
Remove patchwork, use cowplot instead

@@
   "parameters",
-  "patchwork",
   "posterior",
@@
 In some cases the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
-m_f1_eq <- equivalence_test(m_f1)
-m_f2_eq <- equivalence_test(m_f2)
+m_f1_eq <- equivalence_test(m_f1, rule = "bayes")
+m_f2_eq <- equivalence_test(m_f2, rule = "bayes")
 
@@
 
-m_g1_eq <- equivalence_test(m_g1)
-m_g2_eq <- equivalence_test(m_g2)
+m_g1_eq <- equivalence_test(m_g1, rule = "bayes")
+m_g2_eq <- equivalence_test(m_g2, rule = "bayes")
 
@@
 Here, impact factor is a continous variable to determine if greater or lesser impact factor values affect the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
-m_h1_eq <- equivalence_test(m_h1)
-m_h2_eq <- equivalence_test(m_h2)
+m_h1_eq <- equivalence_test(m_h1, rule = "bayes")
+m_h2_eq <- equivalence_test(m_h2, rule = "bayes")
 

### 2022-10-23 analysis/paper/supplementary_materials.Rmd
Update supplementary figures

@@
   "english",
+  "effectsize",
   "extrafont",
@@
 library("Reproducibility.in.Plant.Pathology")
+
+options(mc.cores = parallel::detectCores())
 
@@
 
-```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability.
+```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Effect sizes for a model testing the effect of the publishing journal on articles\' supporting code availability.
 Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
-y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:22, 1:20)]
+m_f1_es <- effectsize(m_f1)
 
-p <- plot(equivalence_test(m_f1)) +
-  scale_y_discrete(labels = y_labs)
+m_f1_es <-
+  filter(m_f1_es,
+         Parameter != "b_Intercept[1]" &
+           Parameter != "b_Intercept[2]")
+
+ylabs <- gsub("b_abbreviation", "", m_f1_es$Parameter)
+
+p <- plot(m_f1_es) +
+   scale_y_discrete(labels = rev(ylabs))
 
@@
 Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
-y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:23, 1:20)]
+m_f2_es <- effectsize(m_f2)
 
-p <- plot(equivalence_test(m_f2)) +
-  scale_y_discrete(labels = y_labs)
+m_f2_es <-
+  filter(
+    m_f2_es,
+    Parameter != "b_Intercept[1]" &
+      Parameter != "b_Intercept[2]" &
+      Parameter != "b_Intercept[3]"
+  )
+
+ylabs <- gsub("b_abbreviation", "", m_f2_es$Parameter)
+
+p <- plot(m_f2_es) +
+   scale_y_discrete(labels = rev(ylabs))
 
@@
 Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
-p <- plot(equivalence_test(m_g1))
+m_g1_es <- effectsize(m_g1)
+
+m_g1_es <-
+  filter(m_g1_es,
+         Parameter != "b_Intercept[1]" &
+           Parameter != "b_Intercept[2]")
+
+ylabs <- gsub("b_abbreviation", "", m_g1_es$Parameter)
+
+p <- plot(m_g1_es) +
+   scale_y_discrete(labels = rev(ylabs))
 
@@
 Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
-p <- plot(equivalence_test(m_g2))
+m_g2_es <- effectsize(m_g2)
+
+m_g2_es <-
+  filter(
+    m_g2_es,
+    Parameter != "b_Intercept[1]" &
+      Parameter != "b_Intercept[2]" &
+      Parameter != "b_Intercept[3]"
+  )
+
+ylabs <- gsub("b_abbreviation", "", m_g2_es$Parameter)
+
+p <- plot(m_g2_es) +
+   scale_y_discrete(labels = rev(ylabs))
 
@@
 Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
-p <- plot(equivalence_test(m_h1))
+m_h1_es <- effectsize(m_h1)
+
+m_h1_es <-
+  filter(m_h1_es,
+         Parameter != "b_Intercept[1]" &
+           Parameter != "b_Intercept[2]")
+
+ylabs <- gsub("b_abbreviation", "", m_h1_es$Parameter)
+
+p <- plot(m_h1_es) +
+   scale_y_discrete(labels = rev(ylabs))
 
@@
 Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
-p <- plot(equivalence_test(m_h2))
+m_h2_es <- effectsize(m_h2)
+
+m_h2_es <-
+  filter(
+    m_h2_es,
+    Parameter != "b_Intercept[1]" &
+      Parameter != "b_Intercept[2]" &
+      Parameter != "b_Intercept[3]"
+  )
+
+ylabs <- gsub("b_abbreviation", "", m_h2_es$Parameter)
+
+p <- plot(m_h2_es) +
+   scale_y_discrete(labels = rev(ylabs))
 

### 2022-10-23 analysis/paper/paper.Rmd
Reinstated patchwork lib loading in paper.Rmd

@@
   "officer",
+  "patchwork",
   "parameters",

### 2022-10-24 analysis/paper/supplementary_materials.Rmd
Add effect size objects for reporting in supplementary tables

--- 2022-10-20 analysis/paper/supplementary_materials.Rmd
@@
 
-## Supplementary Figures
+## Supplementary Figure
 
@@
 ```
-
-\newpage
-
-```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability.
-Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
-y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:22, 1:20)]
-
-p <- plot(equivalence_test(m_f1)) +
-  scale_y_discrete(labels = y_labs)
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
-))
-```
-
-\newpage
-
-```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.
-Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
-y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
-y_labs <- rev(gsub("b_", "", y_labs))
-y_labs <- y_labs[c(21:23, 1:20)]
-
-p <- plot(equivalence_test(m_f2)) +
-  scale_y_discrete(labels = y_labs)
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
-))
-```
-
-\newpage
-
-```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability.
-Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
-p <- plot(equivalence_test(m_g1))
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
-))
-```
-
-\newpage
-
-```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability.
-Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
-p <- plot(equivalence_test(m_g2))
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
-))
-```
-
-\newpage
-
-```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability.
-Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
-p <- plot(equivalence_test(m_h1))
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
-))
-```
-
-\newpage
-
-```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability.
-Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
-p <- plot(equivalence_test(m_h2))
-
-ggsave(
-  filename = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-  ),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-  ),
-  outfile = here(
-    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-  ),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here(
-  "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
-))
-```

### 2022-10-25 analysis/paper/supplementary_materials.Rmd
Add effect sizes to supplementary tables

@@
 load(here("inst/extdata/m_f1_report.Rda"))
+load(here("inst/extdata/m_f1_es.Rda"))
 load(here("inst/extdata/m_f2.Rda"))
 load(here("inst/extdata/m_f2_report.Rda"))
+load(here("inst/extdata/m_f2_es.Rda"))
 
@@
 load(here("inst/extdata/m_g1_report.Rda"))
-
+load(here("inst/extdata/m_g1_es.Rda"))
 load(here("inst/extdata/m_g2.Rda"))
 load(here("inst/extdata/m_g2_report.Rda"))
+load(here("inst/extdata/m_g2_es.Rda"))
 
@@
 load(here("inst/extdata/m_h1_report.Rda"))
+load(here("inst/extdata/m_h1_es.Rda"))
 load(here("inst/extdata/m_h2.Rda"))
 load(here("inst/extdata/m_h2_report.Rda"))
+load(here("inst/extdata/m_h2_es.Rda"))
 ```
@@
 ```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+m_f1_es <- c(m_f1_es, rep(NA, nrow(as_tibble(m_f1_report)) - length(m_f1_es)))
+m_f1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_f1_es))
+
 as_tibble(m_f1_report) %>%
+  bind_cols(m_f1_es) %>%
+  rename("Effect Size" = "...10") %>% 
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
@@
 ```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+m_f2_es <- c(m_f2_es, rep(NA, nrow(as_tibble(m_f2_report)) - length(m_f2_es)))
+m_f2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_f2_es))
+
 as_tibble(m_f2_report) %>%
+  bind_cols(m_f2_es) %>%
+  rename("Effect Size" = "...10") %>% 
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
@@
 ```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+m_g1_es <- c(m_g1_es, rep(NA, nrow(as_tibble(m_g1_report)) - length(m_g1_es)))
+m_g1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g1_es))
+
 as_tibble(m_g1_report) %>%
+  bind_cols(m_g1_es) %>%
+  rename("Effect Size" = "...10") %>% 
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
@@
 ```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+m_g2_es <- c(m_g2_es, rep(NA, nrow(as_tibble(m_g2_report)) - length(m_g2_es)))
+m_g2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g2_es))
+
 as_tibble(m_g2_report) %>%
+  bind_cols(m_g2_es) %>%
+  rename("Effect Size" = "...10") %>% 
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
@@
 ```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+m_h1_es <- c(m_h1_es, rep(NA, nrow(as_tibble(m_h1_report)) - length(m_h1_es)))
+m_h1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_h1_es))
+
 as_tibble(m_h1_report) %>%
+  bind_cols(m_h1_es) %>%
+  rename("Effect Size" = "...10") %>% 
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
@@
 ```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
+m_h2_es <- c(m_h2_es, rep(NA, nrow(as_tibble(m_h2_report)) - length(m_h2_es)))
+m_h2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_h2_es))
+
 as_tibble(m_h2_report) %>%
+  bind_cols(m_h2_es) %>%
+  rename("Effect Size" = "...10") %>% 
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%

### 2022-10-25 analysis/paper/paper.Rmd
Clean up figure cross-refs, removing supplementary figs

@@
 
-There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
-
-When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B, Table S2, Figure S3).
+There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1).
+
+When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B, Table S2).
 
@@
 
-There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
-
-However, the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
+There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A, Table S3).
+
+However, the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4).
 The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
@@
 
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6; Figures S6, S7).
+There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6).
 

### 2022-10-25 analysis/paper/supplementary_materials.Rmd
Remove LOOIC, ESS, etc. from supplementary tables

--- 2022-10-24 analysis/paper/supplementary_materials.Rmd
@@
 ```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_f1_report) %>%
+m_f1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_f1_es))
+
+as_tibble(m_f1_report)[1:length(m_f1_es), ] %>%
+  bind_cols(m_f1_es) %>%
+  filter(
+    Parameter != "Intercept[1]" &
+      Parameter != "Intercept[2]"
+  ) %>%
+  rename("Effect Size" = "...10") %>%
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
   filter(!is.na(Parameter)) %>%
+  select(-Fit) %>%
   mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
@@
 ```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_f2_report) %>%
+m_f2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_f2_es))
+
+as_tibble(m_f2_report)[1:length(m_f2_es), ] %>%
+  bind_cols(m_f2_es) %>%
+  filter(
+    Parameter != "Intercept[1]" &
+      Parameter != "Intercept[2]" &
+      Parameter != "Intercept[3]"
+  ) %>%
+  rename("Effect Size" = "...10") %>%
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
   filter(!is.na(Parameter)) %>%
+  select(-Fit) %>%
   mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
@@
 ```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_g1_report) %>%
+m_g1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g1_es))
+
+as_tibble(m_g1_report)[1:length(m_g1_es), ] %>%
+  bind_cols(m_g1_es) %>%
+  filter(
+    Parameter != "Intercept[1]" &
+      Parameter != "Intercept[2]"
+  ) %>%
+  rename("Effect Size" = "...10") %>%
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
   filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
+  select(-Fit) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
   rename("CI\nLow" = "CI_low",
@@
 ```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_g2_report) %>%
+m_g2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g2_es))
+
+as_tibble(m_g2_report)[1:length(m_g2_es), ] %>%
+  bind_cols(m_g2_es) %>%
+  filter(
+    Parameter != "Intercept[1]" &
+      Parameter != "Intercept[2]" &
+      Parameter != "Intercept[3]"
+  ) %>%
+  rename("Effect Size" = "...10") %>%
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
   filter(!is.na(Parameter)) %>%
-  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
+  select(-Fit) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
   rename("CI\nLow" = "CI_low",
@@
 ```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_h1_report) %>%
+m_h1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_h1_es))
+
+as_tibble(m_h1_report)[1:length(m_h1_es), ] %>%
+  bind_cols(m_h1_es) %>%
+  filter(
+    Parameter != "Intercept[1]" &
+      Parameter != "Intercept[2]"
+  ) %>%
+  rename("Effect Size" = "...10") %>%
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
   filter(!is.na(Parameter)) %>%
+  select(-Fit) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
   rename("CI\nLow" = "CI_low",
@@
 ```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-as_tibble(m_h2_report) %>%
+m_g2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g2_es))
+
+as_tibble(m_g2_report)[1:length(m_g2_es), ] %>%
+  bind_cols(m_g2_es) %>%
+  filter(
+    Parameter != "Intercept[1]" &
+      Parameter != "Intercept[2]" &
+      Parameter != "Intercept[3]"
+  ) %>%
+  rename("Effect Size" = "...10") %>%
+  relocate("Effect Size", .before = Fit) %>%
   filter(!grepl("R2", Parameter)) %>%
   filter(!is.na(Parameter)) %>%
+  select(-Fit) %>%
+  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
   rename("CI\nLow" = "CI_low",

### 2022-10-25 analysis/paper/paper.Rmd
Reflow Examples and Efforts section of discussion

@@
 Plant pathology is not alone in the lack of reproducibility and the closed-nature of data and code.
-In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
-Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
-@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
-@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
-Fernandez2022 provide an R package, 'cndcR', that supports the manuscript: "Dataset characteristics for the determination of critical nitrogen dilution curves: from the past to new guidelines", [Fernandez2022a].
-The package contains source data and R code that @Fernandez2022a used for their sensitivity analyses when fitting critical N dilution curves in crop species using Bayesian models. 
-The package allows the user to recreate the figures in the manuscript and includes the all of the data files required to produce all results and figures presented in the manuscript.
-More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
-However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
-
-@Seibold2021 investigated the types of methods and software used in PLOS ONE articles and whether the were able to reproduce the data analysis using open source software for papers that dealt with longitudinal data and used mixed effect models or generalized estimating equations for analysis and provided the data.
+
+@Seibold2021 carried out a similar study on the types of methods and software used in PLOS ONE articles and whether the were able to reproduce the data analysis using open source software for papers that dealt with longitudinal data and used mixed effect models or generalized estimating equations for analysis and provided the data.
 They found that most articles provided tables and visualisations only.
@@
 Their main conclusion was that reproducing papers is difficult if no code is provided and puts an undue burden on those interested in reproducing the work.
+
+Other disciplines related to plant pathology have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
+Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
+@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
+@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
+@Fernandez2022 provide an R package, 'cndcR', that supports the manuscript: "Dataset characteristics for the determination of critical nitrogen dilution curves: from the past to new guidelines", [Fernandez2022a].
+The package contains source data and R code that @Fernandez2022a used for their sensitivity analyses when fitting critical N dilution curves in crop species using Bayesian models. 
+The package allows the user to recreate the figures in the manuscript and includes the all of the data files required to produce all results and figures presented in the manuscript.
+More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
+However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
 

### 2022-10-25 analysis/paper/paper.Rmd
clarify how predictors were treated

@@
 Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
-Models 1 and 2 were used to predict responses with publishing journal, using the journals' abbreviation as the predictor (formula: response \~ abbreviation).
-Models 3 and 4 were used to predict the two responses with year as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)).
-Models 5 and 6 were used to predict the responses using IF_5year as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) and included assignee as random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
+Models 1 and 2 were used to predict responses with publishing journal, using a factor, the journals' abbreviation, as the predictor (formula: response \~ abbreviation).
+Models 3 and 4 were used to predict the two responses with a continuous value, year, as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)) to detect changes that occurred over the years in which the manuscripts were published that were included.
+Models 5 and 6 were used to predict the responses using a continuous value, IF_5year, as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) and included assignee as random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
 All models included the assigned article evaluator as a random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) to address inter-rater effects on scoring.

### 2022-10-25 analysis/paper/paper.Rmd
Correct tense in writing

@@
 The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) had a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83% of being large (\> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19017).
+The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 19017).
 
@@
 The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
-The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 21692).
+The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).
 

### 2022-10-25 analysis/paper/paper.Rmd
Update caption to match the figure

@@
 ```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
-A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared.
-A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared.
+A test for practical equivalence was unable to detect an effect of year of publication on computational materials (code) being shared.
+A test for practical equivalence found that there was no effect of year of publication on the availability of supporting data.
 The region of practical equivalence (ROPE) is shown between two dotted lines.

### 2022-10-25 analysis/paper/paper.Rmd
Use ";" not "," between refs to tables and figs

@@
 
-When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B, Table S2).
+When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B; Table S2).
 
@@
 
-There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A, Table S3).
-
-However, the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4).
+There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A; Table S3).
+
+However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4).
+
 The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).

### 2022-10-25 analysis/paper/paper.Rmd
Revise Discussion

@@
 Code sharing was extremely rare, but in cases where it was shared, most were included as a part of the journal article's publication as extra materials rather than through data repositories.
-Authors publishing in *Phytopathologia Mediterranea* were more likely than articles published in *Phytopathology*® to share data.
-Several articles published in this journal either made the data available through GenBank or it was noted that all data were available through the article and associated supplementary materials.
-The journal ranking highest for sharing data, *Phytopathologia Mediterranea*, did not have any articles that were sampled in 2018 (Table \@ref(tab:journals)).
-There is no clear reason for the year 2018 to have more data shared than other years other than random chance that we found.
+Authors publishing in *Phytopathologia Mediterranea* were more likely than authors publishing in *Phytopathology*® to share data.
+Several articles published in t*Phytopathologia Mediterranea* either made the data available through GenBank or it was noted that all data were available through the article and associated supplementary materials, which may be the reason for this effect.
+
 The reasons for not sharing code or data were not clearly available from the papers themselves and so this work was unable to determine possible reasons for this situation.

### 2022-10-25 analysis/paper/paper.Rmd
Edit Description for flow

@@
 The second layer is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or some other long-term repository as provided by an institutional library, Zenodo, FigShare, etc.
-Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
+Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here and this illustrates that simply depositing code and data in repositories is not enough.
+Efforts must be made to annotate and structure the raw data to make it FAIR (Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016].
+Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
+Further, fully documenting the code used for the analysis is necessary for other researchers to fully use and understand.
 
@@
 While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
-
-Simply depositing code and data in repositories is not enough.
-Efforts must be made to annotate and structure the raw data to make it FAIR (Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016].
-Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
-Further, fully documenting the code used for the analysis is necessary for other researchers to fully use and understand.
 

### 2022-10-25 analysis/paper/paper.Rmd
Clean up legend for figure 4

@@
     axis.title.x = element_blank(),
-    legend.box.spacing = unit(40, "pt")
+    legend.box.spacing = unit(40, "pt"),
+    legend.position = "bottom",
+    legend.justification = "right",
+    legend.margin = margin(r = -5)
   ) +
@@
     legend.title = element_blank(),
-    legend.box.spacing = unit(40, "pt")
+    legend.box.spacing = unit(40, "pt"),
+    legend.position = "bottom",
+    legend.justification = "left",
+    legend.margin = margin(l = -5)
   ) +

### 2022-10-25 analysis/paper/paper.Rmd
spelling correction

@@
 We believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
-For example, between complicated analyzes, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce our work quickly and easily.
+For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce our work quickly and easily.
 This manuscript was drafted over the course of several years as the authors had time to devote to it.

### 2022-10-25 analysis/paper/paper.Rmd
Restructure Discussion for clarity and flow

@@
 The package allows the user to recreate the figures in the manuscript and includes the all of the data files required to produce all results and figures presented in the manuscript.
-More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
+More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish Findable, Accessible, Interoperable and Reusable (FAIR) data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
 However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
 
-## Examples of Different Layers for Improving Reproducibility
-
-There are different ways to make research more open and reproducible.
-These can be thought of as layers of reproducibility.
-If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, writing the manuscript then the next logical steps are depositing any code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
+## Suggestions for Improving Computational Reproducibility
+
+While sharing code and data for computational reproducibility is important, it is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
+When making science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
+Provide a full description of all equipment used, e.g., "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
+This allows end-users to identify what was used and identify the methods used more accurately.
+Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
+This also helps to ensure that researchers can reconstruct what they did more easily since good notes exist and documentation and be able to identify if something changes, e.g., a package version, what effect it had on the research.
+
+To help create a good set of data and code that can easily be shared, the use of programming or scripting languages such as R, Julia, SAS or Python enables us scientists to keep very detailed records of what was computationally performed.
+This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
+Text files for saving small sets of data are preferable.
+Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
+In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, e.g., comma separated (CSV) or tab separated (TSV) files.
+This also helps to ensure that the data are reusable.
+Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
+Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
+While databases may offer many advantages for speed and data integrity, the trade-off is that they are more complex to set up and administer, especially for a small data set.
+
+Ideally, once the data are complete, best practices for keeping our data as we perform our work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
+It should be noted that the use of a database management system also allows for both at the expense of added complexity.
+Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
+Unexpected changes to values in the data [@Ziemann2016] may also occur when using proprietary formats.
+
+Once these practices are in place, sharing the code and data becomes easier and can be thought of as a layered approach to computational reproducibility.
+
+Proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
+Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
+Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
+That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.
+
+If steps are followed to make the data FAIR, then it will be readable by humans and machines alike and this will help support discoveries and support further research.
+In turn, sharing data can lead to new citations for the work as others discover and use it.
+To make data the most widely discoverable and usable, ensure that it has a persistent identifier.
+A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but the Handle.Net Registry (HNR) (<https://handle.net/>) is also an option.
+There are different options for generating a DOI for our data and other materials.
+FigShare, Zenodo and OSF.io all offer persistent archives along with a service to generate a DOI for our materials.
+The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
+For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.
+
+Once it has been determined how to best manage the source code and the data sets for analysis, the next step is to consider how to share the data.
+Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and provide metadata and generate a DOI for sharing the project once it is finished.
+Other providers exist that allow for us to not only track changes but also to share the data openly, these include GitHub, Gitlab and Bitbucket and GitHub is arguably the most popular and widely used open-source software development platform currently.
+However, we would advise against the practice of depositing data on a laboratory website or a site such as GitHub only as these are not an optimal way to preserve and share our work over the long term.
+Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
+It is a best practice to always ensure that we have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF.io and generated a DOI for the materials to help ensure continued accessibility.
+Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
+If readers are uncertain, we suggest to also consult with local librarians about possible resources.
+Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development or data repositories as well.
+The important aspect is that data once deposited cannot be modified any more.
+
+Once these points have been addressed, if a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, writing the manuscript then the next logical steps are depositing any code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 Here we define three layers of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
@@
 Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here and this illustrates that simply depositing code and data in repositories is not enough.
-Efforts must be made to annotate and structure the raw data to make it FAIR (Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016].
+Efforts must be made to annotate and structure the raw data to make it FAIR [@Wilkinson2016].
 Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
@@
 
-The third layer is the use of proper code repositories such as a library resource, or code repository (e.g.
-GitHub or GitLab) and data repositories (e.g., FigShare, Zenodo or OSF.io), allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
+The third layer is the use of proper code repositories such as a library resource, or code repository (e.g., GitHub or GitLab) and data repositories (e.g., FigShare, Zenodo or OSF.io), allowing for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation.
 As an example, Sparks et al.
@@
 While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
-
-Proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
-Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
-Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
-That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.
-
-The first layer, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-When making science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
-Provide a full description of all equipment used, e.g., "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
-This allows end-users to identify what was used and identify the methods used more accurately.
-Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
-This also helps to ensure that researchers can reconstruct what they did more easily since good notes exist and documentation and be able to identify if something changes, e.g., a package version, what effect it had on the research.
-
-The use of programming or scripting languages such as R, Julia, SAS or Python enables us scientists to keep very detailed records of what was computationally performed.
-This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
-
-Text files for saving small sets of data are preferable.
-Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
-In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, e.g., comma separated (CSV) or tab separated (TSV) files.
-This also helps to ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
-Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
-While databases may offer many advantages for speed and data integrity, the trade-off is that they are more complex to set up and administer, especially for a small data set.
-
-Ideally, once the data are complete, best practices for keeping our data as we perform our work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
-It should be noted that the use of a database management system also allows for both at the expense of added complexity.
-Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
-Unexpected changes to values in the data [@Ziemann2016] may also occur when using proprietary formats.
-
-If steps are followed to make the data FAIR, then it will be readable by humans and machines alike and this will help support discoveries and support further research.
-In turn, sharing data will lead to new citations for our work as others discover and use it.
-To make our data the most widely discoverable and usable, ensure that it has a persistent identifier.
-A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but the Handle.Net Registry (HNR) (<https://handle.net/>) is also an option.
-There are different options for generating a DOI for our data and other materials.
-FigShare, Zenodo and OSF.io all offer persistent archives along with a service to generate a DOI for our materials.
-The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
-For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.
-
-Once it has been determined how to best manage the source code and the data sets for analysis, the next step is to consider how to share the data.
-Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and provide metadata and generate a DOI for sharing the project once it is finished.
-
-Other providers exist that allow for us to not only track changes but also to share the data openly, these include GitHub, Gitlab and Bitbucket.
-GitHub is arguably the most popular and widely used software development platform currently.
-Data that is encoded in CSV or other plain text formats can easily be deposited in a repository along with code for analysis to enable tracking of changes and other users to download and replicate the work.
-
-We would advise against the practice of depositing data on a laboratory website or a site such as GitHub only as these are not an optimal way to preserve and share our work over the long term.
-Doing either of these leaves the work in an unstable state where future users may be unable to access the work as they are fraught with link-rot and other issues.
-It is a best practice to always ensure that we have deposited the data with a provider such as GenBank, Zenodo, FigShare or OSF.io and generated a DOI for the materials to help ensure continued accessibility.
-Many of these providers provide rather easy ways to link the project with a software development repository to help ensure that the data are available in perpetuity.
-If readers are uncertain, we suggest to also consult with local librarians about possible resources.
-Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development or data repositories as well.
-The important aspect is that data once deposited cannot be modified any more.
 

### 2022-10-25 analysis/paper/paper.Rmd
Update Fernandez citations

@@
 @Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
-@Fernandez2022 provide an R package, 'cndcR', that supports the manuscript: "Dataset characteristics for the determination of critical nitrogen dilution curves: from the past to new guidelines", [Fernandez2022a].
+@Fernandez2022 provide an R package, 'cndcR' [@Fernandez2022b], that supports the manuscript: "Dataset characteristics for the determination of critical nitrogen dilution curves: from the past to new guidelines", [@Fernandez2022a].
 The package contains source data and R code that @Fernandez2022a used for their sensitivity analyses when fitting critical N dilution curves in crop species using Bayesian models. 

### 2022-10-28 analysis/paper/paper.Rmd
Update Nik's affiliations`

@@
   - Zachary S. L. Foster:
-      institute: OSU
+      institute: ARS
   - Niklaus J. Grünwald:
@@
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
-  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
-  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
+  - ARS: Horticultural Crops Disease and Pest Management Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
 output: 

### 2022-10-28 analysis/paper/paper.Rmd
Remove "do" from title
implement Nik and Emerson's edits

@@
 ---
-title: "Openness and computational reproducibility in plant pathology: where do we stand and a way forward"
+title: "Openness and computational reproducibility in plant pathology: where we stand and a way forward"
 author:
@@
 Open research practices have been highlighted extensively during the last ten years in many fields of scientific study as essential standards needed to promote transparency and reproducibility of scientific results.
-Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyzes were conducted.
+Scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses were conducted.
 Openly sharing protocols, data and computational code is central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow.
@@
 We propose that use of open-source tools facilitates computationally reproducible work and analyses benefitting not just readers, but the authors as well.
-Finally, we provide ideas and tools to promote open, reproducible computational research practices among plant pathologists.
+Finally, we provide ideas and suggest tools to promote open, reproducible computational research practices among plant pathologists.
 
@@
 Reproducibility is one component under the umbrella of open science.
-By proactively practising open science, the work increases the chance to become more reproducible through the availability of data and code.
+By proactively practicing open science, the work increases the chance to become more reproducible through the availability of data and code.
 That is, open science enables reproducibility and replicability.
 
-For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
+To discuss the topic, it helps to first define what we mean so that we may clearly communicate.
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
@@
 In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing.
-One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyzes".
+One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
 > @Peng2009.
@@
 
-Therefore, our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyzes or for use in instructional purposes.
+Therefore, our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes.
 And that the software used are also easily obtained and preferably open-source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats.
@@
 
-To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swath of publications to evaluate our collective status.
-We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, e.g., quartile range or citation index, to represent the discipline.
+To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles representing a wide swath of publications to evaluate our collective status.
+We hand-picked 21 journals which represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, including applied and fundamental work, country of origin and ranking metrics, e.g., quartile range or citation index.
 The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
 From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
-Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
+Using R [@RCT2022], two lists were created.
+The first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
 Initially there were four evaluators, later a fifth was added and the list was recreated.
@@
 
-A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for each sampling event.
+A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of 21 journals for each sampling event.
 This was done to ensure that the the randomly generated number had a corresponding number in the journal.
@@
 For example, a reviewer noted that all data were deposited in GenBank but the data score was '0', this was changed to '3' to align with the definition.
-Or in other cases, some software packages used were Excel add-ins but Excel was not recorded as being used; Excel was added to the list of software used to rectify this.
+Or in other cases, some software packages used were Excel add-ins, but Excel was not recorded as being used; Excel was added to the list of software used to rectify this.
 
@@
 We fit Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
-The cumulative logit family is often used for ordinal data as it uses cumulative probabilities up to a threshold, making all of the of ordinal categories binary at that threshold.
+The cumulative logit family is often used for ordinal data as it uses cumulative probabilities up to a threshold, making all of the ordinal categories binary at that threshold.
 Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
@@
 The remainder of the top ten programs we found were mostly related to sequence analysis, *i.e.*, Clustal (`r scales::ordinal(which(tab_s == "CLUSTAL"))`), BLAST (`r scales::ordinal(which(tab_s == "BLAST"))`), and BioEdit (9th) or phylogenetic analysis MrBayes (8th), tied with the most general-purpose software cited in the top 10, Excel®.
-In tenth place was FigTree, used for phylogenetic trees.
+In tenth place was FigTree, used for rendering phylogenetic trees.
 The Python programming language was cited only twice.
@@
 Except for a few isolated cases, most papers were not fully computationally reproducible.
-Very few authors choose to share both data and code.
+Very few authors chose to share both data and code.
 More authors shared data due to journal requirements to share sequence data, but other types of data related to field experiments or other laboratory studies were not likely to be shared.
@@
 Authors publishing in *Phytopathologia Mediterranea* were more likely than authors publishing in *Phytopathology*® to share data.
-Several articles published in t*Phytopathologia Mediterranea* either made the data available through GenBank or it was noted that all data were available through the article and associated supplementary materials, which may be the reason for this effect.
+Several articles published in *Phytopathologia Mediterranea* either made the data available through GenBank or it was noted that all data were available through the article and associated supplementary materials, which may be the reason for this effect.
 
@@
 This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
-In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.
+Despite some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.
 
@@
 @Seibold2021 carried out a similar study on the types of methods and software used in PLOS ONE articles and whether the were able to reproduce the data analysis using open source software for papers that dealt with longitudinal data and used mixed effect models or generalized estimating equations for analysis and provided the data.
-They found that most articles provided tables and visualisations only.
+They found that most articles provided tables and visualizations only.
 However, unlike our analysis, even with the data being supplied they found that only one article used open source software, whereas R prominently featured in the articles we examined along with other free open-source software packages.
@@
 The first layer is including tables of raw data or code with the paper as a supplemental file or even within the paper as tables where possible.
-This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyzes where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
+This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
 @Hill2019 also shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
@@
 
-Taking this approach even further, packaging the full analysis in a containerized software application, e.g., Docker is a way to help ensure computational reproducibility but at the expense of added complexity.
-Docker is an open-source containerization platform that enables users to package several applications and an operating system into containers, thereby standardizing the executable components by combining application source code (or analyzes) with the operating system required to run that analysis on a user's computer.
+Taking this approach even further, packaging the full analysis in a containerized software application, e.g., Docker is a way to help ensure computational reproducibility but at the expense of added complexity [@Merkel2014].
+Docker is an open-source containerization platform that enables users to package several applications and an operating system into containers, thereby standardizing the executable components by combining application source code (or analyses) with the operating system required to run that analysis on a user's computer.
 However, there are drawbacks to using Docker.
@@
 If they have the ability to start with depositing the computational materials and data and generating DOIs all parties will benefit from it.
-However, we recognise that these steps may not be appropriate or attractive for various reasons and so have detailed other layers that improve openness and reproducibility.
+However, we recognize that these steps may not be appropriate or attractive for various reasons and so have detailed other layers that improve openness and reproducibility.
 
@@
 
-All code used in the analyzes and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
+All code used in the analyses and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
 A webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.
@@
   set_caption(
-    "Journal titles selected for inclusion representing 21 plant pathology journals or specialised journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
+    "Journal titles selected for inclusion representing 21 plant pathology journals or specialized journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
   )
@@
 
-```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
+```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the effect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public.
 A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code).
-However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*&reg;.
+However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely to have data available than articles found in *Phytopathology*&reg;.
 Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;.
@@
 If the entire distribution falls outside the ROPE, the hypothesis is rejected.
-In some cases the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
+In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
 m_f1_eq <- equivalence_test(m_f1, rule = "bayes")
@@
 
-```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
+```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the effect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.
 A test for practical equivalence was unable to detect an effect of year of publication on computational materials (code) being shared.
@@
 If the entire distribution falls outside the ROPE, the hypothesis is rejected.
-In some cases the data do not provide a definitive answer and the decision on H0 is undecided.
-Here, year is treated as a continous variable to determine if there are changes over time in the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
+In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.
+Here, year is treated as a continuous variable to determine if there are changes over time in the likelihood of sharing code and data.', cache=FALSE, fig.env='figure'}
 
@@
 If the entire distribution falls outside the ROPE, the hypothesis is rejected.
-In some cases the data do not provide a definitive answer and the decision on H0 is undecided.
-Here, impact factor is a continous variable to determine if greater or lesser impact factor values affect the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
+In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.
+Here, impact factor is a continuous variable to determine if greater or lesser impact factor values affect the likelihood of sharing code and data.', cache=FALSE, fig.env='figure'}
 m_h1_eq <- equivalence_test(m_h1, rule = "bayes")

### 2022-10-28 analysis/paper/paper.Rmd
Incorporate Zach's changes and a few others I found

@@
 Collectively, they contribute to increasing our basic and applied knowledge of several aspects of pathogen biology and disease development to ultimately improve plant disease management.
-Scientific research in the field varies from the purely observational or descriptive nature to inferential, based on experimental or simulation-derived data sets.
-Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of the methods and results.
-These research findings include biological materials (host and pathogen genotypes), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated during the research activities.
-
-Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@Barton2022].
+Scientific research in the field varies from the purely observational or descriptive in nature to inferential (based on experimental or simulation-derived data sets).
+Whatever the case, the verifiability of research findings depends on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of the methods and results.
+Examples of such resources include biological materials (host and pathogen genotypes), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code.
+
+Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022].
+Journals in the field are promoting the sharing of data [@DelPonte2020], and more scientists are becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make published work less useful [@Barton2022].
 
 Reproducibility is one component under the umbrella of open science.
-By proactively practicing open science, the work increases the chance to become more reproducible through the availability of data and code.
+By proactively practicing open science, scientists increase the chance that their works become more reproducible due to the availability of data and code.
 That is, open science enables reproducibility and replicability.
 
-To discuss the topic, it helps to first define what we mean so that we may clearly communicate.
+To ensure clear communication on this topic, we first must define terms like reproducibility. 
 Many of the terms used in this area have varying definitions that may or may not agree with each other.
@@
 
-In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, e.g., field trials that span years and locations or complex glasshouse experiments.
+However, in the biological sciences it is not always possible to use identical test material or environmental conditions, e.g., field trials that span years and locations or complex glasshouse experiments.
+In other cases there is insufficient time and resources to reproduce the entire study.
 Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":
@@
 
-Therefore, our definition of reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes.
-And that the software used are also easily obtained and preferably open-source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats.
+Therefore, our definition of computational reproducibility will be that the computer code and data are made freely available to others for verification and conducting alternate analyses or for use in instructional purposes.
+In addition, the software used should be easily obtained and preferably open-source to avoid licensing or other issues related to accessibility for end-users related to costs or non-standard file formats.
+
+Plant pathologists often provide information on protocols and chemicals allowing for reproducibility.
+However, biological specimens such as strains, cultures or cultivars are often not available after publication.
+These cases do constitute a lack of reproducibility but will not be covered here.
 
@@
 There were three evaluation events that took place to increase the yearly coverage of the evaluations.
-During each scoring event, each evaluator was randomly assigned 50 unique articles to evaluate during an evaluation event.
+During each scoring event, each evaluator was randomly assigned 50 unique articles to evaluate.
 
 A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of 21 journals for each sampling event.
-This was done to ensure that the the randomly generated number had a corresponding number in the journal.
+This was done to ensure that the randomly generated number had a corresponding number in the journal.
+
+A Google Sheets file was created to hold the article details and metadata for the paper's authors to refer in finding their assigned articles.
+The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate and entered in the spreadsheet with the article details for the respective journals.
+The authors entered article scores and comments about the article in a separate spreadsheet in the Google Sheets file to keep the original details intact and avoid overwriting or making possible errors that would lead to the loss of data.
+The entire workbook was downloaded and saved as an Open Document Spreadsheet (ODS) file for analysis after all the values were recorded.
 
@@
 
-Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomized list of journal articles using scoring criteria devised for the purposes of this research in each of the three different scoring events as their time allowed for their participation.
+During three scoring events, two to five of this paper's authors were each assigned to rate a randomized list of journal articles using scoring criteria devised for the purposes of this research as their time allowed for their participation.
 In the first event, three authors (AS, EDP, and ZF) evaluated a total of 200 unique articles, in the second event two authors evaluated a total of 100 unique articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated a total of 150 unique articles for a total of 450 articles.
@@
 ## Scoring Criteria
-
-The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
-This was downloaded, saved as an Open Document Spreadsheet (ODS) file for analysis.
 
@@
 
-For the purposes of this research paper, the word "code" in "code availability" was defined as including any materials that were used in the data import, cleaning, analysis, genome assembly or manuscript preparation or in the case of modelling papers, the model's software code itself.
+For the purposes of this research paper, the word "code" in "code availability" was defined as including any software that were used in the data import, cleaning, analysis, genome assembly or manuscript preparation or in the case of modelling papers, the model's software code itself.
 The word "data" in "data availability" was defined as including any data created or collected and presented in the research manuscript.
@@
 
-While sharing code and data for computational reproducibility is important, it is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
-When making science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
-Provide a full description of all equipment used, e.g., "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
-This allows end-users to identify what was used and identify the methods used more accurately.
+When making science more open and computationally reproducible, methods and software used (e.g.
+R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
+Provide a full description of all equipment used, e.g., “a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals”.
+This allows end-users to identify the tools and methods used more accurately.
 Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
-This also helps to ensure that researchers can reconstruct what they did more easily since good notes exist and documentation and be able to identify if something changes, e.g., a package version, what effect it had on the research.
+This also helps to ensure that researchers can reconstruct what they did more easily since good notes and documentation exist and be able to identify if something changes, e.g., a package version, what effect it had on the research.
 
@@
 This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
-Text files for saving small sets of data are preferable.
+Text files for saving small sets of data are preferable to proprietary file formats.
 Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
@@
 This also helps to ensure that the data are reusable.
-Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefits but two important benefits to mention here are (i) data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
-Databases such a GenBank are preferable for molecular data ensuring data integrity and machine readability.
-While databases may offer many advantages for speed and data integrity, the trade-off is that they are more complex to set up and administer, especially for a small data set.
+Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefit.
+Two important benefits to mention here are (i) avoiding data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
+Databases such as GenBank are preferable for molecular data and ensure data integrity and machine readability.
+While databases may offer many advantages such as speed and data integrity, they are also more complex to set up and administer, and so they may not be the best choice for a small data set.
 
@@
 A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but the Handle.Net Registry (HNR) (<https://handle.net/>) is also an option.
-There are different options for generating a DOI for our data and other materials.
-FigShare, Zenodo and OSF.io all offer persistent archives along with a service to generate a DOI for our materials.
+There are different options for generating a DOI for data and other materials.
+FigShare, Zenodo and OSF.io all offer persistent archives along with a service to generate a DOI.
 The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
@@
 Once it has been determined how to best manage the source code and the data sets for analysis, the next step is to consider how to share the data.
-Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and provide metadata and generate a DOI for sharing the project once it is finished.
-Other providers exist that allow for us to not only track changes but also to share the data openly, these include GitHub, Gitlab and Bitbucket and GitHub is arguably the most popular and widely used open-source software development platform currently.
+Providers such as FigShare, Dataverse, OSF.io and Zenodo allow us to deposit our data and provide metadata and generate a DOI for sharing the project once it is finished.
+Other providers exist that allow for us to not only track changes but also to share the data openly.
+These include GitHub, Gitlab and Bitbucket.
+GitHub is arguably the most popular and widely used open-source software development platform currently.
 However, we would advise against the practice of depositing data on a laboratory website or a site such as GitHub only as these are not an optimal way to preserve and share our work over the long term.
@@
 Most universities and other research-focused workplaces provide a facility for staff to deposit papers and other academic materials, but this may extend to software development or data repositories as well.
-The important aspect is that data once deposited cannot be modified any more.
-
-Once these points have been addressed, if a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, writing the manuscript then the next logical steps are depositing any code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
+It is important that data once deposited cannot be modified.
+
+If a general workflow for producing academic research involves defining a research question, obtaining data for testing the hypothesis, analyzing, summarizing and presenting data and results, and writing the manuscript, then the next logical steps are depositing any code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
 Here we define three layers of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.
@@
 The second layer is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or some other long-term repository as provided by an institutional library, Zenodo, FigShare, etc.
-Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here and this illustrates that simply depositing code and data in repositories is not enough.
+Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>), but we were unable to find a DOI that refers to these materials or a citation to properly cite them here and this illustrates that simply depositing code and data in repositories is not enough.
 Efforts must be made to annotate and structure the raw data to make it FAIR [@Wilkinson2016].
@@
 As an example, Sparks et al.
-[-@Sparks2011; -@Sparks2014, @Sparks2016] used FigShare to provide models, data and code necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
+[-@Sparks2011; -@Sparks2014; -@Sparks2016] used FigShare to provide models, data and code necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
 Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
@@
 
-Taking this approach even further, packaging the full analysis in a containerized software application, e.g., Docker is a way to help ensure computational reproducibility but at the expense of added complexity [@Merkel2014].
+Taking this approach even further, packaging the full analysis in a containerized software application (Docker) is a way to help ensure computational reproducibility but at the expense of added complexity [@Merkel2014].
 Docker is an open-source containerization platform that enables users to package several applications and an operating system into containers, thereby standardizing the executable components by combining application source code (or analyses) with the operating system required to run that analysis on a user's computer.

### 2022-10-28 analysis/paper/supplementary_materials.Rmd
Correct captions in supp materials

@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of journal title on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of the year of publication on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of the year of publication on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of five-year impact factor on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of five-year impact factor on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
@@
   set_caption(
-    "Full description of model fit for the effect of five-year impact factor on data availability.
+    "Full description of model fit for the affect of five-year impact factor on data availability.
 Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

### 2022-10-28 analysis/paper/paper.Rmd
Edit for clarity

@@
 
-To help create a good set of data and code that can easily be shared, the use of programming or scripting languages such as R, Julia, SAS or Python enables us scientists to keep very detailed records of what was computationally performed.
+To help create a good set of data and code that can easily be shared, the use of programming or scripting languages such as R, Julia, SAS or Python enables us to keep very detailed records of what was computationally performed.
 This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.

### 2022-10-28 analysis/paper/paper.Rmd
standardise libs between documents

@@
   "officer",
+  "parameters",
   "patchwork",
-  "parameters",
   "posterior",
   "report",
+  "rope",
   "rsvg",
-  "rstan",
   "tidyr",

### 2022-10-28 analysis/paper/paper.Rmd
Add computational details about the paper itself
Clarify closing statment

@@
 Without the code used to generate the paper and the data that were gathered for the paper, we as a community cannot adequately evaluate the work as it is presented.
-That is, while we may be standing on the shoulders of giants in doing our work, we cannot see where they have been to do our work, which hinders our efforts to be able to see farther ahead.
+So, while we may be standing on the shoulders of giants as we are doing our work, when we cannot see where they have been by examining the code and data, it hinders our efforts to move plant pathology forward.
 
@@
 
-# Data and Code Availability
+# Technical Details
 
@@
 A webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.
+
+## Computational Details
+
+All relevant computational information (R and package versions, operating system) are given in the Methods for the data gathering and analysis.
+The relevant details for this article itself are shown here.
+
+```{r article-details}
+pander::pander(sessionInfo())
+```
 

### 2022-10-28 analysis/paper/paper.Rmd
Remove FSI from affiliation

@@
 institute:
-  - DPIRD: Farming Systems Innovation, Department of Primary Industries and Regional Development, Perth WA 6000, Australia
+  - DPIRD: Department of Primary Industries and Regional Development, Perth WA 6000, Australia
   - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia

### 2022-10-28 analysis/paper/paper.Rmd
Reword model fitness descriptions

@@
 
-Model fitness was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
+The fitness of all models was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
 

### 2022-10-28 analysis/paper/paper.Rmd
remove unclear paragraph

@@
 We can and should embrace this and move the discipline forward and have a greater impact with our work.
-
-Without the code used to generate the paper and the data that were gathered for the paper, we as a community cannot adequately evaluate the work as it is presented.
-So, while we may be standing on the shoulders of giants as we are doing our work, when we cannot see where they have been by examining the code and data, it hinders our efforts to move plant pathology forward.
 

### 2022-10-28 analysis/paper/paper.Rmd
Remove figures from resulting doc
Having this results in duplicated figures in the proofs for review

@@
 No article scored 3 for data availability.
-Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
+The fitness was found to be good for all models.", cache=FALSE, fig.env='figure'}
 
@@
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
 ```
@@
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
 ```
@@
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
 ```
@@
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
 ```
@@
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
 ```
@@
 )
-
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
-```
+```

### 2022-10-31 README.rmd
Update address in README

@@
 Department of Primary Industries and Regional Development
-Level 6.35, 1 Nash St., Perth WA 6000
+Level 6.34, 1 Nash St., Perth WA 6000
 

### 2022-10-31 analysis/paper/paper.Rmd
Include figures to include captions
Fix caption breaking across pages and standardise template names

--- 2022-10-28 analysis/paper/paper.Rmd
@@
      number_sections: FALSE
-     reference_docx: "../templates/phytopath_template.docx"
+     reference_docx: "../templates/phytopath-template.docx"
      pandoc_args:
@@
   dev = "cairo_ps",
-  cache = FALSE
+  cache = FALSE,
+  ft.keepnext = FALSE
 )
@@
   rowwise() %>%
-  mutate(n = sum(c_across(where(is.numeric)), na.rm = T))
+  mutate(n = sum(c_across(where(is.numeric)), na.rm = TRUE))
 
@@
   set_table_properties(layout = "autofit", width = 1) %>%
-  set_caption(
-    "Journal titles selected for inclusion representing 21 plant pathology journals or specialized journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
-  )
+  set_caption("Journal titles selected for inclusion representing 21 plant pathology journals or specialized journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated.")
 ```

### 2022-10-31 analysis/paper/supplementary_materials.Rmd
Update supplementary materials, remove OSU affiliation

@@
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
-  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
   - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA

### 2022-10-31 analysis/paper/supplementary_materials.Rmd
affect > effect in captions

@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of journal title on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of the year of publication on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of the year of publication on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
@@
   set_caption(
-    "Full description of the model that was fit to scoring data, which were used to evaluate the affect of five-year impact factor on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of five-year impact factor on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
 Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
@@
   set_caption(
-    "Full description of model fit for the affect of five-year impact factor on data availability.
+    "Full description of model fit for the effect of five-year impact factor on data availability.
 Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

### 2022-10-31 analysis/paper/supplementary_materials.Rmd
Final changes for resubmission

@@
   set_caption(
+    word_stylename = "Caption",
     "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
@@
   set_caption(
+    word_stylename = "Caption",
     "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
@@
   set_caption(
+    word_stylename = "Caption",
     "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
@@
   set_caption(
+    word_stylename = "Caption",
     "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
@@
   set_caption(
+    word_stylename = "Caption",
     "Full description of the model that was fit to scoring data, which were used to evaluate the effect of five-year impact factor on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
@@
   set_caption(
+    word_stylename = "Caption",
     "Full description of model fit for the effect of five-year impact factor on data availability.

### 2023-01-03 analysis/paper/paper.Rmd
Remove redundant text
Remove more redundant text

@@
 Plant pathologists often provide information on protocols and chemicals allowing for reproducibility.
-However, biological specimens such as strains, cultures or cultivars are often not available after publication.
-These cases do constitute a lack of reproducibility but will not be covered here.
-
-Plant pathologists often provide information on protocols and chemicals allowing for reproducibility.
 However, frequently biological specimens such as strains, cultures or cultivars are not available after publication.
@@
 Models 3 and 4 were used to predict the two responses with a continuous value, year, as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)) to detect changes that occurred over the years in which the manuscripts were published that were included.
-Models 5 and 6 were used to predict the responses using a continuous value, IF_5year, as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) and included assignee as random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
+Models 5 and 6 were used to predict the responses using a continuous value, IF_5year, as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
 All models included the assigned article evaluator as a random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) to address inter-rater effects on scoring.

### 2023-01-03 analysis/paper/paper.Rmd
Correct figure order and references in text

@@
 Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the original data were not available or mentioned in the article.
-However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).
+However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)B).
 
@@
 # Figures
+
+```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the two categories evaluated, (A) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+(B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
+
+a <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
+  geom_bar(fill = "black") +
+  ylab("Count") +
+  xlab("Article Score") +
+  ggtitle("Code")
+
+b <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
+  geom_bar(fill = "black") +
+  ylab("Count") +
+  xlab("Article Score") +
+  ggtitle("Data")
+
+p <- a + b
+p <- p +
+  plot_annotation(tag_levels = "A") &
+  theme(text = element_text("Arial"))
+
+ggsave(
+  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  plot = p,
+  width = 6,
+  height = 6,
+  units = "in",
+  device = cairo_ps
+)
+embed_fonts(
+  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
+  options = "-dEPSCrop"
+)
+include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
+```
+
+\newpage
 
@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  plot = p,
-  width = 6,
-  height = 6,
-  units = "in",
-  device = cairo_ps
-)
-embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
-  options = "-dEPSCrop"
-)
-include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
-```
-
-\newpage
-
-```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the two categories evaluated, (A) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-(B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
-
-a <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
-  geom_bar(fill = "black") +
-  ylab("Count") +
-  xlab("Article Score") +
-  ggtitle("Code")
-
-b <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
-  geom_bar(fill = "black") +
-  ylab("Count") +
-  xlab("Article Score") +
-  ggtitle("Data")
-
-p <- a + b
-p <- p +
-  plot_annotation(tag_levels = "A") &
-  theme(text = element_text("Arial"))
-
-ggsave(
   filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),

### 2023-01-03 analysis/paper/paper.Rmd
replace 'two hundred fifty-five' with '255'

@@
 
-There were `r as.character(english(length(unique(rrpp_software$software_used))))` unique software applications recorded being used in the articles that were evaluated (Table \@ref(tab:software-used)).
+There were `r length(unique(rrpp_software$software_used))` unique software applications recorded being used in the articles that were evaluated (Table \@ref(tab:software-used)).
 These included desktop programs, web-based software and databases.

### 2023-01-03 analysis/paper/paper.Rmd
remove redundant 'availability'

@@
 
-When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B; Table S2).
+When predicting the availability of data as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B; Table S2).
 

### 2023-01-03 analysis/paper/supplementary_materials.Rmd
update author affiliations in supplement

@@
 institute:
-  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
+  - DPIRD: Department of Primary Industries and Regional Development, Perth WA 6000, Australia
   - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
   - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
-  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
+  - ARS: Horticultural Crops Disease and Pest Management Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
 output: 

### 2023-01-03 analysis/paper/supplementary_materials.Rmd
update supplement title

@@
 ---
-title: "Supplementary materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward'"
+title: "Supplementary materials for 'Openness and computational reproducibility in plant pathology: where we stand and a way forward'"
 author:

### 2023-01-03 analysis/paper/paper.Rmd
Clarify that much of the software in the papers examined was FOSS

@@
 
-Much of the software used are Free open-source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
+Much of the software that was used in the papers examined were Free Open-Source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
 However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.

### 2023-01-03 analysis/paper/paper.Rmd
Remove Kool et al. citation, not computational

@@
 @SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
-@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
 @Fernandez2022 provide an R package, 'cndcR' [@Fernandez2022b], that supports the manuscript: "Dataset characteristics for the determination of critical nitrogen dilution curves: from the past to new guidelines", [@Fernandez2022a].
@@
 R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
-Provide a full description of all equipment used, e.g., “a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals”.
 This allows end-users to identify the tools and methods used more accurately.
@@
 It is important that data once deposited cannot be modified.
+
+## Layered Reproducibility
 

### 2023-01-03 analysis/paper/paper.Rmd
'web' is now lowercase in common English

@@
 Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
-@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
+@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using web interfaces.
 @Fernandez2022 provide an R package, 'cndcR' [@Fernandez2022b], that supports the manuscript: "Dataset characteristics for the determination of critical nitrogen dilution curves: from the past to new guidelines", [@Fernandez2022a].

### 2023-01-03 analysis/paper/paper.Rmd
remove portion of sentence about inter-rater repeatability in the literature
escape '>' characters in text

@@
 
-The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
+The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).
@@
 We acknowledge that the number of article that are cross-scored is low.
-However, our aim was not to test inter-rater reproducibility, this is covered at length in the plant pathology literature.
+However, our aim was not to test inter-rater reproducibility.
 Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
@@
 However, we recognize that these steps may not be appropriate or attractive for various reasons and so have detailed other layers that improve openness and reproducibility.
+
+## Closing
 

### 2023-01-03 analysis/paper/paper.Rmd
Reword statistical analysis findings for clarity

@@
 
-There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A; Table S3).
-
-However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4).
-
-The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30).
+The analysis for the effect of year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A; Table S3).
+
+The null hypothesis that the year of publication had no effect on the availability of data was not rejected.
+The analysis found that there was no effect of year of publication on the availability of data (Median = 0.08, 95% CI [-8.06e-03, 0.18]) with a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30) (Figure \@ref(fig:year-parameters)B, Table S4).
 The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).
 
-There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6).
+The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6).
 

### 2023-01-03 analysis/paper/paper.Rmd
Reword statistical analysis findings for clarity again after in put from Tin
Add Tin to acknowledgements

@@
 
-The null hypothesis that the year of publication had no effect on the availability of data was not rejected.
+We failed to reject the null hypothesis that the year of publication had no effect on the availability of data.
 The analysis found that there was no effect of year of publication on the availability of data (Median = 0.08, 95% CI [-8.06e-03, 0.18]) with a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30) (Figure \@ref(fig:year-parameters)B, Table S4).
@@
 
-The authors are grateful for insightful comments from Dr David Ferris and Dr Rebecca O'Leary the USQ Centre for Crop Health Advisory Group on the final manuscript that helped improve the paper and from Ms Anna Hepworth for statistical guidance on evaluating inter-rater scores and for the comments from the anonymous reviewers and Dr Nian Wang that greatly improved the quality of this manuscript.
+The authors are grateful for insightful comments from Dr David Ferris, Dr Rebecca O'Leary, Mr Tinula Kariyawasam and the USQ Centre for Crop Health Advisory Group on the final manuscript that helped improve the paper and from Ms Anna Hepworth for statistical guidance on evaluating inter-rater scores and for the comments from the anonymous reviewers and Dr Nian Wang that greatly improved the quality of this manuscript.
 

### 2023-01-03 analysis/paper/paper.Rmd
Add missing ',' after 'e.g.' on line 407

@@
 
-When making science more open and computationally reproducible, methods and software used (e.g.
-R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
+When making science more open and computationally reproducible, methods and software used (e.g., R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
 This allows end-users to identify the tools and methods used more accurately.

### 2023-01-03 analysis/paper/supplementary_materials.Rmd
append "S" to table and figure numbers, still incorrect formatting

@@
 output: 
-  bookdown::word_document2:
-     fig_caption: yes
+  officedown::rdocx_document:
+    base_format: bookdown::word_document2
     number_sections: FALSE
     reference_docx: "../templates/phytopath-template.docx"
+    fig_caption: yes
     pandoc_args:
@@
 
-```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
+```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE, tab.cap="Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
+Scoring for 'Code Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
+The model included assignee as random effect (formula: ~1 | assignee).
+Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.", tab.style="Caption"}
 m_f1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_f1_es))
@@
   ) %>%
-  autofit() %>% 
-  set_caption(
-    word_stylename = "Caption",
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
-Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
-The model included assignee as random effect (formula: ~1 | assignee).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
+  autofit()
 ```
@@
 
-## Supplementary Figure
+## Supplementary Figures
 

### 2023-01-03 analysis/paper/supplementary_materials.Rmd
Rename Figure S1

@@
 ggsave(
-  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
+  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"),
   plot = p,
@@
 embed_fonts(
-  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
-  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
+  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"),
+  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"),
   options = "-dEPSCrop"
 )
-include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"))
+include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"))
 ```

### 2023-01-03 analysis/paper/paper.Rmd
Remove single line tables and put in text

@@
 
-The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) had a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83% of being large (\> 0.30).
+The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95\% CI [0.78, 2.57]) had a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83\% of being large (\> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 19017).
 
-The analysis for the effect of year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A; Table S3).
+The analysis for the effect of year when predicting the availability of computational methods was undecided (Median = 0.20, 95\% CI [-0.13, 0.58]) and had a 88.38% probability of being positive (\> 0), 81.03\% of being significant (\> 0.05), and 28.31% of being large (\> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19643).
 
 We failed to reject the null hypothesis that the year of publication had no effect on the availability of data.
-The analysis found that there was no effect of year of publication on the availability of data (Median = 0.08, 95% CI [-8.06e-03, 0.18]) with a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30) (Figure \@ref(fig:year-parameters)B, Table S4).
+The analysis found that there was no effect of year of publication on the availability of data (Median = 0.08, 95\% CI [-8.06e-03, 0.18]) with a 96.19% probability of being positive (\> 0), 75.92\% of being significant (\> 0.05), and 0.00% of being large (\> 0.30) (Figure \@ref(fig:year-parameters)B, Table S4).
 The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).
 
-The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6).
+The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data
+The effect of five-year impact factor (Median = 0.45, 95% CI [-0.05, 1.04]) had a
+96.00% probability of being positive (> 0), 94.25% of being significant
+(> 0.05), and 72.26% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 14595).
+The effect of the five-year impact factor on data availability (Median = 0.15, 95% CI [-3.75e-03, 0.30]) had a 97.21% probability of being positive (> 0), 89.41% of being
+significant (> 0.05), and 2.48% of being large (> 0.30).
+The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 4188).
 

### 2023-01-03 analysis/paper/supplementary_materials.Rmd
Remove single line tables and put in text

@@
   fig.cap.pre = "Figure S",
-  tab.cap.pre = "Table S"
+  tab.cap.pre = "Table S",
+  tab.cap.style = "Caption"
 )
@@
     "Full description of the model that was fit to scoring data, which were used to evaluate the effect of journal title on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
-Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
+Scoring for 'Data Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
 We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
@@
 
-```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-m_g1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g1_es))
-
-as_tibble(m_g1_report)[1:length(m_g1_es), ] %>%
-  bind_cols(m_g1_es) %>%
-  filter(
-    Parameter != "Intercept[1]" &
-      Parameter != "Intercept[2]"
-  ) %>%
-  rename("Effect Size" = "...10") %>%
-  relocate("Effect Size", .before = Fit) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  select(-Fit) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename("CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>% 
-  set_caption(
-    word_stylename = "Caption",
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
-Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
-We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-m_g2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g2_es))
-
-as_tibble(m_g2_report)[1:length(m_g2_es), ] %>%
-  bind_cols(m_g2_es) %>%
-  filter(
-    Parameter != "Intercept[1]" &
-      Parameter != "Intercept[2]" &
-      Parameter != "Intercept[3]"
-  ) %>%
-  rename("Effect Size" = "...10") %>%
-  relocate("Effect Size", .before = Fit) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  select(-Fit) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename("CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>% 
-  set_caption(
-    word_stylename = "Caption",
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of the year of publication on data availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
-Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
-We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation).
-We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict data_avail with year (formula: data_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.
-"
-  )
-```
-
-\newpage
-
-```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
-m_h1_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_h1_es))
-
-as_tibble(m_h1_report)[1:length(m_h1_es), ] %>%
-  bind_cols(m_h1_es) %>%
-  filter(
-    Parameter != "Intercept[1]" &
-      Parameter != "Intercept[2]"
-  ) %>%
-  rename("Effect Size" = "...10") %>%
-  relocate("Effect Size", .before = Fit) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  select(-Fit) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename("CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>% 
-  set_caption(
-    word_stylename = "Caption",
-    "Full description of the model that was fit to scoring data, which were used to evaluate the effect of five-year impact factor on code availability for 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals.
-Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
-m_g2_es <- gsub("\\s*\\([^\\)]+\\)", "", as.character(m_g2_es))
-
-as_tibble(m_g2_report)[1:length(m_g2_es), ] %>%
-  bind_cols(m_g2_es) %>%
-  filter(
-    Parameter != "Intercept[1]" &
-      Parameter != "Intercept[2]" &
-      Parameter != "Intercept[3]"
-  ) %>%
-  rename("Effect Size" = "...10") %>%
-  relocate("Effect Size", .before = Fit) %>%
-  filter(!grepl("R2", Parameter)) %>%
-  filter(!is.na(Parameter)) %>%
-  select(-Fit) %>%
-  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
-  rename("CI\nLow" = "CI_low",
-         "CI\nHigh" = "CI_high") %>%
-  flextable() %>%
-  fontsize(size = 8, part = "all") %>%
-  colformat_double(digits = 2) %>%
-  set_formatter(
-    `ROPE %` = function(x)
-      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
-  ) %>%
-  autofit() %>% 
-  set_caption(
-    word_stylename = "Caption",
-    "Full description of model fit for the effect of five-year impact factor on data availability.
-Scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.
-We fit a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year).
-The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
-Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
-  )
-```
-
-\newpage
-
-## Supplementary Figures
+## Supplementary Figure
 
@@
 Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators.
-Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-And the scoring for 'Data Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
+Scoring for 'Code Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
+And the scoring for 'Data Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
 p <- import_notes() %>%

### 2023-01-05 analysis/paper/paper.Rmd
Update paper.Rmd with Emerson's final comments

@@
 However, our aim was not to test inter-rater reproducibility.
-Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
-Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
+Our goal was to evaluate as many articles as we realistically possible to obtain as broad an overview of the discipline as possible.
+Because of this, aside from the five that were used to compare the inter-rater differences, each article was evaluated by only one of this paper's co-author.
 Therefore, we concluded that the inter-rater agreement was good enough for this paper to illustrate that code and data are not being widely shared with peer-reviewed publications.
@@
 The package allows the user to recreate the figures in the manuscript and includes the all of the data files required to produce all results and figures presented in the manuscript.
-More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish Findable, Accessible, Interoperable and Reusable (FAIR) data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
+More broadly within agricultural research, articles have been published highlighting the advantages of, the need for and how to publish Findable, Accessible, Interoperable and Reusable (FAIR) data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
 However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.

### 2023-01-05 analysis/paper/supplementary_materials.Rmd
Reknit Supplementary Figures

@@
 output: 
-  officedown::rdocx_document:
-    base_format: bookdown::word_document2
+  bookdown::word_document2:
+     fig_caption: yes
      number_sections: FALSE
      reference_docx: "../templates/phytopath-template.docx"
-    fig_caption: yes
      pandoc_args:
@@
        - '--lua-filter=pagebreak.lua'
-bibliography: references.bib
-link-citations: no
-csl: "../templates/american-phytopathological-society.csl"
 ---

### 2023-01-05 analysis/paper/paper.Rmd
Supress the inclusion of figures in the documents for final submission

@@
 
-# Figures
+# Figure Captions
 
 ```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the two categories evaluated, (A) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-(B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
+(B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 
@@
 No article scored 3 for data availability.
-The fitness was found to be good for all models.", cache=FALSE, fig.env='figure'}
+The fitness was found to be good for all models.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 
@@
 If the entire distribution falls outside the ROPE, the hypothesis is rejected.
-In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
+In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 m_f1_eq <- equivalence_test(m_f1, rule = "bayes")
@@
 In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.
-Here, year is treated as a continuous variable to determine if there are changes over time in the likelihood of sharing code and data.', cache=FALSE, fig.env='figure'}
+Here, year is treated as a continuous variable to determine if there are changes over time in the likelihood of sharing code and data.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 
@@
 In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.
-Here, impact factor is a continuous variable to determine if greater or lesser impact factor values affect the likelihood of sharing code and data.', cache=FALSE, fig.env='figure'}
+Here, impact factor is a continuous variable to determine if greater or lesser impact factor values affect the likelihood of sharing code and data.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 m_h1_eq <- equivalence_test(m_h1, rule = "bayes")
@@
 Data are used in analysis and any binary files or code are made available as supplements to the manuscript.
-Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}
+Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
 

### 2023-01-05 analysis/paper/supplementary_materials.Rmd
Supress the inclusion of figures in the documents for final submission

@@
 
-## Supplementary Figure
+## Supplementary Figure Caption
 
@@
 Scoring for 'Code Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
-And the scoring for 'Data Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
+And the scoring for 'Data Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", , out.width=0, out.height=0}
 p <- import_notes() %>%

### 2023-01-05 analysis/paper/paper.Rmd
Fix grammatical mistakes

@@
 However, in the biological sciences it is not always possible to use identical test material or environmental conditions, e.g., field trials that span years and locations or complex glasshouse experiments.
-In other cases there is insufficient time and resources to reproduce the entire study.
+In other cases, there is insufficient time and resources to reproduce the entire study.
 Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":
@@
 The criteria scores were checked for inconsistencies using the evaluators' comments in the spreadsheet and based on the software used.
-In some cases these comments were used to adjust the criteria score to align with the scoring definitions.
+In some cases, these comments were used to adjust the criteria score to align with the scoring definitions.
 This was not possible in all cases but only in cases where the evaluator had left comments that could be checked and acted upon.
-For example, a reviewer noted that all data were deposited in GenBank but the data score was '0', this was changed to '3' to align with the definition.
+For example, a reviewer noted that all data were deposited in GenBank, but the data score was '0', this was changed to '3' to align with the definition.
 Or in other cases, some software packages used were Excel add-ins, but Excel was not recorded as being used; Excel was added to the list of software used to rectify this.
@@
 SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
-It is interesting to note however, that even with the popularity of Python in scientific programming it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
+It is interesting to note however, that even with the popularity of Python in scientific programming it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most cited.
 
@@
 
-We acknowledge that the number of article that are cross-scored is low.
+We acknowledge that the number of articles that are cross scored is low.
 However, our aim was not to test inter-rater reproducibility.
@@
 
-Plant pathology is not alone in the lack of reproducibility and the closed-nature of data and code.
-
-@Seibold2021 carried out a similar study on the types of methods and software used in PLOS ONE articles and whether the were able to reproduce the data analysis using open source software for papers that dealt with longitudinal data and used mixed effect models or generalized estimating equations for analysis and provided the data.
+Plant pathology is not alone in the lack of reproducibility and the closed nature of data and code.
+
+@Seibold2021 carried out a similar study on the types of methods and software used in PLOS ONE articles and whether they were able to reproduce the data analysis using open-source software for papers that dealt with longitudinal data and used mixed effect models or generalized estimating equations for analysis and provided the data.
 They found that most articles provided tables and visualizations only.
-However, unlike our analysis, even with the data being supplied they found that only one article used open source software, whereas R prominently featured in the articles we examined along with other free open-source software packages.
+However, unlike our analysis, even with the data being supplied they found that only one article used open-source software, whereas R prominently featured in the articles we examined along with other free open-source software packages.
 Not surprisingly they found that replication was mostly difficult and required the results to be reverse engineered or contacting the authors.
@@
 The package contains source data and R code that @Fernandez2022a used for their sensitivity analyses when fitting critical N dilution curves in crop species using Bayesian models. 
-The package allows the user to recreate the figures in the manuscript and includes the all of the data files required to produce all results and figures presented in the manuscript.
+The package allows the user to recreate the figures in the manuscript and includes all of the data files required to produce all results and figures presented in the manuscript.
 More broadly within agricultural research, articles have been published highlighting the advantages of, the need for and how to publish Findable, Accessible, Interoperable and Reusable (FAIR) data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
@@
 @Hill2019 also shared code and example data to reproduce the results of the paper as supplementary materials, citing all packages used and the versions.
-The scripts provided used an R package, *checkpoint* [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that were necessary to reproduce the work rather than defaulting to the latest versions, which may cause failures due to changes in the package code-bases.
+The scripts provided used an R package, *checkpoint* [@Ooi2022], to provide a mechanism to help ensure reproducibility by installing the package versions used by the authors that were necessary to reproduce the work rather than defaulting to the latest versions, which may cause failures due to changes in the package codebases.
 However, the scripts did not run unhindered as the supplementary materials suggested without changes to the data.
@@
 It can be difficult to understand for a new user and new platforms, like the Apple M1 chip, may not be fully supported, which hinder the ability to share the container.
-But, in most cases using an open-source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
+But, in most cases using an open-source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run the same on every computer.
 For more on using Docker for reproducible research, we would refer readers to @Nuest2020.
@@
 This enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected.
-It also allows for more in-depth investigation by stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
+It also allows for more in-depth investigation by stepping through other points where weather data were investigated, and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
 When this layer is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks, a "web application for creating and sharing computational documents" [@jupyter2022], as Mioroni et al.
@@
 Authors need not start with Level 1 before moving to Level 2 and then Level 3.
-If they have the ability to start with depositing the computational materials and data and generating DOIs all parties will benefit from it.
+If they can start with depositing the computational materials and data and generating DOIs all parties will benefit from it.
 However, we recognize that these steps may not be appropriate or attractive for various reasons and so have detailed other layers that improve openness and reproducibility.

### 2023-03-04 README.rmd
Add DOI for article and prep for v1.0.0 release
Fix DOI on Zenodo to point at all, not first release & increment version number

@@
 J.
-(YYYY).
-_Openness and computational reproducibility in plant pathology: where do we stand and a way forward_.
-Name of journal/book <https://doi.org/xxx/xxx>
+(2023).
+_Openness and computational reproducibility in plant pathology: where do we stand and a way forward_, _Phytopathology_ <https://doi.org/10.1094/PHYTO-10-21-0430-PER>.
 
@@
 J.
-(2022).
+(2023).
 _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_.
@@
 Accessed `r format(Sys.Date(), "%d %b %Y")`.
-Online at <https://doi.org/10.5281/zenodo.1250665>
+Online at <https://doi.org/10.5281/zenodo.1250664>
 

### 2024-08-07 README.rmd
update repo badge and clean up website files

@@
 [![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
-[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
+[![Project Status: Inactive – The project has reached a stable, usable state but is no longer being actively developed; support/maintenance will be provided as time allows.](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
 <!-- badges: end -->

### 2024-08-07 analysis/paper/paper.Rmd
Fix some scale in figures

@@
   pp_check(m_f1, type = "bars", ndraws = 50) +
-    scale_x_continuous(,
+    scale_x_continuous(
+      labels = c("0", "1", "2", "3"),
       breaks = c(1, 2, 3, 4),
-                       limits = c(0.5, 4.5)) +
+      limits = c(0.5, 4.5)
+    ) +
     theme(
@@
   pp_check(m_g1, type = "bars", ndraws = 50) +
-    scale_x_continuous(,
+    scale_x_continuous(
+      labels = c("0", "1", "2", "3"),
       breaks = c(1, 2, 3, 4),
-                       limits = c(0.5, 4.5)) +
+      limits = c(0.5, 4.5)
+    ) +
     theme(
@@
   pp_check(m_h2, type = "bars", ndraws = 50) +
-    scale_x_continuous(labels = c("0", "1", "2", "3"),
+    scale_x_continuous(
+      labels = c("0", "1", "2", "3"),
       breaks = c(1, 2, 3, 4),
-                       limits = c(0.5, 4.5)) +
+      limits = c(0.5, 4.5)
+    ) +
     xlab("Score (0 to 3)") +
@@
   plot_layout(guides = "collect") &
-  plot_annotation(title = "Bayesian posterior distributions of evaluation score models",
-                  tag_levels = "A") &
+  plot_annotation(title = "Bayesian posterior distributions of evaluation score models", tag_levels = "A") &
   theme(text = element_text("Arial"))

### 2024-08-08 analysis/paper/paper.Rmd
Fix missing "." and linebreaks

@@
 
-The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data
-The effect of five-year impact factor (Median = 0.45, 95% CI [-0.05, 1.04]) had a
-96.00% probability of being positive (> 0), 94.25% of being significant
-(> 0.05), and 72.26% of being large (> 0.30).
+The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data.
+The effect of five-year impact factor (Median = 0.45, 95% CI [-0.05, 1.04]) had a 96.00% probability of being positive (> 0), 94.25% of being significant (> 0.05), and 72.26% of being large (> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 14595).
-The effect of the five-year impact factor on data availability (Median = 0.15, 95% CI [-3.75e-03, 0.30]) had a 97.21% probability of being positive (> 0), 89.41% of being
-significant (> 0.05), and 2.48% of being large (> 0.30).
+The effect of the five-year impact factor on data availability (Median = 0.15, 95% CI [-3.75e-03, 0.30]) had a 97.21% probability of being positive (> 0), 89.41% of being significant (> 0.05), and 2.48% of being large (> 0.30).
 The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 4188).
